---
title: 'GTFCC Cholera Database Scoping'
date: `r Sys.Date()`
output: html_document
---

<br>

## Outline

##### 1) Data availability 2010-2020: totals by country
* Number of observations by country
* Number of observations by country and geographic level

##### 2) Data availability 2010-2020: timeline
* Types of data by year, country, and geographic level

##### 2) Data availability 2010-2020: zeros in the data
* Total observations and zeros by region and geographic level
* Proportion of observations zero by region and geographic level
* Proportion of observations zero by country and geographic level

__Note__: an observation is the count of cases over a timeframe, which can be ≥0

<br>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
rm(list = ls())
```


```{r packages and functions, include = FALSE}
# packages
package_list <- c("sf", "ggplot2", "data.table", "kableExtra", "tidyverse")
invisible(lapply(package_list, library, character.only = TRUE))
# functions
source("Analysis/R/notebooks/gtfcc_data_scoping/data_scoping_functions.R")
```


```{r load data, include = FALSE}
# parent directories
dir <- "Analysis/R/notebooks/gtfcc_data_scoping/"
# country data file
dt_countries <- fread(paste0(dir, "outputs/country_data_summary_2020-11-06.csv"))
# fix data mismatch
dt_countries[country == "CAM", country := "CMR"]
# region data file
dt_region <- fread(paste0(dir, "outputs/region_data_summary_2020-11-06.csv"))
# shapefile
shp <- st_read(paste0(dir, "inputs/ne_50m_admin_0_countries/ne_50m_admin_0_countries.shp"))
shp <- shp[c("ISO_A3", "NAME_EN", "geometry")]
# country meta-data and clean up
meta <- fread(paste0(dir, "inputs/db_country_codes_20201026.csv"))
meta[, region := get_region(country_code)]
meta <- meta[region != "WHO"]
meta <- merge(meta, data.table(country = shp$ISO_A3, name = shp$NAME_EN), by = "country")
```

## Data availability 2010-2020: totals by country
Represent primary observations for Africa, and all observations for the rest of the world.

### Number of observations by country

```{r total observations, fig.height = 3, fig.width = 8}
# subset data
dt_ctry <- copy(dt_countries)
dt_ctry <- dt_ctry[((region == "AFR" & primary == TRUE) | region != "AFR") & year >= 2010 & suspected_report != 0]
# aggregate
dt <- copy(dt_ctry)
dt <- dt[, lapply(.SD, sum),
  .SDcols = c("suspected_report", "suspected_zero"),
  by = c("country")
]
# add geo group (which will be title of the plot)
dt[, c("geo_group", "group") := c("All geographic levels")]
# plot number of observations
print(data_map(dt, "All geographic levels", "suspected_report", "Observations"))
```

### Number of observations by country and geographic level

```{r geography observations, fig.height = 3, fig.width = 8}
# set geography groups
dt <- copy(dt_ctry)
dt[geo_group >= 2 & geo_group < 99, geo_group := 2]
dt[, group := get_geo_name(geo_group), by = V1]
# aggregate
dt <- dt[, lapply(.SD, sum),
  .SDcols = c("suspected_report", "suspected_zero"),
  by = c("country", "geo_group", "group")
]
# plot number of observations
for (i in c(0:2, 99)) print(data_map(dt, i, "suspected_report", "Observations"))
```

<br>

## Data availability 2010-2020: timeline
Represent primary observations for Africa, and all observations for the rest of the world.

### Types of data by year, country, and geographic level
* "National" is country-level, "Subnational" refers to levels 1, 2+ and ? (or unknown).
* Numbers indicate the proportion of observations that are non-zero in a given location/year.
    + __Teal__:    includes non-zero observations
    + __Purple__:  includes only zero observations
    + __Yellow__:  no observations

```{r timeline}
# set just two geography groups
tab <- copy(dt_ctry)
tab[geo_group == 0, group := "National"]
tab[geo_group != 0, group := "Subnational"]
# columns to work with
val_cols <- c("suspected_report", "suspected_zero")
id_cols <- c("country", "group", "year")
# aggregate
tab <- tab[, lapply(.SD, sum), .SDcols = val_cols, by = id_cols]
# get data types
tab[, prop_non_zero := round((suspected_report - suspected_zero) / suspected_report, 2)]
# reshape
tab <- dcast(tab, country ~ group + year, value.var = "prop_non_zero")
# add region and more informative country name
cols_tmp <- names(tab)
tab <- merge(meta[, c("region", "country", "name")], tab, by = "country")
tab[, country := name]
tab[, name := NULL]
# order
setcolorder(tab, c("region", cols_tmp))
setorderv(tab, c("region", "country"))
# make table
prettier_table(tab)
```

<br>
<br>

## Data availability 2010-2020: zeros in the data
Represent primary observations for Africa, and all observations for the rest of the world.

### Total observations and zeros by region and geographic level

```{r table region summaries, fig.width = 10}
# subset data
dt_reg <- copy(dt_region)
dt_reg <- dt_reg[((region == "AFR" & primary == TRUE) | region != "AFR") & year >= 2010 & suspected_report != 0]
# calling missing values non-primary (since this is how mapping handles them)
dt_reg[is.na(primary), primary := FALSE]
# set geography groups
dt_reg[, group := get_geo_name(geo_group), by = V1]
# reshape
tab <- copy(dt_reg)
tab <- tab[, lapply(.SD, function(x) format(sum(x), format = "d", big.mark = ",")),
  .SDcols = c("suspected_report", "suspected_zero", "confirmed_report", "confirmed_zero"),
  by = c("region", "group")
]
# rename columns
setnames(tab, c("Region", "Geography", "Total observations", "Total zeros", "Total observations", "Total zeros"))
# make a pretty table for numbers
pretty_table(tab) %>%
  add_header_above(c(" " = 1, " " = 1, "Suspected cases" = 2, "Confirmed cases" = 2))
```

<br>

### Proportion of observation zeros by region and geographic level

```{r plot region summaries, fig.width = 10}
# aggregate data
tab <- copy(dt_reg)
tab <- tab[, lapply(.SD, sum),
  .SDcols = c("suspected_report", "suspected_zero"),
  by = c("region", "group", "phantom")
]
# percent
tab[, total_obs := sum(suspected_report), by = c("region", "group")]
tab[, zero := suspected_zero / total_obs, by = c("region", "group", "phantom")]
tab[, non_zero := (suspected_report - suspected_zero) / total_obs, by = c("region", "group", "phantom")]
# melt
tab <- melt(tab,
  id.vars = c("region", "group", "phantom", "total_obs"), variable.name = "data_type",
  measure.vars = c("zero", "non_zero"), value.name = "proportion"
)
# also get number
tab[, number := total_obs * proportion, by = .I]
# name plotting groups
tab[is.na(phantom), data_type := paste0("unknown_", data_type)]
tab[phantom == FALSE, data_type := paste0("actual_", data_type)]
tab[phantom == TRUE, data_type := paste0("phantom_", data_type)]
# make a pretty graph
pretty_graph(tab,
  colors = c(
    "#660066", "#CC99CC", "darkgreen",
    "lightgreen", "#333333", "#999999"
  ),
  color_names = c(
    "Zero: unaudited", "Non-zero: unaudited",
    "Zero: actual", "Non-zero: actual",
    "Zero: phantom", "Non-zero: phantom"
  )
)
```

### Proportion of observation zeros by country and geographic level

```{r plot zeros, fig.height = 3, fig.width = 8}
# calculate proportion zeros
dt[, prop_zero := suspected_zero / suspected_report, by = .I]
# plot
for (i in c(0:2, 99)) print(data_map(dt, i, "prop_zero", "Proportion\nwith zero"))
```
