---
title: "Data by age report"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('age_data_functions.R')
```

```{r input, include =FALSE}
library(dplyr)
library(stringr)
data<-read.csv("age_specific_data.csv") %>% 
  filter(tl != "" & tr !="" & !is.na(tl) & !is.na(tr)) %>% #3685 rows have this issue
  filter(location != '') # 4914 rows have this issue
data$location <- str_remove(data$location, regex("^CT-World::"))
```

```{r clean data, include =FALSE}
clean_data <- data %>%
  clean_age_cols(lt1_year = 0.5) %>%
  standardize_age_group(age_splitter = c(5,14,50,70))

clean_data <- clean_data %>%
  mutate(
    tl = parse_date(tl),
    tr = parse_date(tr)
  ) %>%
  mutate(tl = as.Date(tl),tr = as.Date(tr))
```

# Summary of observations by age group
```{r Summary of observations by age group, echo = F, message=F}
summary_obs_table(clean_data)
```
# Summary of observations by country for 0-5
```{r Summary of observations by country for 0-5 , echo = F, message=F}
table_list <- tables_by_age_group(clean_data)
table_list[[1]]
```

# Summary of observations by country for 6-14
```{r Summary of observations by country for 6-14 , echo = F, message=F}
table_list[[2]]
```

# Summary of observations by country for 15-50
```{r Summary of observations by country for 15-50 , echo = F, message=F}
table_list[[3]]
```

# Summary of observations by country for 51-70
```{r Summary of observations by country for 51-70 , echo = F, message=F}
table_list[[4]]
```

# Summary of observations by country for 71+
```{r Summary of observations by country for 71+ , echo = F, message=F}
table_list[[5]]
```

# Heatmaps for number of cases at different spatial scales for each age group by country over time
*Note: Case counts in all the Heatmaps were aggregated through the following steps: 1. Initial aggregation: For each combination of location, year (using the year from the TL), and age group, all observations that did not overlap in time were aggregated. 2. Selection of representative observation: Among the aggregated observations for each location-year-age group, the one with the longest temporal coverage was selected to represent the annual case count. 3. National-level aggregation by spatial scale: For each spatial scale, year, and age group combination, case counts were summed across all locations in the country to generate national totals at that spatial scale. As a result of this approach, some overlap may exist due to multi-year observations being included in the aggregation. Also, some observations may be excluded due to shorter temporal coverage.*

## Heatmaps for number of national cases for 0-5
```{r Heatmaps for number of national cases for 0-5 by country over time, echo = F, message=F}
data_list_by_sp_age <- summarize_scd(clean_data)

plots<-make_heatmaps_by_age_scale(data_list_by_sp_age %>% filter(spatial_scale == "country"))
plots[[1]]
```

## Heatmaps for number of national cases for 6-14
```{r Heatmaps for number of national cases for 6-14 by country over time, echo = F, message=F}
plots[[2]]
```

## Heatmaps for number of national cases for 14-50
```{r Heatmaps for number of national cases for 14-50 by country over time, echo = F, message=F}
plots[[3]]
```

## Heatmaps for number of national cases for 51-70
```{r Heatmaps for number of national cases for 51-70 by country over time, echo = F, message=F}
plots[[4]]
```

## Heatmaps for number of national cases for 71+
```{r Heatmaps for number of national cases for 71+ by country over time, echo = F, message=F}
plots[[5]]
```

## Heatmaps for number of adm1 cases for 0-5
```{r Heatmaps for number of admin1 cases for 0-5 by country over time, echo = F, message=F}
plots<-make_heatmaps_by_age_scale(data_list_by_sp_age %>% filter(spatial_scale == "admin1"))
plots[[1]]
```

## Heatmaps for number of adm1 cases for 6-14
```{r Heatmaps for number of admin1 cases for 6-14 by country over time, echo = F, message=F}
plots[[2]]
```

## Heatmaps for number of adm1 cases for 14-50
```{r Heatmaps for number of admin1 cases for 14-50 by country over time, echo = F, message=F}
plots[[3]]
```

## Heatmaps for number of adm1 cases for 51-70
```{r Heatmaps for number of admin1 cases for 51-70 by country over time, echo = F, message=F}
plots[[4]]
```

## Heatmaps for number of adm1 cases for 71+
```{r Heatmaps for number of admin1 cases for 71+ by country over time, echo = F, message=F}
plots[[5]]
```


## Heatmaps for number of adm2 cases for 0-5
```{r Heatmaps for number of adm2 cases for 0-5 by country over time, echo = F, message=F}
plots<-make_heatmaps_by_age_scale(data_list_by_sp_age %>% filter(spatial_scale == "admin2"))
plots[[1]]
```

## Heatmaps for number of adm2 cases for 6-14
```{r Heatmaps for number of adm2 cases for 6-14 by country over time, echo = F, message=F}
plots[[2]]
```

## Heatmaps for number of adm2 cases for 14-50
```{r Heatmaps for number of adm2 cases for 14-50 by country over time, echo = F, message=F}
plots[[3]]
```

## Heatmaps for number of adm2 cases for 51-70
```{r Heatmaps for number of adm2 cases for 51-70 by country over time, echo = F, message=F}
plots[[4]]
```

## Heatmaps for number of adm2 cases for 71+
```{r Heatmaps for number of adm2 cases for 71+ by country over time, echo = F, message=F}
plots[[5]]
```

## Heatmaps for number of adm3 cases for 71+
```{r Heatmaps for number of adm2 cases for 71+ by country over time, echo = F, message=F}
plots<-make_heatmaps_by_age_scale(data_list_by_sp_age %>% filter(spatial_scale == "admin3"))
```

# CFR distribution by age groups
```{r cfr distribution, echo = F, message=F}
data_list_by_sp_age <- summarize_scd(clean_data) %>% 
  mutate(cfr = deaths_total/sCh_total *100)

ggplot(data_list_by_sp_age %>% mutate(spatial_scale = factor(spatial_scale, levels = c("country","admin1","admin2","admin3","admin4 or lower"))), aes(x = age_group, y = cfr)) +
  geom_boxplot(fill = "skyblue", alpha = 0.7) +
  scale_y_continuous(transform = 'log10') +
  labs(
    title = "Case Fatality Ratio by Age Group",
    x = "Age Group",
    y = "Case Fatality Ratio (%)"
  ) +
  theme_bw(base_size = 14) +
  facet_wrap(~spatial_scale, ncol = 2, scales = "free")
```


# Confirmed cases ratio by age groups
```{r Confirmed cases ratio distribution, echo = F, message=F}
data_list_by_sp_age <- summarize_scd(clean_data) %>% 
  mutate(confirm_rate = cCh_total/sCh_total *100)

ggplot(data_list_by_sp_age %>% mutate(spatial_scale = factor(spatial_scale, levels = c("country","admin1","admin2","admin3","admin4 or lower"))), aes(x = age_group, y = confirm_rate)) +
  geom_boxplot(fill = "skyblue", alpha = 0.7) +
  scale_y_continuous(transform = 'log10') +
  labs(
    title = "Confirmation rate by Age Group",
    x = "Age Group",
    y = "cCh/sCh (%)"
  ) +
  theme_bw(base_size = 14) +
  facet_wrap(~spatial_scale, ncol = 2, scales = "free")
```