---
title: "Continent Map Report"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  cholera_directory: "~/code/cholera-mapping-pipeline/"
  config_directory: "Analysis/configs/2015_2019_full_base/"
  output_dir: "Analysis/output/2015_2019_full_base/"
  max_countries: Inf
---
```{r setup, include=FALSE, dev="CairoPNG"}
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(RColorBrewer)
library(MCMCvis)
library(sf)
library(sp)
library(abind)
library(taxdat)

options(bitmapType = 'cairo')
knitr::opts_chunk$set(
  echo = FALSE,
  dev = "CairoPNG",
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache.lazy = F,
  error = TRUE,
  bitmapType = "cairo")
```

```{r dir_settings}
dir.create(stringr::str_c(params$cholera_directory, params$output_dir), showWarnings = FALSE)
```

```{r datapull}
orig_configs <- list.files(stringr::str_c(params$cholera_directory, params$config_directory), full.names = TRUE)
orig_locations <- stringr::str_extract(orig_configs, "[A-Z]{3}")

skip_cntry <- c("BWA", "COG", "DJI", "ERI", "GAB", "GMB", "GNQ", "LSO", "MDG", "NAM", "SEN", "SWZ")
if (sum(orig_locations %in% skip_cntry) > 1) {
  indexes <- unlist(lapply(skip_cntry, function(cntry){
    which(stringr::str_detect(orig_configs, cntry))
  }))
  all_configs <- orig_configs[-indexes]
} else {
  all_configs <- orig_configs
}

all_locations <- stringr::str_extract(all_configs, "[A-Z]{3}")
print(all_configs)
print(all_locations)

sf_cases_resized <- list()
sf_grid <- list()
country_count <- 0
for(config_filename in all_configs){
  print(config_filename)
  if(country_count >= params$max_countries){break}
  config <- yaml::read_yaml(config_filename)
  file_names <- taxdat::get_filenames(config, params$cholera_directory)
  print(file_names)
  if(all(file.exists(file_names))){
    stan_input <- taxdat::read_file_of_type(file_names[['stan_input']], "stan_input")
    model.rand <- taxdat::read_file_of_type(file_names[['stan_output']], "model.rand")
    niter_per_chain <- dim(MCMCvis::MCMCchains(model.rand,params='lp__',chain_num=1))[1]
    nchain <- dim(MCMCvis::MCMCchains(model.rand,params='lp__'))[1] / niter_per_chain
    stan_output <- lapply(rstan::extract(model.rand), function(x){array(x,c(niter_per_chain, nchain, dim(x)[-1]))})

    
    stan_input$sf_grid <- stan_input$sf_grid %>% dplyr::ungroup() %>% dplyr::select(t,id)
    stan_input$sf_grid[paste('cases','chain',seq_len(nchain),sep='_')] <- apply(stan_output$grid_cases, c(3,2), mean)
    stan_input$sf_grid[paste('rate','chain',seq_len(nchain),sep='_')] <- apply(exp(stan_output$log_lambda), c(3,2), mean)
    stan_input$sf_grid$row_index <- seq_len(nrow(stan_input$sf_grid))
    stan_input$sf_grid <- data.frame(stan_input$sf_grid) # workaround to prevent warning: https://github.com/r-spatial/sf/issues/1149
    stan_input$sf_grid <- tidyr::pivot_longer(
      stan_input$sf_grid,
      cols=c(
        paste('cases','chain',seq_len(nchain),sep='_'),
        paste('rate','chain',seq_len(nchain),sep='_')
      ),
      names_to="scenario",
      values_to="modeled"
    ) %>% sf::st_sf()
    stan_input$sf_grid <- tidyr::separate(col=scenario, into = c('type',NA,'chain'),stan_input$sf_grid)
  
    stan_input$sf_cases_resized <- dplyr::rename(
      dplyr::select(sf::st_as_sf(dplyr::ungroup(stan_input$sf_cases_resized)), locationPeriod_id, OC_UID,TL,TR,attributes.fields.suspected_cases),
      observed = attributes.fields.suspected_cases
    )
    stan_input$sf_cases_resized[paste('cases','chain',seq_len(nchain),sep='_')] <- apply(stan_output$modeled_cases, c(3,2), mean)
    stan_input$sf_cases_resized$row_index <- seq_len(nrow(stan_input$sf_cases_resized))
    stan_input$sf_cases_resized <- data.frame(stan_input$sf_cases_resized) # workaround to prevent warning: https://github.com/r-spatial/sf/issues/1149
    stan_input$sf_cases_resized <- tidyr::pivot_longer(stan_input$sf_cases_resized,cols=paste('cases','chain',seq_len(nchain),sep='_'),names_to="scenario",values_to="modeled") %>% sf::st_sf()
    stan_input$sf_cases_resized <- tidyr::separate(col=scenario, into = c('type',NA,'chain'),stan_input$sf_cases_resized)

    stan_input$sf_cases_resized$filename <- config_filename
    stan_input$sf_grid$filename <- config_filename
  
    if("list" %in% class(sf_grid)){
      sf_grid <- stan_input$sf_grid
    } else {
      sf_grid <- rbind(sf_grid, stan_input$sf_grid)
    }
    if("list" %in% class(sf_cases_resized)){
      sf_cases_resized <- stan_input$sf_cases_resized
    } else {
      sf_cases_resized <- rbind(sf_cases_resized, stan_input$sf_cases_resized)
    }

    country_count <- country_count + 1
  }
}

afr_shp <- sf::st_boundary(sf::st_read(paste(params$cholera_directory,"Layers/Africa.shp",sep='/')))

# add CRS
afr_shp <- as(afr_shp, 'Spatial')
sp::proj4string(afr_shp) <- sp::CRS("+init=epsg:4326 +proj=longlat +datum=WGS84 +no_defs")
afr_shp <- as(afr_shp, 'sf')
```

# Mapping results summary for `r paste(all_locations, collapse =', ')`

```{r makenosplit}
single_sf_grid <- sf_grid %>% dplyr::group_by(id, type) %>% dplyr::summarize(modeled = mean(modeled), geometry = geom) %>% dplyr::ungroup() %>% unique()
```

### Plot Grid Output Cases {.tabset}

#### Cases

```{r gridoutcase, fig.height=7}
taxdat::plot_map(dplyr::filter(single_sf_grid,type=='cases'),"modeled", facet_column='type', colorscale_type = 'cases', render=TRUE, plot_border = afr_shp)
```

#### Cases with log transform

```{r gridoutcaselog, fig.height=7}
taxdat::plot_map(dplyr::filter(single_sf_grid,type=='cases'),"modeled", facet_column='type', colorscale_type = 'cases', render=TRUE, plot_border = afr_shp, use_log=TRUE)
```

### Plot Grid Output Rates {.tabset}

#### Rates

```{r gridoutrate, fig.height=7}
taxdat::plot_map(dplyr::filter(single_sf_grid,type=='rate'),"modeled", facet_column='type', colorscale_type = 'rates', render=TRUE, plot_border = afr_shp)
```

#### Rates with log transform

```{r gridoutratelog, fig.height=7}
taxdat::plot_map(dplyr::filter(single_sf_grid,type=='rate'),"modeled", facet_column='type', colorscale_type = 'rates', render=TRUE, plot_border = afr_shp, use_log=TRUE)
```

```{r makechainsplit}
rm(single_sf_grid)
chain_sf_grid <- sf_grid %>% dplyr::group_by(id,chain,type) %>% dplyr::summarize(modeled = mean(modeled), geometry = geom) %>% dplyr::ungroup() %>% unique()
```

### Plot Grid Output Cases by Chain {.tabset}

#### Cases by chain

```{r chaingrdioutcase, fig.height=7}
taxdat::plot_map(dplyr::filter(chain_sf_grid,type=='cases'), "modeled", "chain", colorscale_type = 'cases', render=TRUE, plot_border = afr_shp)
```

#### Cases with log transform by chain

```{r chaingridoutcaselog, fig.height=7}
taxdat::plot_map(dplyr::filter(chain_sf_grid,type=='cases'), "modeled", "chain", colorscale_type = 'cases', render=TRUE, plot_border = afr_shp, use_log = TRUE)
```

### Plot Grid Output Rates by Chain {.tabset}

#### Rates by chain

```{r chaingridoutrate, fig.height=7}
taxdat::plot_map(dplyr::filter(chain_sf_grid,type=='rate'), "modeled", "chain", colorscale_type = 'rates', render=TRUE, plot_border = afr_shp)
```

#### Rates with log transform by chain

```{r chaingridoutratelog, fig.height=7}
taxdat::plot_map(dplyr::filter(chain_sf_grid,type=='rate'), "modeled", "chain", colorscale_type = 'rates', render=TRUE, plot_border = afr_shp, use_log = TRUE)
```

### Plot Grid Output Cases by Time {.tabset}

```{r maketimesplit}
rm(chain_sf_grid)
time_sf_grid <- sf_grid %>% dplyr::group_by(id,t,type) %>% dplyr::summarize(modeled = mean(modeled), geometry = geom) %>% dplyr::ungroup() %>% unique()
```

#### Cases by time

```{r timegrdioutcase, fig.height=7}
taxdat::plot_map(dplyr::filter(time_sf_grid,type=='cases'), "modeled", "t", colorscale_type = 'cases', render=TRUE, plot_border = afr_shp)
```

#### Cases with log transform by time

```{r timegridoutcaselog, fig.height=7}
taxdat::plot_map(dplyr::filter(time_sf_grid,type=='cases'), "modeled", "t", colorscale_type = 'cases', render=TRUE, plot_border = afr_shp, use_log = TRUE)
```

### Plot Grid Output Rates by Time {.tabset}

#### Rates by time

```{r timegridoutrate, fig.height=7}
taxdat::plot_map(dplyr::filter(time_sf_grid,type=='rate'), "modeled", "t", colorscale_type = 'rates', render=TRUE, plot_border = afr_shp)
```

#### Rates with log transform by time

```{r timegridoutratelog, fig.height=7}
taxdat::plot_map(dplyr::filter(time_sf_grid,type=='rate'), "modeled", "t", colorscale_type = 'rates', render=TRUE, plot_border = afr_shp, use_log = TRUE)
```

```{r cleantimesplit, echo=FALSE, warning=FALSE,message=FALSE}
rm(time_sf_grid)
```

### Plot Observed vs Modeled

```{r modelfit}
sf_cases_resized %>%
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x=modeled+1,y=observed+1,color=as.character(chain))) +
  ggplot2::scale_x_continuous(trans="log10") +
  ggplot2::scale_y_continuous(trans="log10")
```
