---
title: "Country Data Reports Comparison"
output: html_document
params: 
  cholera_directory: "/home/kaiyuezou/mapping_pipeline/2016_2020_no_covariate_run/cholera-mapping-pipeline"
  config1: "/Analysis/configs/production_tests/2016_2020_covariate_selection/2016_2020_dist_to_water/2016_2020_country/config_AGO_2016_2020.yml"
  config2: "/Analysis/configs/production_tests/2016_2020_covariate_selection/2016_2020_no_covariate_run/2016_2020_country/config_AGO_2016_2020.yml"
  drop_nodata_years: TRUE
  admin_level_for_summary_table: '1'
  args: 'myarg'
  old_runs: FALSE
---
```{r setup, include=FALSE, dev="CairoPNG",message=FALSE}
library(knitr)
knitr::opts_chunk$set(
  cache=FALSE,
  cache.lazy = FALSE,
  echo = FALSE,
  dev="CairoPNG",
  error = FALSE,
  fig.align = "center",
  message = TRUE,
  warning = TRUE
  )
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(taxdat)
library(sf)
library(raster)
library(stars)
library(gridExtra)
sf::sf_use_s2(FALSE)

### other new packages (mainly for "rgeoboundaries")
chooseCRANmirror(ind = 77)

package_list <- c(
  "fasterize", 
  "remotes",
  "rgeoboundaries", 
  "ggrepel"
)

for (package in package_list) {
  if (!require(package = package, character.only = T)) {
    if (package == "rgeoboundaries"){
      try({
        remotes::install_gitlab("dickoa/rgeoboundaries")
        remotes::install_github("wmgeolab/rgeoboundaries")
      })
    }else{
      install.packages(pkgs = package)
      library(package = package, character.only = T)
    }
  }
}

#Figure Caption Numbering,
capFigNo = 1
#Function to add the Figure Number
capFig = function(x){
    x = paste0("Figure ",capFigNo,". ",x)
    capFigNo <<- capFigNo + 1
    x
}

```


```{r include=FALSE, message=FALSE}
# # Parameters to use for development purposes ************************************************************************************************************************
# params <- new.env() 
# params$cholera_directory <- "/home/kaiyuezou/mapping_pipeline/2016_2020_no_covariate_run/cholera-mapping-pipeline"
# params$config1 <- "/Analysis/configs/production_tests/2016_2020_covariate_selection/2016_2020_dist_to_water/2016_2020_country/config_AGO_2016_2020.yml"
# params$config2 <- "/Analysis/configs/production_tests/2016_2020_covariate_selection/2016_2020_no_covariate_run/2016_2020_country/config_AGO_2016_2020.yml"
# params$drop_nodata_years <- TRUE
# params$admin_level_for_summary_table <- '1'
# params$args <- 'myarg'
# params$old_runs <- FALSE

# Whether or not to include the stan model output
skip_stan <- FALSE
if (Sys.getenv("CHOLERA_SKIP_STAN","FALSE") == "TRUE") {
  print("Skipping stan model in accordance with the environment variable CHOLERA_SKIP_STAN.")
  warning("Skipping stan model in accordance with the environment variable CHOLERA_SKIP_STAN.")
  skip_stan <- TRUE
}

```


# Mapping results summary for `r stringr::str_extract(params$config1, "[A-Z]{3}")` and period `r stringr::str_extract(params$config1, "[0-9]{4}_[0-9]{4}")`
```{r include=FALSE, message=FALSE}
## Some parameters
country_iso = as.character(stringr::str_extract(params$config1, "[A-Z]{3}"))
year_string <- stringr::str_extract(params$config1, "[0-9]{4}_[0-9]{4}")
year_vector <- as.numeric(stringr::str_extract(stringr::str_extract(year_string, "[0-9]{4}_"), "[0-9]{4}")):as.numeric(stringr::str_extract(stringr::str_extract(year_string, "_[0-9]{4}"), "[0-9]{4}"))

## Initialize the cache 
cache1 <- new.env()
cache2 <- new.env()
comparison_cache <- new.env()

## The configs
get_config(cache = cache1, config = params$config1, cholera_directory = params$cholera_directory)
get_config(cache = cache2, config = params$config2, cholera_directory = params$cholera_directory)

stitch_configs(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## GAM input and output
taxdat::get_initial_values(name = "initial_values_data", cache = cache1, 
  config = params$config1, cholera_directory = params$cholera_directory)
taxdat::get_initial_values(name = "initial_values_data", cache = cache2, 
  config = params$config2, cholera_directory = params$cholera_directory)

cache1[["gam_output_df"]] <- get_gam_values_no_cache(cache = cache1, config = params$config1, cholera_directory = params$cholera_directory)
cache2[["gam_output_df"]] <- get_gam_values_no_cache(cache = cache2, config = params$config2, cholera_directory = params$cholera_directory)

stitch_gam_input(output_cache = comparison_cache, input_caches = list(cache1, cache2))
stitch_gam_output(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## Table 1 and table 2
cache1$used_data_table <- plot_ObservationSummary_table(config = params$config1, cache = cache1, cholera_directory = params$cholera_directory, aesthetic = FALSE)
cache2$used_data_table <- plot_ObservationSummary_table(config = params$config2, cache = cache2, cholera_directory = params$cholera_directory, aesthetic = FALSE)

cache1$dropped_data_table <- plot_DroppedData_table(config = params$config1, cache = cache1, cholera_directory = params$cholera_directory, aesthetic = FALSE)
cache2$dropped_data_table <- plot_DroppedData_table(config = params$config2, cache = cache2, cholera_directory = params$cholera_directory, aesthetic = FALSE)

stitch_used_data_table(output_cache = comparison_cache, input_caches = list(cache1, cache2))
stitch_dropped_data_table(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## The covariates side by side comparison 
get_covar_cube(name = "covar_cube", config = params$config1, cache = cache1, cholera_directory = params$cholera_directory)
get_sf_grid(name = "sf_grid", config = params$config1, cache = cache1, cholera_directory = params$cholera_directory)

get_covar_cube(name = "covar_cube", config = params$config2, cache = cache2, cholera_directory = params$cholera_directory)
get_sf_grid(name = "sf_grid", config = params$config2, cache = cache2, cholera_directory = params$cholera_directory)

stitch_covar_cube(output_cache = comparison_cache, input_caches = list(cache1, cache2))
stitch_sf_grid(output_cache = comparison_cache, input_caches = list(cache1, cache2))
```


```{r eval=as.logical(!skip_stan), include=FALSE, message=FALSE}
## The case raster comparison
cache1[["disaggregated_case_sf"]] <- get_disaggregated_cases_sf(
                                                cache = cache1, config = params$config1,
                                                cholera_directory = params$cholera_directory)
cache2[["disaggregated_case_sf"]] <- get_disaggregated_cases_sf(
                                                cache = cache2, config = params$config2,
                                                cholera_directory = params$cholera_directory)                                                
stitch_disaggregated_case_sf(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## The case scatter plot comparison 
cache1[["data_fidelity"]] <- get_data_fidelity(cache = cache1, cholera_directory = params$cholera_directory, config = params$config1)
cache2[["data_fidelity"]] <- get_data_fidelity(cache = cache2, cholera_directory = params$cholera_directory, config = params$config2)
stitch_data_fidelity(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## Cases by admin comparison
cache1[["admin_case_summary_table"]] <- taxdat::plot_cases_by_admin(cache = cache1, config = params$config1, cholera_directory = params$cholera_directory, 
  admin_level_for_summary_table = params$admin_level_for_summary_table, aesthetic = FALSE)
cache2[["admin_case_summary_table"]] <- taxdat::plot_cases_by_admin(cache = cache2, config = params$config2, cholera_directory = params$cholera_directory, 
  admin_level_for_summary_table = params$admin_level_for_summary_table, aesthetic = FALSE) 
taxdat::stitch_admin_case_summary_table(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## WHO cases table
cache1[["who_data_comparison_table"]] <- plot_WHOcomparison_table(config = params$config1, cache = cache1, 
  cholera_directory = params$cholera_directory, aesthetic = FALSE)
cache2[["who_data_comparison_table"]] <- plot_WHOcomparison_table(config = params$config2, cache = cache2, 
  cholera_directory = params$cholera_directory, aesthetic = FALSE)
stitch_who_data_comparison_table(output_cache = comparison_cache, input_caches = list(cache1, cache2))

## The cases by chain table
cache1[["case_by_chain_time_table"]] <- plot_modeled_cases_by_chain_time(config = params$config1, cache = cache1, 
  cholera_directory = params$cholera_directory, aesthetic = FALSE)
cache2[["case_by_chain_time_table"]] <- plot_modeled_cases_by_chain_time(config = params$config2, cache = cache2, 
  cholera_directory = params$cholera_directory, aesthetic = FALSE)
comparison_cache[["nchain"]] <- cache1[["nchain"]] #either config works
stitch_case_by_chain_time_table(output_cache = comparison_cache, input_caches = list(cache1, cache2))

```


**Table 1. Configs Comparison Table:**
```{r echo = FALSE}
plot_config_comparison_table(configs = list(params$config1, params$config2), cache = comparison_cache)
```

**Observations input for the GAM model:**
```{r gam input of cases, fig.height=5, fig.width=10, fig.cap=capFig("Observations input for the GAM model (cases)")}
plot_gam_fit_input_cases_stitched(cache = comparison_cache)
```
```{r gam input of rates, fig.height=5, fig.width=10, fig.cap=capFig("Observations input for the GAM model (rates)")}
plot_gam_fit_input_rates_stitched(cache = comparison_cache)
```

**Observations output of the GAM model:**
```{r gam output of cases, fig.height=25, fig.width=10, fig.cap=capFig("Observations input for the GAM model (cases)")}
plot_gam_fit_output_cases_stitched(cache = comparison_cache, year_vector = year_vector)
```
```{r gam output of rates, fig.height=25, fig.width=10, fig.cap=capFig("Observations input for the GAM model (rates)")}
plot_gam_fit_output_rates_stitched(cache = comparison_cache, year_vector = year_vector)
```

**Table 2. Data used within the model by comparison between two runs:**
```{r echo = FALSE}
comparison_cache$used_data_table
```

**Table 3. Data dropped from the model by comparison between two runs:**
```{r echo=FALSE}
comparison_cache$dropped_data_table
```

### Covariates
#### Population
**Population raster by time slices:**
```{r pop, fig.height=25, fig.width=10, fig.cap=capFig("Population density")}
taxdat::plot_time_varying_pop_raster_stitched(cache = comparison_cache, config = params$config1, cholera_directory = params$cholera_directory) #the config can be either one 
```

#### Other covariates
**Covariate rasters:**
```{r covars, fig.height=25, fig.width=10, fig.cap=capFig("Covariate rasters")}
plot1 <- plot_raster_covariates_sidebyside_comparison(cache = cache1, cholera_directory = params$cholera_directory, config = params$config1)
plot2 <- plot_raster_covariates_sidebyside_comparison(cache = cache2, cholera_directory = params$cholera_directory, config = params$config2)
gridExtra::grid.arrange(plot1, plot2, ncol = 2, left = "covariates from config1", right = "covariates from config2")
rm(plot1, plot2)
```

### GAM Output Comparison Scatter Plots 
#### GAM cases output
```{r gamscattercase, fig.cap=capFig("GAM output cases comparison"), fig.height=10, fig.width=10}
plot_gam_cases_scatter_plot_stitched(cache = comparison_cache)
```
#### GAM rates output
```{r gamscatterrate, fig.cap=capFig("GAM output rates comparison"), fig.height=10, fig.width=10}
plot_gam_rates_scatter_plot_stitched(cache = comparison_cache)
```

### Modeled cases
**Modeled cases raster by time slices:**
```{r caserast1, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases"), fig.height=25, fig.width=10}
plot_disaggregated_modeled_cases_time_varying_stitched(disaggregated_case_sf = comparison_cache[["disaggregated_case_sf"]], 
  country_iso = country_iso, year_vector = year_vector, diff_only = FALSE)
```

**Cases difference raster by time slices:**
```{r caserast2, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases difference"), fig.height=10, fig.width=10}
plot_disaggregated_modeled_cases_time_varying_stitched(disaggregated_case_sf = comparison_cache[["disaggregated_case_sf"]], 
  country_iso = country_iso, year_vector = year_vector, diff_only = TRUE)
```

**Modeled cases comparison by grids:**
```{r caserast3, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases grid comparison (fixed coordinates scale)"), fig.height=10, fig.width=10}
plot_modeled_cases_scatter_plot_by_grids_stitched(cache = comparison_cache, year_vector = year_vector, coord_fixed = TRUE)
```
```{r caserast4, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases grid comparison (free scales)"), fig.height=10, fig.width=10}
plot_modeled_cases_scatter_plot_by_grids_stitched(cache = comparison_cache, year_vector = year_vector, coord_fixed = FALSE)
```

**Modeled cases comparison by admin1:**
```{r caserast5, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases admin comparison (fixed coordinates scale)"), fig.height=10, fig.width=10}
plot_modeled_cases_scatter_plot_by_admin_stitched(cache = comparison_cache, country_iso = country_iso, admin_level = 1, district_name = TRUE, label_threshold = 0.1, 
  year_vector = year_vector, coord_fixed = TRUE)
```
```{r caserast6, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases admin comparison (free scales)"), fig.height=10, fig.width=10}
plot_modeled_cases_scatter_plot_by_admin_stitched(cache = comparison_cache, country_iso = country_iso, admin_level = 1, district_name = TRUE, label_threshold = 0.1, 
  year_vector = year_vector, coord_fixed = FALSE)
```

**Modeled cases comparison by oc_uid:**
```{r caserast7, eval=as.logical(!skip_stan), fig.cap=capFig("Modeled cases observation comparison"), fig.height=25, fig.width=10}
plot_modeled_cases_scatter_plot_by_oc_uid_stitched(cache = comparison_cache)
```

**Table 4. Modeled cases stacked from different sources by admin level and time:**
```{r eval=as.logical(!skip_stan), echo = FALSE}
taxdat::plot_cases_by_admin_table_stitched(cache = comparison_cache, type = "intersperse")
```

**Table 5. Modeled cases difference by admin level and time:**
```{r eval=as.logical(!skip_stan), echo = FALSE}
taxdat::plot_cases_by_admin_table_stitched(cache = comparison_cache, type = "difference")
```

**Table 6. BIC and AIC Comparison Table:**
```{r echo = FALSE}
plot_AIC_BIC_comparison_table(cache1 = cache1, cache2 = cache2)
```

**Table 7. Observed and estimates of WHO annual cholera reports:**
```{r eval=as.logical(!skip_stan), echo = FALSE}
plot_WHOcomparison_table_stitched(cache = comparison_cache)
```

**Table 8. Estimated cases by chain and time slice:**
```{r eval=as.logical(!skip_stan), echo = FALSE}
plot_modeled_cases_by_chain_time_stitched(cache = comparison_cache)
```
