---
title: "Country Data Report"
output: html_document
params: 
  cholera_directory: "/home/.../cholera-mapping-pipeline"
  config: "Analysis/.../config.yml"
  drop_nodata_years: TRUE
  admin_level_for_summary_table: '1'
  args: 'myarg'
  old_runs: FALSE
---
```{r eval = FALSE, include = FALSE}
# Set all the parameters for development purposes (need to comment them out when running the whole script)
# params <- new.env()
# params$cholera_directory <- "/home/kaiyuezou/mapping_pipeline/2016_2020_no_covariate_run/cholera-mapping-pipeline"
# params$config <- "Analysis/configs/no_covariate_production_2016_2020/2016_2020_country/config_BEN_2016_2020.yml"
# params$drop_nodata_years <- TRUE
# params$admin_level_for_summary_table <- '1'
# params$args <- 'myarg'
# params$old_runs <- FALSE
```

```{r setup, include=FALSE, dev="CairoPNG",message=FALSE}
library(knitr)
knitr::opts_chunk$set(
  cache=FALSE,
  cache.lazy = FALSE,
  echo = FALSE,
  dev="CairoPNG",
  error = FALSE,
  fig.align = "center",
  message = TRUE,
  warning = TRUE
  )
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(taxdat)
library(sf)
library(raster)
library(stars)
library(taxdat)
sf::sf_use_s2(FALSE)

### other new packages (mainly for "rgeoboundaries")
chooseCRANmirror(ind = 77)

package_list <- c(
  "fasterize", 
  "remotes",
  "rgeoboundaries"
)

for (package in package_list) {
  if (!require(package = package, character.only = T)) {
    if (package == "rgeoboundaries"){
      try({
        remotes::install_gitlab("dickoa/rgeoboundaries")
        remotes::install_github("wmgeolab/rgeoboundaries")
      })
    }else{
      install.packages(pkgs = package)
      library(package = package, character.only = T)
    }
  }
}

#Figure Caption Numbering,
capFigNo = 1
#Function to add the Figure Number
capFig = function(x){
    x = paste0("Figure ",capFigNo,". ",x)
    capFigNo <<- capFigNo + 1
    x
}

```

# Mapping results summary for `r stringr::str_extract(params$config, "[A-Z]{3}")` and period `r stringr::str_extract(params$config, "[0-9]{4}_[0-9]{4}")`

## Cholera input data
**Data input:**
```{r load data,message=FALSE}
# Load data
cache<-new.env()
get_stan_input(name="stan_input",cache=cache,config = params$config,cholera_directory = params$cholera_directory)
get_sf_cases_resized(name="sf_cases_resized",cache=cache,config = params$config,cholera_directory = params$cholera_directory)
get_sf_cases(name="sf_cases",cache=cache,config=params$config,cholera_directory=params$cholera_directory)

get_genquant(name="genquant",cache=cache,config=params$config,cholera_directory = params$cholera_directory)
get_model_rand(name="model.rand",cache=cache,config = params$config,cholera_directory = params$cholera_directory)
get_modeled_cases(name="modeled_cases",cache=cache,config=params$config,cholera_directory = params$cholera_directory)
get_modeled_rates(name="modeled_rates",cache=cache,config = params$config,cholera_directory = params$cholera_directory)

cache[["modeled_cases_by_chain"]]<-aggregate_modeled_cases_by_chain_no_cache(cache=cache,config = params$config,cholera_directory = params$cholera_directory)
cache[["cases_chains"]]<-aggregate_modeled_cases_by_chain_gridtime_no_cache(cache=cache,config = params$config,cholera_directory = params$cholera_directory)
cache[["niter_per_chain"]]<-get_stan_model_niter_per_chain_no_cache(cache=cache,config = params$config,cholera_directory = params$cholera_directory)
cache[["nchain"]]<-get_stan_model_nchain_no_cache(cache=cache,config = params$config,cholera_directory = params$cholera_directory)
cache[["stan_output"]]<-get_stan_output_no_cache(cache=cache,config = params$config,cholera_directory = params$cholera_directory)

get_initial_values(name="initial_values_data",cache=cache,config = params$config,cholera_directory = params$cholera_directory)
cache[["gam_output_df"]]<-get_gam_values_no_cache(cache=cache,config = params$config,cholera_directory = params$cholera_directory)

get_covar_cube (name="covar_cube", config = params$config,cache=cache,cholera_directory = params$cholera_directory)
get_sf_grid(name="sf_grid",config = params$config,cache=cache,cholera_directory = params$cholera_directory)
```

### GAM Input
**Observations input for the GAM model:**
```{r gam input of cases,fig.height=10, fig.width=15, fig.cap=capFig("Observations input for the GAM model (cases)")}
plot_gam_fit_input (name="initial_values_data", cache=cache, mean=FALSE, type="cases")
```

```{r gam input of rates,fig.height=10, fig.width=15, fig.cap=capFig("Observations input for the GAM model (rates)")}
plot_gam_fit_input (name="initial_values_data", cache=cache, mean=FALSE, type="rates")
```

### GAM Output
**Observations output of the GAM model:**
```{r gam output of cases,fig.height=10, fig.width=15, fig.cap=capFig("Observations output from the GAM model (cases)")}
plot_gam_fit_output(name="gam_output_df",cache=cache,type='cases')
```

```{r gam output of rates,fig.height=10, fig.width=15, fig.cap=capFig("Observations output from the GAM model (rates)")}
plot_gam_fit_output(name="gam_output_df",cache=cache,type='rates')
```

### GAM Output v.s GAM Input Comparison
**GAM Output v.s Raw GAM Input Rates Scatterplot:**
```{r gam output input rates comparison,fig.height=10, fig.width=15, fig.cap=capFig("GAM Output v.s Raw GAM Input Rates")}
plot_gam_input_vs_output_rate_scatter_plot(cache = cache, type = 'raw') 
```
**GAM Output v.s Averaged GAM Input Rates Scatterplot:**
```{r gam output input rates comparison averaged,fig.height=10, fig.width=15, fig.cap=capFig("GAM Output v.s Averaged GAM Input Rates")}
plot_gam_input_vs_output_rate_scatter_plot(cache = cache, type = 'averaged') 
```


**Table 1. Data used within the model:**
```{r echo = FALSE}
plot_ObservationSummary_table(config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

**Table 2. Data dropped from the model:**
```{r echo=FALSE}
plot_DroppedData_table (config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

```{r disjoint set sf cases, message=FALSE}
aggregate_observed_polygon_cases_disjoint_aggregated(name="observed_polygon_cases_disjoint_aggregated",config=params$config,cholera_directory=params$cholera_directory,cache=cache)
disjoint_set_sf_cases <- cache[["observed_polygon_cases_disjoint_aggregated"]]
```

**Averaged annual cases by spatial scales:**
```{r rawobsmap, fig.height=10, fig.width=30, out.width="150%",fig.cap=capFig("Observed case counts by time adjusted for time fraction cases/year")}
plot_observed_cases_polygon_raw(config=params$config,cache=cache,cholera_directory=params$cholera_directory) 
```

**Averaged area adjusted annual cases by spatial scales:**
```{r areadjustedmap, fig.height=10, fig.width=30, out.width="150%",fig.cap=capFig("Area adjusted average observed case counts by time adjusted for time fraction cases/(year * kilometer)")}
plot_area_adjusted_observed_cases(config=params$config,cache=cache,cholera_directory=params$cholera_directory)
```

**Number of observations by unique observed location periods:**
```{r obsmap, fig.height=10, fig.width=30, out.width="150%",fig.cap=capFig("Number of observations by unique observed location periods.")}
plot_raw_observations(config=params$config,cache=cache,cholera_directory=params$cholera_directory)
```
### Covariates

#### Population
**Population raster by time slices:**
```{r pop, fig.height=5, fig.width=10, fig.cap=capFig("Population density")}
plot_time_varying_pop_raster(cache=cache,config=params$config,cholera_directory=params$cholera_directory)
```

**Table 3. Population by admin level:**
```{r echo = FALSE}
plot_pop_by_admin(cache=cache,cholera_directory=params$cholera_directory,config=params$config,admin_level_for_summary_table=params$admin_level_for_summary_table)
warning("Here we're using 20*20 km pop raster to estimate the population!")
```

#### Other covariates
**Covariate rasters:**
```{r covars, fig.height=5, fig.width=10, fig.cap=capFig("Covariate rasters")}
if(length(dimnames(cache[["covar_cube"]])[[3]])>=2){
plot_raster_covariates(cache=cache,cholera_directory=params$cholera_directory,config=params$config)
}else{
  warning("no covariates")
}
```

### Output maps
```{r analysisyears}
obs_years <- min(lubridate::year(cache[["stan_input"]]$sf_cases_resized$TL)):max(lubridate::year(cache[["stan_input"]]$sf_cases_resized$TR))
rstan::get_elapsed_time(cache[["model.rand"]])
```


```{r importcase}
cache[["case_raster"]] <-get_case_raster(cache=cache,config=params$config,cholera_directory=params$cholera_directory)
cache[["disaggregated_rate_sf"]]<-get_disaggregated_rates_sf(cache=cache,config=params$config,cholera_directory=params$cholera_directory)
cache[["disaggregated_case_sf"]]<-get_disaggregated_cases_sf (cache=cache,config=params$config,cholera_directory=params$cholera_directory)

config_file<-yaml::read_yaml(paste0(params$cholera_directory,"/",params$config))
analysis_years <- lubridate::year(config_file$start_time):lubridate::year(config_file$end_time)
obs_years <- min(lubridate::year(cache[["sf_cases_resized"]]$TL)):max(lubridate::year(cache[["sf_cases_resized"]]$TR))

 if(all(analysis_years %in% obs_years)){
   message("All analysis years are represented by OCs.")
 } else{
   drop_year_ix <- which(!analysis_years %in% obs_years)
   message(paste(paste(analysis_years[drop_year_ix], collapse = ", "), "are not represented in OCs"))
   if(params$drop_nodata_years){
     message(paste("Dropping", paste(analysis_years[drop_year_ix], collapse = ", "), "from case_raster"))
     case_raster <- dplyr::filter(case_raster, !(t %in% drop_year_ix))
   }
 }
```

#### Modeled cases
**Modeled cases raster by time slices:**
```{r caserast, fig.cap=capFig("Modeled cases"), fig.height=5, fig.width=10}
plot_disaggregated_modeled_cases_time_varying(disaggregated_case_sf=cache[["disaggregated_case_sf"]])
```

### Stan Output v.s GAM Output
**Stan Output v.s GAM Output Rates by Time Slices:**
```{r stangamrates, fig.cap=capFig("Stan Output v.s GAM Output Rates"), fig.height=5, fig.width=10}
plot_stan_output_vs_gam_output_rate_scatter_plot(cache = cache)
```

**Stan Output v.s GAM Output Cases by Time Slices:**
```{r stangamcates, fig.cap=capFig("Stan Output v.s GAM Output Cases"), fig.height=5, fig.width=10}
plot_stan_output_vs_gam_output_case_scatter_plot(cache = cache) #this will output plots 
```



**Table 4. Modeled cases by admin level and time:**
```{r echo = FALSE}
plot_cases_by_admin(cache=cache,config=params$config,cholera_directory=params$cholera_directory,admin_level_for_summary_table=params$admin_level_for_summary_table)
```

#### Modeled incidence rates
**Modeled incidence rates raster by time slices:**
```{r raterast, fig.cap=capFig("Modeled rates by time"), fig.height=5, fig.width=10}
plot_modeled_rates_time_varying(disaggregated_rate_sf=cache[["disaggregated_rate_sf"]], render = T)
```

**Table 5. Modeled incidence rates by admin level and time:**
```{r echo = FALSE}
plot_incidence_by_admin(cache=cache,config=params$config,cholera_directory=params$cholera_directory,admin_level_for_summary_table=params$admin_level_for_summary_table)
warning("Here we're using 20*20 km pop raster!")
```

### Validation
```{r import_modelfidel}
cache[["data_fidelity"]]<-get_data_fidelity(cache=cache,cholera_directory=params$cholera_directory,config=params$config)
```

**Actual observations versus modeled cases scatter plot:**
```{r datafidelity1, fig.cap=capFig("Observations vs. modeled cases"), fig.height=10, fig.width=10}
if(!is.null(cache[["data_fidelity"]])){
plot_model_fidelity_tfrac_adjusted(cache=cache,cholera_directory=params$cholera_directory,config=params$config,render = T)
}else{
  warning("data_fidelity is NULL!")
}
```

```{r datafidelity3, fig.cap=capFig("Observations vs. modeled cases (tfrac adjusted)"), fig.height=15, fig.width=10}
if(!is.null(cache[["data_fidelity"]])){
plot_model_fidelity_tfrac_adjusted_by_year(cache=cache,cholera_directory=params$cholera_directory,config=params$config,render = T)
}else{
  warning("data_fidelity is NULL!")
}
```

```{r datafidelity4, fig.cap=capFig("Observations vs. modeled cases"), fig.height=8, fig.width=10}
if(!is.null(cache[["data_fidelity"]])){
plot_model_fidelity_tfrac_unadjusted(cache=cache,cholera_directory=params$cholera_directory,config=params$config,render = T)
}else{
  warning("data_fidelity is NULL!")
}
```

```{r datafidelity5, fig.cap=capFig("Observation vs. modeled_cases by chains"),fig.height=8,fig.width=10}
if(!is.null(cache[["data_fidelity"]])){
plot_model_fidelity_by_chain(cache=cache,cholera_directory=params$cholera_directory,config=params$config,render=T)
}else{
  warning("data_fidelity is NULL!")
}
```

**Stan trace plots:**
```{r traceplots, fig.height=8, fig.width=10, fig.cap=capFig("Stan trace plots")}
plot_chain_convergence(cache=cache,name="model.rand")
```

**Parameter posteriors:**
```{r params, fig.height=6, fig.width=6, fig.cap=capFig("Parameter posteriors")}
plot_MCMCpars(name="model.rand",cache=cache)
```

**Gelman-Rubin Rhat:**
```{r rhat, fig.height=5, fig.width=10, fig.cap=capFig("Gelman-Rubin Rhat")}
plot_Rhat(name="model.rand",cache)
```

**Table 6. Observed and estimates of WHO annual cholera reports:**
```{r WHO output, fig.height=510, fig.width=10, fig.cap = "comparison with WHO Output"}
plot_WHOcomparison_table(config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

**Table 7. Estimated cases by chain and time slice:**
```{r cases_chain_table, fig.width=10, fig.cap = "Sum of grid cases by chain and year"}
plot_modeled_cases_by_chain_time (config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

```{r full country modeled cases, fig.cap = "comparison with WHO Output"}
total_cases <- cache[["modeled_cases"]] %>% apply(3, mean) %>% sum()
print(paste("There are",format(round(total_cases), big.mark=","),"total cases"))
```
