---
title: "Country Map Comparisons"
output: html_document
params:
  cholera_directory: "~/gh/cholera-mapping-pipeline/"
  config_directory: "Analysis/configs/2015_2019_full_base/"
  output_dir: "Analysis/output/2015_2019_full_base/"
  old_map_rate: "old_products/rate.tif"
  old_map_case: "old_products/case.tif"
  shapefiles_dir: "shapefiles/"
  max_countries: Inf
---

```{r setup, include=FALSE, dev="CairoPNG"}
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(RColorBrewer)
library(MCMCvis)
library(sf)
library(abind)
library(taxdat)

options(bitmapType = 'cairo')
#knitr::opts_chunk$set(include = FALSE, dev="CairoPNG")
knitr::opts_chunk$set(
  echo = FALSE,
 # dev.args = list(png = list(type = "cairo")),
  dev = "CairoPNG",
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache.lazy = F,
  bitmapType = "cairo",
  error=TRUE
)


```

```{r dir_settings}


dir.create(params$shapefiles_dir, showWarnings = FALSE)
dir.create(stringr::str_c(params$cholera_directory, params$output_dir), showWarnings = FALSE)


```
# Country Data Pull
Extract Stan model outputs

```{r data_pull}
orig_configs <- list.files(stringr::str_c(params$cholera_directory, params$config_directory), full.names = TRUE)
skip_cntry <- c("BWA", "COG", "DJI", "ERI", "GAB", "GMB", "GNQ", "LSO", "MDG", "NAM", "SEN", "SWZ")
indexes <- unlist(lapply(skip_cntry, function(cntry){
  which(stringr::str_detect(orig_configs, cntry))
}))
all_configs <- orig_configs[-indexes]
# all_configs <- list.files(stringr::str_c(params$cholera_directory, params$config_directory), full.names = TRUE)

all_locations <- stringr::str_extract(all_configs, "[A-Z]{3}")
print(all_locations)

all_times <- unique(stringr::str_extract(params$config_directory, "[0-9]{4}_[0-9]{4}"))
first_time <- as.numeric(unlist(strsplit(all_times, split = "_"))[1])
second_time <- as.numeric(unlist(strsplit(all_times, split = "_"))[2])
print(all_times)


sf_cases_resized <- list()
sf_grid <- list()
country_summ <- list()
eta_summ <- list()
country_count <- 0
for(i in 1:length(all_configs)){
  config_filename <- all_configs[i]
  print(config_filename)
  if(country_count >= params$max_countries){break}
  config <- yaml::read_yaml(config_filename)
  file_names <- taxdat::get_filenames(config, params$cholera_directory)
  if(!all(file.exists(file_names))){
    print("These files don't exist:")
    print(file_names[which(!file.exists(file_names))])
  }

  try({
    stan_input <- taxdat::read_file_of_type(file_names[['stan_input']], "stan_input")
    stan_input$sf_grid <- stan_input$sf_grid %>% 
        dplyr::ungroup() %>% 
        dplyr::select(t,id)
  }, silent = TRUE)

  try({
    model.rand <- taxdat::read_file_of_type(file_names[['stan_output']], "model.rand")
    niter_per_chain <- dim(MCMCvis::MCMCchains(model.rand, params='lp__', chain_num=1))[1]
    nchain <- dim(MCMCvis::MCMCchains(model.rand, params='lp__'))[1] / niter_per_chain
    stan_output <- lapply(rstan::extract(model.rand), function(x){array(x,c(niter_per_chain, nchain, dim(x)[-1]))})

    cases_chains <- apply(stan_output$grid_cases, c(3,2), mean)
    rates_chains <- apply(exp(stan_output$log_lambda), c(3,2), mean)

    eta_chains <- purrr::map_dfr(1:(dim(stan_output$eta)[3]), function(i){
        dummy <- data.frame(stan_output$eta[,,i])
        names(dummy) <- paste0("chain_", 1:length(names(dummy)))
        rc <- dplyr::mutate(dummy, year = i)
        return(rc)
      }) %>%
      tidyr::pivot_longer(dplyr::contains("chain"), values_to = "eta_est", names_to = "chain") %>%
      dplyr::mutate(chain = as.numeric(stringr::str_remove(chain, "chain_"))) %>%
      dplyr::group_by(year, chain) %>%
      dplyr::summarise(eta_mean = mean(eta_est), 
                      eta_q025 = quantile(eta_est, probs = c(.025)),
                      eta_q975 = quantile(eta_est, probs = c(.975))) %>%
      dplyr::mutate(country = all_locations[i])

    pop_est <- cases_chains[,1]/rates_chains[,1]
  })

  try({
    stan_input$sf_grid[paste('cases','chain',seq_len(nchain),sep='_')] <- cases_chains
    stan_input$sf_grid[paste('rate','chain',seq_len(nchain),sep='_')] <- rates_chains
    stan_input$sf_grid['pop'] <- pop_est
    stan_input$sf_grid$row_index <- seq_len(nrow(stan_input$sf_grid))
    sf_grid_wider <- sf::st_drop_geometry(stan_input$sf_grid)
    
    # stan_input$sf_grid <- tidyr::pivot_longer(
    #   stan_input$sf_grid,
    #   cols=c(
    #     paste('cases','chain',seq_len(nchain),sep='_'),
    #     paste('rate','chain',seq_len(nchain),sep='_')
    #   ),
    #   names_to="scenario",
    #   values_to="modeled"
    # ) %>% sf::st_sf()
    # stan_input$sf_grid <- tidyr::separate(col=scenario, into = c('type',NA,'chain'),stan_input$sf_grid)
    # stan_input$sf_grid$filename <- config_filename
  
    # if("list" %in% class(sf_grid)){
    #   sf_grid <- stan_input$sf_grid
    # } else {
    #   sf_grid <- rbind(sf_grid, stan_input$sf_grid)
    # }

    calc_country_summ <- sf_grid_wider %>%
      dplyr::group_by(t) %>%
      dplyr::summarise(dplyr::across(dplyr::contains("cases_"), sum),
                       dplyr::across(dplyr::contains("rate_"), mean),
                       ## dplyr::across(dplyr::contains("rate_"), ~weighted.mean(.x, w=pop)), ## something weird with the pop estimates
                       dplyr::across(pop, sum)) %>%
      tidyr::pivot_longer(
              cols=c(
              paste('cases','chain',seq_len(nchain),sep='_'),
              paste('rate','chain',seq_len(nchain),sep='_')
              ),
              names_to="scenario",
              values_to="modeled") %>%
      tidyr::separate(col = scenario, into = c('type', NA, 'chain')) %>%
      dplyr::mutate(country = all_locations[i])
  })


  try({

    if("list" %in% class(country_summ)){
      country_summ <- calc_country_summ
    } else {
      country_summ <- rbind(country_summ, calc_country_summ)
    }
    if("list" %in% class(eta_summ)){
      eta_summ <- eta_chains
    } else {
      eta_summ <- rbind(eta_summ, eta_chains)
    }

    country_count <- country_count + 1

  })


}

```


## Comparison to Lancet maps

Load old maps - incidence and incidence rate
```{r load_old_output}
allafr_rate <- taxdat::load_orig_map(stringr::str_c(params$cholera_directory, params$old_map_rate))
allafr_cases <- taxdat::load_orig_map(stringr::str_c(params$cholera_directory, params$old_map_case))

```
Process old maps country by country
```{r country_datapull}
country_summ_old <- list()
for (cntry in all_locations){

  shp <- GADMTools::gadm_sf_loadCountries(c(cntry), level = 0, basefile = params$shapefiles_dir)$sf

  # raster::crs(allafr_rate) <- raster::crs(shp)
  # raster::crs(allafr_cases) <- raster::crs(shp)
  shp <- dplyr::mutate(shp, value = 1) %>%
    sf::st_as_sf()
  shp_raster <- fasterize::fasterize(shp, raster::raster(allafr_rate), field = "value", fun = "last", background = 0)

  country_rate <- shp_raster * allafr_rate
  names(country_rate) <- "rate"
  country_case <- shp_raster * allafr_cases
  names(country_case) <- "case"

  calc_country_summ_old <- data.frame(cases_old = sum(raster::values(country_case), na.rm=TRUE),
                                      rate_old = mean(raster::values(country_rate), na.rm = TRUE)) %>%
    tidyr::pivot_longer(cols = c("cases_old", "rate_old"), names_to = "type", values_to = "modeled") %>%
    dplyr::mutate(country = cntry)

  if("list" %in% class(country_summ)){
    country_summ_old <- calc_country_summ_old
  } else {
    country_summ_old <- rbind(country_summ_old, calc_country_summ_old)
  }
}


```

Export a table of chain vs time for new estimates and mean annual value for old estimates
```{r prep_plot}
labels_yrs <- seq(first_time, second_time, by = 1)
levels_yrs <- seq.int(labels_yrs)

plot_df <- dplyr::bind_rows(dplyr::select(country_summ, -pop), country_summ_old) %>%
  dplyr::mutate(type_lab = paste(type, chain, sep = "_")) %>%
  dplyr::arrange(country, type, t) %>%
  dplyr::mutate(t = factor(t, levels = levels_yrs, labels = labels_yrs),
                modeled_trunc = ifelse(modeled > 1.5E4, 1.5E4, modeled))
readr::write_csv(plot_df, paste0(params$cholera_directory, params$output_dir, "national_estimates_new_old.csv"))

plot_df2 <- plot_df %>% 
  dplyr::group_by(country, type) %>%
  dplyr::summarise(modeled = mean(modeled)) %>%
  dplyr::mutate(modeled_trunc = ifelse(modeled > 1.5E4, 1.5E4, modeled)) %>%
  dplyr::mutate(type = recode(type, rate = "rate_new", cases = "cases_new"))
plot_df2 %>% kbl %>% kable_minimal()
```

## Examine new model estimates

```{r bar_incid_t_chain, fig.height=12, fig.width=8, fig.cap = "Truncated modeled case estimates by country, chain, and year (facets)"}

p_bar_incid <- ggplot2::ggplot(dplyr::filter(plot_df, type == "cases"), ggplot2::aes(x = chain, y = modeled_trunc)) +
  ggplot2::geom_col() +
  ggplot2::scale_y_continuous("modeled cases (trunc > 1.5E4)") +
  ggplot2::facet_grid(country ~ t, scales = "free_y")
p_bar_incid
ggplot2::ggsave(paste0(params$cholera_directory, params$output_dir, "national_incid_chain_t_trunc.png"), p_bar_incid, width = 7, height = 14)
```

```{r bar_eta_chain, fig.height = 12, fig.width = 6, fig.cap = "Yearly random effects"}
p_eta <- ggplot2::ggplot(eta_summ, ggplot2::aes(x = chain, y = eta_mean)) +
  ggplot2::geom_point() + 
  ggplot2::geom_errorbar(ggplot2::aes(ymin = eta_q025, ymax = eta_q975)) +
  ggplot2::facet_grid(country~year, scales = "free_y")
p_eta
ggplot2::ggsave(paste0(params$cholera_directory, params$output_dir, "eta_chain.png"), p_eta, width = 7, height = 14)
```


## Incidence comparison 

```{r plot_incid, fig.height=10, fig.width=8, fig.cap = "Log 10 modeled incidence, new vs old (NA chain)"}
  
p_case <- ggplot2::ggplot(dplyr::filter(plot_df2, grepl("case", type)), ggplot2::aes(x = country, y = modeled)) +
  ggplot2::geom_point(ggplot2::aes(colour = type), alpha = 0.7) +
  ggplot2::coord_flip() +
  ggplot2::scale_y_log10("Log 10 modeled incidence") +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "bottom")
p_case
```

```{r plot_incid_zm, fig.height=10, fig.width=8}
  
p_case_zm <- ggplot2::ggplot(dplyr::filter(plot_df2, grepl("case", type)), ggplot2::aes(x = country, y = modeled_trunc)) +
  ggplot2::geom_point(ggplot2::aes(colour = type), alpha = 0.7) +
  ggplot2::coord_flip() +
  ggplot2::scale_y_continuous("Modeled incidence (trunc > 1.5E4)") +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "bottom")
p_case_zm
ggplot2::ggsave(paste0(params$cholera_directory, params$output_dir, "national_incid_trunc_new_old.png"), p_case_zm, width = 8, height = 10)
```

## Incidence Rate comparison 
Note that these are only approximations of the incidence rate in that country (mean value across cells). It would be more appropriate to actually do a population-weighted average across lambdas in order to estimate country incidence rate.

```{r plot_incidrate, fig.height=10, fig.width=8}

p_ir <- ggplot2::ggplot(dplyr::filter(plot_df2, grepl("rate", type)), ggplot2::aes(x = country, y = modeled)) +
  ggplot2::geom_point(ggplot2::aes(colour = type), alpha = 0.7) +
  ggplot2::coord_flip() +
  ggplot2::scale_y_log10("Log 10 modeled incidence rate") +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "bottom")
p_ir
```


```{r plot_incidrate_zm, fig.height=10, fig.width=8}

p_ir_zm <- ggplot2::ggplot(dplyr::filter(plot_df2, grepl("rate", type)), ggplot2::aes(x = country, y = modeled_trunc)) +
  ggplot2::geom_point(ggplot2::aes(colour = type), alpha = 0.7) +
  ggplot2::coord_flip() +
  ggplot2::scale_y_continuous("Modeled incidence rate (trunc > 1.5E4)") +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "bottom")
p_ir_zm
ggplot2::ggsave(paste0(params$cholera_directory, params$output_dir, "national_incidrate_trunc_new_old.png"), p_ir_zm, width = 8, height = 10)
```
