---
title: "Data and Model Outputs Report"
output: html_document
params:
  cholera_directory: "~/cholera-mapping-pipeline"
  config: "/Analysis/configs/config.yml"
  drop_nodata_years: TRUE
  admin_level_for_summary_table: '1'
  args: 'myarg'
---
```{r setup, include=FALSE, dev="CairoPNG"}
knitr::opts_chunk$set(
  echo = FALSE,
  dev="CairoPNG",
  error = FALSE,
  fig.align = "center",
  message = TRUE,
  warning = TRUE
  )
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(taxdat)
library(sf)
library(raster)
library(stars)

### other new packages (mainly for "rgeoboundaries")
chooseCRANmirror(ind = 77)

package_list <- c(
  "fasterize", 
  "remotes",
  "rgeoboundaries"
)

for (package in package_list) {
  if (!require(package = package, character.only = T)) {
    if (package == "rgeoboundaries"){
      try({
        remotes::install_gitlab("dickoa/rgeoboundaries")
        remotes::install_github("wmgeolab/rgeoboundaries")
      })
    }else{
      install.packages(pkgs = package)
      library(package = package, character.only = T)
    }
  }
  # detach(pos = which(grepl(package, search())))
}


#Figure Caption Numbering,
capFigNo = 1
#Function to add the Figure Number
capFig = function(x){
    x = paste0("Figure ",capFigNo,". ",x)
    capFigNo <<- capFigNo + 1
    x
}

```

# Mapping results summary for `r stringr::str_extract(params$config, "[A-Z]{3}")` and period `r stringr::str_extract(params$config, "[0-9]{4}_[0-9]{4}")`

## Cholera input data
**Data input:**
```{r load data}
# Load data directory
config <- yaml::read_yaml(paste0(params$cholera_directory, params$config))
file_names <- taxdat::get_filenames(config, params$cholera_directory)

####the following lines are needed if this report is for old runs (file names are different)####
# file_names[["stan_input"]]<-stringr::str_remove(file_names[["stan_input"]],"allOCs_")
# file_names[["stan_output"]]<-stringr::str_remove(file_names[["stan_output"]],"allOCs_")
# file_names[["stan_output"]]<-stringr::str_remove(file_names[["stan_output"]],"-csF-teT-teaF-weT-F")
# file_names[["stan_output"]]<-stringr::str_remove(file_names[["stan_output"]],"-F")
# file_names[["covar"]]<-stringr::str_remove(file_names[["covar"]],"allOCs_")
# file_names[["data"]]<-stringr::str_remove(file_names[["data"]],"allOCs_")
################################################################################################

stan_input <- NULL
try({
  stan_input <- taxdat::read_file_of_type(file_names[['stan_input']], "stan_input")
})
if (is.null(stan_input)) {
  cat(file_names[['stan_input']])
  stop("Stan input not found")
}

sf_cases <- NULL
sf_cases_resized <- NULL
model.rand <- NULL
stan_output <- NULL
cases_chains <- NULL
try({
  sf_cases <- taxdat::read_file_of_type(file_names["data"], "sf_cases")
  sf_cases_resized <- stan_input$sf_cases_resized
  model.rand <- taxdat::read_file_of_type(file_names["stan_output"], "model.rand")
  niter_per_chain <- dim(MCMCvis::MCMCchains(model.rand, params='lp__', chain_num=1))[1]
  nchain <- dim(MCMCvis::MCMCchains(model.rand, params='lp__'))[1] / niter_per_chain
  stan_output <- lapply(rstan::extract(model.rand), function(x){array(x,c(niter_per_chain, nchain, dim(x)[-1]))})
  cases_chains <- apply(stan_output$grid_cases, c(3,2), mean)
})
```

## GAM Input
**Observations input for the GAM model:**
```{r gam input,fig.cap=capFig("Observations input for the GAM model")}
try({
  initial_values_data <- read_file_of_type(file_names["initial_values"], "initial_values_data")
  
  initial_values_data$gam_fit_input %>%
    dplyr::group_by(sx, sy) %>%
    dplyr::summarize(y = mean(y)) %>%
    ggplot() +
    geom_tile(aes(x = sx, y = sy, fill = y)) +
    taxdat::color_scale(type = "cases", use_case = "ggplot map", use_log = FALSE)+
    ggplot2::labs(fill="Cases")

  initial_values_data$gam_fit_input %>%
    dplyr::group_by(sx, sy) %>%
    dplyr::summarize(y = mean(y), pop = mean(pop)) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(y = ifelse(y == 0, 1e-99, y)) %>%
    ggplot() +
    geom_tile(aes(x = sx, y = sy, fill = y / pop)) +
    taxdat::map_theme() +
    taxdat::color_scale(type = "rates", use_case = "ggplot map", use_log = TRUE)+
    ggplot2::labs(fill="Incidence rate")
  
})
```


# GAM Output
**Observations input for the GAM model:**
```{r gam output,fig.cap=capFig("Observations input for the GAM model")}
try({
initial_values_data <- read_file_of_type(file_names["initial_values"], "initial_values_data")
  gam_output_df<-taxdat::get_gam_values(config,params$cholera_directory)
  
  gam_output_df %>%
  ggplot() +
  geom_tile(aes(x = sx, y = sy, fill =y)) +
  taxdat::map_theme() +
  taxdat::color_scale(type = "cases", use_case = "ggplot map", use_log = FALSE)+
  ggplot2::labs(fill="Cases")


  gam_output_df %>%
  ggplot() +
  geom_tile(aes(x = sx, y = sy, fill =lambda)) +
  taxdat::map_theme() +
  taxdat::color_scale(type = "rates", use_case = "ggplot map", use_log = TRUE)+
  ggplot2::labs(fill="Incidence rate")
})
```


**Table 1. Data used within the model:**
```{r cases}
if(!is.null(sf_cases_resized)){
  # Get case data statistics
  obs_stats <- taxdat::get_obs_stats(sf_cases_resized)

  obs_stats %>%
    dplyr::select(-dplyr::contains("u_")) %>%
    dplyr::mutate_if(is.numeric, function(x) {format(x , big.mark=",")}) %>%
    kableExtra::kable(col.names = c("year", "# observations", "# suspected cases", "# location periods", "# observation collections")) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = T) %>%
    kableExtra::row_spec(nrow(obs_stats), bold = T)
} else{
  warning("sf_cases_resized is NULL")
}

```

**Table 2. Data dropped from the model:**
```{r dropcases}
### 11/02/2021 update -- dropped = all - used
if(!is.null(sf_cases) & !is.null(sf_cases_resized)){
  used_obs_stats <- obs_stats[order(obs_stats$year), ]
  all_obs_stats <- taxdat::get_obs_stats(sf_cases)
  all_obs_stats <- all_obs_stats[order(all_obs_stats$year), ]
  dropped_obs_stats <- all_obs_stats %>% 
    mutate(n_obs = all_obs_stats$n_obs - used_obs_stats$n_obs) %>% 
    mutate(n_cases = all_obs_stats$n_cases - used_obs_stats$n_cases) %>% 
    mutate(n_lp = all_obs_stats$n_lp - used_obs_stats$n_lp) %>% 
    mutate(n_OCs = all_obs_stats$n_OCs - used_obs_stats$n_OCs)

  for (i in 1:nrow(all_obs_stats)){
    dropped_obs_stats$u_lps[i] <- paste(sort(unique(setdiff(stringr::str_split(all_obs_stats$u_lps[i], ',')[[1]], 
                                                            stringr::str_split(used_obs_stats$u_lps[i], ',')[[1]]))), collapse = ",")
    dropped_obs_stats$u_OCs[i] <- paste(sort(unique(setdiff(stringr::str_split(all_obs_stats$u_OCs[i], ',')[[1]], 
                                                            stringr::str_split(used_obs_stats$u_OCs[i], ',')[[1]]))), collapse = ",")
  }

  dropped_obs_stats %>%
    dplyr::mutate_if(is.numeric, function(x) {format(x , big.mark=",")}) %>%
    kableExtra::kable(col.names = c("year", "# dropped observations", "# dropped suspected cases", "# dropped location periods",  "dropped location periods", "# dropped  observation collections",  "dropped observation collections")) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F) %>%
    kableExtra::row_spec(nrow(dropped_obs_stats), bold = T)
} else{
  warning("sf_cases or sf_cases_resized is NULL")
}

```

```{r disjoint set sf cases}
disjoint_set_sf_cases <- NULL
try({
  disjoint_set_sf_cases <- taxdat::get_disjoint_set_sf_cases(stan_input_filename = file_names["stan_input"])
})
```

**Cases by time:**
```{r rawobsmap, fig.height=5, fig.width=10, fig.cap=capFig("Observed case counts by time adjusted for time fraction cases/year")}
if(!is.null(disjoint_set_sf_cases)){
  taxdat::plot_raw_observed_cases(
    disjoint_set_sf_cases,
    render = T
  )
} else{
  warning("disjoint_set_sf_cases is NULL")
}

capFig("Observed case counts by time adjusted for time fraction cases/year")
```

**Area adjusted cases by time:**
```{r areadjustedmap, fig.height=5, fig.width=10, fig.cap=capFig("Area adjusted average observed case counts by time adjusted for time fraction cases/(year * kilometer)")}
if(!is.null(disjoint_set_sf_cases)){
  taxdat::plot_area_adjusted_observed_cases(
    disjoint_set_sf_cases,
    render = T
  )
} else{
  warning("disjoint_set_sf_cases is NULL")
}

```

**Cases unique location periods:**
```{r obsmap, fig.height=5, fig.width=10, fig.cap=capFig("Number of observations by unique observed location periods.")}
if(!is.null(disjoint_set_sf_cases)){
  taxdat::plot_raw_observations(disjoint_set_sf_cases,
                                render = T)
} else{
  warning("disjoint_set_sf_cases is NULL")
}
```


## Covariates

### Population
**Population raster by time slices:**
```{r pop, fig.height=5, fig.width=10, fig.cap=capFig("Population density")}
pop_raster_data <- raster(paste0(params$cholera_directory,"/Analysis/2000_1km_Aggregated.tif"))
country_shp <- rgeoboundaries::gb_adm0(as.character(stringr::str_extract(params$config, "[A-Z]{3}")))
pop_raster_data_cropped <- crop(pop_raster_data,extent(country_shp))
pop_raster_data_cropped_masked<-mask(pop_raster_data_cropped,country_shp)

pop_raster_data_cropped_sf <- pop_raster_data_cropped_masked%>%as(.,'SpatialPolygonsDataFrame')%>% sf::st_as_sf(.)

plt<-ggplot2::ggplot()+ggplot2::geom_sf(data = pop_raster_data_cropped_sf, ggplot2::aes(fill = X2000_1km_Aggregated,
            color = X2000_1km_Aggregated)) + ggplot2::scale_fill_viridis_c("Population",
            trans = "log", breaks = c(100, 1000, 10000,
                1e+05), aesthetics = c("colour", "fill"),
            guide = ggplot2::guide_colorbar(title = "Population density [per grid cell]"),
            option = "E", na.value = "white") + ggplot2::theme_bw() +
            ggplot2::theme(legend.position = "bottom",
                legend.text = ggplot2::element_text(angle = 45,hjust = 1, vjust = 1))
plt
```


**Table 3. Population by admin level:**
```{r echo = FALSE}
## the rest of this section is added on 11/03/2021, and can be turned into a function in model_evaluation_helpers.R later
## ======================================================================================================================
### Get the pltdata
covar_data_filename = file_names["covar"]
covar_cube_output <- taxdat::read_file_of_type(covar_data_filename, "covar_cube_output")
covar_cube <- covar_cube_output$covar_cube
sf_grid <- covar_cube_output$sf_grid
pop_layer <- covar_cube[,,1, drop = F] ## population is always the first layer

if(nrow(sf_grid) == prod(dim(pop_layer))){
  covar <- data.frame(covar = unlist(lapply(1:ncol(pop_layer), function(x){
    pop_layer[, x, 1]
  })))
  pltdata <- dplyr::bind_cols(sf_grid, covar)
  
  ### Use the geo package
  iso_code <- as.character(stringr::str_extract(params$config, "[A-Z]{3}"))
  admin_level <- as.numeric(params$admin_level_for_summary_table)
  if (admin_level == 1){
    boundary_sf <- rgeoboundaries::gb_adm1(iso_code)
  }else if (admin_level == 2){
    boundary_sf <- rgeoboundaries::gb_adm2(iso_code)
    warning('The current admin level is set at 2. ')
  }else if (admin_level == 3){
    boundary_sf <- rgeoboundaries::gb_adm3(iso_code)
    warning('The current admin level is set at 3. ')
  }else{
    stop('Error: the current admin level is unnecessarily high or invalid, 
    please check and change the parameters for the country data report before running again. ')
  }
    
  ### For loops and make the table
  admin_pop_table <- data.frame(matrix(NA, length(boundary_sf$shapeName), length(unique(pltdata$t)) + 1))
  
start_year <- as.numeric(stringr::str_extract(stringr::str_extract(params$config, "[A-Z]{3}_[0-9]{4}"), "[0-9]{4}"))
  if(is.na(start_year)){
  start_year <- as.numeric(stringr::str_extract(params$config, "[0-9]{1,4}"))
  if(!start_year%in%c(2015,2016,2017,2018,2019)){
      start_year <- as.numeric(stringr::str_extract(params$config, "\\d+(?=.yml)"))
  }
  }
  
  year_list <- unique(pltdata$t) + (start_year-1)
  colnames(admin_pop_table) <- c('adminlevel', year_list)
  admin_pop_table$adminlevel <- boundary_sf$shapeName

    ## across different locations
    for (locs in admin_pop_table$adminlevel){
      cropped <- raster::crop(pop_raster_data, boundary_sf[boundary_sf$shapeName == locs, ], snap = "out")
      masked <- raster::mask(cropped, boundary_sf[boundary_sf$shapeName == locs, ], updatevalue = NA)
      sum_pop <- sum(raster::getValues(masked), na.rm = TRUE)
      #admin_pop_table[match(locs, admin_pop_table$adminlevel), (match(ts, unique(pltdata$t)) + 1)] <- sum_pop
      admin_pop_table[match(locs, admin_pop_table$adminlevel), !colnames(admin_pop_table)%in%"adminlevel"]<-round(sum_pop,4) 
      rm(cropped, masked)
    } 

  ### Add a total row, change colnames, and display the table
  total_row <- c('Total', apply(data.frame(admin_pop_table[, -1]), 2, sum))
  admin_pop_table <- rbind(admin_pop_table, total_row)
  
  admin_pop_table %>%
    dplyr::mutate_if(is.numeric, function(x) {format(x , big.mark=",")}) %>%
    kableExtra::kable(col.names = c('Admin Level', year_list)) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F) %>%
    kableExtra::row_spec(nrow(admin_pop_table), bold = T)
  
} else{
  warning("sf_grid has a different number of cells or timepoints than covar_cube")
}
## ===============================================

```

### Other covariates
**Covariate rasters:**
```{r covars, fig.height=5, fig.width=8, fig.cap=capFig("Covariate rasters")}
taxdat::plot_raster_covariates(covar_data_filename = file_names["covar"], render = T)
```

## Output maps

```{r analysisyears}
analysis_years <- lubridate::year(config$start_time):lubridate::year(config$end_time)
obs_years <- min(lubridate::year(stan_input$sf_cases_resized$TL)):max(lubridate::year(stan_input$sf_cases_resized$TR))
# Runtimes by chain
rstan::get_elapsed_time(model.rand)
```


```{r importcase}
case_raster <- NULL
  case_raster <- taxdat::get_case_raster(preprocessed_data_filename = file_names["data"],
                                       covar_data_filename = file_names["covar"],
                                       model_output_filenames = file_names["stan_output"])

  #disaggregate incidence raster to 1*1KM 
  rate_raster <- case_raster %>%
    dplyr::select(dplyr::contains("modeled rates"),id,t,x,y,geom) %>%
    tidyr::gather(dplyr::contains("iterations: Chain"), key = "chain", value = "value") %>%
    dplyr::mutate(chain = stringr::str_replace(chain, "modeled rates", ""),value=value)
  
  empty_raster <- raster::raster(rate_raster, res = max(0.00833333, 0.00833333))
  disaggregated_rate_raster <- fasterize::fasterize(rate_raster, empty_raster, field = c("value"),by="t")
  
if(length(unique(pltdata$t))>1){
  disaggregated_rate_sf=disaggregated_rate_raster%>%as(.,'SpatialPolygonsDataFrame')%>% sf::st_as_sf(.)%>%dplyr::rename("1"=X1,"2"=X2,"3"=X3,"4"=X4,"5"=X5)%>%tidyr::pivot_longer(.,cols=c("1","2","3","4","5"),names_to="t")%>%as.data.frame(.)%>%sf::st_as_sf(.)
  colnames(disaggregated_rate_sf)[stringr::str_detect(colnames(disaggregated_rate_sf),"value")]=colnames(case_raster)[stringr::str_detect(colnames(case_raster),"modeled rate")]
  disaggregated_rate_sf$id<-rep(1:(nrow(disaggregated_rate_sf)/length(unique(disaggregated_rate_sf$t))),each=5)
}  else{
 #single year runs
  disaggregated_rate_sf=disaggregated_rate_raster%>%as(.,'SpatialPolygonsDataFrame')%>% sf::st_as_sf(.)%>%dplyr::rename("1"=X1)%>%tidyr::pivot_longer(.,cols=c("1"),names_to="t")%>%as.data.frame(.)%>%sf::st_as_sf(.)
  colnames(disaggregated_rate_sf)[stringr::str_detect( colnames(disaggregated_rate_sf),"value")]=colnames(case_raster)[stringr::str_detect(colnames(case_raster),"modeled rate")]
  disaggregated_rate_sf$id<-rep(1:(nrow(disaggregated_rate_sf)/length(unique(disaggregated_rate_sf$t))),each=1)
}

#disaggregate population raster to 1*1 KM
#newplydata is the 1*1 KM raster #crop the country boundary
#Crop the raster
  pop_cropped <- raster::crop(pop_raster_data,disaggregated_rate_raster)
  origin(pop_cropped)<-origin(disaggregated_rate_raster)
  disaggregated_case_raster<-pop_cropped*disaggregated_rate_raster

##aggregate 1*1 case raster to 20*20 raster
 if(length(unique(pltdata$t))>1){
  disaggregated_case_sf=disaggregated_case_raster%>%as(.,'SpatialPolygonsDataFrame')%>% sf::st_as_sf(.)%>%dplyr::rename("1"=layer.1,"2"=layer.2,"3"=layer.3,"4"=layer.4,"5"=layer.5)%>%tidyr::pivot_longer(.,cols=c("1","2","3","4","5"),names_to="t")%>%as.data.frame(.)%>%sf::st_as_sf(.)
  colnames(disaggregated_case_sf)[stringr::str_detect( colnames(disaggregated_case_sf),"value")]=colnames(case_raster)[stringr::str_detect(colnames(case_raster),"modeled case")]
  disaggregated_case_sf$id<-rep(1:(nrow(disaggregated_case_sf)/length(unique(disaggregated_case_sf$t))),each=5)
 
  }else{
    disaggregated_case_sf=disaggregated_case_raster%>%as(.,'SpatialPolygonsDataFrame')%>% sf::st_as_sf(.)
  colnames(disaggregated_case_sf)[stringr::str_detect( colnames(disaggregated_case_sf),"layer")]=colnames(case_raster)[stringr::str_detect(colnames(case_raster),"modeled case")]
  disaggregated_case_sf$t=1
  disaggregated_case_sf$id<-rep(1:(nrow(disaggregated_case_sf)/length(unique(disaggregated_case_sf$t))),each=1)
}

  if(all(analysis_years %in% obs_years)){
    message("All analysis years are represented by OCs.")
  } else{
    drop_year_ix <- which(!analysis_years %in% obs_years)
    message(paste(paste(analysis_years[drop_year_ix], collapse = ", "), "are not represented in OCs"))
    if(params$drop_nodata_years){
      message(paste("Dropping", paste(analysis_years[drop_year_ix], collapse = ", "), "from case_raster"))
      case_raster <- dplyr::filter(case_raster, !(t %in% drop_year_ix))
    }
  }

```

### Modeled cases
**Modeled cases raster by time slices:**
```{r caserast, fig.cap=capFig("Modeled cases"), fig.height=5, fig.width=10}
if(!is.null(case_raster)){
  plt_case_raster <- disaggregated_case_sf %>%
    dplyr::select(dplyr::contains("modeled cases"),id,t) %>%
    tidyr::gather(dplyr::contains("iterations: Chain"), key = "chain", value = "value") %>%
    # tidyr::pivot_longer(contains("iterations: Chain"), names_to = "chain", values_to = "value") %>%
    dplyr::mutate(chain = stringr::str_replace(chain, "modeled cases", ""))
  
 plt_2020_case_raster <- case_raster %>%
    dplyr::select(dplyr::contains("modeled cases"),id,t) %>%
    tidyr::gather(dplyr::contains("iterations: Chain"), key = "chain", value = "value") %>%
    dplyr::mutate(chain = stringr::str_replace(chain, "modeled cases", ""))

 plt_case_raster <- plt_case_raster %>%subset(plt_case_raster$t%in%unique(plt_2020_case_raster$t))%>%mutate(value=ifelse(value<exp(-5),exp(-5),value))

    ggplot2::ggplot() +
    ggplot2::geom_sf(
      data = plt_case_raster,
      ggplot2::aes(fill = value),color=NA,size=0.00001)+
      taxdat::color_scale(type = "cases", use_case = "ggplot map", use_log = TRUE)+
    ggplot2::geom_sf(data=plt_2020_case_raster%>%mutate(value=NA),fill=NA,color="black",size=0.05)+
    ggplot2::labs(fill="Incidence\n [cases/year]")+
    ggplot2::theme_bw() +
    ggplot2::theme(legend.position = "bottom") +
    ggplot2::theme(legend.text =  ggplot2::element_text(angle = 45, vjust = 1, hjust = 1))+
    ggplot2::facet_wrap(~t,ncol = length(unique(plt_case_raster$t))) 
    
} else{
  warning("case_raster is NULL")
}

```



**Table 4. Modeled cases by admin level and time:**
```{r echo = FALSE}
### Clean up the sf dataset
case_raster_admin<-disaggregated_case_sf
colnames(case_raster_admin)[stringr::str_detect(colnames(case_raster_admin),"modeled case")] <- "value"

### For loops and make the table
admin_case_table <- data.frame(matrix(NA, length(boundary_sf$shapeName), length(unique(case_raster_admin$t)) + 1))
year_list <- unique(as.numeric(case_raster_admin$t)) + (start_year-1)
colnames(admin_case_table) <- c('adminlevel', year_list)
admin_case_table$adminlevel <- boundary_sf$shapeName

for (ts in unique(case_raster_admin$t)){
  ## filter and rasterize
  case_raster_admin_ts <- case_raster_admin %>% filter(t == ts)
    empty_raster <- raster::raster(case_raster_admin_ts, res = res(disaggregated_case_raster))
  raster_data <- fasterize::fasterize(case_raster_admin_ts, empty_raster, field = "value")

  ## across different locations
  for (locs in admin_case_table$adminlevel){
    cropped <- raster::crop(raster_data, boundary_sf[boundary_sf$shapeName == locs, ], snap = "near")
    masked <- raster::mask(cropped, boundary_sf[boundary_sf$shapeName == locs, ], updatevalue = NA)
    sum_case <- sum(raster::getValues(masked), na.rm = TRUE)
    admin_case_table[match(locs, admin_case_table$adminlevel), (match(ts, unique(case_raster_admin$t)) + 1)] <- sum_case
    rm(cropped, masked)
  } 

  ## optimize memory
  rm(case_raster_admin_ts, empty_raster, raster_data)
}

### Add a total row, change colnames, and display the table
total_row <- c('Total', apply(data.frame(admin_case_table[, -1]), 2, sum))
admin_case_table <- rbind(admin_case_table, total_row)
admin_case_table[, -1] <- apply(as.matrix(noquote(admin_case_table[, -1])),  # Using apply function
                                  2,
                                  as.numeric)
admin_case_table$mean_across_years <- apply(admin_case_table[, -1], 1, mean)
admin_case_table <- admin_case_table %>% 
 mutate_if(is.numeric, round, digits=4)

admin_case_table %>%
  dplyr::mutate_if(is.numeric, function(x) {format(x , big.mark=",")}) %>%
  kableExtra::kable(col.names = c('Admin Level', year_list, 'Mean across Years')) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(nrow(admin_case_table), bold = T)

```



### Modeled incidence rates
**Modeled incidence rates raster by time slices:**
```{r raterast, fig.cap=capFig("Modeled rates by time"), fig.height=5, fig.width=10}
if(!is.null(case_raster)){
  taxdat::plot_modeled_rates(case_raster, render = T)
} else{
  warning("case_raster is NULL")
}
```

**Table 5. Modeled population-weighted incidence rates by admin level and time:**
```{r echo = FALSE}
### Clean up the sf dataset
rate_raster_admin<-disaggregated_rate_sf
colnames(rate_raster_admin)[stringr::str_detect(colnames(rate_raster_admin),"modeled rate")] <- "value"

##### Multiply two rasters together
### For loops and make the table
admin_rate_table <- data.frame(matrix(NA, length(boundary_sf$shapeName), length(unique(rate_raster_admin$t)) + 1))
year_list <- as.numeric(unique(rate_raster_admin$t)) + (start_year-1)
colnames(admin_rate_table) <- c('adminlevel', year_list)
admin_rate_table$adminlevel <- boundary_sf$shapeName

total_w_rate<-c()

for (ts in unique(rate_raster_admin$t)){
  ## the rates raster
  rate_raster_admin_ts <- rate_raster_admin %>% filter(t == ts)
  raster_data_cal_case <- disaggregated_case_raster[[as.numeric(ts)]]
  raster_data_pop <- pop_cropped

  ## across different locations
  for (locs in admin_rate_table$adminlevel){
    ## the calculated case raster
    cropped <- raster::crop(raster_data_cal_case, boundary_sf[boundary_sf$shapeName == locs, ], snap = "near")
    masked <- raster::mask(cropped, boundary_sf[boundary_sf$shapeName == locs, ], updatevalue = NA)
    sum_cal_case <- sum(raster::getValues(masked), na.rm = TRUE)
    ## the pop raster
    cropped <- raster::crop(raster_data_pop, boundary_sf[boundary_sf$shapeName == locs, ], snap = "near")
    masked <- raster::mask(cropped, boundary_sf[boundary_sf$shapeName == locs, ], updatevalue = NA)
    sum_pop <- sum(raster::getValues(masked), na.rm = TRUE)
    ## the table
    w_rate <- (sum_cal_case / sum_pop) * 1e4
    admin_rate_table[match(locs, admin_rate_table$adminlevel), (match(ts, unique(rate_raster_admin$t)) + 1)] <- w_rate
    rm(cropped, masked)
  } 

  ## the total weighted rate
  if(exists('total_w_rate')){
    total_w_rate <- c(total_w_rate,
                      sum(raster::getValues(raster_data_cal_case), na.rm = TRUE) / sum(raster::getValues(raster_data_pop), na.rm = TRUE))
  }else{
    total_w_rate <- sum(raster::getValues(raster_data_cal_case), na.rm = TRUE) / sum(raster::getValues(raster_data_pop), na.rm = TRUE)
  }
  
  ## optimize memory
  #rm(rate_raster_admin_ts, empty_raster, raster_data_pop, raster_data_rate, raster_data_cal_case)
  rm(rate_raster_admin_ts, raster_data_cal_case,raster_data_pop)
  
}

### Add a total row, change colnames, and display the table
total_row <- c('Weighted Total', total_w_rate * 1e4)
admin_rate_table <- rbind(admin_rate_table, total_row)
admin_rate_table[, -1] <- apply(as.matrix(noquote(admin_rate_table[, -1])),  # Using apply function
                                  2,
                                  as.numeric)
admin_rate_table$mean_across_years <- apply(admin_rate_table[, -1], 1, mean)
admin_rate_table <- admin_rate_table %>% 
 mutate_if(is.numeric, round, digits=4)

admin_rate_table %>%
  dplyr::mutate_if(is.numeric, function(x) {format(x , big.mark=",")}) %>%
  kableExtra::kable(col.names = c('Admin Level', year_list, 'Mean across Years')) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = F) %>%
  kableExtra::row_spec(nrow(admin_rate_table), bold = T)

```


## Validation

```{r import_modelfidel}
data_fidelity <- NULL
try({
  if(file.exists(file_names["initial_values"])){
  data_fidelity <- taxdat::get_data_fidelity(stan_input_filenames = file_names["stan_input"],
                                          model_output_filenames = file_names["stan_output"])
  
  }else{
    stan_input_filenames = file_names["stan_input"]
    model_output_filenames = file_names["stan_output"]
    if (length(stan_input_filenames) != length(model_output_filenames))
    stop("Need to provide same number of stan_input and stan_output files")
  
  rc <- list()
  layer_index <- 1
  for (i in 1:length(model_output_filenames)) {
    filename <- model_output_filenames[i]
    model.rand <- read_file_of_type(filename, "model.rand")
    nchain <- dim(MCMCvis::MCMCchains(model.rand, params='lp__'))[1] / niter_per_chain
    
    stan_data <- read_file_of_type(stan_input_filenames[i], "stan_input")$stan_data
    modeled_cases <- as.array(model.rand)[, , grepl("modeled_cases", names(model.rand)), drop = FALSE]
    modeled_cases_chain_mean <- apply(modeled_cases, c(2, 3), mean)
    actual_cases <- matrix(stan_data$y, nrow(modeled_cases_chain_mean), ncol(modeled_cases_chain_mean), byrow=TRUE)
    dimnames(actual_cases) <- dimnames(modeled_cases_chain_mean)
    modeled_cases_chain_mean <- reshape2::melt(modeled_cases_chain_mean)
    actual_cases <- reshape2::melt(actual_cases)
    actual_cases$censoring <- rep(stan_data$censoring_inds, each = nchain)
    actual_cases$oc_uid <- rep(taxdat::read_file_of_type(stan_input_filenames[i], "stan_input")$sf_cases_resized$OC_UID, 
                               each = nchain) #newly added
    actual_cases$oc_year <- rep(paste0(format(taxdat::read_file_of_type(stan_input_filenames[i], "stan_input")$sf_cases_resized$TL, '%Y'),
                                       "_",
                                       format(taxdat::read_file_of_type(stan_input_filenames[i], "stan_input")$sf_cases_resized$TR, '%Y')),
                               each = nchain) #newly added and updated on 21-12-14
    
    stan_data<-read_file_of_type(file_names["data"],"stan_data")
    obs_tfrac=data.frame(
      obs = stan_data$map_obs_loctime_obs,
      tfrac = stan_data$tfrac
    ) %>%
      dplyr::group_by(obs) %>%
      dplyr::summarize(tfrac = sum(tfrac))
    actual_cases$tfrac<-1
    actual_cases[stringr::str_detect(actual_cases$parameters,"tfrac"),]$tfrac<-rep(obs_tfrac$tfrac,each=nchain)
    
    comparison <- dplyr::left_join(modeled_cases_chain_mean, actual_cases, by = c(chains = "chains", parameters = "parameters"))
    names(comparison)[3:4] <- c("modeled cases", "actual cases")
    rc[[filename]] <- comparison
    names(rc)[[layer_index]] <- paste(
      paste(filename_to_stubs(filename)[2:3], collapse = " "),
      "\niterations: Chain", filename_to_stubs(filename)[5])
    layer_index <- layer_index + 1
  }
  
  data_fidelity<-rc
}
  
})

```


**Actual observations versus modeled cases scatter plot:**
```{r datafidelity1, fig.cap=capFig("Observations vs. modeled cases"), fig.height=10, fig.width=10}

if(!is.null(data_fidelity)){
  
  taxdat::plot_model_fidelity_tfrac_adjusted(data_fidelity = data_fidelity,
                                              case_raster = case_raster,
                                              render = T)
  
} else{
  warning("data_fidelity is NULL")
}

```

```{r datafidelity2, fig.cap=capFig("Observations/tfrac vs. modeled cases/tfrac"), fig.height=10, fig.width=10}

if(!is.null(data_fidelity)){
  
  taxdat::plot_model_fidelity_tfrac_converted(data_fidelity = data_fidelity,
                                              case_raster = case_raster,
                                              render = T)
  
} else{
  warning("data_fidelity is NULL")
}

```


```{r datafidelity3, fig.cap=capFig("Observations vs. modeled cases (tfrac adjusted)"), fig.height=15, fig.width=10}

if(!is.null(data_fidelity)){
  
  taxdat::plot_model_fidelity_tfrac_adjusted_by_year(data_fidelity = data_fidelity,
                                                      case_raster = case_raster,
                                                      render = T)
  
} else{
  warning("data_fidelity is NULL")
}

```

```{r datafidelity4, fig.cap=capFig("Observations vs. modeled cases"), fig.height=8, fig.width=10}

if(!is.null(data_fidelity)){
  
  taxdat::plot_model_fidelity_tfrac_unadjusted(data_fidelity = data_fidelity,
                                                case_raster = case_raster,
                                                render = T)

} else{
  warning("data_fidelity is NULL")
}

```


**Stan trace plots:**
```{r traceplots, fig.height=8, fig.width=10, fig.cap=capFig("Stan trace plots")}

if(!is.null(model.rand)){
taxdat::plot_chain_convergence(file_names[["stan_output"]],
                               pars =  c("rho", "betas", "log_std_dev_w", "eta"),
                               render = T)
}

```


**Parameter posteriors:**
```{r params, fig.height=6, fig.width=6, fig.cap=capFig("Parameter posteriors")}
if(!is.null(model.rand)){
  rstan::plot(model.rand, pars =  c("rho", "betas", "log_std_dev_w", "eta"))

} else{
  warning("model.rand is NULL")
}
```


**Gelman-Rubin Rhat:**
```{r rhat, fig.height=5, fig.width=10, fig.cap=capFig("Gelman-Rubin Rhat")}
if(!is.null(model.rand)){
  taxdat::plot_rhat(model.rand, render = T)
} else{
  warning("model.rand is NULL")
}
```


**Table 6. Observed and estimates of WHO annual cholera reports:**
```{r WHO output, fig.height=5, fig.width=10, fig.cap = "comparison with WHO Output"}

if(!is.null(sf_cases_resized) & !is.null(model.rand)){

  who_annual_cases <- sf_cases_resized
  chains <- rstan::extract(model.rand)
  who_annual_cases$modeled <- apply(chains$modeled_cases,2,mean)
  who_annual_cases$observed <- who_annual_cases$attributes.fields.suspected_cases # fix me
  who_annual_cases_from_db <- NULL
  try({
    who_annual_cases_from_db <- taxdat::pull_output_by_source(who_annual_cases, "%WHO Annual Cholera Reports%",
                                                              database_api_key_rfile = stringr::str_c(params$cholera_directory, "Analysis/R/database_api_key.R"))
  })
  if(!is.null(who_annual_cases_from_db)) {
    who_annual_cases_from_db %>%
      as.data.frame() %>%
      dplyr::select(OC_UID, TL, TR, observed, modeled) %>%
      dplyr::mutate_if(is.numeric, function(x) {format(round(x) , big.mark=",")}) %>%
      kableExtra::kable(col.names = c("OC id", "start time", "end time", "# Observed cases", "# Modeled Cases")) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped"))
  }

} else{
  warning("sf_cases_resized or model.rand is NULL")
}
```


**Table 7. Estimated cases by chain and time slice:**
```{r cases_chain_table, fig.width=10, fig.cap = "Sum of grid cases by chain and year"}

if(!is.null(model.rand) && !is.null(stan_input)){
  stan_input$sf_grid <- stan_input$sf_grid %>%
    dplyr::ungroup() %>%
    dplyr::select(t,id)
  stan_input$sf_grid[paste('cases','chain',seq_len(nchain),sep='_')] <- cases_chains

  if(params$drop_nodata_years & !all(analysis_years %in% obs_years)){
      drop_year_ix <- which(!analysis_years %in% obs_years)
      message(paste("Dropping", paste(analysis_years[drop_year_ix], collapse = ", "), "from cases_chains"))
      stan_input$sf_grid <- dplyr::filter(stan_input$sf_grid, !(t %in% drop_year_ix))
    }

  sf_grid_wider <- sf::st_drop_geometry(stan_input$sf_grid)

  by_years <- sf_grid_wider %>%
    dplyr::group_by(t) %>%
    dplyr::summarise(dplyr::across(dplyr::contains("cases_chain"), sum)) %>%
    dplyr::mutate(t = as.character(t))
  mai <- by_years %>%
    dplyr::summarise(dplyr::across(dplyr::contains("cases_chain"), mean)) %>%
    dplyr::mutate(t = "mean annual cases")

  dplyr::bind_rows(by_years, mai) %>%
    kableExtra::kable(col.names = c("time slice", paste("chain", 1:nchain))) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped"))

} else{
  warning("stan_input is NULL")
}
```

```{r full country modeled cases, fig.cap = "comparison with WHO Output"}

if(!is.null(sf_cases_resized) & !is.null(model.rand)){
  grid_cases_mean <- apply(chains$grid_cases,2,mean)
  total_cases <- sum(grid_cases_mean)
  print(paste("There are",format(round(total_cases), big.mark=","),"total cases"))

} else{
  warning("chains was not extracted from model.rand")
}
```
