---
title: "Country Data Report"
output: html_document
params:
  cholera_directory: "../../"
  config: "Analysis/configs/config.yml"
  drop_nodata_years: TRUE
---
```{r setup, include=FALSE, dev="CairoPNG",message=FALSE}
library(knitr)
knitr::opts_chunk$set(
  cache=FALSE,
  cache.lazy = FALSE,
  echo = FALSE,
  dev="CairoPNG",
  error = FALSE,
  fig.align = "center",
  message = TRUE,
  warning = TRUE
  )
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(taxdat)
library(sf)
library(raster)
library(stars)
library(taxdat)
sf::sf_use_s2(FALSE)

### other new packages (mainly for "rgeoboundaries")
chooseCRANmirror(ind = 77)

package_list <- c(
  "fasterize",
  "remotes",
  "rgeoboundaries"
)

for (package in package_list) {
  if (!require(package = package, character.only = T)) {
    if (package == "rgeoboundaries"){
      try({
        remotes::install_gitlab("dickoa/rgeoboundaries")
        remotes::install_github("wmgeolab/rgeoboundaries")
      })
    }else{
      install.packages(pkgs = package)
      library(package = package, character.only = T)
    }
  }
}

#Figure Caption Numbering,
capFigNo = 1
#Function to add the Figure Number
capFig = function(x){
    x = paste0("Figure ",capFigNo,". ",x)
    capFigNo <<- capFigNo + 1
    x
}
cache<-new.env()

```

# Mapping results summary for `r stringr::str_extract(params$config, "[A-Z]{3}")` and period `r stringr::str_extract(params$config, "[0-9]{4}_[0-9]{4}")`

## Cholera input data

### GAM Input
**Observations input for the GAM model:**
```{r gam input of cases,fig.height=5, fig.width=10, fig.cap=capFig("Observations input for the GAM model (cases)")}
taxdat::plot_gam_fit_input_cases(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
```

```{r gam input of rates,fig.height=5, fig.width=10, fig.cap=capFig("Observations input of the GAM model (rates)")}
taxdat::plot_gam_fit_input_rates(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
```

### GAM Output
**Observations output of the GAM model:**
```{r gam output of cases,fig.height=5, fig.width=10, fig.cap=capFig("Observations output for the GAM model (cases)")}
taxdat::plot_gam_fit_output_cases(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
```

```{r gam output of rates,fig.height=5, fig.width=10, fig.cap=capFig("Observations output for the GAM model (rates)")}
taxdat::plot_gam_fit_output_rates(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
```

**Table 1. Data used within the model:**
```{r echo = FALSE}
taxdat::table_observation_summary(config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

**Table 2. Data dropped from the model:**
```{r echo=FALSE}
taxdat::table_observation_summary(config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

```{r disjoint set sf cases, message=FALSE}
# aggregate_observed_polygon_cases_disjoint_aggregated(name="observed_polygon_cases_disjoint_aggregated",config=params$config,cholera_directory=params$cholera_directory,cache=cache)
# disjoint_set_sf_cases <- cache[["observed_polygon_cases_disjoint_aggregated"]]
```

**Cases by time:**
```{r rawobsmap, fig.height=5, fig.width=10, fig.cap=capFig("Observed case counts by time adjusted for time fraction cases/year")}
taxdat::plot_observed_cases_polygon_raw(config=params$config,cache=cache,cholera_directory=params$cholera_directory)
```

**Area adjusted cases by time:**
```{r areadjustedmap, fig.height=5, fig.width=10, fig.cap=capFig("Area adjusted average observed case counts by time adjusted for time fraction cases/(year * kilometer)")}
taxdat::plot_area_adjusted_observed_cases(config=params$config,cache=cache,cholera_directory=params$cholera_directory)
```

**Cases unique location periods:**
```{r obsmap, fig.height=5, fig.width=10, fig.cap=capFig("Number of observations by unique observed location periods.")}
taxdat::plot_raw_observations(config=params$config,cache=cache,cholera_directory=params$cholera_directory)
```
### Covariates

#### Population
**Population raster by time slices:**
```{r pop, fig.height=5, fig.width=10, fig.cap=capFig("Population density")}
taxdat::plot_time_varying_pop_raster(cache=cache,config=params$config,cholera_directory=params$cholera_directory)
```

**Table 3. Population by admin level:**
```{r echo = FALSE}
warning("Removed this plot for now")
# taxdat::plot_pop_by_admin(cache=cache,cholera_directory=params$cholera_directory,config=params$config)
```

#### Other covariates
**Covariate rasters:**
```{r covars, fig.height=5, fig.width=10, fig.cap=capFig("Covariate rasters")}
taxdat::plot_raster_covariates(cache=cache,cholera_directory=params$cholera_directory,config=params$config)
```

### Output maps
```{r analysisyears}
# taxdat::get_obs_year(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
# taxdat::get_elapsed_time(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
```


```{r importcase}
# cache[["case_raster"]] <-get_case_raster(cache=cache,config=config,cholera_directory=cholera_directory)
# cache[["disaggregated_rate_sf"]]<-get_disaggregated_rates_sf(
#                                                 cache=cache,config=params$config,
#                                                 cholera_directory=params$cholera_directory)
#
# cache[["disaggregated_case_sf"]]<-get_disaggregated_cases_sf (
#                                                 cache=cache,config=params$config,
#                                                 cholera_directory=params$cholera_directory)
#
# config_file<-yaml::read_yaml(paste0(params$cholera_directory,params$config))
# analysis_years <- lubridate::year(config_file$start_time):lubridate::year(config_file$end_time)
# obs_years <- min(lubridate::year(cache[["sf_cases_resized"]]$TL)):max(lubridate::year(cache[["sf_cases_resized"]]$TR))


get_dropped_years(config = params$config, cache = cache, cholera_directory = params$cholera_directory)
if(length(cache[["dropped_years"]]) == 0){
  message("All modeled years are represented by OCs.")
} else {
  message(paste(paste(cache[["dropped_years"]], collapse = ", "), "are not represented in OCs"))
  if(params$drop_nodata_years){
    message(paste("Dropping", paste(cache[["dropped_years"]], collapse = ", "), "from case_raster"))
    ## case_raster <- dplyr::filter(case_raster, !(t %in% drop_year_ix))
  }
}
```

#### Modeled cases
**Modeled cases raster by time slices:**
```{r caserast, fig.cap=capFig("Modeled cases"), fig.height=5, fig.width=10}
plot_disaggregated_modeled_cases_time_varying(disaggregated_case_sf=cache[["disaggregated_case_sf"]])
```

**Table 4. Modeled cases by admin level and time:**
```{r echo = FALSE}
plot_cases_by_admin(cache=cache,config=params$config,cholera_directory=params$cholera_directory)
```

#### Modeled incidence rates
**Modeled incidence rates raster by time slices:**
```{r raterast, fig.cap=capFig("Modeled rates by time"), fig.height=5, fig.width=10}
plot_modeled_rates_time_varying(disaggregated_rate_sf=cache[["disaggregated_rate_sf"]], render = T)
```

**Table 5. Modeled population-weighted incidence rates by admin level and time:**
```{r echo = FALSE}
plot_incidence_by_admin(cache=cache,config=params$config,cholera_directory=params$cholera_directory)
```

### Validation
```{r import_modelfidel}
cache[["data_fidelity"]]<-get_data_fidelity(cache=cache,cholera_directory=params$cholera_directory,config=params$config)
```

**Actual observations versus modeled cases scatter plot:**
```{r datafidelity1, fig.cap=capFig("Observations vs. modeled cases"), fig.height=10, fig.width=10}
plot_model_fidelity_tfrac_adjusted(data_fidelity = cache[["data_fidelity"]],case_raster = cache[["case_raster"]],render = T)
```

```{r datafidelity3, fig.cap=capFig("Observations vs. modeled cases (tfrac adjusted)"), fig.height=15, fig.width=10}
plot_model_fidelity_tfrac_adjusted_by_year(data_fidelity = cache[["data_fidelity"]],case_raster = cache[["case_raster"]],render = T)
```

```{r datafidelity4, fig.cap=capFig("Observations vs. modeled cases"), fig.height=8, fig.width=10}
plot_model_fidelity_tfrac_unadjusted(data_fidelity = cache[["data_fidelity"]],case_raster = cache[["case_raster"]],render = T)
```

**Stan trace plots:**
```{r traceplots, fig.height=8, fig.width=10, fig.cap=capFig("Stan trace plots")}
plot_chain_convergence(cache=cache,name="model.rand")
```

**Parameter posteriors:**
```{r params, fig.height=6, fig.width=6, fig.cap=capFig("Parameter posteriors")}
plot_MCMCpars(name="model.rand",cache=cache)
```

**Gelman-Rubin Rhat:**
```{r rhat, fig.height=5, fig.width=10, fig.cap=capFig("Gelman-Rubin Rhat")}
plot_Rhat(name="model.rand",cache)
```

**Table 6. Observed and estimates of WHO annual cholera reports:**
```{r WHO output, fig.height=510, fig.width=10, fig.cap = "comparison with WHO Output"}
plot_WHOcomparison_table(config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

**Table 7. Estimated cases by chain and time slice:**
```{r cases_chain_table, fig.width=10, fig.cap = "Sum of grid cases by chain and year"}
plot_modeled_cases_by_chain_time (config=params$config, cache=cache, cholera_directory=params$cholera_directory)
```

```{r full country modeled cases, fig.cap = "comparison with WHO Output"}
  total_cases <- cache[["modeled_cases"]] %>% apply(3, mean) %>% sum()
  print(paste("There are",format(round(total_cases), big.mark=","),"total cases"))
```
