---
title: "dropped_data_diagnostics"
output: 
  html_document:
    toc: true
    toc_float: true
params: 
  cholera_directory: "cholera-mapping-pipeline"
  config: "Analysis/configs/.../*.yml"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(dplyr)
library(gt)
library(DT)
library(taxdat)
library(purrr)
sf::sf_use_s2(FALSE)

option_list <- list(
  optparse::make_option(
    c("-c", "--config"),
    action = "store",
    default = Sys.getenv("CHOLERA_CONFIG", "config.yml"),
    type = "character",
    help = "Model run configuration file"
  ),
  optparse::make_option(c("-d", "--cholera_directory"), action = "store", default = NULL, type="character", help = "Cholera directory"),
  optparse::make_option(c("-l", "--layers_directory"), action = "store", default = NULL, type="character", help = "Layers directory"),
  optparse::make_option(c("-v", "--verbose"), action = "store", default = FALSE, type="logical", help = "Print extra messages")
)

opt <- optparse::OptionParser(option_list = option_list) %>% optparse::parse_args()

source(paste0(params$cholera_directory,"/Analysis/R/database_api_key.R"))
try(
  {
    username <- taxonomy_username
    password <- taxonomy_password
  },
  silent = TRUE
)

cases_column <-'suspected_cases'

config<-yaml::read_yaml(paste0(params$cholera_directory,"/",params$config))

# summary functions ----
summarize_dropped_rows_df <- function(df_before, df_after) {
  library(dplyr)
  
  dropped_df <- anti_join(df_before, df_after, by = c("location_name", "OC_UID", "TL", "TR"))
  
  if (nrow(dropped_df) == 0) {
    message("No rows were dropped.")
    return(tibble(
      location_name = character(),
      OC_UID = character(),
      total_cases = numeric(),
      minTL = as.Date(character()),
      maxTR = as.Date(character()),
      n_obs = integer(),
      location_ids = character(),
      location_period_ids = character(),
      UID = integer()
    ))
  }
  
  dropped_summary <- dropped_df %>%
    group_by(location_name, OC_UID) %>%
    summarise(
      total_cases = sum(suspected_cases, na.rm = TRUE),
      minTL = min(TL, na.rm = TRUE),
      maxTR = max(TR, na.rm = TRUE),
      n_obs = n(),
      location_ids = paste(unique(location_id), collapse = ", "),
      location_period_ids = paste(unique(attributes.location_period_id), collapse = ", "),
      .groups = "drop"
    ) %>% 
    mutate(UID = 1:n())
  
  return(dropped_summary)
}

summarize_dropped_rows_df_short <- function(df_before, df_after) {
  library(dplyr)
  
  dropped_df <- anti_join(df_before, df_after, by = c("location_name", "OC_UID", "TL", "TR"))
  
  if (nrow(dropped_df) == 0) {
    message("No rows were dropped.")
    return(tibble(
      location_name = character(),
      OC_UID = character(),
      total_cases = numeric(),
      minTL = as.Date(character()),
      maxTR = as.Date(character()),
      n_obs = integer(),
      location_period_ids = character(),
      UID = integer()
    ))
  }
  
  dropped_summary <- dropped_df %>%
    group_by(location_name, OC_UID) %>%
    summarise(
      total_cases = sum(suspected_cases, na.rm = TRUE),
      minTL = min(TL, na.rm = TRUE),
      maxTR = max(TR, na.rm = TRUE),
      n_obs = n(),
      location_period_ids = paste(unique(attributes.location_period_id), collapse = ", "),
      .groups = "drop"
    ) %>% 
    mutate(UID = 1:n())
  
  return(dropped_summary)
}

identify_input_coverage <- function(sf_cases_resized, dropped_summary_df) {
  library(dplyr)
  library(purrr)
  library(sf)

  purrr::pmap_dfr(
    dropped_summary_df,
    function(UID, minTL, maxTR, ...) {
      sf_cases_resized %>% 
        st_drop_geometry() %>% 
        select(OC_UID,locationPeriod_id,location_name,TL,TR,attributes.fields.suspected_cases) %>% 
        filter(TL <= minTL, TR >= maxTR) %>%
        mutate(UID = UID)
    }
  )
}
```

```{r Input data, echo=F}
# Raw data
cases <- taxdat::pull_taxonomy_data(
  username = username,
  password = password,
  locations = as.numeric(config$countries),
  time_left = as.Date(config$start_time),
  time_right = as.Date(config$end_time),
  source = 'sql',
  uids = NULL,
  website = ""
) %>%
  taxdat::rename_database_fields(source = 'sql') %>% 
  filter(is_primary, !is.na(suspected_cases)) %>% 
  dplyr::select(OC_UID,TL,TR,suspected_cases,deaths,location_name,location_id,attributes.location_period_id)

# sf_cases_resized
load(paste0(params$cholera_directory,'/Analysis/data/',config$file_names$stan_input_filename))
sf_cases_resized_orig <- stan_input$sf_cases_resized
```

# Processing step 1: Dropping observations with missing shapefiles
```{r Step 1 dropping missing obs, echo = F, message=F}
## Composite locations are dropped here
cases_dropping_missing_shps <- taxdat::drop_missing_shapefiles(cases = cases,
                                         cases_column = cases_column)

dropped_summary_df <- summarize_dropped_rows_df(cases %>% st_drop_geometry(),
                          cases_dropping_missing_shps %>% st_drop_geometry())

dropped_summary_df %>% 
  select(!location_period_ids) %>% 
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (missing shapefiles)",
    subtitle = "Grouped by Location and OC_UID"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    OC_UID = "OC UID",
    location_name = "Location",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    total_cases = "sCh",
    n_obs = "N Obs",
    location_ids = "Location ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 1 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 2: Dropping observations with invalid shapefiles
```{r Shapefiles, echo =F, message=F}
cases <- cases_dropping_missing_shps

shapefiles <- taxdat::get_valid_shapefiles(cases)
iso_code <- taxdat::get_country_isocode(config)
shapefiles <- taxdat::clip_shapefiles_to_adm0(iso_code = iso_code,
                                              shapefiles = shapefiles)
sf::st_crs(cases) <- sf::st_crs(shapefiles)
sf::st_geometry(cases) <- NULL
sf_cases <- sf::st_as_sf(
  dplyr::inner_join(cases,
                    shapefiles,
                    by = c("attributes.location_period_id" = "location_period_id",
                           "location_name" = "location_name")
  )
)

if (any(sf::st_is_empty(sf_cases))) {
  warning(
    paste(
      "Missing shapefiles for ",
      sum(sf::st_is_empty(sf_cases)),
      "observations. They correspond to the following location period IDs:",
      paste(sf_cases[sf::st_is_empty(sf_cases), ]$locationPeriod_id, collapse = ", ")
    )
  )
  sf_cases <- sf_cases[!sf::st_is_empty(sf_cases), ]
}

dropped_summary_df<-summarize_dropped_rows_df(cases %>% st_drop_geometry(),
                          sf_cases %>% st_drop_geometry())
dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (invalid shapefiles)",
    subtitle = "Grouped by Location and OC_UID"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  )  %>%
  cols_label(
    OC_UID = "OC UID",
    location_name = "Location",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    total_cases = "sCh",
    n_obs = "N Obs",
    location_ids = "Location ID(s)",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 2 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 3: Dropping multi-year adm0 observations (pre-aggregation)
```{r Preaggregation multiyear adm0 obs, echo =F, message=F}
cases <- sf_cases

# snap to time period
sf_cases <- taxdat::snap_to_time_period_df(df = sf_cases,
                                           TL_col = "TL",
                                           TR_col = "TR",
                                           res_time = config$res_time,
                                           tol = config$snap_tol)
# drop multi-year adm0 obs
sf_cases <- sf_cases %>% 
  dplyr::mutate(admin_level = purrr::map_dbl(location_name, ~ taxdat::get_admin_level(.)))

# Drop multi-year observations if present
if (config$drop_multiyear_adm0) {
  sf_cases <- taxdat::drop_multiyear(df = sf_cases,
                                     admin_levels = 0)
}

dropped_summary_df<-summarize_dropped_rows_df(cases %>% st_drop_geometry() ,
                          sf_cases %>% st_drop_geometry())
dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (multiyear adm0 obs)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_ids = "Location ID(s)",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 3 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

```{r Prepare stan input, echo =F, message=F}
load(paste0(params$cholera_directory,'/Analysis/data/', config$file_names$covariate_filename))  

covar_cube <- covar_cube_output
non_na_gridcells <- covar_cube_output$non_na_gridcells
sf_grid <- covar_cube_output$sf_grid
location_periods_dict <- covar_cube_output$location_periods_dict

res_time = '1 years'
  left_bounds <- seq.Date(as.Date(config$start_time), as.Date(config$end_time), by = res_time)
  time_change_func <- taxdat::time_unit_to_aggregate_function(res_time)
  aggregate_to_start <- taxdat::time_unit_to_start_function(res_time)
  aggregate_to_end <- taxdat::time_unit_to_end_function(res_time)

 time_slices <- taxdat::modeling_time_slices(start_time = as.Date(config$start_time),
                                              end_time = as.Date(config$end_time),
                                              res_time = res_time,
                                              time_change_func = time_change_func,
                                              aggregate_to_start = aggregate_to_start,
                                              aggregate_to_end = aggregate_to_end)  
```

# Processing step 4: Dropping duplicated observations (pre-aggregation)
```{r Preaggregation duplicated obs, echo =F, message=F}
cases <- sf_cases

sf_cases_dup_obs <- sf_cases %>% 
    sf::st_drop_geometry() %>%
    dplyr::select(-dplyr::one_of("id", "deaths")) %>%
    duplicated()
  
sf_cases <- sf_cases[!sf_cases_dup_obs, ]

dropped_summary_df<-summarize_dropped_rows_df(cases %>% st_drop_geometry(),
                          sf_cases %>% st_drop_geometry())
dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (dups before aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_ids = "Location ID(s)",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 4 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 5: Dropping NA observations (pre-aggregation)
```{r Before aggregation NA obs, echo =F, message=F}
cases <- sf_cases

# aggregation
ind_mapping <- taxdat::get_space_time_ind_speedup(
    df = sf_cases %>% mutate(locationPeriod_id = attributes.location_period_id),
    lp_dict = location_periods_dict,
    model_time_slices = time_slices,
    res_time = res_time,
    n_cpus = config$ncpus_parallel_prep,
    do_parallel = config$do_parallel_prep)
  
non_na_obs <- sort(unique(ind_mapping$map_obs_loctime_obs))
sf_cases_resized <- sf_cases[non_na_obs, ]

dropped_summary_df<-summarize_dropped_rows_df(cases %>% st_drop_geometry(),
                          sf_cases_resized %>% st_drop_geometry())
dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (NA obs pre-aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_ids = "Location ID(s)",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 5 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

```{r Aggregation, echo =F, message=F}
sf_cases_resized <- taxdat::aggregate_observations(sf_cases_resized = sf_cases_resized %>% mutate(locationPeriod_id = attributes.location_period_id),
                                                       non_na_obs = non_na_obs,
                                                       ind_mapping = ind_mapping,
                                                       cases_column = cases_column,
                                                       verbose = opt$verbose,
                                                       n_cpus = config$ncpus_parallel_prep,
                                                       do_parallel = config$do_parallel_prep)
    
# Snap to time period after aggregation
sf_cases_resized <- taxdat::snap_to_time_period_df(df = sf_cases_resized,
                                                    TL_col = "TL",
                                                    TR_col = "TR",
                                                    res_time = res_time,
                                                    tol = config$snap_tol)
    
# Re-compute space-time indices based on aggretated data
ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
  df = sf_cases_resized,
  lp_dict = location_periods_dict,
  model_time_slices = time_slices,
  res_time = res_time,
  n_cpus = config$ncpus_parallel_prep,
  do_parallel = config$do_parallel_prep)
```

# Processing step 6: Dropping low tfrac observations (after-aggregation)
```{r After aggregation low tfrac obs, echo =F, message=F}
cases <- sf_cases_resized

if (config$tfrac_thresh > 0) {
    # Which observations to remove
    obs_remove_thresh <- unique(ind_mapping_resized$obs[ind_mapping_resized$tfrac < as.numeric(config$tfrac_thresh)])
    
    if (length(obs_remove_thresh) == 0){
      cat("---- FOUND none of", nrow(sf_cases_resized), "observations that are under the tfrac threshold of", config$tfrac_thresh, "\n")
    } else {
      
      cat("---- REMOVING", length(obs_remove_thresh), "of", nrow(sf_cases_resized), "observations that are under the tfrac threshold of", config$tfrac_thresh, "\n")
      # Remove observations
      sf_cases_resized <- sf_cases_resized[-c(obs_remove_thresh), ]
      
      # Re-compute space-time indices based on aggretated data
      ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
        df = sf_cases_resized,
        lp_dict = location_periods_dict,
        model_time_slices = time_slices,
        res_time = res_time,
        n_cpus = config$ncpus_parallel_prep,
        do_parallel = config$do_parallel_prep)
    }
  }

dropped_summary_df<-summarize_dropped_rows_df(cases %>% st_drop_geometry(),
                          sf_cases_resized %>% st_drop_geometry())

dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (below tfrac obs pre-aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_ids = "Location ID(s)",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 6 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 7: Dropping multi-year observations (after-aggregation)
```{r After aggregation multiyear obs, echo =F, message=F}
cases <- sf_cases_resized

sf_cases_resized <- sf_cases_resized %>% 
    dplyr::mutate(admin_level = purrr::map_dbl(location_name, ~ taxdat::get_admin_level(.)))
  
# Drop multi-year observations if present
if (config$drop_multiyear_adm0) {
    sf_cases_resized <- taxdat::drop_multiyear(df = sf_cases_resized,
                                               admin_levels = 0)
    
    # Re-compute space-time indices based on aggretated data
    ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
      df = sf_cases_resized, 
      lp_dict = location_periods_dict,
      model_time_slices = time_slices,
      res_time = res_time,
      n_cpus = config$ncpus_parallel_prep,
      do_parallel = config$do_parallel_prep)
  }

dropped_summary_df<-summarize_dropped_rows_df(cases %>% st_drop_geometry(),
                          sf_cases_resized %>% st_drop_geometry())

dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs, location_ids,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (multiyear obs after aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_ids = "Location ID(s)",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 7 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 8: Dropping censored 0 observations (after-aggregation)
```{r After aggregation censored 0 obs, echo =F, message=F}
cases <- sf_cases_resized
sf_cases_resized$censoring <- taxdat::get_censoring_inds(ind_mapping_resized = ind_mapping_resized,
                                                           censoring_thresh = config$censoring_thresh)
  
sf_cases_resized <- sf_cases_resized %>% 
    dplyr::mutate(ref_TL = taxdat::get_start_timeslice(TL, res_time),
                  ref_TR = taxdat::get_end_timeslice(TR, res_time),
                  obs_id = dplyr::row_number()) 

sf_cases_resized <- sf_cases_resized %>% 
    dplyr::mutate(admin_level = purrr::map_dbl(location_name, ~ taxdat::get_admin_level(.)))
if (config$censoring) {
    
    cat("-- Checking for 0 censored observations \n")
    
    y <- sf_cases_resized[[cases_column]]
    
    censored_zero_obs <- which(y == 0 & sf_cases_resized$censoring == "right-censored")
    
    if (length(censored_zero_obs) > 0) {
      
      cat("-- Dropping", length(censored_zero_obs), "observations that are 0 and censored.\n")
      
      sf_cases_resized <- sf_cases_resized[-c(censored_zero_obs), ]
      
      
      # Re-compute indices
      ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
        df = sf_cases_resized,
        lp_dict = location_periods_dict,
        model_time_slices = time_slices,
        res_time = res_time,
        n_cpus = config$ncpus_parallel_prep,
        do_parallel = config$do_parallel_prep)
      
    }
  }

dropped_summary_df<-summarize_dropped_rows_df_short(cases  %>% st_drop_geometry() %>% mutate(attributes.location_period_id = locationPeriod_id),sf_cases_resized %>% st_drop_geometry()%>% mutate(attributes.location_period_id = locationPeriod_id))

dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (censored 0 obs after aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 8 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 9: Dropping censored adm0 observations (after-aggregation)
```{r After aggregation censored adm0 obs, echo =F, message=F}
cases <- sf_cases_resized

if (config$drop_censored_adm0) {
    
    sf_cases_resized <- taxdat::drop_censored_adm0(sf_cases_resized = sf_cases_resized,
                                                   thresh = config$drop_censored_adm0_thresh,
                                                   res_time = res_time,
                                                   cases_column = cases_column)
    
    # Re-compute indices
    ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
      df = sf_cases_resized, 
      lp_dict = location_periods_dict,
      model_time_slices = time_slices,
      res_time = res_time,
      n_cpus = config$ncpus_parallel_prep,
      do_parallel = config$do_parallel_prep)
  }
  
dropped_summary_df<-summarize_dropped_rows_df_short(cases  %>% st_drop_geometry() %>% mutate(attributes.location_period_id = locationPeriod_id),
                          sf_cases_resized %>% st_drop_geometry()%>% mutate(attributes.location_period_id = locationPeriod_id))

dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (censored 0 obs after aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 9 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized_orig, dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 10: Dropping adm0 observations < max tfrac within an OC (after-aggregation)
```{r After aggregation adm0 obs below max tfrac in an OC, echo =F, message=F}
cases <- sf_cases_resized

if (config$drop_censored_adm0) {
    
    sf_cases_resized <- taxdat::drop_censored_adm0(sf_cases_resized = sf_cases_resized,
                                                   thresh = config$drop_censored_adm0_thresh,
                                                   res_time = res_time,
                                                   cases_column = cases_column)
    
    # Re-compute indices
    ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
      df = sf_cases_resized, 
      lp_dict = location_periods_dict,
      model_time_slices = time_slices,
      res_time = res_time,
      n_cpus = config$ncpus_parallel_prep,
      do_parallel = config$do_parallel_prep)
  }
  
dropped_summary_df<-summarize_dropped_rows_df_short(cases  %>% st_drop_geometry() %>% mutate(attributes.location_period_id = locationPeriod_id), sf_cases_resized %>% st_drop_geometry()%>% mutate(attributes.location_period_id = locationPeriod_id))

dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (adm0 obs below max tfrac after aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 10 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized %>% mutate(attributes.fields.suspected_cases=suspected_cases), dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Processing step 11: Dropping observations with low pop (after-aggregation)
```{r After aggregation obs with low pop, echo =F, message=F}
cases <- sf_cases_resized

if (config$drop_low_pop_lps) {
    
    # Compute lp populations
    lp_pops <- taxdat::compute_pop_loctimes(stan_data = stan_data)
    
    # Which loctimes to drop
    ind_drop_loctimes <- which(lp_pops < config$drop_low_pop_lps_thresh)
    
    # Which obs to drop
    ind_drop_obs <- stan_data$map_obs_loctime_obs[stan_data$map_obs_loctime_loc %in% ind_drop_loctimes]
    
    if (length(ind_drop_obs) > 0) {
      
      cat("-- Dropping", length(ind_drop_obs), 
          "observations due to low location period population.\n")
      
      # Drop the observations and reindex
      sf_cases_resized <- sf_cases_resized[-c(ind_drop_obs),]
      
      ind_mapping_resized <- taxdat::get_space_time_ind_speedup(
        df = sf_cases_resized,
        lp_dict = location_periods_dict,
        model_time_slices = time_slices,
        res_time = res_time,
        n_cpus = config$ncpus_parallel_prep,
        do_parallel = config$do_parallel_prep)
    }
  }
  
dropped_summary_df<-summarize_dropped_rows_df_short(cases  %>% st_drop_geometry() %>% mutate(attributes.location_period_id = locationPeriod_id),
                          sf_cases_resized %>% st_drop_geometry()%>% mutate(attributes.location_period_id = locationPeriod_id))

dropped_summary_df %>%
  select(UID, location_name, minTL, maxTR, total_cases, OC_UID, n_obs,location_period_ids) %>%
  gt() %>%
  tab_header(
    title = "Summary of Dropped Observations (low pop obs after aggregation)"
  ) %>%
  fmt_number(
    columns = c(total_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    OC_UID = "OC UID",
    total_cases = "sCh",
    minTL = "Earliest TL",
    maxTR = "Latest TR",
    n_obs = "N Obs",
    location_period_ids = "Period ID(s)"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```

## Summary of Dropped Data Coverage in Model Input
```{r Step 11 checking data coverage in sf_cases_resized, echo = F, message=F}
coverage_df <- identify_input_coverage(sf_cases_resized %>% mutate(attributes.fields.suspected_cases=suspected_cases), dropped_summary_df)

if (nrow(coverage_df) == 0) {
  htmltools::tags$h4("No dropped data coverage found.")
} else {
  coverage_df %>%
    select(
      location_name,
      OC_UID,
      attributes.fields.suspected_cases,
      TL,
      TR,
      locationPeriod_id,
      UID
    ) %>%
    datatable(
      filter = "top",
      rownames = FALSE,
      options = list(pageLength = 10),
      colnames = c(
        "Location",
        "OC UID",
        "Suspected Cases",
        "TL",
        "TR",
        "Period ID(s)",
        "Dropped Data UID"
      )
    )
}
```

# Summary of All Adm0 Observations in Model Input (sf_cases_resized)
```{r adm0 obs in sf_cases_resized, echo = F, message=F}
sf_cases_resized_orig %>%
  sf::st_drop_geometry() %>% 
  filter(admin_level == 0) %>% 
  select(location_name, TL, TR,  attributes.fields.suspected_cases) %>%
  gt() %>%
  tab_header(
    title = "Adm0 Observations"
  ) %>%
  fmt_number(
    columns = c(attributes.fields.suspected_cases),
    decimals = 0
  ) %>%
  cols_label(
    location_name = "Location",
    attributes.fields.suspected_cases = "sCh"
  ) %>% 
  tab_options(
    container.width = pct(100)
  )
```