---
title: "Model run report"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: false
params:
  cholera_directory: "~/projects/cholera-mapping-pipeline"
  config_directory: "Analysis/configs/2015_2019_country_tfrac"
  max_countries: Inf
---
```{r setup, include=FALSE, dev="CairoPNG"}
knitr::opts_chunk$set(inlude = FALSE, dev="CairoPNG")
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache.lazy = F,
  bitmapType = "cairo"
)
library(stringr)
library(dplyr)
library(tidyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(RColorBrewer)
library(MCMCvis)
library(sf)
library(abind)
```

```{r datapull, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
all_configs <- list.files(params$config_directory, full.names=TRUE)
all_locations <- str_extract(all_configs, "(?<=g_)[A-Z]{3}(?=_)")
all_times <- unique(str_extract(all_configs, "(?<=_)[0-9]{4}_[0-9]{4}(?=\\.)"))
if(length(all_times) > 1){
  stop("This report was not intended to compile runs from different time ranges")
}

out_dir <- str_c(params$cholera_directory, "/Analysis/output/reports/", str_split(params$config_directory, "/")[[1]]  %>% last())
```

Results summary for `r paste(all_locations, collapse =', ')` and period `r all_times`


## Input data 
#### Statistics
```{r obsstats, fig.height=8, fig.width=6, fig.cap="Input data statistics. Number of cases, observations, location periods and observations collections for each country and per modeling year."}
obs_stats <- dir(out_dir, 
                 pattern = "obs_stats", full.names = T) %>% 
  map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)}) %>% 
  select(year, country, contains("n_")) %>% 
  tidyr::gather(var, value, -year, -country)

ggplot(obs_stats, aes(y = country, x = value, fill = year)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~var, scales = "free") +
  ggthemes::scale_fill_few() +
  theme_bw() 

```

### Spatial coverage
```{r spat cov, fig.width=8, fig.height=10, fig.cap="Spatial coverage. Color gives the number of location periods x observations that cover a given hex cell."}
# 
# all_coverage <- map(dir(out_dir, pattern = "covera", full.names = T)[1:2] , function(resfile) {
# 
#   sf_cases_grids <- readRDS(resfile)
#   if(nrow(sf_cases_grids) ==0)
#     return(NULL)
# 
#   sf_cases_grids %>%
#     ggplot(aes(x = long, y = lat)) +
#     geom_hex() +
#     scale_fill_viridis_c(trans = "log",
#                          breaks = c(1, 10, 100, 1000, 1e4, 1e5),
#                          guide = guide_colorbar(title = "# lp x obs")) +
#     facet_wrap(~t, nrow = 1) +
#     theme_bw() +
#     ggtitle(sf_cases_grids$country[1])
# })
# 
# cowplot::plot_grid(plotlist = all_coverage[1:3],
#                    # align = "v",
#                    ncol = 1)

```

### Data variability
```{r datavar, fig.width=8, fig.height=6, fig.cap="Variability of observations per location period and year."}
data <- dir(out_dir, 
            pattern = "rhats", full.names = T) %>% 
  map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)}) %>% 
  distinct(obs, y, location_period_id, tfrac, t, n_cell, country) %>% 
  mutate(annual_cases = y/tfrac,
         location_period_id = factor(location_period_id),
         t = factor(t))


annual_stats <- data %>%
  # filter(tfrac > .9) %>% 
  group_by(location_period_id, t, country) %>%
  summarise(range = max(annual_cases) - min(annual_cases),
            sd = sd(annual_cases),
            var = var(annual_cases),
            mean = mean(annual_cases),
            n = n()) %>%
  arrange(country, t)

# annual_stats %>%
#   ggplot(aes(x = log10(range+1))) +
#   geom_histogram() +
#   facet_wrap(~country, scales = "free_y") +
#   theme_bw()

# quantiel_data <- data %>% 
#   filter(tfrac < .1) %>% 
#   group_by(country, t, location_period_id) %>% 
#   group_map(.f = function(x, y) {
#     ecdf_dat <- ecdf(x$annual_cases)
#     x <- seq(0, 1, by = 0.01)
#     q_dat <- quantile(ecdf_dat, x)
#     tibble(x = x, quant = q_dat) %>% cbind(y)
#   }) %>% 
#   bind_rows()

# pcdf <- ggplot(quantiel_data, aes(x = log10(quant), y = x, group = location_period_id, color = t)) +
#   geom_step(alpha = .1) +
#   facet_wrap(~country) +
#   theme_bw() +
#   labs(x = "log10(annual cases)", y = "P(X <= x)")

# ggsave(pcdf, filename = "ecdf_annual_cases.png", width = 8, height = 6)
# 
pvarmean <- annual_stats %>%
  filter(n > 1) %>%
  ggplot(aes(x = log10(mean+1), y = log10(var+1))) +
  geom_point(alpha = .3, aes(size = n)) +
  facet_wrap(~country) +
  theme_bw() +
  geom_abline(aes(intercept = 0, slope = 1), lty = 2, col = "red") +
  geom_abline(aes(intercept = 0, slope = 2), lty = 3, col = "blue")
pvarmean

ggsave(pvarmean, filename = "mean_var_plot.png", width = 8, height = 6)
```



## Runtimes

```{r runtimes, fig.height=5, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Stan model run time per country. Bars indicate the mean across chains, and errobars the min and max chain runtimes."}
runtimes <- dir(out_dir, 
                pattern = "runtime", full.names = T) %>% 
  map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)}) %>% 
  group_by(country, chain) %>% 
  summarise(runtime = (warmup + sample)/3600) %>% 
  group_by(country) %>% 
  summarise(min = min(runtime),
            max = max(runtime),
            mean = mean(runtime))

ggplot(runtimes, aes(y = country, x = mean, xmin = min, xmax = max)) +
  geom_bar(stat = "identity") +
  geom_errorbarh(height = .2) +
  theme_bw() +
  labs(x = "Runtime (hours)")

```


## MCMC convergence on modeled cases

```{r rhats, fig.height=10, fig.width=10, fig.cap="Chain convegence for observations"}
rhats <- dir(out_dir, 
             pattern = "rhats", full.names = T) %>% 
  map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)}) 

# Rhat threshold
rhat_thresh <- 1.05

# Case cuts for plotting
case_cuts <- c(-Inf, 0, 10^seq(1:6))

# Compute fraction above threshold for each country
rhats_frac <- rhats %>% 
  filter(max_diff_chains > 1) %>% 
  mutate(y_class = cut(y, case_cuts)) %>% 
  rbind(mutate(., y_class = "all")) %>% 
  group_by(country, y_class) %>% 
  summarise(n_above = sum(Rhat > rhat_thresh),
            n_obs = n(),
            frac_above = n_above/n()) %>% 
  mutate(label = str_c(n_above, "/", n_obs))

ggplot(rhats_frac, aes(y = country, x = frac_above, fill = n_above)) +
  geom_point() +
  geom_bar(stat = "identity") +
  geom_label(aes(label = label), color = "white", size = 2) +
  theme_bw() +
  facet_wrap(~y_class) +
  scale_fill_viridis_c(trans = "log",
                       breaks = 10^seq(4)) +
  labs(x = str_c("Fraction of observations above threshold of ", rhat_thresh))

```


## Model validation
### Observed vs. modeled by chain
```{r casecomp, fig.height=12, fig.width=8, fig.cap="Observations against mean modeled cases. Colors indicate the MCMC chain."}
case_comp <- dir(out_dir,
                 pattern = "case_comp", full.names = T) %>%
  map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)})

case_comp %>%
  ggplot(aes(x = actual, y = modeled, color = chain)) +
  geom_abline(aes(intercept = 0, slope = 1), lty = 2) +
  geom_point() +
  facet_wrap(~country, scales = "free", ncol = 3) +
  theme_bw()
```

### Observed vs. modeled with CrIs
```{r casecomp2, fig.height=30, fig.width=8, fig.cap="Observations against mean modeled cases. Colors indicate the MCMC chain."}

tfrac_cuts <- c(0, .1, .5, .9, 1)
all_comp <- map(unique(rhats$country), function(cntry) {
  dat <- rhats %>%
    mutate(tfrac_class = cut(tfrac, tfrac_cuts),
           rhat_above = factor(as.character(Rhat > rhat_thresh), levels = c("TRUE", "FALSE"))) %>%
    filter(country == cntry)
  
  dat %>%
    ggplot(aes(x = y, y = mean)) +
    geom_abline(aes(intercept = 0, slope = 1), lty = 2) +
    geom_errorbar(data = filter(dat, rhat_above == "FALSE"),
                  aes(ymin = q025, max = q975, color = Rhat > rhat_thresh), width = 0, alpha = .3) +
    geom_point(data = filter(dat, rhat_above == "FALSE"),
               aes(color = rhat_above), size = .8, alpha = .3) +
    geom_errorbar(data = filter(dat, rhat_above == "FALSE"),
                  aes(ymin = q025, max = q975, color = Rhat > rhat_thresh), width = 0, alpha = .3) +
    geom_point(data = filter(dat, rhat_above == "TRUE"),
               aes(color = rhat_above), size = .8, alpha = 1) +
    facet_wrap( ~ tfrac_class,
                ncol = 4,
                labeller = label_both,
                drop = F) +
    # coord_equal() +
    theme_bw()+
    guides(alpha = "none", pch = "none", color = "none", size = "none") +
    geom_text(data = tibble(
      y = .15*(max(dat$y) - min(dat$y)),
      mean = .9 * (max(dat$mean) - min(dat$mean)),
      tfrac_class = "(0,0.1]"
    ),
    label = cntry,
    size = 3) +
    labs(x = "observed", y = "modeled") +
    theme(axis.title = element_text(size = 6),
          strip.text = element_text(size = 6),
          axis.text = element_text(size = 4),
          strip.background = element_blank(),
          plot.background = element_blank(),
          plot.margin = unit(rep(1, 4), units = "mm"))
})

gridExtra::grid.arrange(grobs = all_comp, ncol = 1)
```


### Observed vs. modeled with CrIs by year
```{r casecomp3, fig.height=30, fig.width=8, fig.cap="Observations against mean modeled cases. Colors indicate the MCMC chain."}

tfrac_cuts <- c(0, .1, .5, .9, 1)
all_comp <- map(unique(rhats$country), function(cntry) {
  dat <- rhats %>%
    mutate(tfrac_class = cut(tfrac, tfrac_cuts),
           rhat_above = factor(as.character(Rhat > rhat_thresh), levels = c("TRUE", "FALSE")),
           t = factor(t)) %>%
    filter(country == cntry)
  
  dat %>%
    ggplot(aes(x = y, y = mean)) +
    geom_abline(aes(intercept = 0, slope = 1), lty = 2) +
    geom_errorbar(aes(ymin = q025, max = q975, color = t), width = 0, alpha = .3) +
    geom_point(aes(color = t), size = .8, alpha = .3) +
    facet_wrap( ~ tfrac_class,
                ncol = 4,
                labeller = label_both,
                drop = F) +
    # coord_equal() +
    theme_bw()+
    guides(alpha = "none", pch = "none", color = "none", size = "none") +
    geom_text(data = tibble(
      y = .15*(max(dat$y) - min(dat$y)),
      mean = .9 * (max(dat$mean) - min(dat$mean)),
      tfrac_class = "(0,0.1]"
    ),
    label = cntry,
    size = 3) +
    labs(x = "observed", y = "modeled") +
    theme(axis.title = element_text(size = 6),
          strip.text = element_text(size = 6),
          axis.text = element_text(size = 4),
          strip.background = element_blank(),
          plot.background = element_blank(),
          plot.margin = unit(rep(1, 4), units = "mm"))
})

gridExtra::grid.arrange(grobs = all_comp, ncol = 1)
```
### Country-level comparison with WHO annual reports
```{r who, fig.width = 10, fig.height=8, fig.cap="Comparison of annual country-level modeled number of cases against WHO annual reports when available."}
who_comp <- dir(out_dir, 
                pattern = "who", full.names = T) %>% 
  map2_df(.x = ., .y = str_extract(., "[A-Z]{3}"), .f = function(x, y) {res <- read_csv(x); if(nrow(res) > 0) return(res %>% mutate(country = y))}) %>% 
  mutate(year = as.character(lubridate::year(TL)))

who_comp %>% 
  pivot_longer(cols = c("observed", "modeled")) %>% 
  mutate(name = case_when(name == "modeled" ~ "modeled",
                          T ~ "WHO annual report")) %>%
  ggplot(aes(x = year, y = value, fill = name)) +
  geom_bar(stat = "identity", position = position_dodge(width = 1)) +
  geom_point(aes(color = name), position = position_dodge(width = 1)) +
  facet_wrap(~country, scales = "free", ncol = 4) +
  theme_bw() +
  ggthemes::scale_fill_few(guide = guide_legend(""))+
  ggthemes::scale_color_few(guide = guide_legend("")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(x = "year", 
       y = "annual number of cases")

```
## Maps

### Incidence rates [cases/10'000/year]
```{r maps, fig.width=8, fig.height=10, fig.cap="Maximum modeled case incidence rate on the log10-scale, with limtis 1e-3 - 1e5 cases/100'000/year (values lower and larger than these are shown in gray)"}
case_rast <- dir(out_dir,
                 pattern = "rast", full.names = T) %>%
  map_df(function(x) {res <- readRDS(x); if(nrow(res) > 0) return(res)})

# Get years for which we have at least one observation
avail_times <- rhats %>%
  count(country, t)

all_maps <- map(unique(case_rast$country), function(cntry) {
  taxdat::plot_map(case_rast %>%
                     filter(country == cntry) %>%
                     inner_join(avail_times) %>% 
                     group_by(country, rid, x, y) %>%
                     summarise(modeled_rates = mean(`modeled rates`, na.rm = T)),
                   column = "modeled_rates",
                   colorscale_type = "rates",
                   facet_column = NULL,
                   plot_border = F,  
                   render = T,
                   use_log = T) +
    guides(fill = "none")
  
})

cowplot::plot_grid(plotlist = all_maps,
                   # align = "hv",
                   ncol = 4)
```

### Incidence [cases\year]

```{r casemaps, fig.width=8, fig.height=10, fig.cap="Maximum modeled case incidence rate on the log10-scale, with limtis 1e-3 - 1e5 cases/year (values lower and larger than these are shown in gray)"}

all_maps <- map(unique(case_rast$country), function(cntry) {
  taxdat::plot_map(case_rast %>%
                     filter(country == cntry) %>%
                     inner_join(avail_times) %>% 
                     group_by(country, rid, x, y) %>%
                     summarise(modeled_cases = mean(`modeled cases`, na.rm = T)),
                   column = "modeled_cases", 
                   colorscale_type = "cases",
                   facet_column = NULL,
                   plot_border = F,
                   render = T,
                   use_log = T) +
    guides(fill = "none")
})

cowplot::plot_grid(plotlist = all_maps,
                   # align = "hv",
                   ncol = 4)
```

## Covariates
```{r betas, fig.height=10, fig.width=8, fig.cap="Covariate coefficients by country"}
betas <- dir(out_dir, 
             pattern = "betas", full.names = T) %>% 
  map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)}) 


ggplot(betas, aes(x = mean, y = country)) +
  geom_point() +
  geom_errorbarh(aes(xmin = `2.5%`, xmax = `97.5%`), height = 0) +
  geom_vline(aes(xintercept = 0), lty = 2, size = .3, col = "red") +
  facet_wrap(~ covar) +
  theme_bw()

```
## Negative binomial aggregation
```{r negbinom, fig.height=8, fig.width=6, fig.cap="Covariate coefficients by country"}

if (str_detect(params$config_directory, "negbinom")) {
  phis <- dir(out_dir, 
              pattern = "negbinom", full.names = T) %>% 
    map_df(function(x) {res <- read_csv(x); if(nrow(res) > 0) return(res)}) 
  
  ggplot(phis, aes(x = q50, y = country)) +
    geom_point() +
    geom_errorbarh(aes(xmin = q025, xmax = q975), height = 0) +
    geom_vline(aes(xintercept = 0), lty = 2, size = .3, col = "red") + 
    scale_x_continuous(trans = "log10") +
    theme_bw() +
    labs(x = "Aggregation parameter")
}
```
