---
title: "Manuscript statistics in results section"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  postprocessed_output_directory: "/home/cholerapipelinerestmp/postprocess/processed_outputs"
  interm_directory: "/home/cholerapipelinerestmp/postprocess/interm"
  output_directory: "/home/cholerapipelinerestmp/paper_stats/"
---

```{r setup, include=FALSE}
package_list <- c(
  "taxdat",
  "sf",
  "tidyverse"
)
for (package in package_list) {
  if(!require(package = package, character.only = T)){
    install.packages(pkgs = package)
    library(package = package, character.only = T)
  } else{
    library(package = package, character.only = T)
  }
}

### Debug
options(error = traceback)
options(dplyr.summarise.inform = FALSE)
```

## Paragraph 1
```{r Results_paragraph_1_table1, echo=FALSE,warning=FALSE}
output_obs_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_obs.rds'))
output_obs_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_obs.rds'))
output_obs_1120 <- dplyr::bind_rows(
  output_obs_1115 %>% dplyr::mutate(time_period = '2011-2015'),
  output_obs_1620 %>% dplyr::mutate(time_period = '2016-2020')
)

output_obs_counts_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_obs_counts.rds'))
output_obs_counts_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_obs_counts.rds'))
output_obs_counts_1120 <- dplyr::bind_rows(
  output_obs_counts_1115 %>% dplyr::mutate(time_period = '2011-2015'),
  output_obs_counts_1620 %>% dplyr::mutate(time_period = '2016-2020')
) %>% 
  group_by(locationPeriod_id,location_name,admin_level,imputed,country) %>% 
  summarize(n_obs = sum(n_obs), n_cases=sum(n_cases)) %>% 
  mutate(time_period ="2011-2020")

#load phantom 0s in WHO annual report
who_phantoms <- read.csv(paste0(params$output_directory,'/WHO_annual_report_phantom_0s.csv'))

#2011-2015
output_obs_counts_1115$WHO_phantoms = 0
for (loc_idx in unique(who_phantoms[who_phantoms$time_period=="2011-2015",]$location_name)) {
  if(nrow(output_obs_counts_1115[output_obs_counts_1115$imputed & output_obs_counts_1115$location_name==loc_idx,])==0 & nrow(output_obs_counts_1115 %>% 
      subset(location_name==loc_idx))>0){
    tmp <- output_obs_counts_1115 %>% 
      subset(location_name==loc_idx) %>% 
      mutate(imputed = TRUE,
             n_obs=who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1115 <- bind_rows(output_obs_counts_1115,tmp) 
    
    output_obs_counts_1115[output_obs_counts_1115$location_name == loc_idx & output_obs_counts_1115$imputed==FALSE,]$WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs
  
  }else if(nrow(output_obs_counts_1115[output_obs_counts_1115$imputed & output_obs_counts_1115$location_name==loc_idx,])==0 & nrow(output_obs_counts_1115 %>% 
      subset(location_name==loc_idx))==0){
    tmp <- output_obs_counts_1115 %>% 
      subset(location_name=="AFR::AGO" & imputed) %>% 
      mutate(locationPeriod_id = as.character(who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$location_period_id),
             location_name = loc_idx, 
             imputed = TRUE,
             n_obs=who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1115 <- bind_rows(output_obs_counts_1115,tmp)
    
  } else  {
    output_obs_counts_1115[output_obs_counts_1115$location_name == loc_idx,]$WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs
    
    if(output_obs_counts_1115[output_obs_counts_1115$location_name == loc_idx & output_obs_counts_1115$imputed,]$n_cases>0){
    tmp <- output_obs_counts_1115 %>% 
      subset(location_name==loc_idx & imputed) %>% 
      mutate(
             n_obs=who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2015" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1115 <- bind_rows(output_obs_counts_1115,tmp) 
    
    } else {
    output_obs_counts_1115[output_obs_counts_1115$location_name == loc_idx & output_obs_counts_1115$imputed,]$n_obs = output_obs_counts_1115[output_obs_counts_1115$location_name == loc_idx & output_obs_counts_1115$imputed,]$n_obs+output_obs_counts_1115[output_obs_counts_1115$location_name == loc_idx & output_obs_counts_1115$imputed,]$WHO_phantoms
    }
  }
}

output_obs_counts_1115[output_obs_counts_1115$imputed==FALSE,]$n_obs = output_obs_counts_1115[output_obs_counts_1115$imputed==FALSE,]$n_obs - output_obs_counts_1115[output_obs_counts_1115$imputed==FALSE,]$WHO_phantoms #remove WHO phantom 0 obs from the non-imputed summaries

# Table 1 observation summaries
summary_obs_counts_1115 <- output_obs_counts_1115 %>%
  dplyr::group_by(imputed) %>% 
  dplyr::summarise(
    time_period = '2011-2015',
    unique_OCs = length(unique(output_obs_1115[!output_obs_1115$OC_UID%in%c("imputed_0_nodata","imputed_subnat_rate","imputed_subnat_sum"),]$OC_UID)),
    unique_loc = length(unique(location_name)),
    unique_admin_units = length(unique(admin_level)),
    
    total_obs = sum(n_obs), #total number of observations
    total_national_obs = sum(n_obs[admin_level==0]), # total number of national observations
    total_subnational_obs = sum(n_obs[!admin_level==0]), # total number of subnational observations
    total_imputed_zero_obs = sum(n_obs[n_cases==0]), #total number of imputed zero observations, including phantom 0 observations from WHO annual report and imputed national-level 0s.
    total_imputed_non_zero_obs = sum(n_obs[!n_cases == 0]), #total number of imputed non-zero observations
    
    unique_countries = length(unique(country)),
    total_cases = sum(n_cases),
    total_national_cases = sum(n_cases[admin_level==0]),
    total_subnational_cases = sum(n_cases[!admin_level==0])
  ) %>% 
  ungroup() %>% 
  mutate(
    total_imputed_zero_obs = ifelse(imputed,total_imputed_zero_obs,0),
    total_imputed_non_zero_obs = ifelse(imputed,total_imputed_non_zero_obs,0)
  )


#2016-2020
output_obs_counts_1620$WHO_phantoms = 0
for (loc_idx in unique(who_phantoms[who_phantoms$time_period=="2016-2020",]$location_name)) {
  if(nrow(output_obs_counts_1620[output_obs_counts_1620$imputed & output_obs_counts_1620$location_name==loc_idx,])==0 & nrow(output_obs_counts_1620 %>% 
      subset(location_name==loc_idx))>0){
    tmp <- output_obs_counts_1620 %>% 
      subset(location_name==loc_idx) %>% 
      mutate(imputed = TRUE,
             n_obs=who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1620 <- bind_rows(output_obs_counts_1620,tmp) 
    
    output_obs_counts_1620[output_obs_counts_1620$location_name == loc_idx & output_obs_counts_1620$imputed==FALSE,]$WHO_phantoms = who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs
  
  }else if(nrow(output_obs_counts_1620[output_obs_counts_1620$imputed & output_obs_counts_1620$location_name==loc_idx,])==0 & nrow(output_obs_counts_1620 %>% 
      subset(location_name==loc_idx))==0){
    tmp <- output_obs_counts_1620 %>% 
      subset(location_name=="AFR::AGO" & imputed) %>% 
      mutate(locationPeriod_id = as.character(who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$location_period_id),
             location_name = loc_idx, 
             imputed = TRUE,
             n_obs=who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1620 <- bind_rows(output_obs_counts_1620,tmp)
    
  } else  {
    output_obs_counts_1620[output_obs_counts_1620$location_name == loc_idx,]$WHO_phantoms = who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs
    
    if(output_obs_counts_1620[output_obs_counts_1620$location_name == loc_idx & output_obs_counts_1620$imputed,]$n_cases>0){
    tmp <- output_obs_counts_1620 %>% 
      subset(location_name==loc_idx & imputed) %>% 
      mutate(
             n_obs=who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2016-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1620 <- bind_rows(output_obs_counts_1620,tmp) 
    
    } else {
    output_obs_counts_1620[output_obs_counts_1620$location_name == loc_idx & output_obs_counts_1620$imputed,]$n_obs = output_obs_counts_1620[output_obs_counts_1620$location_name == loc_idx & output_obs_counts_1620$imputed,]$n_obs+output_obs_counts_1620[output_obs_counts_1620$location_name == loc_idx & output_obs_counts_1620$imputed,]$WHO_phantoms
    }
  }
}

output_obs_counts_1620[output_obs_counts_1620$imputed==FALSE,]$n_obs = output_obs_counts_1620[output_obs_counts_1620$imputed==FALSE,]$n_obs - output_obs_counts_1620[output_obs_counts_1620$imputed==FALSE,]$WHO_phantoms #remove WHO phantom 0 obs from the non-imputed summaries


summary_obs_counts_1620 <- output_obs_counts_1620 %>%
  dplyr::group_by(imputed) %>% 
  dplyr::summarise(
    time_period = '2016-2020',
    unique_OCs = length(unique(output_obs_1620[!output_obs_1620$OC_UID%in%c("imputed_0_nodata","imputed_subnat_rate","imputed_subnat_sum"),]$OC_UID)),
    unique_loc = length(unique(location_name)),
    unique_admin_units = length(unique(admin_level)),
    
    total_obs = sum(n_obs), #total number of observations
    total_national_obs = sum(n_obs[admin_level==0]), # total number of national observations
    total_subnational_obs = sum(n_obs[!admin_level==0]), # total number of subnational observations
    total_imputed_zero_obs = sum(n_obs[n_cases==0]), #total number of imputed zero observations, including phantom 0 observations from WHO annual report and imputed national-level 0s.
    total_imputed_non_zero_obs = sum(n_obs[!n_cases == 0]), #total number of imputed non-zero observations
    
    unique_countries = length(unique(country)),
    total_cases = sum(n_cases),
    total_national_cases = sum(n_cases[admin_level==0]),
    total_subnational_cases = sum(n_cases[!admin_level==0])
  ) %>% 
  ungroup() %>% 
  mutate(
    total_imputed_zero_obs = ifelse(imputed,total_imputed_zero_obs,0),
    total_imputed_non_zero_obs = ifelse(imputed,total_imputed_non_zero_obs,0)
  )


#2011-2020
who_phantoms <- who_phantoms %>% group_by(country,location_name,location_period_id) %>% summarize(n_who_phantom_0_obs=sum(n_who_phantom_0_obs)) %>% mutate(time_period = '2011-2020')

output_obs_counts_1120$WHO_phantoms = 0
for (loc_idx in unique(who_phantoms[who_phantoms$time_period=="2011-2020",]$location_name)) {
  if(nrow(output_obs_counts_1120[output_obs_counts_1120$imputed & output_obs_counts_1120$location_name==loc_idx,])==0 & nrow(output_obs_counts_1120 %>% 
      subset(location_name==loc_idx))>0){
    tmp <- output_obs_counts_1120 %>% 
      subset(location_name==loc_idx) %>% 
      mutate(imputed = TRUE,
             n_obs=who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1120 <- bind_rows(output_obs_counts_1120,tmp) 
    
    output_obs_counts_1120[output_obs_counts_1120$location_name == loc_idx & output_obs_counts_1120$imputed==FALSE,]$WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs
  
  }else if(nrow(output_obs_counts_1120[output_obs_counts_1120$imputed & output_obs_counts_1120$location_name==loc_idx,])==0 & nrow(output_obs_counts_1120 %>% 
      subset(location_name==loc_idx))==0){
    tmp <- output_obs_counts_1120 %>% 
      subset(location_name=="AFR::AGO" & imputed) %>% 
      mutate(locationPeriod_id = as.character(who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$location_period_id),
             location_name = loc_idx, 
             imputed = TRUE,
             n_obs=who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1120 <- bind_rows(output_obs_counts_1120,tmp)
    
  } else  {
    output_obs_counts_1120[output_obs_counts_1120$location_name == loc_idx,]$WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs
    
    if(output_obs_counts_1120[output_obs_counts_1120$location_name == loc_idx & output_obs_counts_1120$imputed,]$n_cases>0){
    tmp <- output_obs_counts_1120 %>% 
      subset(location_name==loc_idx & imputed) %>% 
      mutate(
             n_obs=who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs,
             n_cases=0,
             mean_cases=0,
             WHO_phantoms = who_phantoms[who_phantoms$time_period == "2011-2020" & who_phantoms$location_name == loc_idx,]$n_who_phantom_0_obs)
    
    output_obs_counts_1120 <- bind_rows(output_obs_counts_1120,tmp) 
    
    } else {
    output_obs_counts_1120[output_obs_counts_1120$location_name == loc_idx & output_obs_counts_1120$imputed,]$n_obs = output_obs_counts_1120[output_obs_counts_1120$location_name == loc_idx & output_obs_counts_1120$imputed,]$n_obs+output_obs_counts_1120[output_obs_counts_1120$location_name == loc_idx & output_obs_counts_1120$imputed,]$WHO_phantoms
    }
  }
}

output_obs_counts_1120[output_obs_counts_1120$imputed==FALSE,]$n_obs = output_obs_counts_1120[output_obs_counts_1120$imputed==FALSE,]$n_obs - output_obs_counts_1120[output_obs_counts_1120$imputed==FALSE,]$WHO_phantoms #remove WHO phantom 0 obs from the non-imputed summaries

summary_obs_counts_1120 <- output_obs_counts_1120 %>%
  dplyr::group_by(imputed) %>% 
  dplyr::summarise(
    time_period = 'all years',
    unique_OCs = length(unique(output_obs_1120[!output_obs_1120$OC_UID%in%c("imputed_0_nodata","imputed_subnat_rate","imputed_subnat_sum"),]$OC_UID)),
    unique_loc = length(unique(location_name)),
    unique_admin_units = length(unique(admin_level)),
    
    total_obs = sum(n_obs), #total number of observations
    total_national_obs = sum(n_obs[admin_level==0]), # total number of national observations
    total_subnational_obs = sum(n_obs[!admin_level==0]), # total number of subnational observations
    total_imputed_zero_obs = sum(n_obs[n_cases==0]), #total number of imputed zero observations, including phantom 0 observations from WHO annual report and imputed national-level 0s.
    total_imputed_non_zero_obs = sum(n_obs[!n_cases == 0]), #total number of imputed non-zero observations
    
    unique_countries = length(unique(country)),
    total_cases = sum(n_cases),
    total_national_cases = sum(n_cases[admin_level==0]),
    total_subnational_cases = sum(n_cases[!admin_level==0])
  ) %>% 
  ungroup() %>% 
  mutate(
    total_imputed_zero_obs = ifelse(imputed,total_imputed_zero_obs,0),
    total_imputed_non_zero_obs = ifelse(imputed,total_imputed_non_zero_obs,0)
  )



table1 <- dplyr::bind_rows(
  summary_obs_counts_1115,
  summary_obs_counts_1620,
  summary_obs_counts_1120
) %>% 
  dplyr::arrange(time_period) %>% 
  dplyr::mutate(row_number = dplyr::row_number())

table1 %>% 
  dplyr::select(!row_number) %>% 
  kableExtra::kbl(caption = "Table 1. Observation summary") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::row_spec(.,c(table1[which(table1$time_period == 'all years'),]$row_number), bold = T, background = "yellow")

print("unique_OCs: total number of unique observation collections")
print("unique_loc: total number of unique locations")
print("unique_admin_units: total number of unique administrative levels")
print("total_obs: total number of observations")
print("total_national_obs: total number of national observations")
print("total_subnational_obs: total number of subnational observations")
print("total_imputed_zero_obs: total number of imputed zero observations, including phantom 0 observations from WHO annual report and imputed national-level 0s.")
print("total_imputed_non_zero_obs: total number of imputed non-zero observations")
print("unique_countries: total number of unique countries")
print("total_cases: total number of reported cases")
print("total_national_cases: total number of reported cases at the national levels")
print("total_subnational_cases: total number of reported cases at the subnational levels")
    

invisible(gc())
```


```{r Results_paragraph_1_other_tables, echo=FALSE,warning=FALSE}
# Table 2 subnational data coverage by country
#it seems the location periods in these two time periods are the same
sf::sf_use_s2(FALSE)
shp_adm2_1115 <- sf::st_make_valid(readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_shapefiles.rds')) %>% dplyr::filter(admin_level >=2))
shp_adm2_1620 <- sf::st_make_valid(readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_shapefiles.rds')) %>% dplyr::filter(admin_level >=2))

# join shapefiles from two periods (a shapefile will be included if it's in either of the time period)
shp_adm2 <- rbind(shp_adm2_1115,shp_adm2_1620) %>% 
  dplyr::group_by(locationPeriod_id) %>% 
    dplyr::slice(1) %>% 
    dplyr::arrange(admin_level, location_name) 

output_adm0_sf_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_adm0_sf.rds'))

if(file.exists(paste0(params$output_directory,"/subnational_obs_coverage.rds"))){
  subnational_obs_coverage<-readRDS(paste0(params$output_directory,"/subnational_obs_coverage.rds"))
} else{
  subnational_obs_coverage <- data.frame()
for (country_tmp in unique(shp_adm2$country)) {
  #st_union adm2 shapefiles for a specific country
  shp_union <- sf::st_make_valid(sf::st_union(shp_adm2[shp_adm2$country==country_tmp,]$geom))

  #get country shapefiles
  shp_adm0 <- output_adm0_sf_1620 %>% dplyr::filter(country == country_tmp)
  #calculate the proportion of area covered by adm2 or lower obs
  subnational_obs_coverage <- subnational_obs_coverage %>% dplyr::bind_rows(data.frame(country = country_tmp, subnational_cov = 100*round(as.numeric(sf::st_area(shp_union)/sf::st_area(shp_adm0)),4)))
  
  saveRDS(shp_union,paste0(params$output_directory,"/",country_tmp,"_adm2_shp_union.rds"))
}

saveRDS(subnational_obs_coverage,paste0(params$output_directory,"/subnational_obs_coverage.rds"))

}

table2 <- subnational_obs_coverage %>% 
  dplyr::rename(`% of area covered by adm2 or lower obs` = subnational_cov)

table2 %>% 
  kableExtra::kbl(caption = "Table 2. Subnational data coverage, 2011-2020") %>% 
  kableExtra::kable_styling(full_width = FALSE)

saveRDS(table2,paste0(params$output_directory,"/figure1.rds"))

#print out the median and range for table 2
print(paste0("The median % of area covered by admin2 or lower observations is ",median(table2$`% of area covered by adm2 or lower obs`),"% (",min(table2$`% of area covered by adm2 or lower obs`),"% - ",max(table2$`% of area covered by adm2 or lower obs`),"%)"))

# Figure 1. figure version of table 2
  table2 %>% 
  dplyr::arrange(desc(`% of area covered by adm2 or lower obs`)) %>% 
  ggplot(aes(x= `% of area covered by adm2 or lower obs`, y=reorder(country,`% of area covered by adm2 or lower obs`))) +
  geom_bar(stat="identity", position=position_dodge(),fill="gold")+
  theme_minimal() +
  ylab("Country")+
  labs(title = "Figure 1. % of area covered by adm2 or lower obs by country")

# Table 3. fully observation coverage
table3 <- output_obs_1120 %>% 
  dplyr::summarise(
    `% of full observations` = scales::percent(sum(censoring == 'full') / n()),
        total_full_obs = sum(censoring == 'full'),
        total_obs = n()
  ) %>% 
  dplyr::mutate(time_period = 'all years') %>% 
  dplyr::bind_rows(
    output_obs_1115 %>% 
      dplyr::summarise(
        `% of full observations` = scales::percent(sum(censoring == 'full') / n()),
        total_full_obs = sum(censoring == 'full'),
        total_obs = n()
        ) %>% 
  dplyr::mutate(time_period = '2011-2015')
  ) %>% 
  dplyr::bind_rows(
    output_obs_1620 %>% 
      dplyr::summarise(
        `% of full observations` = scales::percent(sum(censoring == 'full') / n()),
        total_full_obs = sum(censoring == 'full'),
        total_obs = n()
        ) %>% 
  dplyr::mutate(time_period = '2016-2020')
  ) %>% 
  dplyr::select(time_period, total_obs, total_full_obs, `% of full observations`) %>% 
  dplyr::arrange(time_period) %>% 
  dplyr::mutate(row_number = dplyr::row_number())

#make table3
table3 %>% 
  dplyr::select(!row_number) %>% 
  kableExtra::kbl(caption = "Table 3. Full observation summary by time periods") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::row_spec(.,c(table3[which(table3$time_period == 'all years'),]$row_number), bold = T, background = "yellow")

#table 4 full observation coverage by admin levels
table4 <- output_obs_1120 %>% 
  dplyr::group_by(admin_level) %>% 
  dplyr::summarise(
    `% of full observations` = scales::percent(sum(censoring == 'full') / n()),
        total_full_obs = sum(censoring == 'full'),
        total_obs = n()
  ) %>% 
  dplyr::mutate(time_period = 'all years') %>% 
  dplyr::bind_rows(
    output_obs_1115 %>% 
      dplyr::group_by(admin_level) %>% 
      dplyr::summarise(
        `% of full observations` = scales::percent(sum(censoring == 'full') / n()),
        total_full_obs = sum(censoring == 'full'),
        total_obs = n()
        ) %>% 
  dplyr::mutate(time_period = '2011-2015')
  ) %>% 
  dplyr::bind_rows(
    output_obs_1620 %>% 
      dplyr::group_by(admin_level) %>% 
      dplyr::summarise(
        `% of full observations` = scales::percent(sum(censoring == 'full') / n()),
        total_full_obs = sum(censoring == 'full'),
        total_obs = n()
        ) %>% 
  dplyr::mutate(time_period = '2016-2020')
  ) %>% 
  dplyr::select(time_period, admin_level, total_obs, total_full_obs, `% of full observations`) %>% 
  dplyr::arrange(time_period,admin_level) %>% 
  dplyr::mutate(row_number = dplyr::row_number())

table4 %>% 
  dplyr::select(!row_number) %>% 
  kableExtra::kbl(caption = "Table 4. Full observation summary by time periods and admin levels") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::row_spec(.,c(table4[which(table4$time_period == 'all years'),]$row_number), bold = T, background = "yellow")

# ??? does one full country-level observation per year include multi-year data? (excluded here)
summary_full_obs_full_modeling_period_adm0 <- output_obs_1120 %>% 
  subset(lubridate::year(ref_TL)==lubridate::year(ref_TR)) %>% 
  dplyr::mutate(year = lubridate::year(ref_TL)) %>% 
      subset(admin_level == 0 ) %>% 
      dplyr::group_by(admin_level, country, year) %>% 
      dplyr::summarise(
        total_full_obs = sum(censoring == 'full')
        ) %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(total_full_obs >0) %>% 
  dplyr::group_by(country) %>%
  dplyr::filter(
    n() == 10
  ) 

print(paste(length(unique(summary_full_obs_full_modeling_period_adm0$country)) ,"countries having at least one full country-level observation per year in both modeling periods."))

invisible(gc())
```
## Paragraph 2
```{r Results_paragraph_2, echo=FALSE,warning=FALSE,message=FALSE}
# load average cases raster
output_mai_cases_all_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_mai_cases_all.rds')) %>% 
  dplyr::mutate(
    time_period = '2011-2015'
  )
output_mai_cases_all_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_mai_cases_all.rds')) %>% 
  dplyr::mutate(
    time_period = '2016-2020'
  )


# print out average suspected cases summary
print(
  paste0(
  "Annual average cholera cases across Africa in 2011-2015: ", round(output_mai_cases_all_1115$mean,0), 
  " (95% Credible Intervals, CrI: ", round(output_mai_cases_all_1115$q2.5,0), " - ", round(output_mai_cases_all_1115$q97.5,0), ")"
  )
)
print(
  paste0(
  "Annual average cholera cases across Africa in 2016-2020: ", round(output_mai_cases_all_1620$mean,0), 
  " (95% Credible Intervals, CrI: ", round(output_mai_cases_all_1620$q2.5,0), " - ", round(output_mai_cases_all_1620$q97.5,0), ")"
  )
)

#cases by region
output_mai_cases_by_region_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_mai_cases_by_region.rds')) %>% 
  dplyr::mutate(
    time_period = '2011-2015'
  )
output_mai_cases_by_region_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_mai_cases_by_region.rds')) %>% 
  dplyr::mutate(
    time_period = '2016-2020'
  )

output_mai_cases_by_region_1115 %>% 
  mutate(region = str_remove(variable,"country_cases_"),
         `Mean annual cholera cases` = round(mean,0),
         `95% Credible Intervals` = paste0(round(q2.5,0),'-',round(q97.5,0))) %>% 
  select(region,`Mean annual cholera cases`,`95% Credible Intervals`) %>% 
  dplyr::arrange(dplyr::desc(`Mean annual cholera cases`)) %>% 
  kableExtra::kbl(caption = "Table 5. Annual average cholera cases by region in 2011-2015") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")


output_mai_cases_by_region_1620 %>% 
  mutate(region = str_remove(variable,"country_cases_"),
         `Mean annual cholera cases` = round(mean,0),
         `95% Credible Intervals` = paste0(round(q2.5,0),'-',round(q97.5,0))) %>% 
  select(region,`Mean annual cholera cases`,`95% Credible Intervals`) %>% 
  dplyr::arrange(dplyr::desc(`Mean annual cholera cases`)) %>% 
  kableExtra::kbl(caption = "Table 6. Annual average cholera cases by region in 2016-2020") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")

rm(output_mai_cases_by_region_1115)
rm(output_mai_cases_by_region_1620)
invisible(gc())

```


```{r Results_paragraph_2_grid_level_rates_cases, echo=FALSE,warning=FALSE,message=FALSE}
# Grid-level cases summary
output_mai_grid_cases_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_mai_grid_cases.rds')) 
output_mai_grid_cases_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_mai_grid_cases.rds')) 

data.frame(
  time_period = "2011-2015",
  `% of grid cells with >1 modeled cases/year` = scales::percent(nrow(output_mai_grid_cases_1115[output_mai_grid_cases_1115$mean>1,])/nrow(output_mai_grid_cases_1115))
  ) %>% 
  dplyr::bind_rows(
   data.frame(
  time_period = "2016-2020",
  `% of grid cells with >1 modeled cases/year` = scales::percent(nrow(output_mai_grid_cases_1620[output_mai_grid_cases_1620$mean>1,])/nrow(output_mai_grid_cases_1620))
  ) 
  ) %>% 
  dplyr::rename("% of grid cells with >1 mean modeled cases/year"=X..of.grid.cells.with..1.modeled.cases.year) %>%
  kableExtra::kbl(caption = "Table 7. Grid-level cases summary") %>% 
  kableExtra::kable_styling(full_width = FALSE)

# Grid-level cases by country summary
output_adm0_sf_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_adm0_sf.rds')) 
output_adm0_sf_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_adm0_sf.rds')) 

if(file.exists(paste0(params$output_directory,"/grid_case_adm0_1115.rds"))){
  grid_case_adm0_1115<-readRDS(paste0(params$output_directory,"/grid_case_adm0_1115.rds"))
} else{
  grid_case_adm0_1115<-data.frame()
for (row_tmp in 1:nrow(output_adm0_sf_1115)) {
  grid_case_adm0_1115_tmp <- sf::st_intersection(output_mai_grid_cases_1115,output_adm0_sf_1115[row_tmp,])
  grid_case_adm0_1115<-grid_case_adm0_1115 %>% dplyr::bind_rows(
    data.frame(
    time_period = "2011-2015",
    country = output_adm0_sf_1115$shapeName[row_tmp],
    `% of grid cells with >1 modeled cases/year` = nrow(grid_case_adm0_1115_tmp[grid_case_adm0_1115_tmp$mean>1,])/nrow(grid_case_adm0_1115_tmp) * 100      
    )
  )
}
saveRDS(grid_case_adm0_1115,paste0(params$output_directory,"/grid_case_adm0_1115.rds"))
}

rm(output_mai_grid_cases_1115)
invisible(gc())

if(file.exists(paste0(params$output_directory,"/grid_case_adm0_1620.rds"))){
    grid_case_adm0_1620<-readRDS(paste0(params$output_directory,"/grid_case_adm0_1620.rds"))
} else {
  grid_case_adm0_1620<-data.frame()
for (row_tmp in 1:nrow(output_adm0_sf_1620)) {
  grid_case_adm0_1620_tmp <- sf::st_intersection(output_mai_grid_cases_1620,output_adm0_sf_1620[row_tmp,])
  grid_case_adm0_1620<-grid_case_adm0_1620 %>% dplyr::bind_rows(
    data.frame(
    time_period = "2016-2020",
    country = output_adm0_sf_1620$shapeName[row_tmp],
    `% of grid cells with >1 modeled cases/year` = nrow(grid_case_adm0_1620_tmp[grid_case_adm0_1620_tmp$mean>1,])/nrow(grid_case_adm0_1620_tmp) * 100      
    )
  )
}

saveRDS(grid_case_adm0_1620,paste0(params$output_directory,"/grid_case_adm0_1620.rds"))

}

rm(output_mai_grid_cases_1620)
invisible(gc())

#make tables
grid_case_adm0_1115 %>% 
  dplyr::mutate(X..of.grid.cells.with..1.modeled.cases.year = round(X..of.grid.cells.with..1.modeled.cases.year,2)) %>% 
  dplyr::rename("% of grid cells with >1 mean modeled cases/year"=X..of.grid.cells.with..1.modeled.cases.year) %>% 
  dplyr::arrange(dplyr::desc(`% of grid cells with >1 mean modeled cases/year`)) %>% 
  kableExtra::kbl(caption = "Table 8. % of grid cells with >1 case/year in 2011-2015") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")

#print out the median and range for table 8
print(paste0("The median % of grid cells with >1 case/year in 2011-2015 is ",round(median(grid_case_adm0_1115$X..of.grid.cells.with..1.modeled.cases.year),2),"% (",round(min(grid_case_adm0_1115$X..of.grid.cells.with..1.modeled.cases.year),2),"% - ",round(max(grid_case_adm0_1115$X..of.grid.cells.with..1.modeled.cases.year),2),"%)"))

grid_case_adm0_1620 %>% 
  dplyr::mutate(X..of.grid.cells.with..1.modeled.cases.year = round(X..of.grid.cells.with..1.modeled.cases.year,2)) %>% 
  dplyr::rename("% of grid cells with >1 mean modeled cases/year"=X..of.grid.cells.with..1.modeled.cases.year) %>% 
  dplyr::arrange(dplyr::desc(`% of grid cells with >1 mean modeled cases/year`)) %>% 
  kableExtra::kbl(caption = "Table 9. % of grid cells with >1 case/year in 2016-2020") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")

#print out the median and range for table 9
print(paste0("The median % of grid cells with >1 case/year in 2016-2020 is ",round(median(grid_case_adm0_1620$X..of.grid.cells.with..1.modeled.cases.year),2),"% (",round(min(grid_case_adm0_1620$X..of.grid.cells.with..1.modeled.cases.year),2),"% - ",round(max(grid_case_adm0_1620$X..of.grid.cells.with..1.modeled.cases.year),2),"%)"))
```

```{r Results_paragraph_2_grid_level_pop, echo=FALSE,warning=FALSE,message=FALSE}
# ??? Grid-level population by country summary
# 2011-2015 ----
if(file.exists(paste0(params$output_directory,"/grid_pop_adm0_1115_pop_num.rds"))){
  grid_pop_adm0_1115 <- readRDS(paste0(params$output_directory,"/grid_pop_adm0_1115_pop_num.rds"))
} else {
  grid_pop_adm0_1115<-data.frame()
for (row_tmp in 1:nrow(output_adm0_sf_1115)) {

  iso = output_adm0_sf_1115$country[row_tmp]
  
  tmp_country_grid_case_1115 = readRDS(paste0(params$interm_directory,"/",intersect(list.files(path = params$interm_directory,pattern = "_mai_grid_cases_draws.rds"), list.files(path = params$interm_directory,pattern = paste0(iso,"_2011-01-01_2015-12-31"))))) %>% 
    rename(cases = value) %>% 
    data.frame() %>%
    select(!postproc_var)
    
  tmp_country_grid_case_1115_mean_across_draw <- tmp_country_grid_case_1115 %>% 
    group_by(rid,x,y,grid_id,geom) %>% 
    summarize(
      mean_cases = mean(cases)
    )
  
  tmp_country_grid_rate_1115 = readRDS(paste0(params$interm_directory,"/",intersect(list.files(path = params$interm_directory,pattern = "_mai_grid_rates_draws.rds"), list.files(path = params$interm_directory,pattern = paste0(iso,"_2011-01-01_2015-12-31"))))) %>% 
    rename(rates = value) %>% 
    data.frame() %>%
    select(!postproc_var)

# join case and rate rasters by rid, x, y, grid_id, .draw and geom
  grid_pop_adm0_1115_tmp <- inner_join(tmp_country_grid_case_1115,tmp_country_grid_rate_1115,by=c("rid",'x','y',"grid_id",'.draw',"geom")) %>%
    mutate(pop = cases/rates) %>% 
    left_join(tmp_country_grid_case_1115_mean_across_draw,by=c("rid",'x','y',"grid_id","geom")) %>% 
    group_by(.draw) %>% 
    summarize(
      pop_case_1 = sum(pop[mean_cases>1]),
      total_pop = sum(pop),
      pop_prop = pop_case_1/total_pop*100
    )

  grid_pop_adm0_1115<-grid_pop_adm0_1115 %>% dplyr::bind_rows(
    data.frame(
    time_period = "2011-2015",
    country = output_adm0_sf_1115$shapeName[row_tmp],
    total_pop = round(median(grid_pop_adm0_1115_tmp$pop_case_1/10^6),2),
    total_pop_CrI = paste0(round(quantile(grid_pop_adm0_1115_tmp$pop_case_1/10^6,probs=0.025)[[1]],2),"-",round(quantile(grid_pop_adm0_1115_tmp$pop_case_1/10^6,probs=0.975)[[1]],2)),
    pop_prop = round(median(grid_pop_adm0_1115_tmp$pop_prop),2),
    pop_prop_CrI = paste0(round(quantile(grid_pop_adm0_1115_tmp$pop_prop,probs=0.025)[[1]],2),"-",round(quantile(grid_pop_adm0_1115_tmp$pop_prop,probs=0.975)[[1]],2))
    )
  )
  
rm(tmp_country_grid_case_1115)
rm(tmp_country_grid_rate_1115)
invisible(gc())

}
  saveRDS(grid_pop_adm0_1115,paste0(params$output_directory,"/grid_pop_adm0_1115_pop_num.rds"))

}
#make tables
grid_pop_adm0_1115<-grid_pop_adm0_1115 %>% 
  select(!c(pop_prop,pop_prop_CrI)) %>% 
  rename (`Number of people living in grid cells with >1 modeled cases/year`= total_pop,
          `95% Credible Intervals, CrI` = total_pop_CrI)
grid_pop_adm0_1115 %>% 
  dplyr::arrange(dplyr::desc(`Number of people living in grid cells with >1 modeled cases/year`)) %>% 
  kableExtra::kbl(caption = "Table 10. Number of people living in grid cells with >1 case/year in 2011-2015") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")

# 2016-2020 ----
if(file.exists(paste0(params$output_directory,"/grid_pop_adm0_1620_pop_num.rds"))){
  grid_pop_adm0_1620 <- readRDS(paste0(params$output_directory,"/grid_pop_adm0_1620_pop_num.rds"))
  
} else {
  grid_pop_adm0_1620<-data.frame()
for (row_tmp in 1:nrow(output_adm0_sf_1620)) {

  iso = output_adm0_sf_1620$country[row_tmp]
  
  tmp_country_grid_case_1620 = readRDS(paste0(params$interm_directory,"/",intersect(list.files(path = params$interm_directory,pattern = "_mai_grid_cases_draws.rds"), list.files(path = params$interm_directory,pattern = paste0(iso,"_2016-01-01_2020-12-31"))))) %>% 
    rename(cases = value) %>% 
    data.frame() %>%
    select(!postproc_var)
    
  tmp_country_grid_case_1620_mean_across_draw <- tmp_country_grid_case_1620 %>% 
    group_by(rid,x,y,grid_id,geom) %>% 
    summarize(
      mean_cases = mean(cases)
    )
  
  tmp_country_grid_rate_1620 = readRDS(paste0(params$interm_directory,"/",intersect(list.files(path = params$interm_directory,pattern = "_mai_grid_rates_draws.rds"), list.files(path = params$interm_directory,pattern = paste0(iso,"_2016-01-01_2020-12-31"))))) %>% 
    rename(rates = value) %>% 
    data.frame() %>%
    select(!postproc_var)

# join case and rate rasters by rid, x, y, grid_id, .draw and geom
  grid_pop_adm0_1620_tmp <- inner_join(tmp_country_grid_case_1620,tmp_country_grid_rate_1620,by=c("rid",'x','y',"grid_id",'.draw',"geom")) %>%
    mutate(pop = cases/rates) %>% 
    left_join(tmp_country_grid_case_1620_mean_across_draw,by=c("rid",'x','y',"grid_id","geom")) %>% 
    group_by(.draw) %>% 
    summarize(
      pop_case_1 = sum(pop[mean_cases>1]),
      total_pop = sum(pop),
      pop_prop = pop_case_1/total_pop*100
    )

  grid_pop_adm0_1620<-grid_pop_adm0_1620 %>% dplyr::bind_rows(
    data.frame(
    time_period = "2011-2015",
    country = output_adm0_sf_1620$shapeName[row_tmp],
    total_pop = round(median(grid_pop_adm0_1620_tmp$pop_case_1/10^6),2),
    total_pop_CrI = paste0(round(quantile(grid_pop_adm0_1620_tmp$pop_case_1/10^6,probs=0.025)[[1]],2),"-",round(quantile(grid_pop_adm0_1620_tmp$pop_case_1/10^6,probs=0.975)[[1]],2)),
    pop_prop = round(median(grid_pop_adm0_1620_tmp$pop_prop),2),
    pop_prop_CrI = paste0(round(quantile(grid_pop_adm0_1620_tmp$pop_prop,probs=0.025)[[1]],2),"-",round(quantile(grid_pop_adm0_1620_tmp$pop_prop,probs=0.975)[[1]],2))
    )
  )
  
rm(tmp_country_grid_case_1620)
rm(tmp_country_grid_rate_1620)
invisible(gc())

}
  saveRDS(grid_pop_adm0_1620,paste0(params$output_directory,"/grid_pop_adm0_1620_pop_num.rds"))

}

#make tables
grid_pop_adm0_1620<-grid_pop_adm0_1620 %>% 
  select(!c(pop_prop,pop_prop_CrI)) %>% 
  rename (`Number of people living in grid cells with >1 modeled cases/year`= total_pop,
          `95% Credible Intervals, CrI` = total_pop_CrI)
grid_pop_adm0_1620 %>% 
  dplyr::arrange(dplyr::desc(`Number of people living in grid cells with >1 modeled cases/year`)) %>% 
  kableExtra::kbl(caption = "Table 11. Number of people living in grid cells with >1 case/year in 2016-2020") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")

#print out the median and range for table 10 and 11
print(paste0("The median number of people (million) living in cells with >1 case/year in 2011-2015 is ",round(median(grid_pop_adm0_1115$`Number of people living in grid cells with >1 modeled cases/year`),2)," (",round(min(grid_pop_adm0_1115$`Number of people living in grid cells with >1 modeled cases/year`),2)," - ",round(max(grid_pop_adm0_1115$`Number of people living in grid cells with >1 modeled cases/year`),2),")"))

print(paste0("The median number of people (million) living in cells with >1 case/year in 2016-2020 is ",round(median(grid_pop_adm0_1620$`Number of people living in grid cells with >1 modeled cases/year`),2)," (",round(min(grid_pop_adm0_1620$`Number of people living in grid cells with >1 modeled cases/year`),2)," - ",round(max(grid_pop_adm0_1620$`Number of people living in grid cells with >1 modeled cases/year`),2),")"))

invisible(gc())

```
## Paragraph 3
**2011-2015** 
```{r Results_paragraph_3, echo=FALSE}
mai_ratio_stats_adm2 <-data.frame(readRDS(paste0(params$postprocessed_output_directory,'/mai_ratio_stats.rds'))) %>% 
  dplyr::select(country,admin_level,location_period_id,q2.5,q97.5) %>% 
  dplyr::filter(admin_level == "ADM2") %>% 
  mutate(change_direction = case_when(
    q2.5 > 1 ~ "increase",
    q97.5 < 1 ~ "decrease",
    T ~ "no change"
  )) %>% 
  dplyr::group_by(country,change_direction) %>% 
  dplyr::summarise(total_adm2 = n()) %>% 
  dplyr::filter(!change_direction == "no change") %>%
  dplyr::ungroup() %>% 
  dplyr::group_by(country) %>% 
  dplyr::filter(n()>=2)

print(paste("A total of",length(unique(mai_ratio_stats_adm2$country)), "countries had subnational units with both significant increase and decrease at the ADM2 level."))

# Population living in ADM2 units with significantly increasing or decreasing in irr between the two time periods
# here, using 2016-2020 population to estimate
merge(data.frame(readRDS(paste0(params$postprocessed_output_directory,'/mai_ratio_stats.rds'))) %>% dplyr::filter(admin_level == "ADM2") %>% dplyr::select(!geom),
data.frame(readRDS(paste0(params$postprocessed_output_directory,'/pop_density.rds'))) %>% dplyr::filter(admin_level == "ADM2")  %>% group_by(location_period_id) %>% dplyr::top_n(1),
by=c("country",'admin_level','location_period_id',"shp_id")) %>% 
  mutate(change_direction = case_when(
    q2.5 > 1 ~ "increase",
    q97.5 < 1 ~ "decrease",
    T ~ "no change"
  )) %>% 
  dplyr::filter(!change_direction == 'no change') %>% 
  dplyr::group_by(change_direction) %>% 
  dplyr::summarise(
    total_pop_millions = sum(pop)/10^6
  ) %>% 
  kableExtra::kbl(caption = "Table 12. Population living in ADM2 units with significantly increasing/decreasing incidence rate between the two periods") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::scroll_box(width = "100%")

invisible(gc())

```

## Paragraph 4
**Table 13. Population at risk, 2011-2015** 
```{r Results_paragraph_4, echo=FALSE}
risk_cat_map <- taxdat:::get_risk_cat_dict()
names(risk_cat_map) <- janitor::make_clean_names(risk_cat_map) %>% 
  str_remove("x")
    
readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_pop_at_risk_all.rds')) %>% 
  dplyr:: mutate(
    risk_cat = str_extract(variable, str_c(rev(names(risk_cat_map)), collapse = "|")),
    `Risk category (per 100,000 population) ` = risk_cat_map[risk_cat] %>% factor(levels = risk_cat_map),
    admin_level = str_c("ADM", str_extract(variable, "(?<=adm)[0-9]+")),
    `mean (millions)` = round(mean/10^6,0),
    `95% PI (millions)` = paste0(round(q2.5/10^6,0),"-", round(q97.5/10^6,0))
      ) %>% 
  subset(
    admin_level == "ADM2"
  ) %>% 
  dplyr::select(
    `Risk category (per 100,000 population) `, `mean (millions)`, `95% PI (millions)` 
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

invisible(gc())

```

**Table 14. Population at risk, 2016-2020**
```{r Results_paragraph_4_2016-2020, echo=FALSE}
readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_pop_at_risk_all.rds')) %>% 
  dplyr:: mutate(
    risk_cat = str_extract(variable, str_c(rev(names(risk_cat_map)), collapse = "|")),
    `Risk category (per 100,000 population) ` = risk_cat_map[risk_cat] %>% factor(levels = risk_cat_map),
    admin_level = str_c("ADM", str_extract(variable, "(?<=adm)[0-9]+")),
    `mean (millions)` = round(mean/10^6,0),
    `95% PI (millions)` = paste0(round(q2.5/10^6,0),"-", round(q97.5/10^6,0))
      ) %>% 
  subset(
    admin_level == "ADM2"
  ) %>% 
  dplyr::select(
    `Risk category (per 100,000 population) `, `mean (millions)`, `95% PI (millions)` 
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

invisible(gc())

```

**Table 15. Population at risk by region. 2011-2015**
```{r Results_paragraph_4_risk_by_region_1115, echo=FALSE}
readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_pop_at_risk_by_region.rds')) %>% 
  dplyr:: mutate(
    region = str_extract(variable, str_c(c("central_africa","eastern_africa","southern_africa","western_africa"), collapse = "|")),
    risk_cat = str_extract(variable, str_c(rev(names(risk_cat_map)), collapse = "|")),
    `Risk category (per 100,000 population) ` = risk_cat_map[risk_cat] %>% factor(levels = risk_cat_map),
    admin_level = str_c("ADM", str_extract(variable, "(?<=adm)[0-9]+")),
    `mean (millions)` = round(mean/10^6,0),
    `95% PI (millions)` = paste0(round(q2.5/10^6,0),"-", round(q97.5/10^6,0))
      ) %>% 
  subset(
    admin_level == "ADM2"
  ) %>% 
  dplyr::select(
    region, `Risk category (per 100,000 population) `, `mean (millions)`, `95% PI (millions)` 
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

invisible(gc())

```

**Table 16. Population at risk by region. 2016-2020**
```{r Results_paragraph_4_risk_by_region_1620, echo=FALSE}
readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_pop_at_risk_by_region.rds')) %>% 
  dplyr:: mutate(
    region = str_extract(variable, str_c(c("central_africa","eastern_africa","southern_africa","western_africa"), collapse = "|")),
    risk_cat = str_extract(variable, str_c(rev(names(risk_cat_map)), collapse = "|")),
    `Risk category (per 100,000 population) ` = risk_cat_map[risk_cat] %>% factor(levels = risk_cat_map),
    admin_level = str_c("ADM", str_extract(variable, "(?<=adm)[0-9]+")),
    `mean (millions)` = round(mean/10^6,0),
    `95% PI (millions)` = paste0(round(q2.5/10^6,0),"-", round(q97.5/10^6,0))
      ) %>% 
  subset(
    admin_level == "ADM2"
  ) %>% 
  dplyr::select(
    region, `Risk category (per 100,000 population) `, `mean (millions)`, `95% PI (millions)` 
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

invisible(gc())

```

**Table 17. Population at high risk by time period**
```{r Results_paragraph_4_high_risk_by_time_period, echo=FALSE}
readRDS(paste0(params$postprocessed_output_directory,'/pop_high_risk_all_stats.rds')) %>% 
  mutate(
    `Population at high risk (millions)` = round(mean/10^6,0),
    `95% PI (millions)` = paste0(round(q025/10^6,0),"-",round(q975/10^6,0)),
    `Time period` = period
  ) %>% 
  select(
    `Time period`,`Population at high risk (millions)`,`95% PI (millions)`
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

invisible(gc())

```

**Table 18. Population at high risk by region by time period**
```{r Results_paragraph_4_high_risk_by_time_period_by_region, echo=FALSE}
readRDS(paste0(params$postprocessed_output_directory,'/pop_high_risk_region_stats.rds')) %>% 
  mutate(
    `Population at high risk (millions)` = round(mean/10^6,0),
    `95% PI (millions)` = paste0(round(q025/10^6,0),"-",round(q975/10^6,0)),
    `Africa region` = AFRO_region,
    `Time period` = period
  ) %>% 
  select(
    `Time period`,`Africa region`,`Population at high risk (millions)`,`95% PI (millions)`
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

invisible(gc())

```

**Table 19. % of adm2 at high risk by time periods**
```{r Results_paragraph_4_high_risk_by_country, echo=FALSE}
## The same object/stats as Figure 4B
output_endemicity<-readRDS(paste0(params$postprocessed_output_directory,'/endemicity.rds')) 
summary_high_risk_either_period <- output_endemicity %>% 
  ungroup() %>% 
  group_by(endemicity) %>% 
  summarise(pop = round(sum(pop)/10^6,1),
            adm2_prop = round(100*length(unique(location_period_id))/nrow(output_endemicity),1),
            total_country = length(unique(country))) %>% 
  filter(endemicity == "history of high risk")

print(paste(summary_high_risk_either_period$pop,"million people across",summary_high_risk_either_period$adm2_prop,"% of adm2 units in",summary_high_risk_either_period$total_country,"countries living in adm2 units with a history of high risk"))

# % adm2 at high risk by country
readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_risk_categories.rds')) %>% 
      st_drop_geometry() %>% 
  dplyr::filter(admin_level == "ADM2") %>% 
  dplyr::mutate(high_risk = ifelse(risk_cat %in% c('1-10','<1'),FALSE, TRUE)) %>% 
  dplyr::group_by(country) %>% 
  dplyr::summarise(highrisk_adm2_units = 100 * length(high_risk[high_risk==TRUE])/n()) %>% 
  dplyr::mutate(time_period = '2011-2015') %>% 
  dplyr::bind_rows(
    readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_risk_categories.rds')) %>% 
      st_drop_geometry() %>% 
  dplyr::filter(admin_level == "ADM2") %>% 
  dplyr::mutate(high_risk = ifelse(risk_cat %in% c('1-10','<1'),FALSE, TRUE)) %>% 
  dplyr::group_by(country) %>% 
  dplyr::summarise(highrisk_adm2_units = 100 * length(high_risk[high_risk==TRUE])/n()) %>% 
  dplyr::mutate(time_period = '2016-2020')
  ) %>% 
  dplyr::rename(`% of high-risk adm2 units` = highrisk_adm2_units)  %>% 
  dplyr::select(
    time_period, country, `% of high-risk adm2 units`
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

# across all country summary:
summary_pop_risk_adm2_1115 <- readRDS(paste0(params$postprocessed_output_directory,'/2011_2015_risk_categories.rds')) %>% 
      st_drop_geometry() %>% 
  dplyr::filter(admin_level == "ADM2") %>% 
  dplyr::mutate(high_risk = ifelse(risk_cat %in% c('1-10','<1'),FALSE, TRUE)) %>% 
  dplyr::summarise(highrisk_adm2_units = 100 * length(high_risk[high_risk==TRUE])/n(),
                   country_prop = 100 * length(unique(country[high_risk]))/43,
                   total_country = length(unique(country[high_risk])))

print(paste("Between 2011-2015, there are", round(summary_pop_risk_adm2_1115$highrisk_adm2_units,4),"% of adm2 units in the high risk category (>10 per 100000) among ", round(summary_pop_risk_adm2_1115$country_prop,4),"% countries(",summary_pop_risk_adm2_1115$total_country,"/43)."))

summary_pop_risk_adm2_1620 <- readRDS(paste0(params$postprocessed_output_directory,'/2016_2020_risk_categories.rds')) %>% 
      st_drop_geometry() %>% 
  dplyr::filter(admin_level == "ADM2") %>% 
  dplyr::mutate(high_risk = ifelse(risk_cat %in% c('1-10','<1'),FALSE, TRUE)) %>% 
  dplyr::summarise(highrisk_adm2_units = 100 * length(high_risk[high_risk==TRUE])/n(),
                   country_prop = 100 * length(unique(country[high_risk]))/43,
                   total_country = length(unique(country[high_risk])))

print(paste("Between 2016-2020, there are", round(summary_pop_risk_adm2_1620$highrisk_adm2_units,4),"% of adm2 units in the high risk category (>10 per 100000) among ", round(summary_pop_risk_adm2_1620$country_prop,4),"% countries(",summary_pop_risk_adm2_1620$total_country,"/43)."))

invisible(gc())

```

**Table 20. % of adm2 at high risk in both time periods (sustained high cholera risk)**
```{r Results_paragraph_4_high_risk_both_time_periods_by_country, echo=FALSE}
# population living in regions with sustained high cholera risk by country
table20<- output_endemicity %>% # output endemicity is from endemicity object in 4B
  dplyr::group_by(country) %>% 
  dplyr::summarise(highrisk_adm2_units = 100 * length(endemicity[endemicity=="sustained high risk"])/n(),
                   highrisk_adm2_units_number = length(endemicity[endemicity=="sustained high risk"]),
                   total_adm_units = n()) %>% 
  select(country,highrisk_adm2_units,highrisk_adm2_units_number,total_adm_units)

table20 %>% 
  bind_rows(
    data.frame(
    country = "All country",
    highrisk_adm2_units_number = sum(table20$highrisk_adm2_units_number),
    total_adm_units = sum(table20$total_adm_units)      
    ) %>% 
      mutate(
        highrisk_adm2_units = round(100 * highrisk_adm2_units_number/total_adm_units,2),
      )
  ) %>% 
  dplyr::rename(`% of adm2 units at high-risk in both periods` = highrisk_adm2_units,
                `Number of adm2 units at high-risk in both periods` = highrisk_adm2_units_number,
                `Total number of adm2 units` = total_adm_units) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

summary_both_high_risk_adm2_1120 <- output_endemicity %>% 
  dplyr::ungroup() %>% 
  dplyr::summarise(bothhighrisk_adm2_units = 100 * length(endemicity[endemicity=="sustained high risk"])/n(),
                   country_prop = 100 * length(unique(country[endemicity=="sustained high risk"]))/43,
                   total_country = length(unique(country[endemicity=="sustained high risk"])))

print(paste("There are", round(summary_both_high_risk_adm2_1120$bothhighrisk_adm2_units,4),"% of the adm2 units in high risk category (>10 per 100000) for both time periods and they are concentrated in ",round(summary_both_high_risk_adm2_1120$country_prop,4),"% (",summary_both_high_risk_adm2_1120$total_country,"/43)of the countries."))

invisible(gc())

```