---
title: "Data Comparison Report"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
params:
  config: "Analysis/configs/production_tests/Dev_nocovar/2015_2019_country/config_AGO_2015_2019.yml" #change this parameter accordingly 
  cholera_directory: "/home/kaiyuezou/mapping_pipeline/dev_production/cholera-mapping-pipeline" #change this parameter accordingly 
  local_output_dir: "" #this is the absolute directory of model output if a folder other than "data" is used to store the output 
  credential_directory: ""
  args: 'run-comparison'
  filter_zeros: 'FALSE'
  cut_across_year_observations: 'FALSE'
  period_OC_divided_by_timelength: 'TRUE'
  OC_filter: ''
  daily_daily_obs_disagree_threshold: '0'
  daily_period_obs_disagree_threshold: '0'
  report_testing: 'FALSE'
  fake_OCs: '3'
  fake_OCs_daily: '1'
  
---
# Data comparison summary for `r stringr::str_extract(params$config, "[A-Z]{3}")` and period `r stringr::str_extract(params$config, "[0-9]{4}_[0-9]{4}")`

```{r eval=FALSE, include=FALSE}
### 9/27/2021 Temporary plan: detect all the discrepancies and plot the figures if they appear in any of the location-times
###   If there are discrepancies, we think they're all imperfect descriptions of what the real data looks like
###   Describe simply how different sources agree and disagree, plot the only times when they apprear side by side
###   No need for the whole time axis, no need for the cumulative incidences. 
###   Rectangles should be divided by the length of period of time. 
###   By location, not by location period. 
### 10/12/2021 New updates
### 10/20/2021 New updates -- added OC filter and discrepancy threshold
### 10/26/2021 New updates -- tailored it for TZA mainland and considered situation when OCs are not specified
### 10/28/2021 New updates -- generalized to all situations when period OCs or daily OCs might be absent
### 10/29/2021 New updates -- added more descriptive sentences
### 10/30/2021 New updates -- considered the situation where there is only one kind of OC_UID for daily OCs
### 10/31/2021 New updates -- considered zero row situation for the zeros filtering process 
### 11/23/2021 New updates -- added figures for stan input
### 11/30/2021 New updates -- added a table that can summerize #observations 
### 12/6/2021 New updates -- added options to indicate whether filter zeros, whether seperate multi-year observations; 
###                          also added seperate figures just to plot multi-year observations            
### 12/7/2021 New updates -- fixed more bugs
### 12/15/2021 New updates -- added figures that only facet on location_name
### 12/22/2021 New updates -- fixed the disagreement error, added more to the summary table
### 02/17/2022 New updates -- fixed ZNZ issue; fixed plot height issue
### 02/23/2022 New updates -- fixed the comparison table 3.  
### 05/11/2022 New updates -- added new table and plotted dropped observations 
### 05/13/2022 New updates -- added back table 5 to distinguish partially and fully dropped observation collections 
### 06/3/2022 New updates -- fixed some small error related to taxonomy data

```



```{r setup, include=FALSE}
library(lubridate)
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(taxdat)
library(sf)
library(Cairo)
Sys.setlocale("LC_ALL","English")

```



```{r warning=FALSE, include=FALSE}
# Load config
config <- paste0(params$cholera_directory, "/", params$config) %>% yaml::read_yaml() #get the config file
files <- taxdat::get_filenames(config, params$cholera_directory)
if(!is.null(params$local_output_dir) & nchar(params$local_output_dir) > 1){
  files <- unlist(lapply(names(files), function(file){
                  gsub("^.*?/Analysis/data", params$local_output_dir, files[file])
                  }))
}

# Load taxonomy_data, raw_data, and stan_input_data
time_left <- as.Date(config$start_time)
time_right <- as.Date(config$end_time)
if(is.null(params$credential_directory) | length(params$credential_directory) <= 1){
  credential_directory <- paste0(params$cholera_directory, "/Analysis/R/database_api_key.R")
}
source(credential_directory)
taxonomy_data <- taxdat::pull_taxonomy_data(username = taxonomy_username, password = taxonomy_password, 
                                            locations = as.numeric(config$countries), time_left = time_left, time_right = time_right, 
                                            source = 'sql')
rm(taxonomy_username)
rm(taxonomy_password)
taxonomy_data <- taxonomy_data %>% 
  mutate(year = lubridate::year(time_left))


raw_data <- taxdat::read_file_of_type(files["data"], "sf_cases") %>% 
  mutate(year = lubridate::year(TL))

stan_input <- taxdat::read_file_of_type(files["stan_input"], "stan_input")

stan_input_data <- stan_input$sf_cases_resized %>% 
  rename(cases = `attributes.fields.suspected_cases`) %>% 
  mutate(obs = row_number() %>% factor())

# Get the pre-defined parameters into the environment
filter_zeros <- as.logical(params$filter_zeros)
cut_across_year_observations <- as.logical(params$cut_across_year_observations)
period_OC_divided_by_timelength = as.logical(params$period_OC_divided_by_timelength)
report_testing = as.logical(params$report_testing)
fake_OCs = as.numeric(params$fake_OCs)
fake_OCs_daily = as.numeric(params$fake_OCs_daily)

if (!is.null(params$OC_filter) & (nchar(params$OC_filter) > 0 & !identical(params$OC_filter, ' '))) {OC_vector = as.character(as.numeric(strsplit(params$OC_filter, ',')[[1]]))} #a vector of characters
daily_daily_obs_disagree_threshold <- as.numeric(params$daily_daily_obs_disagree_threshold)
daily_period_obs_disagree_threshold <- as.numeric(params$daily_period_obs_disagree_threshold)

```



## Table 1. Parameter settings for this report
```{r echo=FALSE, warning=FALSE}
if (exists('OC_vector')) { OC_vector_for_table <- OC_vector } else { OC_vector_for_table <- 'ALL' }

params_setting = tibble::tibble(params_name = c('Whether filtered out zeros: ', 
                                                'Whether divided observations that span across multiple years: ', 
                                                'Period observations are divided by their time length: ', 
                                                'Observation collections specified: ', 
                                                'The daily vs. daily observations disagreement threshold: ', 
                                                'The daily vs. period observations disagreement threshold: '), 
                                params_value = c(filter_zeros, cut_across_year_observations, 
                                                 period_OC_divided_by_timelength, 
                                                 OC_vector_for_table, 
                                                 daily_daily_obs_disagree_threshold, 
                                                 daily_period_obs_disagree_threshold))

params_setting %>%
  kableExtra::kable(col.names = c('Parameter Names', 'Parameter Values')) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = T)

```



## Table 2. Summary table for the pre-processed dataset
```{r echo=FALSE, warning=FALSE}
print(paste0("There are ", sum(is.na(raw_data$locationPeriod_id)), " NA for location period in the pre-processed data. "))
NA_cases <- sum(raw_data[is.na(raw_data$locationPeriod_id), ]$suspected_cases, na.rm = T)
NA_obs <- nrow(raw_data[is.na(raw_data$locationPeriod_id), ])
NA_ocs <- length(unique(raw_data[is.na(raw_data$locationPeriod_id), ]$OC_UID))
non_NA_ocs <- unique(raw_data[is.na(raw_data$locationPeriod_id), ]$OC_UID)
non_NA_ocs2 <- non_NA_ocs[!all(is.na(raw_data[raw_data$OC_UID %in% non_NA_ocs, ]$locationPeriod_id))]
print(paste0("These NA location periods correspond to ", NA_cases, " cases and ", NA_obs, " observations and ", NA_ocs, " OC in the pre-processed data. "))
if(length(non_NA_ocs) > 0){
  print(paste0("Among the OC with NA location periods, including ", paste(non_NA_ocs, collapse = ', '), ", the following are those with non-NA location periods: ", paste(non_NA_ocs2, collapse = ', ')))
}

sum_obs <- raw_data %>%
  sf::st_drop_geometry() %>% 
  group_by(year) %>%
  summarise(observation = n(), 
            cases = sum(suspected_cases, na.rm = TRUE), 
            location_period = length(unique(locationPeriod_id)),
            all_location_period = paste(unique(locationPeriod_id), collapse = ', '), 
            oc = length(unique(OC_UID)), 
            all_oc = paste(unique(OC_UID), collapse = ', '))

sum_obs %>%
  kableExtra::kable(col.names = c("Year", "#observations", "#suspected cases", "#location-periods", "location-periods", 
                                  "#observation collections", "observation collections")) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = F)
rm(sum_obs)

```



## Table 3. Summary table for the dataset directly drawn from taxonomy database
```{r echo=FALSE, warning=FALSE}
print(paste0("There are ", sum(is.na(taxonomy_data$location_period_id)), " NA for location period in the dataset from taxonomy database. "))
NA_cases <- sum(taxonomy_data[is.na(taxonomy_data$location_period_id), ]$suspected_cases, na.rm = T)
NA_obs <- nrow(taxonomy_data[is.na(taxonomy_data$location_period_id), ])
NA_ocs <- length(unique(taxonomy_data[is.na(taxonomy_data$location_period_id), ]$observation_collection_id))
non_NA_ocs <- unique(taxonomy_data[is.na(taxonomy_data$location_period_id), ]$observation_collection_id)
non_NA_ocs2 <- non_NA_ocs[!all(is.na(taxonomy_data[taxonomy_data$observation_collection_id %in% non_NA_ocs, ]$location_period_id))]
print(paste0("These NA location periods correspond to ", NA_cases, " cases and ", NA_obs, " observations and ", NA_ocs, " OC in the dataset from taxonomy database. "))
if(length(non_NA_ocs) > 0){
  print(paste0("Among the OC with NA location periods, including ", paste(non_NA_ocs, collapse = ', '), ", the following are those with non-NA location periods: ", paste(non_NA_ocs2, collapse = ', ')))
}

sum_obs <- sf::st_drop_geometry(taxonomy_data) %>% 
  mutate(OC_UID = observation_collection_id, 
         locationPeriod_id = location_period_id, 
         year = lubridate::year(time_left)) %>% 
  select(year, suspected_cases, locationPeriod_id, OC_UID) %>% 
  group_by(year) %>%
  summarise(num_observations = n(), 
            num_cases = sum(suspected_cases, na.rm = TRUE), 
            num_locationPeriod_id = length(unique(locationPeriod_id)), 
            all_locationPeriod_id = paste(unique(locationPeriod_id), collapse = ', '), 
            num_OC_UID = length(unique(OC_UID)), 
            all_OC_UID = paste(unique(OC_UID), collapse = ', '))

sum_obs %>%
  kableExtra::kable(col.names = c("Year", "#observations", "#suspected cases", "#location-periods", "location-periods", 
                                  "#observation collections", "observation collections")) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = F)
rm(sum_obs)

```



## Table 4. Summary table for the difference between pre-processed dataset and the dataset directly drawn from taxonomy
### Noted: the dropped observation collections listed below may be or not be fully dropped
```{r echo=FALSE, warning=FALSE}
# try to get the diff dataframe
taxonomy_data_ori <- taxonomy_data

diff_id <- setdiff(taxonomy_data$id, raw_data$id)
taxonomy_data_compare <- taxonomy_data %>% 
  mutate(OC_UID = observation_collection_id, 
         locationPeriod_id = location_period_id, 
         year = lubridate::year(time_left)) %>% 
  select(id, year, suspected_cases, locationPeriod_id, OC_UID)
diff_df <- taxonomy_data_compare[taxonomy_data_compare$id %in% diff_id, ]

taxonomy_data <- sf::st_drop_geometry(taxonomy_data) %>%
  rename(OC_UID = observation_collection_id, TL = time_left, TR = time_right, locationPeriod_id = location_period_id) %>%
  mutate(dropped = ifelse(id %in% diff_id, TRUE, FALSE)) %>% 
  select(id, year, OC_UID, TL, TR, suspected_cases, location_name, location_id, locationPeriod_id, dropped)

diff_df <- sf::st_drop_geometry(diff_df) %>% 
  dplyr::group_by(year, OC_UID, locationPeriod_id) %>%
  dplyr::summarise(dropped_obs = n(), dropped_cases = sum(suspected_cases, na.rm = T))

diff_df %>%
  kableExtra::kable(col.names = c("Year", "dropped observation collections", "dropped location-periods", 
                                  "dropped observations", "dropped cases")) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = F)

```


## Table 5. Summary table for --fully-- dropped location periods and observation collections 
```{r echo=FALSE, warning=FALSE}
sum_obs1 <- sf::st_drop_geometry(raw_data) %>% 
  select(year, suspected_cases, locationPeriod_id, OC_UID) %>% 
  group_by(year) %>%
  summarise(num_observations = n(), 
            num_cases = sum(suspected_cases, na.rm = TRUE), 
            num_locationPeriod_id = length(unique(locationPeriod_id)), 
            num_OC_UID = length(unique(OC_UID)))

sum_obs2 <- sf::st_drop_geometry(taxonomy_data) %>% #QZ: remove the mutate code part
  select(year, suspected_cases, locationPeriod_id, OC_UID) %>% 
  group_by(year) %>%
  summarise(num_observations = n(), 
            num_cases = sum(suspected_cases, na.rm = TRUE), 
            num_locationPeriod_id = length(unique(locationPeriod_id)), 
            num_OC_UID = length(unique(OC_UID)))

if(sum(!sum_obs2$year %in% sum_obs1$year) > 0){
  for (years in sum_obs2$year[!sum_obs2$year %in% sum_obs1$year]){
    sum_obs1 <- sum_obs1 %>%
      add_row(year = years,
              num_observations = 0, 
              num_cases = 0, 
              num_locationPeriod_id = 0, 
              num_OC_UID = 0)
  }
}

sum_obs <- tibble::tibble(
  year = sum_obs2$year, 
  num_observations = sum_obs2$num_observations - sum_obs1$num_observations, 
  num_cases = sum_obs2$num_cases - sum_obs1$num_cases, 
  num_locationPeriod_id = sum_obs2$num_locationPeriod_id - sum_obs1$num_locationPeriod_id, 
  num_OC_UID = sum_obs2$num_OC_UID - sum_obs1$num_OC_UID
)

dropped_locationPeriod_id <- c()
dropped_OC_UID <- c()
for (years in sum_obs2$year){
  list1 <- unique(raw_data[raw_data$year == years, ]$locationPeriod_id)
  list2 <- unique(taxonomy_data_ori[taxonomy_data_ori$year == years, ]$location_period_id)
  if(length(setdiff(list2, list1)) == 0){
    dropped_locationPeriod_id <- c(dropped_locationPeriod_id, "0")
  }else{
    dropped <- paste(setdiff(list2, list1), collapse = ', ')
    dropped_locationPeriod_id <- c(dropped_locationPeriod_id, dropped)
  }
  
  list1 <- unique(raw_data[raw_data$year == years, ]$OC_UID)
  list2 <- unique(taxonomy_data_ori[taxonomy_data_ori$year == years, ]$observation_collection_id)
  if(length(setdiff(list2, list1)) == 0){
    dropped_OC_UID <- c(dropped_OC_UID, "0")
  }else{
    dropped <- paste(setdiff(list2, list1), collapse = ', ')
    dropped_OC_UID <- c(dropped_OC_UID, dropped)
  }
}
sum_obs$dropped_locationPeriod_id <- dropped_locationPeriod_id
sum_obs$dropped_OC_UID <- dropped_OC_UID

sum_obs <- sum_obs %>% 
  select(year, num_observations, num_cases, num_locationPeriod_id, dropped_locationPeriod_id, num_OC_UID, dropped_OC_UID)

sum_obs %>%
  kableExtra::kable(col.names = c("Year", "#dropped observations", "#dropped cases", "#dropped location-periods", 
                                  "dropped location-periods", "#dropped observation collections", "dropped observation collections")) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
  kableExtra::kable_paper(full_width = F)

rm(sum_obs)
rm(sum_obs1)
rm(sum_obs2)
rm(taxonomy_data_ori)

```



```{r warning=FALSE, include=FALSE}
##filter out the unnecessary OCs
if (exists('OC_vector')) {raw_data <- subset(raw_data, as.character(OC_UID) %in% OC_vector)}

##prepare for all-zero situations
if(filter_zeros){
  raw_data[, "first_non0"] <- NA
  raw_data[, "last_non0"] <- NA
  for (locations in unique(raw_data$location_name)){
    for (years in unique(raw_data$year)){
      if (length(raw_data[raw_data$location_name == locations 
                    & raw_data$year == years, ]$suspected_cases) == 0){}
      else if (sum(raw_data[raw_data$location_name == locations 
                    & raw_data$year == years, ]$suspected_cases) == 0){
        raw_data <- raw_data[- which(raw_data$location_name == locations 
                              & raw_data$year == years), ]
        if (!exists('fig1_ncol_factor')) {fig1_ncol_factor <- 1}
                }
    }
  }
}



##discard geom and look into multi-year observations
raw_data <- sf::st_drop_geometry(raw_data)

raw_across_year_data_temp <- raw_data %>% 
  mutate(TL_year = as.numeric(format(as.Date(TL), format="%Y")), TR_year = as.numeric(format(as.Date(TR), format="%Y")))

if(any(raw_across_year_data_temp$TL_year != raw_across_year_data_temp$TR_year)){
  
  rm(raw_across_year_data_temp)
  across_year_indicator <- TRUE

  #deal with observations spanning cross two or multiple year seperately 
  raw_across_year_data_filtered <- raw_data %>% 
    mutate(TL_year = as.numeric(format(as.Date(TL), format="%Y")), TR_year = as.numeric(format(as.Date(TR), format="%Y"))) %>% 
    filter(!is.na(suspected_cases)) %>% 
    filter(TL_year != TR_year) %>% 
    mutate(year = paste0(TL_year, '-', TR_year)) 
    
  #cut the multi-year observations into seperate years and then reconnect
  if(cut_across_year_observations){
    raw_across_year_data_cut <- raw_data %>% 
      mutate(TL_year = as.numeric(format(as.Date(TL), format="%Y")), TR_year = as.numeric(format(as.Date(TR), format="%Y"))) %>% 
      filter(TL_year != TR_year) %>% 
      mutate(year_num = TR_year - TL_year + 1) %>% 
      group_by_all() %>% 
      tidyr::expand(year_count = seq(1:year_num)) %>% 
      mutate(year = TL_year - 1 + year_count) %>% #the updated year variable
      mutate(period_length = abs(as.numeric(difftime(TL, TR, units = "days")))) %>% 
      mutate(first_year = as.numeric(year == TL_year), 
            last_year = as.numeric(year == TR_year), 
            middle_year = as.numeric(year > TL_year & year < TR_year)) %>% 
      mutate(year_length = 365 + as.numeric(year %% 4 == 0)) %>% 
      mutate(time_fraction = case_when( first_year == 1 ~ ( year_length - abs(as.numeric(difftime(TL, paste0(year, '-01-01'), units = "days"))) ) / period_length,
                                        middle_year == 1 ~ year_length / period_length,
                                        last_year == 1 ~ ( abs(as.numeric(difftime(TL, paste0(year, '-01-01'), units = "days"))) + 1 ) / period_length, 
                                        TRUE ~ 1                                                                                                                    )) %>% 
      mutate(suspected_cases = suspected_cases * time_fraction) %>%
      ungroup() %>% 
      select(-TL_year, -TR_year, -year_num, -year_count, -period_length, -first_year, -last_year, -middle_year, -year_length, -time_fraction)

    raw_data <- raw_data %>% 
      mutate(TL_year = as.numeric(format(as.Date(TL), format="%Y")), TR_year = as.numeric(format(as.Date(TR), format="%Y"))) %>% 
      filter(TL_year == TR_year) %>% 
      select(-TL_year, -TR_year)
    
    raw_data <- rbind(raw_data, raw_across_year_data_cut)
  }
  
}else{across_year_indicator <- FALSE}



##filter out the zeros or not
if(filter_zeros){
  raw_data_filtered <- raw_data %>% 
    group_by(location_name, year) %>% 
    arrange(TL, OC_UID) %>% 
    mutate( first_non0 = case_when(
              id == id[ (match((suspected_cases[suspected_cases > 0])[1], suspected_cases))[1] ] ~ 1,
              TRUE ~ 0)
          ) %>% 
    arrange(desc(TR, OC_UID)) %>% 
    mutate( last_non0 = case_when(
              id == id[ (match((suspected_cases[suspected_cases > 0])[1], suspected_cases))[1] ] ~ 1,
              TRUE ~ 0)
          ) %>%
    arrange(TL, OC_UID) %>%  
    mutate( between_non0s = case_when(
              id %in% id[min(which(first_non0 == 1)) : max(which(last_non0 == 1))] ~ 1, 
              TRUE ~ 0)
          ) %>% 
    filter(between_non0s == 1) %>% 
    select(-first_non0, -last_non0, -between_non0s)

  raw_data <- raw_data_filtered #this is important because in the code below these two datasets are used interchangably

}else{raw_data_filtered <- raw_data}

    

##do we need to create the fake data? 
if (report_testing & (length(unique(raw_data_filtered$OC_UID)) == 1)){
  #let's create fake data!
  set.seed(20211007)
  random_number = sample(seq(fake_OCs), fake_OCs_daily)
  real_OC_UID = unique(raw_data_filtered$OC_UID)

  for (i in seq(fake_OCs)) {
    OC_UID_temp = paste0('fake_data', as.character(i))
    for (locations in unique(raw_data_filtered$location_name)){
      for (years in unique(raw_data_filtered$year)){
        raw_data_filtered <- raw_data_filtered %>% 
          ungroup() %>% 
          add_row(OC_UID = OC_UID_temp,
                  TL = sample(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL, 1),
                  TR = sample(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL, 1),
                  location_name = locations,
                  suspected_cases = runif(1)*rpois(1, sum(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$suspected_cases)),
                  year = raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$year[1])
        
        raw_data_filtered <- raw_data_filtered %>% 
          mutate(TL = case_when(OC_UID == OC_UID_temp & TL > TR ~ TR,
                                TRUE ~ TL),
                TR = case_when(OC_UID == OC_UID_temp & TL >= TR ~ sample( seq(as.Date(raw_data_filtered[raw_data_filtered$OC_UID == OC_UID_temp & raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL),
                                                                              as.Date(max(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL)), 
                                                                              by="days"), 
                                                                          1 ),
                                TRUE ~ TR))
      }
    } 
    if (i == random_number){
      indices <- as.numeric(row.names(raw_data_filtered[raw_data_filtered$OC_UID == sample(real_OC_UID, 1),]))
      sampled_indices <- sample(indices, sample(seq(length(indices)), 1))            
      
      raw_data_filtered <- raw_data_filtered %>% 
        ungroup() %>% 
        add_row(OC_UID = rep(OC_UID_temp, length(sampled_indices)),
                TL     = raw_data_filtered$TL[sampled_indices],
                TR     = raw_data_filtered$TR[sampled_indices],
                location_name = raw_data_filtered$location_name[sampled_indices],
                suspected_cases = runif(1, 1, 2) * raw_data_filtered$suspected_cases[sampled_indices],
                year   = raw_data_filtered$year[sampled_indices])
    }
  }

}

```



## Fig 1. Overall figure -- all observations by location only
**This comprehensive figure includes all (or specified) pre-processed observations. **
**The daily-based observations are represented in vertical lines **
**The period-based observations are represented in rectangles **
```{r echo=FALSE}
fig1_ncol_factor <- 1 
fig1_height_factor <- 5 * length(unique(raw_data_filtered$location_name)) / fig1_ncol_factor

if (period_OC_divided_by_timelength) {
  print('The rectangles represent daily-averaged cases (total cases/length of period). ')
  }else{print('The rectangles represent total cases over periods. ')}

```

```{r echo=FALSE, fig.height=as.numeric(fig1_height_factor), fig.width=10}
if ( (nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) == 0 | 
      nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) == 0)  ){
  
  if ( nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) == 0 ){
      
    raw_data_filtered %>% 
      filter(TR == TL) %>%
      ggplot(aes(colour = OC_UID)) + 
      geom_segment( aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point( aes(x=ymd(TL), y=suspected_cases),
                  size = 0.7, alpha=0.5, shape=23) +
      scale_x_date(date_labels = "%m-%Y") + 
      facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
    
  } else if ( nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) == 0 ){
  
    if (period_OC_divided_by_timelength){
      raw_data_filtered %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                      colour = OC_UID),
                  fill = NA, size = 0.35 * fig1_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        scale_x_date(date_labels = "%m-%Y") + 
        ylab('Average Daily Cases') + 
        facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
        theme_bw()
    } else{
      raw_data_filtered %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/1, 
                      colour = OC_UID),
                  fill = NA, size = 0.35 * fig1_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        scale_x_date(date_labels = "%m-%Y") + 
        labs(y = 'Total Cases over Period') + 
        facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
        theme_bw()
    }  
    
  }
  
} else {
        
  if (period_OC_divided_by_timelength){
    raw_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                    colour = OC_UID),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      scale_x_date(date_labels = "%m-%Y") + 
      labs(y = 'Average Daily Cases') + 
      facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
  } else{
    raw_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/1, 
                    colour = OC_UID),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      scale_x_date(date_labels = "%m-%Y") + 
      labs(y = 'Total Cases for Period OC and Daily Cases for Daily OC') + 
      facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
  }
}

```



## Fig 2. Overall figure -- all observations with dropped cases denoted
**This comprehensive figure includes all (or specified) taxonomy observations. **
**The dropped taxonomy observations are denoted in dashed lines **
**The daily-based observations are represented in vertical lines **
**The period-based observations are represented in rectangles **
```{r echo=FALSE}
fig2_ncol_factor <- 1 
fig2_height_factor <- 5 * length(unique(taxonomy_data$location_name)) / fig2_ncol_factor

if (period_OC_divided_by_timelength) {
  print('The rectangles represent daily-averaged cases (total cases/length of period). ')
  }else{print('The rectangles represent total cases over periods. ')}

```

```{r echo=FALSE, fig.height=as.numeric(fig2_height_factor), fig.width=10}
if ( (nrow(taxonomy_data[taxonomy_data$TL != taxonomy_data$TR, ]) == 0 | 
      nrow(taxonomy_data[taxonomy_data$TL == taxonomy_data$TR, ]) == 0)  ){
  
  if ( nrow(taxonomy_data[taxonomy_data$TL != taxonomy_data$TR, ]) == 0 ){
      
    taxonomy_data %>% 
      filter(TR == TL) %>%
      ggplot(aes(colour = OC_UID)) + 
      geom_segment( aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases, group = dropped, linetype = dropped), 
                    size=0.3, alpha=0.5) + 
      geom_point( aes(x=ymd(TL), y=suspected_cases),
                  size = 0.7, alpha=0.5, shape=23) +
      scale_x_date(date_labels = "%m-%Y") + 
      facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
    
  } else if ( nrow(taxonomy_data[taxonomy_data$TL == taxonomy_data$TR, ]) == 0 ){
  
    if (period_OC_divided_by_timelength){
      taxonomy_data %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                      group = dropped, linetype = dropped),
                  fill = NA, size = 0.35 * fig1_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        scale_x_date(date_labels = "%m-%Y") + 
        ylab('Average Daily Cases') + 
        facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
        theme_bw()
    } else{
      taxonomy_data %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/1, 
                      group = dropped, linetype = dropped),
                  fill = NA, size = 0.35 * fig1_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        scale_x_date(date_labels = "%m-%Y") + 
        labs(y = 'Total Cases over Period') + 
        facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
        theme_bw()
    }  
    
  }
  
} else {
        
  if (period_OC_divided_by_timelength){
    taxonomy_data %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                    group = dropped, linetype = dropped),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (taxonomy_data %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases, group = dropped, linetype = dropped), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (taxonomy_data %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      scale_x_date(date_labels = "%m-%Y") + 
      labs(y = 'Average Daily Cases') + 
      facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
  } else{
    taxonomy_data %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/1, 
                    group = dropped, linetype = dropped),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (taxonomy_data %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases, group = dropped, linetype = dropped), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (taxonomy_data %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      scale_x_date(date_labels = "%m-%Y") + 
      labs(y = 'Total Cases for Period OC and Daily Cases for Daily OC') + 
      facet_wrap(~location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
  }
}

```



## Fig 3. Overall figure -- all observations by location AND year
**This comprehensive figure includes all (or specified) pre-processed observations. **
**The daily-based observations are represented in vertical lines **
**The period-based observations are represented in rectangles **
```{r echo=FALSE}
fig3_ncol_factor <- 2 #for now
fig4_ncol_factor <- 1

fig3_height_factor <- 3 * nrow(unique(raw_data_filtered[, c('location_name', 'year')])) / fig3_ncol_factor #fixed on 2/17
if(across_year_indicator){ 
  fig4_height_factor <- 3 * length( unique(raw_across_year_data_filtered[c('location_name', 'year'), ]) ) / fig4_ncol_factor
} else {fig4_height_factor <- 10} #10 won't be used

if (period_OC_divided_by_timelength) {
  print('The rectangles represent daily-averaged cases (total cases/length of period). ')
  }else{print('The rectangles represent total cases over periods. ')}

```

```{r echo=FALSE, fig.height=as.numeric(fig3_height_factor), fig.width=10}
if ( (nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) == 0 | 
      nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) == 0)  ){
  
  if ( nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) == 0 ){
      
      raw_data_filtered %>% 
        filter(TR == TL) %>%
        ggplot(aes(color = OC_UID)) + 
        geom_segment( aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                      size=0.3, alpha=0.5) + 
        geom_point( aes(x=ymd(TL), y=suspected_cases),
                    size = 0.7, alpha=0.5, shape=23) +
        facet_wrap(~year + location_name, ncol = as.integer(fig3_ncol_factor), scales = "free") +
        theme_bw()
    
  } else if ( nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) == 0 ){
  
    if (period_OC_divided_by_timelength){
      raw_data_filtered %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                      colour = OC_UID),
                  fill = NA, size = 0.35 * fig3_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        ylab('Average Daily Cases') + 
        facet_wrap(~year + location_name, ncol = as.integer(fig3_ncol_factor), scales = "free") +
        theme_bw()
    } else{
      raw_data_filtered %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/1, 
                      colour = OC_UID),
                  fill = NA, size = 0.35 * fig3_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        labs(y = 'Total Cases over Period') + 
        facet_wrap(~year + location_name, ncol = as.integer(fig3_ncol_factor), scales = "free") +
        theme_bw()
    }  
    
  }
  
} else {
        
  if (period_OC_divided_by_timelength){
    raw_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                    colour = OC_UID),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      labs(y = 'Average Daily Cases') + 
      facet_wrap(~year + location_name, ncol = as.integer(fig3_ncol_factor), scales = "free") +
      theme_bw()
  } else{
    raw_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/1, 
                    colour = OC_UID),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      labs(y = 'Total Cases for Period OC and Daily Cases for Daily OC') + 
      facet_wrap(~year + location_name, ncol = as.integer(fig3_ncol_factor), scales = "free") +
      theme_bw()
  }
}

```



## Fig 4. Overall figure -- all pre-processed observations that span across multiple years by location
**The daily-based observations are represented in vertical lines **
**The period-based observations are represented in rectangles **
```{r echo=FALSE, eval=across_year_indicator, include=across_year_indicator, fig.height=as.numeric(fig4_height_factor), fig.width=10}
if (period_OC_divided_by_timelength) {
  print('The rectangles represent daily-averaged cases (total cases/length of period). ')
  }else{print('The rectangles represent total cases over periods. ')}

if(across_year_indicator){
  
  if (period_OC_divided_by_timelength){
    raw_across_year_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                    colour = OC_UID),
                fill = NA, size = 0.35 * fig1_ncol_factor, alpha = 0.3, 
                stat = "identity") +
      ylab('Average Daily Cases') + 
      facet_wrap(~year + location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
  } else{
    raw_across_year_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/1, 
                    colour = OC_UID),
                fill = NA, size = 0.35 * fig1_ncol_factor, alpha = 0.3, 
                stat = "identity") +
      labs(y = 'Total Cases over Period') + 
      facet_wrap(~year + location_name, ncol = as.integer(fig1_ncol_factor), scales = "free") +
      theme_bw()
  }  

}

```





```{r echo=FALSE}
#######################Whether run the specific figures?#######################
same_OC_UID_daily_compare <- FALSE #call this first

if (  nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) > 0 & 
      nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) == 0  ){
  eval_value2 = FALSE
  include_value2 = FALSE
  eval_value3 = FALSE
  include_value3 = FALSE
  eval_value4 = FALSE
  include_value4 = FALSE
  print('The rest of the disagreement figures will not be generated because the daily OCs are missing. ')
} else if (  nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) == 0 & 
             nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) > 0  ){
  ##what if there is only one kind of OC_UID for daily OCs
  if ( length(unique(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]$OC_UID)) >= 2 ){
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = TRUE
    include_value3 = TRUE
    eval_value4 = FALSE
    include_value4 = FALSE

    ##what if different daily cases don't converge in same location on the same day
    raw_data_temp <- raw_data_filtered %>%
      filter(TL == TR) %>%
      group_by(year, location_name, TL) %>%
      mutate(num_diff_daily = length(unique(OC_UID))) %>%
      ungroup() %>%
      filter(!is.na(num_diff_daily))
    if(all(raw_data_temp$num_diff_daily == 1)){
      eval_value3 = FALSE
      include_value3 = FALSE
    }
    rm(raw_data_temp)

  }else{
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = FALSE
    include_value3 = FALSE
    eval_value4 = FALSE
    include_value4 = FALSE
  }
  
} else if (  nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) == 0 & 
             nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) == 0  ){
  
  stop('There is no valid data for this data comparison report. ')
  
} else{
  ##what if there is only one kind of OC_UID for daily OCs
  if ( length(unique(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]$OC_UID)) >= 2 ){
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = TRUE
    include_value3 = TRUE
    eval_value4 = TRUE
    include_value4 = TRUE

    ##what if different daily cases don't converge in same location on the same day
    raw_data_temp <- raw_data_filtered %>%
      filter(TL == TR) %>%
      group_by(year, location_name, TL) %>%
      mutate(num_diff_daily = length(unique(OC_UID))) %>%
      ungroup() %>%
      filter(!is.na(num_diff_daily))
    if(all(raw_data_temp$num_diff_daily == 1)){
      eval_value3 = FALSE
      include_value3 = FALSE
    }
    rm(raw_data_temp)
    
  }else{
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = FALSE
    include_value3 = FALSE
    eval_value4 = FALSE
    include_value4 = FALSE
    
    ##what if the daily cases and period cases don't converge over the same period
    raw_data_temp <- raw_data_filtered
    for(locations in unique(raw_data_temp$location_name)){
      if(eval_value4 == TRUE){break}
      daily_TLs <- unique(raw_data_temp[raw_data_temp$location_name == locations
                                      & raw_data_temp$TL == raw_data_temp$TR, ]$TL)
      period_TLs <- unique(raw_data_temp[raw_data_temp$location_name == locations
                                       & raw_data_temp$TL != raw_data_temp$TR, ]$TL)
      period_TRs <- unique(raw_data_temp[raw_data_temp$location_name == locations
                                       & raw_data_temp$TL != raw_data_temp$TR, ]$TR)
      if(!is.null(daily_TLs) & !is.null(period_TLs) & length(daily_TLs) != 0 & length(period_TLs) != 0){
        for (i in 1:length(period_TLs)){
          period <- seq(as.Date(period_TLs[i]), as.Date(period_TRs[i]), by = "days")
          if(any(as.Date(daily_TLs) %in% period)){
            eval_value4 <- TRUE
            include_value4 <- TRUE
            break
          }else{next}
        }
        
      }else{next}
    }#the end of the for loop
    rm(raw_data_temp)
    
  }

}

### Another situation is when there are very few daily cases (they are actually period cases instead)
if (  nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) > 0 & 
      nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) > 0 &
      nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) < 365 ){
  eval_value2 = FALSE
  include_value2 = FALSE
  eval_value3 = FALSE
  include_value3 = FALSE
  eval_value4 = FALSE
  include_value4 = FALSE
  print('The rest of the disagreement figures will not be generated because the daily OCs are missing. ')
}

### Just to make sure this variable exists, it won't be used
plot3_height_factor <- 10 
plot4_height_factor <- 10 

```





## Fig 5. Overall figure -- cumulative cases by location AND year
**This comprehensive figure includes all (or specified) pre-processed observations. **
**The daily-based observations are cumulative and represented in connected dots **
**The period-based observations (total number of cases) are represented in rectangles **
```{r echo=FALSE}
plot2_ncol_factor <- 2 #for now
plot2_height_factor <- 3 * nrow(unique(raw_data_filtered[, c('location_name', 'year')])) / plot2_ncol_factor

```

```{r eval=eval_value2, include=include_value2, echo=FALSE, fig.height=as.numeric(plot2_height_factor), fig.width=10}
if ( nrow(raw_data_filtered[raw_data_filtered$TL != raw_data_filtered$TR, ]) > 0 & 
     nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) > 0  ) {
  raw_data_filtered %>% 
    filter(TL != TR) %>% 
    ggplot(aes(x = ymd(TL), y = suspected_cases, 
               color = OC_UID)) +
    geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                  ymax = suspected_cases, 
                  color = OC_UID),
              fill = NA, size = 0.7, alpha = 0.3, 
              stat = "identity") +
    geom_point(data = (raw_data_filtered %>% 
                         filter(TL == TR) %>%
                         group_by(OC_UID, location_name, year) %>% 
                         arrange(TL, .by_group =  TRUE) %>% 
                         mutate(cum_cases = cumsum(suspected_cases))
                       ),
               aes(x=ymd(TL), y=cum_cases),
               size = 0.5, alpha=0.5, shape=23) +
    geom_line(data = (raw_data_filtered %>% 
                        filter(TL == TR) %>%
                        group_by(OC_UID, location_name, year) %>% 
                        arrange(TL, .by_group =  TRUE) %>% 
                        mutate(cum_cases = cumsum(suspected_cases))
                      ),
              aes(x=ymd(TL), y=cum_cases),
              size = 0.3, alpha=0.5) +
    facet_wrap(~year + location_name, ncol = as.integer(plot2_ncol_factor), scales = "free") +
    theme_bw()
}else if (nrow(raw_data_filtered[raw_data_filtered$TL == raw_data_filtered$TR, ]) > 0){
  raw_data_filtered %>%
    ggplot() +  
    geom_point(data = (raw_data_filtered %>% 
                         filter(TL == TR) %>%
                         group_by(OC_UID, location_name, year) %>% 
                         arrange(TL, .by_group =  TRUE) %>% 
                         mutate(cum_cases = cumsum(suspected_cases))
                       ),
               aes(x=ymd(TL), y=cum_cases),
               size = 0.5, alpha=0.5, shape=23) +
    geom_line(data = (raw_data_filtered %>% 
                        filter(TL == TR) %>%
                        group_by(OC_UID, location_name, year) %>% 
                        arrange(TL, .by_group =  TRUE) %>% 
                        mutate(cum_cases = cumsum(suspected_cases))
                      ),
              aes(x=ymd(TL), y=cum_cases),
              size = 0.3, alpha=0.5) +
    facet_wrap(~year + location_name, ncol = as.integer(plot2_ncol_factor), scales = "free") +
    theme_bw()
  }


```



## Fig 6. Disagreement figure -- daily incidence v.s daily incidence from different OC
**This figure compares the discrepancies between all daily-based observations between any two different observation collections for a certain location and a certain year, and only includes those disagree with specified disagreement threshold (default is 0). **
**The daily-based observations are represented in vertical lines **
```{r include=FALSE}
raw_data_filtered_dis_daily <- raw_data_filtered %>% 
  filter(TL == TR) %>% 
  filter(!is.na(location_name) & !is.na(OC_UID) & !is.na(suspected_cases)) %>% 
  mutate(groups_compared = NA, oc1 = NA, oc2 = NA, lower_oc = NA, higher_oc = NA)

raw_data_filtered_dis_daily_stack <- raw_data_filtered_dis_daily[1, ]
raw_data_filtered_dis_daily_stack <- raw_data_filtered_dis_daily_stack[-c(1),]

if(length(unique(raw_data_filtered_dis_daily$OC_UID)) >= 2){
  all_combi <- combn(unique(raw_data_filtered_dis_daily$OC_UID), 2)
}else{eval_value3    <- FALSE
      include_value3 <- FALSE}

plot3_ncol_factor <- 2 #for now

```

```{r echo=FALSE, eval=eval_value3, include=include_value3}
### tailor the dataset
for (locations in unique(raw_data_filtered_dis_daily$location_name)){
  for (years in unique(raw_data_filtered_dis_daily$year)){
    for (combi_num in 1:(dim(all_combi)[2])) {
      combi = all_combi[, combi_num]
      raw_data_filtered_dis_daily_temp1 <- raw_data_filtered_dis_daily[
        raw_data_filtered_dis_daily$location_name == locations
        &raw_data_filtered_dis_daily$year == years
        &raw_data_filtered_dis_daily$OC_UID == combi[1], ] %>% 
        mutate(oc1 = suspected_cases) %>% 
        mutate(groups_compared = paste0('green_', combi[1], '_v.s_red_', combi[2]))
      TLs1 <- unique(raw_data_filtered_dis_daily_temp1$TL)
      raw_data_filtered_dis_daily_temp2 <- raw_data_filtered_dis_daily[
        raw_data_filtered_dis_daily$location_name == locations
        &raw_data_filtered_dis_daily$year == years
        &raw_data_filtered_dis_daily$OC_UID == combi[2], ] %>% 
        mutate(oc2 = suspected_cases) %>% 
        mutate(groups_compared = paste0('green_', combi[1], '_v.s_red_', combi[2]))
      TLs2 <- unique(raw_data_filtered_dis_daily_temp2$TL)
      
      if(is.null(raw_data_filtered_dis_daily_temp1) | is.null(raw_data_filtered_dis_daily_temp2)){
        next
      }else{
        
        ###a little diagnosis
        same_OC_UID_daily_compare <- FALSE
        if (length(unique(raw_data_filtered_dis_daily_temp1$TL)) == length(unique(raw_data_filtered_dis_daily_temp1[c("TL","oc1")])) & length(unique(raw_data_filtered_dis_daily_temp2$TL)) == length(unique(raw_data_filtered_dis_daily_temp2[c("TL","oc2")])) & same_OC_UID_daily_compare == FALSE){
          same_OC_UID_daily_compare <- FALSE
        }else{
          same_OC_UID_daily_compare <- TRUE
        }
        
        TLsTotal <- unique(c(TLs1, TLs2))
        for (TLs in unique(TLsTotal)){
          if(TLs %in% TLs1 & TLs %in% TLs2){
            raw_data_filtered_dis_daily_stack <- rbind(raw_data_filtered_dis_daily_stack,
                                                       raw_data_filtered_dis_daily_temp1[
                                                         raw_data_filtered_dis_daily_temp1$TL == TLs,
                                                       ][1, ])
            raw_data_filtered_dis_daily_stack[
              raw_data_filtered_dis_daily_stack$location_name == locations
              &raw_data_filtered_dis_daily_stack$year == years
              &raw_data_filtered_dis_daily_stack$groups_compared == paste0('green_', combi[1], '_v.s_red_', combi[2])
              &raw_data_filtered_dis_daily_stack$TL == TLs,]$oc2 <- 
              raw_data_filtered_dis_daily_temp2[
                raw_data_filtered_dis_daily_temp2$TL == TLs,]$oc2[1]
              
          }else if(TLs %in% TLs1){
            raw_data_filtered_dis_daily_stack <- rbind(raw_data_filtered_dis_daily_stack,
                                                       raw_data_filtered_dis_daily_temp1[
                                                         raw_data_filtered_dis_daily_temp1$TL == TLs,
                                                       ][1, ])
            raw_data_filtered_dis_daily_stack[
              raw_data_filtered_dis_daily_stack$location_name == locations
              &raw_data_filtered_dis_daily_stack$year == years
              &raw_data_filtered_dis_daily_stack$groups_compared == paste0('green_', combi[1], '_v.s_red_', combi[2])
              &raw_data_filtered_dis_daily_stack$TL == TLs,]$oc2[1] <- - NA
            
          }else if(TLs %in% TLs2){
            raw_data_filtered_dis_daily_stack <- rbind(raw_data_filtered_dis_daily_stack,
                                                       raw_data_filtered_dis_daily_temp2[
                                                         raw_data_filtered_dis_daily_temp2$TL == TLs,
                                                       ][1, ])
            raw_data_filtered_dis_daily_stack[
              raw_data_filtered_dis_daily_stack$location_name == locations
              &raw_data_filtered_dis_daily_stack$year == years
              &raw_data_filtered_dis_daily_stack$groups_compared == paste0('green_', combi[1], '_v.s_red_', combi[2])
              &raw_data_filtered_dis_daily_stack$TL == TLs,]$oc1[1] <- - NA
            
          }
        }
      } #the end of 'next' if-else statement
      
    }
  }
}

raw_data_filtered_dis_daily_stack <- raw_data_filtered_dis_daily_stack %>% 
  #filter(oc1 != oc2 | is.na(oc1) | is.na(oc2)) %>%
  filter(abs(oc1 - oc2) >= daily_daily_obs_disagree_threshold & 
           ( !is.na(oc1) & !is.na(oc2) )) %>%
  select(-suspected_cases) %>% 
  rowwise() %>%
  mutate(lower_oc = min(oc1, oc2), 
         higher_oc = max(oc1, oc2))

raw_data_filtered_dis_daily_stack_temp <- raw_data_filtered_dis_daily_stack
plot3_height_factor <- (3 * nrow(unique(raw_data_filtered_dis_daily_stack_temp[c("location_name", 
                                                                                 "year",
                                                                                 "groups_compared")]))
                          / plot3_ncol_factor)
rm(raw_data_filtered_dis_daily_stack_temp)

###what if there is no row
if (plot3_height_factor == 0){
  eval_value3 <- FALSE
  include_value3 <- FALSE
}

```

```{r echo=FALSE, eval=eval_value3, include=include_value3, fig.height=as.numeric(plot3_height_factor), fig.width=10}
### officially plot the figure 3
raw_data_filtered_dis_daily_stack %>% 
  ggplot() +
  geom_segment( aes(x=ymd(TL), xend=ymd(TL), y=lower_oc, yend=higher_oc), 
                color="orange", size = 0.30 ) +
  geom_point( aes(x=ymd(TL), y=oc1), color=rgb(0.2,0.7,0.1,0.5), 
              size = 0.7, alpha=1, shape=23 ) +
  geom_point( aes(x=ymd(TL), y=oc2), color=rgb(0.7,0.2,0.1,0.5), 
              size = 0.7, alpha=1, shape=23 ) +
  facet_wrap( ~ location_name + groups_compared + year, ncol = as.integer(plot3_ncol_factor), scales = "free") +
  theme_bw()

```



## Fig 7. Disagreement figure -- daily incidence v.s daily incidence from the same OC
**This figure compares the discrepancies between all daily-based observations within the same observation collections for a certain location and a certain year, and only includes those disagree with specified disagreement threshold (default is 0). **
**The daily-based observations are represented in vertical lines **
```{r echo=FALSE, eval=same_OC_UID_daily_compare, include=same_OC_UID_daily_compare}
raw_data_filtered_dis_daily_same = raw_data_filtered_dis_daily %>% 
  group_by(OC_UID, location_name, year, TL) %>% 
  summarise(duplicate = n(), lower_oc = min(suspected_cases, na.rm = TRUE), 
            higher_oc = max(suspected_cases, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(duplicate > 1)

if(is.null(raw_data_filtered_dis_daily_same$OC_UID) | 
   is.null(raw_data_filtered_dis_daily_same$location_name) | 
   is.null(raw_data_filtered_dis_daily_same$year) |
   all(is.na(raw_data_filtered_dis_daily_same$OC_UID)) | 
   all(is.na(raw_data_filtered_dis_daily_same$location_name)) | 
   all(is.na(raw_data_filtered_dis_daily_same$year)) ){
  same_OC_UID_daily_compare <- FALSE
}
```

```{r echo=FALSE, eval=same_OC_UID_daily_compare, include=same_OC_UID_daily_compare}
raw_data_filtered_dis_daily_same %>% 
  ggplot() +
  geom_segment( aes(x=ymd(TL), xend=ymd(TL), y=lower_oc, yend=higher_oc), 
                color="orange", size = 0.30 ) +
  geom_point( aes(x=ymd(TL), y=lower_oc), color=rgb(0.2,0.7,0.1,0.5), 
              size = 0.7, alpha=1, shape=23 ) +
  geom_point( aes(x=ymd(TL), y=higher_oc), color=rgb(0.7,0.2,0.1,0.5), 
              size = 0.7, alpha=1, shape=23 ) +
  facet_wrap( ~ OC_UID+location_name+year, ncol = as.integer(plot3_ncol_factor), scales = "free") +
  theme_bw()

```



## Fig 8. Disagreement figure -- number of cases over periods v.s daily incidence
**This figure compares the discrepancies between daily-based and period-based observations between any two same or different observation collections for a certain location and a certain year, and only includes those disagree with specified disagreement threshold (default is 0). **
**The daily-based observations are represented in vertical lines **
**The period-based observations (total number of cases) are represented in rectangles **
**The horizontal dashed line represents the average of the daily-based observations over the compared period **
```{r echo=FALSE, eval=eval_value4, include=include_value4}
raw_data_filtered_dis_period <- raw_data_filtered %>% 
  filter(!is.na(location_name) & !is.na(OC_UID)) %>% 
  mutate(period_token = case_when(TL != TR ~ 1,
                                  TRUE ~ 0),
         daily_token = case_when(TL == TR ~ 1,
                                  TRUE ~ 0),
         dis_period = 0,
         mean_daily = NA, 
         x_left = NA_Date_,
         x_right = NA_Date_)
period_factor <- length(unique(raw_data_filtered_dis_period[raw_data_filtered_dis_period$period_token == 1, ]$OC_UID))
daily_factor <- length(unique(raw_data_filtered_dis_period[raw_data_filtered_dis_period$daily_token == 1, ]$OC_UID))

raw_data_filtered_dis_period_stack <- raw_data_filtered_dis_period[1, ]
raw_data_filtered_dis_period_stack <- raw_data_filtered_dis_period_stack[-c(1),]

plot4_ncol_factor <- 2 #for now

```

```{r echo=FALSE, eval=eval_value4, include=include_value4}
### tailor the dataset
for (locations in unique(raw_data_filtered_dis_period$location_name)){
  for (years in unique(raw_data_filtered_dis_period$year)){
    for (ocids in unique(raw_data_filtered_dis_period$OC_UID)){
      if (any(raw_data_filtered_dis_period[
        raw_data_filtered_dis_period$location_name == locations
        &raw_data_filtered_dis_period$year == years
        &raw_data_filtered_dis_period$OC_UID == ocids, ]$period_token == 1)){
        TL <- raw_data_filtered_dis_period[
          raw_data_filtered_dis_period$location_name == locations
          &raw_data_filtered_dis_period$year == years
          &raw_data_filtered_dis_period$OC_UID == ocids
          &raw_data_filtered_dis_period$period_token == 1, ]$TL
        TR <- raw_data_filtered_dis_period[
          raw_data_filtered_dis_period$location_name == locations
          &raw_data_filtered_dis_period$year == years
          &raw_data_filtered_dis_period$OC_UID == ocids
          &raw_data_filtered_dis_period$period_token == 1, ]$TR
        for (h in 1:length(TL)){
          TLs <- TL[h]
          TRs <- TR[h]
          extract_cases <- raw_data_filtered_dis_period[
            raw_data_filtered_dis_period$location_name == locations
            &raw_data_filtered_dis_period$year == years
            &raw_data_filtered_dis_period$OC_UID == ocids
            &raw_data_filtered_dis_period$period_token == 1
            &raw_data_filtered_dis_period$TL == TLs
            &raw_data_filtered_dis_period$TR == TRs, ]$suspected_cases
          if(min(extract_cases, na.rm = TRUE) != max(extract_cases, na.rm = TRUE)){warning('The extract_cases has more than one different elements, only the first one is used. ')}
          extract_cases <- extract_cases[1]
          
          for (ocids_2 in unique(raw_data_filtered_dis_period$OC_UID)){
            if (any(raw_data_filtered_dis_period[
              raw_data_filtered_dis_period$location_name == locations
              &raw_data_filtered_dis_period$year == years
              &raw_data_filtered_dis_period$OC_UID == ocids_2, ]$daily_token == 1)){
              sum_cases <- sum(raw_data_filtered_dis_period[
                raw_data_filtered_dis_period$location_name == locations
                &raw_data_filtered_dis_period$year == years
                &raw_data_filtered_dis_period$OC_UID == ocids_2 
                &raw_data_filtered_dis_period$daily_token == 1
                &raw_data_filtered_dis_period$TL %in% seq(as.Date(TLs), as.Date(TRs), by="days"), ]$suspected_cases,
                na.rm = TRUE)
              if (sum_cases != extract_cases & abs(sum_cases - extract_cases) >= daily_period_obs_disagree_threshold){
                new_df1 <- raw_data_filtered_dis_period[
                  raw_data_filtered_dis_period$location_name == locations
                  &raw_data_filtered_dis_period$year == years
                  &raw_data_filtered_dis_period$OC_UID == ocids
                  &raw_data_filtered_dis_period$period_token == 1
                  &raw_data_filtered_dis_period$TL == TLs
                  &raw_data_filtered_dis_period$TR == TRs, ] %>% 
                  mutate(dis_period = paste0("period_from_", ocids, "_daily_from_", ocids_2))
                new_df2 <- raw_data_filtered_dis_period[
                  raw_data_filtered_dis_period$location_name == locations
                  &raw_data_filtered_dis_period$year == years
                  &raw_data_filtered_dis_period$OC_UID == ocids_2 
                  &raw_data_filtered_dis_period$daily_token == 1
                  &raw_data_filtered_dis_period$TL %in% seq(as.Date(TLs), as.Date(TRs), by="days"), ] %>% 
                  mutate(dis_period = paste0("period_from_", ocids, "_daily_from_", ocids_2)) %>% 
                  mutate(mean_daily = mean(suspected_cases), 
                         x_left = TLs, x_right = TRs)
                raw_data_filtered_dis_period_stack <-
                  rbind(raw_data_filtered_dis_period_stack, new_df1)
                raw_data_filtered_dis_period_stack <-
                  rbind(raw_data_filtered_dis_period_stack, new_df2)
              }
            }
          }
        }
      }
    }
  }
}

##diagnose this plot4_height_factor
raw_data_filtered_dis_period_stack <- raw_data_filtered_dis_period_stack %>% 
  filter( !is.na(dis_period) & !is.na(OC_UID) & !is.na(TL) & !is.na(TR) & !is.na(suspected_cases) & !is.na(x_left) & !is.na(x_right) & !is.na(mean_daily) )
  
plot4_height_factor <- (3 * nrow(raw_data_filtered_dis_period_stack[raw_data_filtered_dis_period_stack$period_token == 1, ])
                          / plot4_ncol_factor)

##if there is zero row to display
if (nrow(raw_data_filtered_dis_period_stack[raw_data_filtered_dis_period_stack$period_token == 1, ]) == 0 | 
    is.null(raw_data_filtered_dis_period_stack$location_name) | is.null(raw_data_filtered_dis_period_stack$dis_period) | 
    is.null(raw_data_filtered_dis_period_stack$year)){
  eval_value4 <- FALSE
  include_value4 <- FALSE
  plot4_height_factor <- 10 #not gonna be used
  warning('Fig 7. will not be generated because there is no useful comparison to display. ')
}

```

```{r echo=FALSE, eval=eval_value4, include=include_value4, fig.height=plot4_height_factor, fig.width=10}
### officially plot the figure 4
raw_data_filtered_dis_period_stack %>% 
  filter(TL != TR) %>% 
  ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
             color = OC_UID)) +
  geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                colour = OC_UID),
            fill = NA, size = 1.2, alpha = 0.3, 
            stat = "identity") +
  geom_segment( data = (raw_data_filtered_dis_period_stack %>% filter(TR == TL)),
                aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                size=0.7, alpha=0.7) + 
  geom_point(data = (raw_data_filtered_dis_period_stack %>% filter(TR == TL)),
             aes(x=ymd(TL), y=suspected_cases),
             size=1.2, alpha=1, shape=23) +
  geom_segment( data = (raw_data_filtered_dis_period_stack %>% filter(TR == TL)),
                aes(x=ymd(x_left), xend=ymd(x_right), 
                    y=mean_daily, yend=mean_daily), 
                size=0.5, alpha=1, linetype="dashed") + 
  facet_wrap( ~ location_name + dis_period + year, ncol = as.integer(plot4_ncol_factor), scales = "free") +
  theme_bw()

```



## Fig 9. Stan input data -- number of cases by OC_UID over periods and locations
**This figure illustrates the stan input cases data (stan_input$sf_cases_resized) **
```{r echo=FALSE}
# Just to calculate the width and height
stan_input_data_temp <- sf::st_drop_geometry(stan_input_data)
num_plots <- nrow(unique(stan_input_data_temp[c("OC_UID", "TL", "TR")]))
plot5_height_factor <- ceiling(num_plots / 5) * 5
rm(stan_input_data_temp)

```

```{r echo=FALSE, fig.height=as.numeric(plot5_height_factor), fig.width=10}
stan_input_data %>% 
  dplyr::arrange(dplyr::desc(cases)) %>% 
  ggplot2::ggplot() +
  ggplot2::geom_sf(ggplot2::aes(fill = cases)) +
  ggplot2::geom_sf_text(ggplot2::aes(label = cases), color = 'White', size = 2.0) + 
  ggplot2::scale_fill_gradient2("Stan input cases", low="white",mid="orange",high="red",na.value='blue') +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::facet_wrap(~OC_UID + TL + TR)

```

## Fig 10. Annual data comparison
**This figure compares annual data from sf_cases_resized in stan_input across different admin levels.**
```{r echo=FALSE,fig.height=10,fig.width=10}
iso=config$countries_name
location_lp <- paste0(params$cholera_directory, "/Analysis/R/loc_lp.csv") %>% read.csv() #get location_peiod_location_id_file
unified_oc <- paste0(params$cholera_directory, "/Analysis/R/unified_OC.csv") %>% read.csv() #get unified OC file

  
tmp<-data.frame(stan_input$sf_cases_resized%>%subset(!locationPeriod_id%in%c(unified_oc$lp[unified_oc$country==iso])&TR-TL+1>335&TR-TL+1<395)%>%
                  mutate(country=iso,year=substr(TL,1,4)))%>%
  group_by(country,OC_UID,year,locationPeriod_id)%>%
  mutate(sCh=mean(attributes.fields.suspected_cases))
tmp1<-merge(tmp,location_lp,by=c("locationPeriod_id"))%>%
  group_by(country,OC_UID,year,admin_level)%>%summarize(total_sCh=aggregated_cases<-sum( sCh ))
tmp2<-data.frame(stan_input$sf_cases_resized)%>%
  subset(OC_UID%in%unified_oc$oc[unified_oc$who_annual_report==T])%>%
  mutate(country=iso,year=substr(TL,1,4))%>%
  group_by(country,OC_UID,year)%>%
  summarize(total_sCh=attributes.fields.suspected_cases)%>%
  select(country,OC_UID,year,total_sCh)
tmp2$admin_level<-"admin0"

total_data<-bind_rows(tmp1,tmp2)%>%
  mutate(who_annual_report=ifelse(OC_UID%in%unified_oc$oc[unified_oc$who_annual_report==T],TRUE,FALSE))

ggplot2::ggplot(data=total_data)+
    geom_point(aes(y=total_sCh,x=year,color=admin_level,shape=who_annual_report),size=5)+
    theme(axis.line = element_line(colour = "black"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())+
    ggtitle(label=iso)
```
