---
title: "Plot Data -- TZA Mainland"
date: "`r Sys.time()`"
output: html_document
params:
  config: "/Analysis/configs/Dec_2021_runs/GHA_2015_2019/config_GHA_2015_2019.yml"
  cholera_directory: "/home/kaiyuezou/mapping_pipeline/9_23_dev/cholera-mapping-pipeline"
  args: 'run-comparison'
  period_OC_divided_by_timelength: 'TRUE'
  OC_filter: ''
  daily_daily_obs_disagree_threshold: '5'
  daily_period_obs_disagree_threshold: '10'
  report_testing: 'FALSE'
  fake_OCs: '3'
  fake_OCs_daily: '1'
  
---
### This is a short report to plot data of different observation lengths for GHA 2015 - 2019.

```{r eval=FALSE, include=FALSE}
### 9/27/2021 Temporary plan: detect all the discrepancies and plot the figures if they appear in any of the location-times
### If there are discrepancies, we think they're all imperfect descriptions of what the real data looks like
### Describe simply how different sources agree and disagree, plot the only times when they apprear side by side
### No need for the whole time axis, no need for the cumulative incidences. 
### Rectangles should be divided by the length of period of time. 
### By location, not by location period. 
### 10/12/2021 New updates
### 10/20/2021 New updates -- added OC filter and discrepancy threshold
### 10/26/2021 New updates -- tailored it for TZA mainland and considered situation when OCs are not specified
### 10/28/2021 New updates -- generalized to all situations when period OCs or daily OCs might be absent
### 10/29/2021 New updates -- added more descriptive sentences
### 10/30/2021 New updates -- considered the situation where there is only one kind of OC_UID for daily OCs
### 10/31/2021 New updates -- considered zero row situation for the zeros filtering process 
```



```{r setup, include=FALSE}
# ```{r setup, include=FALSE, dev="CairoPNG"}
# knitr::opts_chunk$set(
#   echo = FALSE,
#   dev="CairoPNG",
#   error = FALSE,
#   fig.align = "center",
#   message = TRUE,
#   warning = TRUE
#   )
library(lubridate)
library(stringr)
library(dplyr)
library(magrittr)
library(purrr)
library(readr)
library(ggplot2)
library(kableExtra)
library(taxdat)
library(sf)
library(Cairo)
Sys.setlocale("LC_ALL","English")

```



```{r warning=FALSE, include=FALSE}
# Load config
config <- paste0(params$cholera_directory, "/", params$config) %>% yaml::read_yaml() #get the config file
files <- taxdat::get_filenames(config, params$cholera_directory)

# Load raw_data and data
raw_data <- taxdat::read_file_of_type(files["data"], "sf_cases") %>% 
  mutate(year = lubridate::year(TL))

stan_input <- read_file_of_type(files["stan_input"], "stan_input")

data <- stan_input$sf_cases_resized %>% 
  rename(cases = `attributes.fields.suspected_cases`) %>% 
  mutate(obs = row_number() %>% factor())

# Get the pre-defined parameters into the environment
period_OC_divided_by_timelength = as.logical(params$period_OC_divided_by_timelength)
report_testing = as.logical(params$report_testing)
fake_OCs = as.numeric(params$fake_OCs)
fake_OCs_daily = as.numeric(params$fake_OCs_daily)

if (!is.null(params$OC_filter) & (nchar(params$OC_filter) > 0 & !identical(params$OC_filter, ' '))) {OC_vector = as.character(as.numeric(strsplit(params$OC_filter, ',')[[1]]))} #a vector of characters
daily_daily_obs_disagree_threshold <- as.numeric(params$daily_daily_obs_disagree_threshold)
daily_period_obs_disagree_threshold <- as.numeric(params$daily_period_obs_disagree_threshold)

```



## Parameter settings for this report
```{r echo=FALSE, warning=FALSE}
paste0('Period observations are divided by their time length in the first figure: ', period_OC_divided_by_timelength)
paste0('This report is just used to test its functionality: ', report_testing)
if (exists('OC_vector')) { paste0('The OCs selected for this report is/are: ', OC_vector) } else { paste0('No OC specified, all relevant OCs are used for this report. ') }
paste0('The daily vs. daily observations disagree threshold (fig. 3): ', daily_daily_obs_disagree_threshold)
paste0('The daily vs. period observations disagree threshold (fig. 4): ', daily_period_obs_disagree_threshold)

```



```{r warning=FALSE, include=FALSE}
##filter out the unnecessary OCs
if (exists('OC_vector')) {raw_data <- subset(raw_data, as.character(OC_UID) %in% OC_vector)}

##get some warnings ready
if ( (nrow(raw_data[raw_data$TL != raw_data$TR, ]) == 0 | 
      nrow(raw_data[raw_data$TL == raw_data$TR, ]) == 0) & !report_testing) {
  warning('This country does not have any daily/period cases data from the OCs you specified, 
  this diagnostic report will not generate all figures. ')
}

##prepare for all-zero situations
raw_data[, "first_non0"] <- NA
raw_data[, "last_non0"] <- NA
for (locations in unique(raw_data$location_name)){
  for (years in unique(raw_data$year)){
    if (length(raw_data[raw_data$location_name == locations 
                   & raw_data$year == years, ]$suspected_cases) == 0){}
    else if (sum(raw_data[raw_data$location_name == locations 
                   & raw_data$year == years, ]$suspected_cases) == 0){
      # min_TL <- min(raw_data[raw_data$location_name == locations 
      #             & raw_data$year == years, ]$TL)
      # max_TR <- max(raw_data[raw_data$location_name == locations 
      #             & raw_data$year == years, ]$TR)
      # raw_data[raw_data$location_name == locations 
      #        & raw_data$year == years
      #        & raw_data$TL == min_TL, ]$first_non0 <- 1
      # raw_data[raw_data$location_name == locations 
      #        & raw_data$year == years
      #        & raw_data$TR == max_TR, ]$last_non0 <- 1

      ##decide to discard these rows and tailor the plot1_ncol_factor
      raw_data <- raw_data[- which(raw_data$location_name == locations 
                            & raw_data$year == years), ]
      if (!exists('plot1_ncol_factor')) {plot1_ncol_factor <- 1}
               }
  }
}

##filter out the zeros for each location-year and discard geom
raw_data_filtered <- raw_data %>% 
  select(-geom) %>% 
  group_by(location_name, year) %>% 
  arrange(TL, OC_UID) %>% 
  mutate( first_non0 = case_when(
            id == id[ (match((suspected_cases[suspected_cases > 0])[1], suspected_cases))[1] ] ~ 1,
            TRUE ~ 0)
         ) %>% 
  arrange(desc(TR, OC_UID)) %>% 
  mutate( last_non0 = case_when(
            id == id[ (match((suspected_cases[suspected_cases > 0])[1], suspected_cases))[1] ] ~ 1,
            TRUE ~ 0)
         ) %>%
  arrange(TL, OC_UID) %>%  
  mutate( between_non0s = case_when(
            id %in% id[min(which(first_non0 == 1)) : max(which(last_non0 == 1))] ~ 1, 
            TRUE ~ 0)
         ) %>% 
  filter(between_non0s == 1) %>% 
  select(-first_non0, -last_non0, -between_non0s)
    



##do we need to create the fake data? 
if (report_testing & (length(unique(raw_data_filtered$OC_UID)) == 1)){
  #let's create fake data!
  set.seed(20211007)
  random_number = sample(seq(fake_OCs), fake_OCs_daily)
  real_OC_UID = unique(raw_data_filtered$OC_UID)

  for (i in seq(fake_OCs)) {
    OC_UID_temp = paste0('fake_data', as.character(i))
    for (locations in unique(raw_data_filtered$location_name)){
      for (years in unique(raw_data_filtered$year)){
        raw_data_filtered <- raw_data_filtered %>% 
          ungroup() %>% 
          add_row(OC_UID = OC_UID_temp,
                  TL = sample(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL, 1),
                  TR = sample(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL, 1),
                  location_name = locations,
                  suspected_cases = runif(1)*rpois(1, sum(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$suspected_cases)),
                  year = raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$year[1])
        
        raw_data_filtered <- raw_data_filtered %>% 
          mutate(TL = case_when(OC_UID == OC_UID_temp & TL > TR ~ TR,
                                TRUE ~ TL),
                TR = case_when(OC_UID == OC_UID_temp & TL >= TR ~ sample( seq(as.Date(raw_data_filtered[raw_data_filtered$OC_UID == OC_UID_temp & raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL),
                                                                              as.Date(max(raw_data_filtered[raw_data_filtered$location_name == locations & raw_data_filtered$year == years, ]$TL)), 
                                                                              by="days"), 
                                                                          1 ),
                                TRUE ~ TR))
      }
    } 
    if (i == random_number){
      indices <- as.numeric(row.names(raw_data_filtered[raw_data_filtered$OC_UID == sample(real_OC_UID, 1),]))
      sampled_indices <- sample(indices, sample(seq(length(indices)), 1))            
      
      raw_data_filtered <- raw_data_filtered %>% 
        ungroup() %>% 
        add_row(OC_UID = rep(OC_UID_temp, length(sampled_indices)),
                TL     = raw_data_filtered$TL[sampled_indices],
                TR     = raw_data_filtered$TR[sampled_indices],
                location_name = raw_data_filtered$location_name[sampled_indices],
                suspected_cases = runif(1, 1, 2) * raw_data_filtered$suspected_cases[sampled_indices],
                year   = raw_data_filtered$year[sampled_indices])
    }
  }

}

```



## Overall figure -- all observation collections by location and year
### This comprehensive figure includes all (or specified) raw observation collections used in the model.
#### The daily-based observations are represented in vertical lines 
#### The period-based observations are represented in rectangles
```{r echo=FALSE}
if (!exists('plot1_ncol_factor')) {plot1_ncol_factor <- 2} #for now
# plot1_height_factor <- 3 * length(unique(raw_data_filtered$location_name)) * length(unique(raw_data_filtered$year)) / plot1_ncol_factor
plot1_height_factor <- 3 * length( unique(cbind(raw_data_filtered$location_name, raw_data_filtered$year)) ) / plot1_ncol_factor

if (period_OC_divided_by_timelength) {
  print('The rectangles represent daily-averaged cases (total cases/length of period). ')
  }else{print('The rectangles represent total cases over periods. ')}

```

```{r echo=FALSE, fig.height=as.numeric(plot1_height_factor), fig.width=10}
if ( (nrow(raw_data[raw_data$TL != raw_data$TR, ]) == 0 | 
      nrow(raw_data[raw_data$TL == raw_data$TR, ]) == 0)  ){
  
  if ( nrow(raw_data[raw_data$TL != raw_data$TR, ]) == 0 ){
      
      raw_data_filtered %>% 
        geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                      aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                      size=0.3, alpha=0.5, color = OC_UID) + 
        geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                  aes(x=ymd(TL), y=suspected_cases),
                  size = 0.7, alpha=0.5, shape=23, color = OC_UID) +
        facet_wrap(~year + location_name, ncol = as.integer(plot1_ncol_factor), scales = "free") +
        theme_bw()
    
  } else if ( nrow(raw_data[raw_data$TL == raw_data$TR, ]) == 0 ){
  
    if (period_OC_divided_by_timelength){
      raw_data_filtered %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                      colour = OC_UID),
                  fill = NA, size = 0.35 * plot1_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        ylab('Average Daily Cases') + 
        facet_wrap(~year + location_name, ncol = as.integer(plot1_ncol_factor), scales = "free") +
        theme_bw()
    } else{
      raw_data_filtered %>% 
        filter(TL != TR) %>% 
        ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                  color = OC_UID)) +
        geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                      ymax = suspected_cases/1, 
                      colour = OC_UID),
                  fill = NA, size = 0.35 * plot1_ncol_factor, alpha = 0.3, 
                  stat = "identity") +
        labs(y = 'Total Cases over Period') + 
        facet_wrap(~year + location_name, ncol = as.integer(plot1_ncol_factor), scales = "free") +
        theme_bw()
    }  
    
  }
  
} else {
        
  if (period_OC_divided_by_timelength){
    raw_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                    colour = OC_UID),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      labs(y = 'Average Daily Cases') + 
      facet_wrap(~year + location_name, ncol = as.integer(plot1_ncol_factor), scales = "free") +
      theme_bw()
  } else{
    raw_data_filtered %>% 
      filter(TL != TR) %>% 
      ggplot(aes(x = ymd(TL), y = suspected_cases/1, 
                color = OC_UID)) +
      geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                    ymax = suspected_cases/1, 
                    colour = OC_UID),
                fill = NA, size = 0.7, alpha = 0.3, 
                stat = "identity") +
      geom_segment( data = (raw_data_filtered %>% filter(TR == TL)),
                    aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                    size=0.3, alpha=0.5) + 
      geom_point(data = (raw_data_filtered %>% filter(TR == TL)),
                aes(x=ymd(TL), y=suspected_cases),
                size = 0.7, alpha=0.5, shape=23) +
      labs(y = 'Total Cases for Period OC and Daily Cases for Daily OC') + 
      facet_wrap(~year + location_name, ncol = as.integer(plot1_ncol_factor), scales = "free") +
      theme_bw()
  }
}

```



```{r echo=FALSE}
#######################Whether run the specific figures?#######################
if (  nrow(raw_data[raw_data$TL != raw_data$TR, ]) > 0 & 
      nrow(raw_data[raw_data$TL == raw_data$TR, ]) == 0  ){
  eval_value2 = FALSE
  include_value2 = FALSE
  eval_value3 = FALSE
  include_value3 = FALSE
  eval_value4 = FALSE
  include_value4 = FALSE
  plot3_height_factor <- 10 #just to make sure this variable exists, it won't be used
  plot4_height_factor <- 10 #just to make sure this variable exists, it won't be used
  print('The rest of the figures will not be generated because the daily OCs are missing. ')
} else if (  nrow(raw_data[raw_data$TL != raw_data$TR, ]) == 0 & 
             nrow(raw_data[raw_data$TL == raw_data$TR, ]) > 0  ){
  ##what if there is only one kind of OC_UID for daily OCs
  if ( length(unique(raw_data[raw_data$TL == raw_data$TR, ]$OC_UID)) >= 2 ){
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = TRUE
    include_value3 = TRUE
    eval_value4 = FALSE
    include_value4 = FALSE
    plot3_height_factor <- 10 #just to make sure this variable exists, it won't be used
    plot4_height_factor <- 10 #just to make sure this variable exists, it won't be used
  }else{
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = FALSE
    include_value3 = FALSE
    eval_value4 = FALSE
    include_value4 = FALSE
    plot3_height_factor <- 10 #just to make sure this variable exists, it won't be used
    plot4_height_factor <- 10 #just to make sure this variable exists, it won't be used
  }
  
} else if (  nrow(raw_data[raw_data$TL != raw_data$TR, ]) == 0 & 
             nrow(raw_data[raw_data$TL == raw_data$TR, ]) == 0  ){
  
  stop('There is no valid data for this data comparison report. ')
  
} else{
  ##what if there is only one kind of OC_UID for daily OCs
  if ( length(unique(raw_data[raw_data$TL == raw_data$TR, ]$OC_UID)) >= 2 ){
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = TRUE
    include_value3 = TRUE
    eval_value4 = TRUE
    include_value4 = TRUE
    
  }else{
    eval_value2 = TRUE
    include_value2 = TRUE
    eval_value3 = FALSE
    include_value3 = FALSE
    eval_value4 = TRUE
    include_value4 = TRUE
    plot3_height_factor <- 10 #just to make sure this variable exists, it won't be used
    plot4_height_factor <- 10 #just to make sure this variable exists, it won't be used
  }

}

### Another situation is when there are very few daily cases (they are actually period cases instead)
if (  nrow(raw_data[raw_data$TL != raw_data$TR, ]) > 0 & 
      nrow(raw_data[raw_data$TL == raw_data$TR, ]) > 0 &
      nrow(raw_data[raw_data$TL == raw_data$TR, ]) < 365 ){
  eval_value2 = FALSE
  include_value2 = FALSE
  eval_value3 = FALSE
  include_value3 = FALSE
  eval_value4 = FALSE
  include_value4 = FALSE
  plot3_height_factor <- 10 #just to make sure this variable exists, it won't be used
  plot4_height_factor <- 10 #just to make sure this variable exists, it won't be used
  print('The rest of the figures will not be generated because the daily OCs are missing. ')
}

```



## Overall figure -- cumulative cases by location and year
### This cumulative cases figure also includes all (or specified) raw observation collections used in the model.
#### The daily-based observations are cumulative and represented in connected dots
#### The period-based observations (total number of cases) are represented in rectangles
```{r echo=FALSE}
plot2_ncol_factor <- 2 #for now
plot2_height_factor <- 3 * length(unique(raw_data_filtered$location_name)) * length(unique(raw_data_filtered$year)) / plot2_ncol_factor

```

```{r eval=eval_value2, include=include_value2, echo=FALSE, fig.height=as.numeric(plot2_height_factor), fig.width=10}

if ( nrow(raw_data[raw_data$TL != raw_data$TR, ]) > 0 & 
     nrow(raw_data[raw_data$TL == raw_data$TR, ]) > 0  ) {
  raw_data_filtered %>% 
    filter(TL != TR) %>% 
    ggplot(aes(x = ymd(TL), y = suspected_cases, 
               color = OC_UID)) +
    geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                  ymax = suspected_cases, 
                  color = OC_UID),
              fill = NA, size = 0.7, alpha = 0.3, 
              stat = "identity") +
    geom_point(data = (raw_data_filtered %>% 
                         filter(TL == TR) %>%
                         group_by(OC_UID, location_name, year) %>% 
                         arrange(TL, .by_group =  TRUE) %>% 
                         mutate(cum_cases = cumsum(suspected_cases))
                       ),
               aes(x=ymd(TL), y=cum_cases),
               size = 0.5, alpha=0.5, shape=23) +
    geom_line(data = (raw_data_filtered %>% 
                        filter(TL == TR) %>%
                        group_by(OC_UID, location_name, year) %>% 
                        arrange(TL, .by_group =  TRUE) %>% 
                        mutate(cum_cases = cumsum(suspected_cases))
                      ),
              aes(x=ymd(TL), y=cum_cases),
              size = 0.3, alpha=0.5) +
    facet_wrap(~year + location_name, ncol = as.integer(plot2_ncol_factor), scales = "free") +
    theme_bw()
}else if (nrow(raw_data[raw_data$TL == raw_data$TR, ]) > 0){
  raw_data_filtered %>%
    geom_point(data = (raw_data_filtered %>% 
                         filter(TL == TR) %>%
                         group_by(OC_UID, location_name, year) %>% 
                         arrange(TL, .by_group =  TRUE) %>% 
                         mutate(cum_cases = cumsum(suspected_cases))
                       ),
               aes(x=ymd(TL), y=cum_cases),
               size = 0.5, alpha=0.5, shape=23) +
    geom_line(data = (raw_data_filtered %>% 
                        filter(TL == TR) %>%
                        group_by(OC_UID, location_name, year) %>% 
                        arrange(TL, .by_group =  TRUE) %>% 
                        mutate(cum_cases = cumsum(suspected_cases))
                      ),
              aes(x=ymd(TL), y=cum_cases),
              size = 0.3, alpha=0.5) +
    facet_wrap(~year + location_name, ncol = as.integer(plot2_ncol_factor), scales = "free") +
    theme_bw()
  }


```



## Disagree -- daily incidence v.s daily incidence from different OC
### This figure compares the discrepancies between all daily-based observations between any two different observation collections for a certain location and a certain year, and only includes those disagree with specified disagreement threshold (default is 0).
#### The daily-based observations are represented in vertical lines 
```{r echo=FALSE, eval=eval_value3, include=include_value3}
### what if daily observations from the same OC don't agree with with each other?!
temp_df <- raw_data_filtered %>% 
  filter(TL == TR) %>% 
  group_by(year, location_name, OC_UID, TL) %>% 
  summarise(n = n())
if (sum(temp_df$n) > nrow(temp_df)){
  print('Warning: some daily observations from the same OC do not agree with with each other, 
        but did not get plotted in the following figure. ')
}


raw_data_filtered_dis_daily <- raw_data_filtered %>% 
  filter(TL == TR) %>% 
  mutate(groups_compared = NA, oc1 = NA, oc2 = NA, lower_oc = NA, higher_oc = NA)

raw_data_filtered_dis_daily_stack <- raw_data_filtered_dis_daily[1, ]
raw_data_filtered_dis_daily_stack <- raw_data_filtered_dis_daily_stack[-c(1),]

all_combi <- combn(unique(raw_data_filtered_dis_daily$OC_UID), 2)

plot3_ncol_factor <- 2 #for now
# plot3_height_factor <- (3 * length(unique(raw_data_filtered_dis_daily$location_name)) 
#                           * length(unique(raw_data_filtered_dis_daily$year))
#                           * dim(all_combi)[2] 
#                           / plot3_ncol_factor)

```

```{r echo=FALSE, eval=eval_value3, include=include_value3}
### tailor the dataset
for (locations in unique(raw_data_filtered_dis_daily$location_name)){
  for (years in unique(raw_data_filtered_dis_daily$year)){
    for (combi_num in 1:dim(all_combi)[2]) {
      combi = all_combi[, combi_num]
      raw_data_filtered_dis_daily_temp1 <- raw_data_filtered_dis_daily[
        raw_data_filtered_dis_daily$location_name == locations
        &raw_data_filtered_dis_daily$year == years
        &raw_data_filtered_dis_daily$OC_UID == combi[1], ] %>% 
        mutate(oc1 = suspected_cases) %>% 
        mutate(groups_compared = paste0('green_', combi[1], '_v.s_red_', combi[2]))
      TLs1 <- unique(raw_data_filtered_dis_daily_temp1$TL)
      raw_data_filtered_dis_daily_temp2 <- raw_data_filtered_dis_daily[
        raw_data_filtered_dis_daily$location_name == locations
        &raw_data_filtered_dis_daily$year == years
        &raw_data_filtered_dis_daily$OC_UID == combi[2], ] %>% 
        mutate(oc2 = suspected_cases) %>% 
        mutate(groups_compared = paste0('green_', combi[1], '_v.s_red_', combi[2]))
      TLs2 <- unique(raw_data_filtered_dis_daily_temp2$TL)
      TLsTotal <- unique(c(TLs1, TLs2))
      for (TLs in unique(TLsTotal)){
        if(TLs %in% TLs1 & TLs %in% TLs2){
          raw_data_filtered_dis_daily_stack <- rbind(raw_data_filtered_dis_daily_stack,
                                                     raw_data_filtered_dis_daily_temp1[
                                                       raw_data_filtered_dis_daily_temp1$TL == TLs,
                                                     ])
          raw_data_filtered_dis_daily_stack[
            raw_data_filtered_dis_daily_stack$location_name == locations
            &raw_data_filtered_dis_daily_stack$year == years
            &raw_data_filtered_dis_daily_stack$groups_compared == paste0('green_', combi[1], '_v.s_red_', combi[2])
            &raw_data_filtered_dis_daily_stack$TL == TLs,]$oc2 <- 
            raw_data_filtered_dis_daily_temp2[
              raw_data_filtered_dis_daily_temp2$TL == TLs,]$oc2
            
        }else if(TLs %in% TLs1){
          raw_data_filtered_dis_daily_stack <- rbind(raw_data_filtered_dis_daily_stack,
                                                     raw_data_filtered_dis_daily_temp1[
                                                       raw_data_filtered_dis_daily_temp1$TL == TLs,
                                                     ])
          raw_data_filtered_dis_daily_stack[
            raw_data_filtered_dis_daily_stack$location_name == locations
            &raw_data_filtered_dis_daily_stack$year == years
            &raw_data_filtered_dis_daily_stack$groups_compared == paste0('green_', combi[1], '_v.s_red_', combi[2])
            &raw_data_filtered_dis_daily_stack$TL == TLs,]$oc2 <- - NA
          
        }else if(TLs %in% TLs2){
          raw_data_filtered_dis_daily_stack <- rbind(raw_data_filtered_dis_daily_stack,
                                                     raw_data_filtered_dis_daily_temp2[
                                                       raw_data_filtered_dis_daily_temp2$TL == TLs,
                                                     ])
          raw_data_filtered_dis_daily_stack[
            raw_data_filtered_dis_daily_stack$location_name == locations
            &raw_data_filtered_dis_daily_stack$year == years
            &raw_data_filtered_dis_daily_stack$groups_compared == paste0('green_', combi[1], '_v.s_red_', combi[2])
            &raw_data_filtered_dis_daily_stack$TL == TLs,]$oc1 <- - NA
          
        }
      }
    }
  }
}

raw_data_filtered_dis_daily_stack <- raw_data_filtered_dis_daily_stack %>% 
  filter(oc1 != oc2 | is.na(oc1) | is.na(oc2)) %>%
  filter(abs(oc1 - oc2) >= daily_daily_obs_disagree_threshold | 
           ( is.na(oc1) | is.na(oc2) )) %>%
  select(-suspected_cases) %>% 
  rowwise() %>%
  mutate(lower_oc = min(oc1, oc2), 
         higher_oc = max(oc1, oc2))

plot3_height_factor <- (3 * nrow(unique(raw_data_filtered_dis_daily_stack[c("location_name", 
                                                                            "year",
                                                                            "groups_compared")]))
                          / plot3_ncol_factor)

###what if there is no row
if (plot3_height_factor == 0){
  print(paste0('The third figure will not be generated because the daily-daily disagreement threshold, which is ', 
                daily_daily_obs_disagree_threshold, ', is too high. '))
  eval_value3 <- FALSE
  include_value3 <- FALSE
}

```

```{r echo=FALSE, eval=eval_value3, include=include_value3, fig.height=as.numeric(plot3_height_factor), fig.width=10}
### officially plot the figure 3
raw_data_filtered_dis_daily_stack %>% 
  ggplot() +
  geom_segment( aes(x=ymd(TL), xend=ymd(TL), y=lower_oc, yend=higher_oc), 
                color="orange", size = 0.30 ) +
  geom_point( aes(x=ymd(TL), y=oc1), color=rgb(0.2,0.7,0.1,0.5), 
              size = 0.7, alpha=1, shape=23 ) +
  geom_point( aes(x=ymd(TL), y=oc2), color=rgb(0.7,0.2,0.1,0.5), 
              size = 0.7, alpha=1, shape=23 ) +
  facet_wrap( ~ location_name + groups_compared + year, ncol = as.integer(plot3_ncol_factor), scales = "free") +
  theme_bw()

```

```{r echo=FALSE, eval=eval_value3, include=include_value3}
### Just a heads up for scenarios where only figure 4 won't be generated
if (eval_value4 == FALSE){
  print('The next disagreement figure will not be generated because the period OCs are missing. ')
  }

```



## Disagree -- #cases over periods v.s daily incidence
### This figure compares the discrepancies between daily-based and period-based observations between any two same or different observation collections for a certain location and a certain year, and only includes those disagree with specified disagreement threshold (default is 0).
#### The daily-based observations are represented in vertical lines 
#### The period-based observations (total number of cases) are represented in rectangles
#### The horizontal dashed line represents the average of the daily-based observations over the compared period
```{r echo=FALSE, eval=eval_value4, include=include_value4}
raw_data_filtered_dis_period <- raw_data_filtered %>% 
  mutate(period_token = case_when(TL != TR ~ 1,
                                  TRUE ~ 0),
         daily_token = case_when(TL == TR ~ 1,
                                  TRUE ~ 0),
         dis_period = 0,
         mean_daily = NA, 
         x_left = NA_Date_,
         x_right = NA_Date_)
period_factor <- length(unique(raw_data_filtered_dis_period[raw_data_filtered_dis_period$period_token == 1, ]$OC_UID))
daily_factor <- length(unique(raw_data_filtered_dis_period[raw_data_filtered_dis_period$daily_token == 1, ]$OC_UID))

raw_data_filtered_dis_period_stack <- raw_data_filtered_dis_period[1, ]
raw_data_filtered_dis_period_stack <- raw_data_filtered_dis_period_stack[-c(1),]

plot4_ncol_factor <- 2 #for now
# plot4_height_factor <- (3 * length(unique(raw_data_filtered_dis_period$location_name)) 
#                           * length(unique(raw_data_filtered_dis_period$year))
#                           * as.integer(period_factor) * as.integer(daily_factor)
#                           / plot4_ncol_factor)

```

```{r echo=FALSE, eval=eval_value4, include=include_value4}
### tailor the dataset
for (locations in unique(raw_data_filtered_dis_period$location_name)){
  for (years in unique(raw_data_filtered_dis_period$year)){
    for (ocids in unique(raw_data_filtered_dis_period$OC_UID)){
      if (any(raw_data_filtered_dis_period[
        raw_data_filtered_dis_period$location_name == locations
        &raw_data_filtered_dis_period$year == years
        &raw_data_filtered_dis_period$OC_UID == ocids, ]$period_token == 1)){
        TL <- raw_data_filtered_dis_period[
          raw_data_filtered_dis_period$location_name == locations
          &raw_data_filtered_dis_period$year == years
          &raw_data_filtered_dis_period$OC_UID == ocids
          &raw_data_filtered_dis_period$period_token == 1, ]$TL
        TR <- raw_data_filtered_dis_period[
          raw_data_filtered_dis_period$location_name == locations
          &raw_data_filtered_dis_period$year == years
          &raw_data_filtered_dis_period$OC_UID == ocids
          &raw_data_filtered_dis_period$period_token == 1, ]$TR
        for (h in 1:length(TL)){
          TLs <- TL[h]
          TRs <- TR[h]
          extract_cases <- raw_data_filtered_dis_period[
            raw_data_filtered_dis_period$location_name == locations
            &raw_data_filtered_dis_period$year == years
            &raw_data_filtered_dis_period$OC_UID == ocids
            &raw_data_filtered_dis_period$period_token == 1
            &raw_data_filtered_dis_period$TL == TLs
            &raw_data_filtered_dis_period$TR == TRs, ]$suspected_cases
          for (ocids_2 in unique(raw_data_filtered_dis_period$OC_UID)){
            if (any(raw_data_filtered_dis_period[
              raw_data_filtered_dis_period$location_name == locations
              &raw_data_filtered_dis_period$year == years
              &raw_data_filtered_dis_period$OC_UID == ocids_2, ]$daily_token == 1)){
              sum_cases <- sum(raw_data_filtered_dis_period[
                raw_data_filtered_dis_period$location_name == locations
                &raw_data_filtered_dis_period$year == years
                &raw_data_filtered_dis_period$OC_UID == ocids_2 
                &raw_data_filtered_dis_period$daily_token == 1
                &raw_data_filtered_dis_period$TL %in% seq(as.Date(TLs), as.Date(TRs), by="days"), ]$suspected_cases,
                na.rm = TRUE)
              if (sum_cases != extract_cases & abs(sum_cases - extract_cases) >= daily_period_obs_disagree_threshold){
                new_df1 <- raw_data_filtered_dis_period[
                  raw_data_filtered_dis_period$location_name == locations
                  &raw_data_filtered_dis_period$year == years
                  &raw_data_filtered_dis_period$OC_UID == ocids
                  &raw_data_filtered_dis_period$period_token == 1
                  &raw_data_filtered_dis_period$TL == TLs
                  &raw_data_filtered_dis_period$TR == TRs, ] %>% 
                  mutate(dis_period = paste0("period_from_", ocids, "_daily_from_", ocids_2))
                new_df2 <- raw_data_filtered_dis_period[
                  raw_data_filtered_dis_period$location_name == locations
                  &raw_data_filtered_dis_period$year == years
                  &raw_data_filtered_dis_period$OC_UID == ocids_2 
                  &raw_data_filtered_dis_period$daily_token == 1
                  &raw_data_filtered_dis_period$TL %in% seq(as.Date(TLs), as.Date(TRs), by="days"), ] %>% 
                  mutate(dis_period = paste0("period_from_", ocids, "_daily_from_", ocids_2)) %>% 
                  mutate(mean_daily = mean(suspected_cases), 
                         x_left = TLs, x_right = TRs)
                raw_data_filtered_dis_period_stack <-
                  rbind(raw_data_filtered_dis_period_stack, new_df1)
                raw_data_filtered_dis_period_stack <-
                  rbind(raw_data_filtered_dis_period_stack, new_df2)
              }
            }
          }
        }
      }
    }
  }
}

plot4_height_factor <- (3 * nrow(raw_data_filtered_dis_period_stack[raw_data_filtered_dis_period_stack$period_token == 1, ])
                          / plot4_ncol_factor)
# ##diagnose this plot4_height_factor
# stop(paste0('The class of plot4_height_factor is ', class(plot4_height_factor), ' and its value is ', plot4_height_factor))
if (nrow(raw_data_filtered_dis_period_stack[raw_data_filtered_dis_period_stack$period_token == 1, ]) == 0){
  print(paste0('The last figure will not be generated because the daily-period disagreement threshold, which is ', 
                daily_period_obs_disagree_threshold, ', is too high. '))
  eval_value4 <- FALSE
  include_value4 <- FALSE
}

```

```{r echo=FALSE, eval=eval_value4, include=include_value4, fig.height=as.numeric(plot4_height_factor), fig.width=10}
### officially plot the figure 4
raw_data_filtered_dis_period_stack %>% 
  filter(TL != TR) %>% 
  ggplot(aes(x = ymd(TL), y = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
             color = OC_UID)) +
  geom_rect(aes(xmin = TL, xmax = TR, ymin = 0, 
                ymax = suspected_cases/(time_length(interval(TL, TR), 'day') + 1), 
                colour = OC_UID),
            fill = NA, size = 1.2, alpha = 0.3, 
            stat = "identity") +
  geom_segment( data = (raw_data_filtered_dis_period_stack %>% filter(TR == TL)),
                aes(x=ymd(TL), xend=ymd(TL), y=0, yend=suspected_cases), 
                size=0.7, alpha=0.7) + 
  geom_point(data = (raw_data_filtered_dis_period_stack %>% filter(TR == TL)),
             aes(x=ymd(TL), y=suspected_cases),
             size=1.2, alpha=1, shape=23) +
  geom_segment( data = (raw_data_filtered_dis_period_stack %>% filter(TR == TL)),
                aes(x=ymd(x_left), xend=ymd(x_right), 
                    y=mean_daily, yend=mean_daily), 
                size=0.5, alpha=1, linetype="dashed") + 
  facet_wrap( ~ location_name + dis_period + year, ncol = as.integer(plot4_ncol_factor), scales = "free") +
  theme_bw()

```
