---
title: "Global Cholera Burden"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  cholera_directory: "cholera-mapping-pipeline"
  config: "configs/"
  data_dir: "data"
  output_dir: "output"
  interm_dir: "interm"
  figures: "figures"
---
```{r setup, include=FALSE, dev="CairoPNG",message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf) 
sf::sf_use_s2(FALSE)
library(lubridate)
library(rstan)
library(cmdstanr)
library(optparse)
library(foreach)
library(rmapshaper)
library(taxdat)
library(whoville)

# Get all configs ----
config_dir <- paste0(params$config)
config_list <- dir(config_dir, pattern = "yml", full.names = T)

# Get intended runs ---------------------------------------
intended_runs <- get_intended_runs(csv_path = 'Data Entry Coordination - Data Entry Tracking - Feb 2022.csv')

# Spatial data  ---------------------------------------
## create ADM0 shapefiles for all countries: 
# boundary_sf <- rgeoboundaries::geoboundaries(country = NULL,adm_lvl = "adm0") %>%
#     dplyr::mutate(country = shapeGroup) %>%
#     dplyr::select(country,shapeName, shapeType, geometry) %>%
#     dplyr::mutate(source = "rgeoboundaries")
# 
#   # Set reference WGS84 projection
#   sf::st_crs(boundary_sf) <- sf::st_crs(4326)
#   sf::st_geometry(boundary_sf) <- "geom"
# 
#   # Fix geometry collections if any
#   boundary_sf <- fix_geomcollections(boundary_sf)
# 
#   # Combine into multipolygons
#   boundary_sf <- sf::st_cast(boundary_sf, "MULTIPOLYGON")
#   boundary_sf <- boundary_sf %>%
#     dplyr::group_by(shapeName,country) %>%
#     dplyr::summarise(
#                      shapeType = shapeType[1],
#                      source = source[1])
#   
# boundary_sf <- boundary_sf %>% mutate(
#   intended_run = country%in%global_sf$country)
# 
# country_data <- iso3_to_regions(global_sf$country)
# global_sf <- global_sf %>% mutate(who_region = iso3_to_regions(country))
# global_sf <- global_sf%>%mutate(intended_run = country%in%intended_runs$country)
# global_sf[global_sf$country=="FRA",]$intended_run=T
#saveRDS(global_sf,"global_sf.rds")
global_sf <- readRDS("global_sf.rds")

# MAI cases at grid level ---- 
## Helper functions ---
postprocess_grid_mai_cases <- function(config_list,
                                       redo_aux = FALSE) {
  
  # Get genquant data
  genquant <- readRDS(config_list$file_names$stan_genquant_filename) 
  
  # Get mean annual incidence rates at space grid level
  mai_summary <- genquant$summary("space_grid_rates", custom_summaries())
  
  # Get population and average over space grid
  mean_pop_sf <- taxdat:::get_mean_pop_grid(config_list = config_list,
                                   redo = redo_aux)
  
  # Get the output shapefiles and join
  res <- mean_pop_sf %>% 
    dplyr::bind_cols(mai_summary) %>% 
    dplyr::select(-variable) %>% 
    dplyr::mutate(dplyr::across(.cols = c("mean", "q2.5", "q97.5"),
                                ~ . * pop)) %>% 
    dplyr::mutate(country = config_list$countries_name)
  
  res
}


collapse_grid <- function(df,
                          by_draw = FALSE) {
  
  u_grid <- df  %>%
    dplyr::group_by(rid, x, y,country) %>% 
    dplyr::slice(1) %>% 
    dplyr::select(rid, x, y, country,geom)
  
  
  if (!by_draw) {
    res <- df %>%
      sf::st_drop_geometry() %>% 
      dplyr::group_by(rid, x, y,country) %>% 
      dplyr::summarise(mean = mean(mean),
                       q2.5 = min(q2.5),
                       q97.5 = max(q97.5),
                       overlap = n() > 1) %>% 
      dplyr::inner_join(u_grid, .)
  } else {
    res <- df %>%
      sf::st_drop_geometry() %>% 
      dplyr::group_by(rid, x, y, country, .draw) %>% 
      dplyr::summarise(value = mean(value),
                       overlap = n() > 1) %>% 
      dplyr::inner_join(u_grid, .)
  }
  
  res
}

mai_grid_cases_stats <- run_all(
  config_dir = config_dir,
  fun = postprocess_grid_mai_cases,
  postprocess_fun = collapse_grid,
  fun_name = "mai_grid_cases",
  post_process_fun = collapse_grid,
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = F,
  redo_interm = F,
  redo_aux = F,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T) %>% 
  mutate(
    intended_run = TRUE
  )

# Cases by region ----
## update the get AFR region to include all other regions ----
### Helper functions ----
get_global_region <- function(data, ctry_col) {
  
  data_with_global_region <- data %>% 
    dplyr::mutate(
      global_region = dplyr::case_when(
        !!rlang::sym(ctry_col) %in% c("BDI","COM","ETH","KEN","MDG","RWA","SSD","UGA","TZA","ERI") ~ "Eastern Africa",
        !!rlang::sym(ctry_col) %in% c("BWA","MOZ","MWI","NAM","SWZ","ZMB","ZWE","ZAF","LSO") ~ "Southern Africa",
        !!rlang::sym(ctry_col) %in% c("AGO","CMR","CAF","TCD","COG","COD","GNQ","GNA","GAB") ~ "Central Africa",
        !!rlang::sym(ctry_col) %in% c("BEN","BFA","CIV","GHA","GIN","GMB","GNB","LBR","MLI","MRT","NER","NGA","SEN","SLE","TGO") ~ "Western Africa",
        !!rlang::sym(ctry_col) %in% c("DOM","HTI") ~ "Americas",
        !!rlang::sym(ctry_col) %in% c("BGD","MMR","NPL","THA","IND") ~ "South-East Asia",
        !!rlang::sym(ctry_col) %in% c("AFG","IRQ","LBN","PAK","SAU","SYR","ARE","YEM","SDN","SOM","DJI") ~ "Eastern Mediterranean",
        !!rlang::sym(ctry_col) %in% c("CHN","PHL") ~ "Western Pacific",
        !!rlang::sym(ctry_col) %in% c("MYT") ~ "Europe",
        TRUE ~ !!rlang::sym(ctry_col)
      ) 
    )
  
  return(data_with_global_region)
}

aggregate_and_summarise_draws_by_global_region <- function(df, 
                                                    col = "country_cases",
                                                    grouping_variables = NULL,
                                                    weights_col = NULL,
                                                    do_summary = TRUE) {
  
  # Define columns from which to extract names
  if (!is.null(grouping_variables)) {
    name_cols <-   c("global_region", grouping_variables)
  } else {
    name_cols <- "global_region"
  }
  
  df %>% 
    get_global_region(ctry_col = "country") %>% 
    dplyr::group_by_at(c(".draw", "global_region", grouping_variables)) %>% 
    {
      x <- .
      if (is.null(weights_col)) {
        dplyr::summarise(x, tot = sum(!!rlang::sym(col))) 
      } else {
        dplyr::summarise(x, tot = sum(!!rlang::sym(col) * !!rlang::sym(weights_col))/sum(!!rlang::sym(weights_col))) 
      }
    } %>% 
    dplyr::ungroup() %>% 
    tidyr::pivot_wider(names_from = name_cols,
                       values_from = "tot") %>% 
    janitor::clean_names() %>% 
    dplyr::select(-draw) %>% 
    magrittr::set_names(stringr::str_c(col, colnames(.), sep = "_")) %>% 
    posterior::as_draws() %>% 
    {
      x <- .
      if(do_summary) {
        posterior::summarise_draws(x, custom_summaries())
      } else {
        posterior::as_draws_df(x) %>% 
          dplyr::as_tibble()
      }
    }
}

get_global_region_levels <- function() {
  c("Eastern Mediterranean","Western Africa", "Central Africa", "Eastern Africa", "Southern Africa","South-East Asia","Western Pacific","Americas","Europe")
}

parse_global_region <- function(df) {
  
  if (!("global_region" %in% colnames(df))) {
    stop("global_region needs to be defined to be parsed")
  }
  
  df %>% 
    mutate(global_region = global_region %>% 
             str_replace("_", " ") %>% 
             str_to_title() %>% 
             str_replace("South East_asia",'South-East Asia'),
           global_region = factor(global_region, 
                                levels = get_global_region_levels()))
}

cases_by_region  <- run_all(
  config_dir = config_dir,
  fun = postprocess_adm0_cases,
  fun_name = "mai_cases_by_region",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws_by_global_region,
  postprocess_fun_opts = list(col = "country_cases"),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T) %>% 
  mutate(
    global_region = str_remove(variable,'country_cases_')
  ) %>% 
  parse_global_region()

overall_sim_stats <- run_all(
  config_dir = config_dir,
  fun = postprocess_mai_adm0_simulated_cases,
  fun_name = "mai_simulated_cases_all",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws,
  postprocess_fun_opts = list(col = "sim_country_cases"),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

# pop at risk ----
## Helper functions ----
aggregate_and_summarise_draws_by_global_region <- function(df, 
                                                    col = "country_cases",
                                                    grouping_variables = NULL,
                                                    weights_col = NULL,
                                                    do_summary = TRUE) {
  
  # Define columns from which to extract names
  if (!is.null(grouping_variables)) {
    name_cols <-   c("global_region", grouping_variables)
  } else {
    name_cols <- "global_region"
  }
  
  df %>% 
    get_global_region(ctry_col = "country") %>% 
    dplyr::group_by_at(c(".draw", "global_region", grouping_variables)) %>% 
    {
      x <- .
      if (is.null(weights_col)) {
        dplyr::summarise(x, tot = sum(!!rlang::sym(col))) 
      } else {
        dplyr::summarise(x, tot = sum(!!rlang::sym(col) * !!rlang::sym(weights_col))/sum(!!rlang::sym(weights_col))) 
      }
    } %>% 
    dplyr::ungroup() %>% 
    tidyr::pivot_wider(names_from = name_cols,
                       values_from = "tot") %>% 
    janitor::clean_names() %>% 
    dplyr::select(-draw) %>% 
    magrittr::set_names(stringr::str_c(col, colnames(.), sep = "_")) %>% 
    posterior::as_draws() %>% 
    {
      x <- .
      if(do_summary) {
        posterior::summarise_draws(x, custom_summaries())
      } else {
        posterior::as_draws_df(x) %>% 
          dplyr::as_tibble()
      }
    }
}
pop_at_risk_regions <- run_all(
  config_dir = config_dir,
  fun = postprocess_pop_at_risk_draws,
  fun_name = "pop_at_risk_by_region",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws_by_global_region,
  postprocess_fun_opts = list(col = "tot_pop_risk",
                              grouping_variables = c("admin_level", "risk_cat")),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

pop_at_risk_all <- run_all(
  config_dir = config_dir,
  fun = postprocess_pop_at_risk_draws,
  fun_name = "pop_at_risk_all",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws,
  postprocess_fun_opts = list(col = "tot_pop_risk",
                              grouping_variables = c("admin_level", "risk_cat")),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

# Adm0 cases ----
mean_adm0_cases_by_time <- run_all(
  config_dir = config_dir,
  fun = postprocess_annual_adm0_cases,
  fun_name = "mai_adm0_cases_by_time",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T
)

# WHO ests from preprocess data ----
## Helper function ----
postprocess_WHO_est <- function(config_list,
                                    redo_aux = FALSE) {
  # Get WHO annual report OCs
  who_OCs <- read.csv('Analysis/output/global_burden_reports/who_annual_report_OCs(World).csv')
  
  # Get preprocess data
  load(config_list$file_names$observations_filename) 
  
  # Get who annual estimates
  who_ests <- sf_cases %>% dplyr::filter(OC_UID %in% who_OCs$Related.WHO.Annual.Report.OC)

  who_ests
}

who_ests_by_time <- run_all(
  config_dir = config_dir,
  fun = postprocess_WHO_est,
  fun_name = "who_est",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T
)

# Plotting helper function ---
colors_global_regions <- function(){
  # colors <- RColorBrewer::brewer.pal("Set2", n = 4)
  colors <- c("#FFA378", "#A8B545", "#8C796D", "#024554","#C93E3E","#E1AF00","#6A5ACA","#009999","#7B7B7B")
  names(colors) <- c("Western Africa", "Central Africa",
                     "Eastern Africa", "Southern Africa",
                     "Americas","South-East Asia","Eastern Mediterranean","Western Pacific","Europe")
  colors
}

color_run_intended <- function(){c("#A1A1A1")}
color_no_run_intended <- function(){c("#FFFFFF")}
color_afr_continent_fill <- function(){c("#FFFFFF")}

colors_lisa_clusters <- function(){c("lightgray", "#D40A07", "#4543C4", "#F26F6D", "#7C7AC2", "#424141", "#A059F7")}
coloramp_cases <- function(){c("#FFFFFF", "#FED98E", "#FE9929", "#D95F0E", "#993404")}

expand_bbox_ratio <- function(bb, ratio = 0.06) {
  w <- bb["xmax"] - bb["xmin"] 
  h <- bb["ymax"] - bb["ymin"]
  dx <- as.numeric(w) * ratio 
  dy <- as.numeric(h) * ratio
  bb["xmin"] <- bb["xmin"] - dx 
  bb["xmax"] <- bb["xmax"] + dx
  bb["ymin"] <- bb["ymin"] - dy 
  bb["ymax"] <- bb["ymax"] + dy
  bb
}

crop_polygon <- function(sf_obj, margin_km = NULL, margin_ratio = 0.06, crs_out = sf::st_crs(sf_obj)) {
  
  if (length(sf_obj) == 0) {
    bb <- sf::st_bbox(sf_obj)
    bb_exp <- expand_bbox_ratio(bb, margin_ratio)
    return(sf::st_as_sfc(bb_exp, crs = sf::st_crs(sf_obj)))
  }

  g <- suppressWarnings(sf::st_make_valid(sf::st_union(sf_obj)))

  if (!is.null(margin_km) && is.finite(margin_km) && margin_km > 0) {
    g_merc <- sf::st_transform(g, 3857)
    g_buf  <- sf::st_buffer(g_merc, margin_km * 1000)
    g_crop <- sf::st_transform(g_buf, crs_out)
  } else {
    bb     <- sf::st_bbox(g)
    bb_exp <- expand_bbox_ratio(bb, margin_ratio)
    g_crop <- sf::st_as_sfc(bb_exp, crs = sf::st_crs(sf_obj))
  }
  g_crop
}

output_plot_map <- function(sf_obj,
                            all_countries_sf,
                            lakes_sf = NULL,
                            rivers_sf = NULL,
                            fill_var,
                            fill_color_scale_type,
                            border_width = 0.005,
                            border_color = "white",
                            lake_alpha = 1,
                            country_border_width = .3,
                            country_border_color = "black",
                            cholera_dir = 'cholera-mapping-pipeline',
                            crop_background = T,
                            crop_margin_km = NULL,
                            crop_margin_ratio = 0.06) {
  
  fv <- rlang::as_string(rlang::ensym(fill_var))
  if (!fv %in% names(sf_obj)) {
    sf_obj[[fv]] <- NA_real_
  }
  
    if (nrow(sf_obj) == 0) {
    sf_obj <- all_countries_sf %>%
      dplyr::mutate(!!fv := NA_real_,
                    intended_run = TRUE)
    sf::st_crs(sf_obj) <- sf::st_crs(all_countries_sf)
  }

  if (crop_background) {
    # whether any of the countries in that region has cases >0
    has_cases <- sum(is.finite(sf_obj[[fv]]), na.rm = TRUE) > 0

    if (has_cases) {
      crop_poly <- crop_polygon(
        sf_obj      = sf_obj,
        margin_km   = crop_margin_km,
        margin_ratio= crop_margin_ratio,
        crs_out     = sf::st_crs(all_countries_sf)
      )
    } else {
      # for com and myt case: 
      base_bb <- sf::st_bbox(all_countries_sf)
      bb_exp <- expand_bbox_ratio(base_bb, margin_ratio)
      crop_poly <- sf::st_as_sfc(bb_exp, crs = sf::st_crs(all_countries_sf))
    }
    
    bg_trim  <- suppressWarnings(sf::st_crop(all_countries_sf, sf::st_bbox(crop_poly)))
    
    all_countries_sf_clipped <- suppressWarnings(sf::st_intersection(sf::st_make_valid(bg_trim),sf::st_make_valid(crop_poly)))
    bb <- sf::st_bbox(crop_poly)
    
  } else {
    all_countries_sf_clipped <- all_countries_sf
    bb <- sf::st_bbox(sf_obj)
  }
  
  sf_obj %>% 
    ggplot2::ggplot(aes(fill = !!sym(fill_var))) +
    ggplot2::geom_sf(data = all_countries_sf_clipped %>%
                       dplyr::filter(!intended_run),
                     inherit.aes = FALSE,
                     lwd = 0,
                     alpha = 1,
                     fill = color_no_run_intended()) +
    ggplot2::geom_sf(data = all_countries_sf_clipped %>% 
                       dplyr::filter(intended_run),
                     inherit.aes = FALSE,
                     lwd = 0,
                     alpha = 1,
                     fill = color_run_intended()) +
    ggplot2::geom_sf(lwd = border_width, color = border_color) + 
    ggplot2::geom_sf(data = all_countries_sf_clipped,
                     fill = color_afr_continent_fill(),
                     color = "black",
                     lwd = country_border_width,
                     alpha = 0) +
    {
      if (!is.null(rivers_sf)) {
        ggplot2::geom_sf(inherit.aes = FALSE,
                         data = rivers_sf,
                         color = color_rivers(),
                         lwd = .1,
                         alpha = 1)
      }
    } +
    {
      if (!is.null(lakes_sf)) {
        ggplot2::geom_sf(inherit.aes = FALSE,
                         data = lakes_sf, 
                         fill = color_lake_fill(),
                         color = color_lake_border(),
                         lwd = .06,
                         alpha = lake_alpha)
      }
    } +
    {  
      if(fill_color_scale_type == "rates") {
        scale_fill_viridis_c(breaks = seq(-1, 2), 
                             labels = formatC(10^(seq(-1, 2)),
                                              digits = 1,
                                              format = "fg", 
                                              big.mark = ",") %>% 
                               {
                                 x <- .
                                 x[1] <- str_c("<= ", x[1])
                                 x[length(x)] <- str_c(">= ", x[length(x)])
                                 x
                               },
                             limits = c(-1, 2.5),
                             option = "plasma",
                             oob = scales::squish)
      } else if(fill_color_scale_type == "ratio") {
        scale_fill_gradient2(breaks = seq(-3, 2), 
                             labels = formatC(10^(seq(-3, 2)),
                                              digits = 1,
                                              format = "fg", 
                                              big.mark = ","),
                             limits = c(-3.1, 2.1),
                             midpoint = 0,
                             oob = scales::squish, 
                             na.value = c("#D4BE77"), 
                             low = "blue",
                             high = "red")
      } else if(fill_color_scale_type == "cases") {
        scale_fill_gradientn(colours = coloramp_cases(),
                             oob = scales::censor, 
                             limits = c(0, NA), 
                             breaks = seq(0, 3), 
                             labels = formatC(10^(seq(0, 3)),
                                              digits = 1,
                                              format = "fg", 
                                              big.mark = ","),
                             na.value = "lightgray")
        
      } else if(fill_color_scale_type == "adm0_cases") {
        scale_fill_gradientn(colours = coloramp_cases(),
                             oob = scales::censor, 
                             limits = c(0, NA), 
                             breaks = seq(0, 3), 
                             labels = formatC(10^(seq(0, 3)),
                                              digits = 1,
                                              format = "fg", 
                                              big.mark = ","),
                             na.value = "lightgray")
        
      } else if(fill_color_scale_type == "mai_exceeding_thresh") {
        scale_fill_manual(values = coloramp_num_years_exceeding_threshold())
      } else if(fill_color_scale_type == "risk category") {
        scale_fill_manual(values = colors_risk_categories())
      } else if(fill_color_scale_type == "lisa cluster") {
        scale_fill_manual(values = colors_lisa_clusters())
      } else if(fill_color_scale_type == "endemicity_high") {
        scale_fill_manual(values = colors_endemicity_high())
      } else if(fill_color_scale_type == "endemicity_low") {
        scale_fill_manual(values = colors_endemicity_low())
      } else if(fill_color_scale_type == "endemicity") {
        scale_fill_manual(values = colors_endemicity(),drop=FALSE)
      } else if(fill_color_scale_type == "admin levels") {
        scale_fill_manual(values = colors_admin_levels(),drop=FALSE)
      }
    } + 
    ggplot2::geom_sf(data = all_countries_sf,
                     inherit.aes = FALSE,
                     lwd = country_border_width,
                     color = country_border_color,
                     alpha = 0) +
    taxdat::map_theme() +
    {if(crop_background){
    ggplot2::coord_sf(xlim = c(bb["xmin"], bb["xmax"]),
                      ylim = c(bb["ymin"], bb["ymax"]),
                      expand = FALSE)       
    }
  } +
    theme(panel.border = element_blank())
  
}

unpack_pop_at_risk <- function(df) {
  
  risk_cat_map <- get_risk_cat_dict()
  names(risk_cat_map) <- janitor::make_clean_names(risk_cat_map) %>% 
    str_remove("x")
  
  
  df %>% 
    mutate(
      risk_cat = str_extract(variable, str_c(rev(names(risk_cat_map)), collapse = "|")),
      risk_cat = factor(risk_cat_map[risk_cat], levels = risk_cat_map),
      admin_level = str_c("ADM", str_extract(variable, "(?<=adm)[0-9]+"))
    )
}
```

## Table 1. List of countries selected for model runs
```{r echo=FALSE,warning=FALSE,message=FALSE}
table1<-data.frame(country = intended_runs$country) %>% 
  get_global_region(ctry_col='country')

table1 %>% 
  arrange(global_region) %>% 
   knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```

## Figure 1. Global Map: MAI cases at grid level
```{r global map, fig.width=12, fig.height=6, echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else{
fig_MAI_grid <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf,
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = F) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid,
         file = "fig1.png",
         width = 12,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}

print("The dark gray area represents countries that have not been modeled yet due to data entry, data audit, location audit, or memory issues. The light gray area represents areas with incidence < 1 case per year. Other white area represents countries which we don't plan to run.")
```

## Maps by region: MAI cases at grid level
### Figure 2. Africa
```{r AFR map,  fig.width=10, fig.height=6, echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_AFR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else{ fig_MAI_grid_Africa <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Africa')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf %>% filter(who_region == "AFR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = F) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_Africa,
         file = "fig1_AFR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 3. Eastern Mediterranean
```{r EMR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_EMR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {fig_MAI_grid_EMR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Eastern Mediterranean')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf %>% filter(who_region == "EMR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = F) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_EMR,
         file = "fig1_EMR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 4. South-East Asia
```{r SEAR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_SEAR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {
  fig_MAI_grid_SEAR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'South-East Asia')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf %>% filter(who_region == "SEAR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = T,
                           crop_margin_km = NULL,
                           crop_margin_ratio = 0.6) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.05, .2),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_SEAR,
         file = "fig1_SEAR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 5. Western Pacific
```{r WPR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_WPR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {# fix the projection of the WPR maps
wpr_sf <- global_sf %>% filter(who_region == "WPR")
wpr_fix <- wpr_sf %>%
  st_make_valid() %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES","DATELINEOFFSET=180"), quiet = TRUE) %>%
  st_shift_longitude()

fig_MAI_grid_WPR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Western Pacific')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = wpr_fix,
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = T,
                           crop_margin_km = NULL,
                           crop_margin_ratio = 0.06) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_WPR,
         file = "fig1_WPR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 6. Americas
```{r AMR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_AMR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {
  fig_MAI_grid_AMR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Americas')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf =  global_sf %>% filter(who_region == "AMR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = T,
                           crop_margin_km = NULL,
                           crop_margin_ratio = 0.06) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_AMR,
         file = "fig1_AMR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

## Figure 7. Bar plot: Cases by region 
```{r echo=FALSE,warning=FALSE,message=FALSE}
fig_cases_region <- cases_by_region %>% 
  mutate(global_region = factor(global_region, levels = get_global_region_levels()),
         period = '2021-2024') %>% 
  ggplot(aes(x = mean, y = global_region, fill = global_region)) +
  geom_bar(stat = "identity")  +
  geom_errorbarh(
    aes(xmin = q2.5, xmax = q97.5, y = global_region),
    height = .2
  )+
  scale_x_continuous(
    breaks = seq(0, 200000, by = 50000),
    labels = function(x) {
      formatC(x, digits = 0, big.mark = ",", format = "f")
    }) +
  scale_fill_manual(values = colors_global_regions()) +
  theme_bw() +
  theme(legend.position = 'none')+
  labs(x = "Mean annual cholera incidence [cases/year]", 
       y = "Region")

ggsave(fig_cases_region,
         file = "fig2.png",
         width = 12,
         height = 6, 
         dpi = 300)
print(fig_cases_region)

```

## Table 2. MAI by region
```{r echo=FALSE, warning=FALSE, message=FALSE}
table2 <- cases_by_region %>% 
  mutate(global_region = factor(global_region, levels = get_global_region_levels())) %>% 
  bind_rows(
    overall_sim_stats %>%
    mutate(global_region ="Total")
  ) %>% 
  mutate(
    `Mean Annual Cases (95% CrI)` = paste0(round(mean,0)," (",round(q2.5,0), " - ",round(q97.5,0),")")
  ) %>% 
  rename(
    `Global region` = global_region,
  ) %>% 
  select(
    `Global region`, `Mean Annual Cases (95% CrI)`
  ) 

table2 %>% 
  filter(`Global region` != 'Total') %>%
  arrange( `Global region`) %>% 
  bind_rows(
    table2[nrow(table2),]
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```

## Figure 8. Bar plot: Pop at risk by region 
```{r echo=FALSE,fig.height=6, fig.width=10, warning=FALSE,message=FALSE}
risk_pop_all <- pop_at_risk_all %>% 
      unpack_pop_at_risk() %>%
  filter( 
         admin_level == "ADM2",
         risk_cat != "<1") %>% 
  select(risk_cat, mean, q2.5, q97.5) %>% 
  mutate(risk_cat = as.character(risk_cat)) %>% 
  mutate(risk_cat = ifelse(risk_cat == ">100","\u2265100",risk_cat)) %>% 
  mutate(risk_cat = factor(risk_cat,levels = c("<1","1-10","10-20","20-50","50-100","\u2265100" )))

risk_pop_regions <- pop_at_risk_regions %>% 
    mutate(global_region = str_extract(variable, "(?<=tot_pop_risk_)(.)*(?=_adm)")) %>%
    parse_global_region() %>% 
    unpack_pop_at_risk() %>% 
  mutate(period = '2021-2024') %>% 
  filter( 
         admin_level == "ADM2",
         risk_cat != "<1") %>% 
  select(global_region, risk_cat, mean, q2.5, q97.5) %>% 
  mutate(risk_cat = as.character(risk_cat)) %>%
  mutate(risk_cat = ifelse(risk_cat == ">100","\u2265100",risk_cat)) %>% 
  mutate(risk_cat = factor(risk_cat,levels = c("<1","1-10","10-20","20-50","50-100","\u2265100" )))

# Figure 3A
fig_risk_cat <- risk_pop_regions %>%
  ggplot(aes(y = risk_cat, x = mean)) +
  geom_bar(aes(fill = global_region), stat = "identity", width = .5) +
  geom_errorbarh(data = risk_pop_all,
                inherit.aes = F,
                aes(xmin = q2.5, xmax = q97.5, y = risk_cat), height = 0.2) +
  geom_point(data = risk_pop_all, aes(x = mean)) +
  theme_bw() +
  scale_fill_manual(values = colors_global_regions()) +
  scale_x_continuous(labels = function(x) {formatC(x/1e6)}) +
  labs(y = "ADM2 incidence category per 100,000 population", x = "Population living in ADM2 units (millions)",fill="Region")+
  geom_segment(x = 250000000, xend = 250000000, y = "10-20", yend = "\u2265100", colour = "black") +
  geom_segment(x = 230000000, xend = 250000000, y = "10-20", yend = "10-20", colour = "black") +
  geom_segment(x = 230000000, xend = 250000000, y = "\u2265100", yend = "\u2265100", colour = "black") +
  annotate("segment", x = 250000000, xend = 260000000, y = 3.5, yend = 3.5, colour = "black") +
  annotate("text", x = 300000000, y = 3.5, label = '"High\nIncidence"')

ggsave(plot = fig_risk_cat,
         filename = 'fig_risk_cat.png',
         width = 12,
         height = 7,
         dpi = 300)
print(fig_risk_cat)

```

## Table 3. Risk cat by region
```{r echo=FALSE, warning=FALSE, message=FALSE}
table3 <- risk_pop_regions %>% 
  mutate(global_region = factor(global_region, levels = get_global_region_levels())) %>% 
  bind_rows(
    risk_pop_all %>%
    mutate(global_region ="Total")
  ) %>% 
  mutate(
    `Population (95% CrI)` = paste0(round(mean,0)," (",round(q2.5,0), " - ",round(q97.5,0),")")
  ) %>% 
  rename(
    `Global region` = global_region,
    `Risk category (per 100,000 population)` = risk_cat
  ) %>% 
  select(
    `Global region`, `Risk category (per 100,000 population)`,`Population (95% CrI)`
  ) 

table3 %>% 
  filter(`Global region` != 'Total') %>%
  arrange( `Global region`) %>% 
  bind_rows(
    table3%>% filter(`Global region` == 'Total') 
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```


## Table 4. WHO Annual Report Comparison at the country level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
modeled_cases_by_country_by_time <- mean_adm0_cases_by_time %>% 
  select(country, TL, mean) %>%
  rename(mean_modeled_cases = mean)

who_ests_by_region_by_time <- who_ests_by_time %>% 
  st_drop_geometry() %>% 
  mutate(
    country = str_sub(location_name, start=-3),
    WHO_cases = suspected_cases
  ) %>% 
  select(country,TL,WHO_cases)
  
modeled_who_cases <- inner_join(modeled_cases_by_country_by_time,who_ests_by_region_by_time) %>% 
  get_global_region(ctry_col = 'country') %>% 
    mutate(WHO_cases_log = ifelse(WHO_cases > 0, WHO_cases, NA),
         mean_modeled_cases_log = ifelse(mean_modeled_cases > 0, mean_modeled_cases, NA))

table4 <- modeled_who_cases %>% 
  mutate(year = lubridate::year(TL),
         mean_modeled_cases = round(mean_modeled_cases,0)) %>% 
  arrange(global_region) %>% 
  select(global_region,country, year, mean_modeled_cases, WHO_cases)


table4 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```


## Figure 9. WHO Annual Report Comparison at the country level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}

library(scales)
library(ggrepel)

ggplot(modeled_who_cases %>% mutate(year = lubridate::year(TL)), 
       aes(x = WHO_cases_log, y = mean_modeled_cases_log, color = global_region)) +
  geom_point(size = 3, alpha = 0.7, na.rm = TRUE) +
  geom_text_repel(aes(label = country), size = 3, show.legend = FALSE, max.overlaps = 20) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  scale_x_log10(
    name = "Reported WHO cases",
    limits = c(1, 1e5),
    breaks = c(1, 100, 1e4)
  ) +
  scale_y_log10(
    name = "Modeled mean cases",
    limits = c(1, 1e5),
    breaks = c(1, 100, 1e4)
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    axis.text.x = element_text(vjust = 0),
    axis.text.y = element_text(hjust = 1)
  )+
  facet_wrap(~ year)

```


## Table 5. WHO Annual Report Comparison at the continent and global level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
table5 <- modeled_who_cases %>% 
  mutate(year = lubridate::year(TL)) %>% 
  group_by(global_region,year) %>% 
  summarize(
    Total_modeled_cases = round(sum(mean_modeled_cases),0),
    Total_WHO_reported_cases = sum(WHO_cases)
  ) %>% 
  ungroup() %>% 
  arrange(global_region) %>% 
  bind_rows(
    modeled_who_cases %>% 
  mutate(year = lubridate::year(TL)) %>% 
  group_by(year) %>% 
  summarize(
    Total_modeled_cases = round(sum(mean_modeled_cases),0),
    Total_WHO_reported_cases = sum(WHO_cases),
    global_region = "Global"
  )
  )


table5 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```


## Figure 10. WHO Annual Report Comparison at the continent and global level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
ggplot(table5, 
       aes(x = Total_WHO_reported_cases, y = Total_modeled_cases, color = global_region)) +
  geom_point(size = 3, alpha = 0.7, na.rm = TRUE) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  scale_x_log10(
    name = "Reported WHO cases",
    limits = c(1, 1e6),
    breaks = c(1, 100, 1e4, 1e6)
  ) +
  scale_y_log10(
    name = "Modeled mean cases",
    limits = c(1, 1e6),
    breaks = c(1, 100, 1e4,1e6)
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    axis.text.x = element_text(vjust = 0),
    axis.text.y = element_text(hjust = 1)
  )+
  facet_wrap(~ year)

```
