---
title: "Global Cholera Burden"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  cholera_directory: "cholera-mapping-pipeline"
  config: "configs/"
  data_dir: "data"
  output_dir: "output"
  interm_dir: "interm"
  figures: "figures"
---
```{r setup, include=FALSE, dev="CairoPNG",message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf) 
sf::sf_use_s2(FALSE)
library(lubridate)
library(rstan)
library(cmdstanr)
library(optparse)
library(foreach)
library(rmapshaper)
library(taxdat)
library(whoville)
library(scales)
library(ggrepel)

# reinstall taxdat function ----
library(taxdat)

# Get all configs ----
config_dir <- paste0(params$config)
config_list <- dir(config_dir, pattern = "yml", full.names = T)

# Get intended runs ---------------------------------------
#' get_intended_runs_global
#'
#' List of all countries with intended run
#' Sheet Data Entry Tracking Feb 2022 from spreadsheet that can be downloaded from
#' https://docs.google.com/spreadsheets/d/17MtTdUlC2tNLk3QPYdTzgFqiPacUg4rbi8cVTYoOaZE/edit#gid=1264119518

get_intended_runs_global <- function(csv_path = "Analysis/output/Data Entry Coordination - Data Entry Tracking - Feb 2022.csv") {
  readr::read_csv(csv_path) %>% 
    janitor::clean_names() %>% 
    dplyr::mutate(isocode = dplyr::case_when(
      stringr::str_detect(country, "TZA") ~ "TZA",
      T ~ country))
}

intended_runs <- get_intended_runs_global()

# Spatial data  ---------------------------------------
## create ADM0 shapefiles for all countries: 
# boundary_sf <- rgeoboundaries::geoboundaries(country = NULL,adm_lvl = "adm0") %>%
#     dplyr::mutate(country = shapeGroup) %>%
#     dplyr::select(country,shapeName, shapeType, geometry) %>%
#     dplyr::mutate(source = "rgeoboundaries")
# 
#   # Set reference WGS84 projection
#   sf::st_crs(boundary_sf) <- sf::st_crs(4326)
#   sf::st_geometry(boundary_sf) <- "geom"
# 
#   # Fix geometry collections if any
#   boundary_sf <- fix_geomcollections(boundary_sf)
# 
#   # Combine into multipolygons
#   boundary_sf <- sf::st_cast(boundary_sf, "MULTIPOLYGON")
#   boundary_sf <- boundary_sf %>%
#     dplyr::group_by(shapeName,country) %>%
#     dplyr::summarise(
#                      shapeType = shapeType[1],
#                      source = source[1])
#   
# boundary_sf <- boundary_sf %>% mutate(
#   intended_run = country%in%global_sf$country)
# 
# country_data <- iso3_to_regions(global_sf$country)
# global_sf <- global_sf %>% mutate(who_region = iso3_to_regions(country))
# global_sf <- global_sf%>%mutate(intended_run = country%in%intended_runs$country)
# global_sf[global_sf$country=="FRA",]$intended_run=T
#saveRDS(global_sf,"global_sf.rds")
global_sf <- readRDS("global_sf.rds")
#global_sf <- global_sf%>%mutate(intended_run = country%in%intended_runs$country)
#global_sf[global_sf$country=="FRA",]$intended_run=T

# Observations ----
all_obs <- run_all(
  config_dir = config_dir,
  fun = postprocess_observations,
  fun_name = "obs",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = F,
  redo_interm = F,
  redo_aux = F,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T) 

# Shapefiles ----
# All the data shapfiles for spatial coverage
all_shapefiles <- run_all(
  config_dir = config_dir,
  fun = postprocess_lp_shapefiles,
  fun_name = "shapefiles",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = F,
  redo_interm = F,
  redo_aux = F,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T) 

# Summarize spatial, temporal, and case coverage at different spatial scales compared to national burden ----
summary_coverage <- function(
  df = all_obs,
  TL_col = "TL",
  TR_col ="TR",
  sCh_col = "attributes.fields.suspected_cases",
  ref_TL_col ="ref_TL",
  ref_TR_col = "ref_TR",
  admin_level_col ="admin_level",
  censoring_col = "censoring",
  location_name_col = "location_name",
  sf_obj = all_shapefiles
) {
  library(dplyr)
  library(lubridate)
  library(rlang)
  library(sf)
  
  TL_sym  <- sym(TL_col)
  TR_sym    <- sym(TR_col)
  sCh_sym  <- sym(sCh_col)
  ref_TL_sym  <- sym(ref_TL_col)
  ref_TR_sym  <- sym(ref_TR_col)
  adm_sym <- sym(admin_level_col)
  cens_sym<- sym(censoring_col)
  loc_sym <- sym(location_name_col)
  
  df <- df %>%
    mutate(
      !!TL_sym     := as.Date(!!TL_sym),
      !!TR_sym     := as.Date(!!TR_sym)
    )

  
split_row_to_years <- function(row) {
    TL <- row[[TL_col]]
    TR <- row[[TR_col]]
    
    start_year <- year(TL)
    end_year   <- year(TR)
    total_days <- as.numeric(TR - TL + 1)
    
    # Single-year obs
    if (start_year == end_year) {
      year_start <- as.Date(paste0(start_year, "-01-01"))
      year_end   <- as.Date(paste0(start_year, "-12-31"))
      
      row[[ref_TL_col]] <- year_start
      row[[ref_TR_col]] <- year_end
      return(row)
    }
    
    # Multi-year: one row per year, time-weighted sChs
    rows_out <- list()
    idx <- 1L
    
    for (yr in start_year:end_year) {
      year_start <- as.Date(paste0(yr, "-01-01"))
      year_end<- as.Date(paste0(yr, "-12-31"))
      
      TL_part <- max(TL, year_start)
      TR_part <- min(TR, year_end)
      days_part <- as.numeric(TR_part - TL_part + 1)
      if (is.na(days_part) || days_part <= 0) next
      
      row_i <- row
      row_i[[TL_col]] <- TL_part
      row_i[[TR_col]]  <- TR_part
      row_i[[ref_TL_col]]<- year_start
      row_i[[ref_TR_col]]<- year_end
      row_i[[sCh_col]]<- row[[sCh_col]] * days_part / total_days
      
      rows_out[[idx]] <- row_i
      idx <- idx + 1L
    }
    
    dplyr::bind_rows(rows_out)
  }
  
  df_year <- dplyr::bind_rows(
    lapply(seq_len(nrow(df)), function(i) split_row_to_years(df[i, ]))
  ) %>%
    mutate(
      !!ref_TL_sym := as.Date(!!ref_TL_sym),
      !!ref_TR_sym := as.Date(!!ref_TR_sym)
    )
  
nat <- df_year %>%
    filter(!!adm_sym == 0, !!cens_sym == "full") %>%
    group_by(!!ref_TL_sym, !!ref_TR_sym, country) %>%
    summarise(
      national_cases = max(!!sCh_sym, na.rm = TRUE),
      nat_TL  = min(!!TL_sym),
      nat_TR  = max(!!TR_sym),
      .groups        = "drop"
    )
  
 subnat_loc <- df_year %>%
  filter(!!adm_sym != 0) %>%
  group_by(!!adm_sym, country, !!loc_sym, !!ref_TL_sym, !!ref_TR_sym) %>%
  summarise(
    cases_total  = {
      full_mask <- .data[[censoring_col]] == "full"
      if (any(full_mask, na.rm = TRUE)) {
        max(.data[[sCh_col]][full_mask], na.rm = TRUE)
      } else {
        sum(.data[[sCh_col]], na.rm = TRUE)
      }
  },
   TL_min  = min(.data[[TL_col]], na.rm = TRUE),
    TR_max  = min(.data[[TR_col]], na.rm = TRUE),
    .groups = "drop"
  ) 

  subnat_adm <- subnat_loc %>%
    group_by(!!adm_sym, country, !!ref_TL_sym, !!ref_TR_sym) %>%
    summarise(
      cases_full_total = sum(cases_total, na.rm = TRUE),
      TL_min_all = min(TL_min, na.rm = TRUE),
      TR_max_all = max(TR_max, na.rm = TRUE),
      .groups   = "drop"
    )
  
  coverage <- subnat_adm %>%
    left_join(
      nat,
      by = setNames(
        c(ref_TL_col, ref_TR_col, "country"),
        c(ref_TL_col, ref_TR_col, "country")
      )
    ) %>%
    mutate(
      year = year(as.Date(.data[[ref_TL_col]])),
      case_coverage = round(100 * cases_full_total / national_cases,2),
      temporal_coverage = round(100 * as.numeric(TR_max_all - TL_min_all + 1) / 365,2)
    ) %>% 
    select(
      year,country, admin_level, national_cases , case_coverage, temporal_coverage
    ) %>% 
    arrange(case_coverage,desc(national_cases)) %>% 
    arrange(country, admin_level) %>% 
    rename(
      `Proportion of subnational cases (%)` = case_coverage,
      `Proportion of the year covered by subnational cases (%)` = temporal_coverage
    )
  
  coverage
}


summary_spatial_coverage <- function(sf_obj){
    
  sf_df <- st_transform(sf_obj, 6933)

  sf_area <- sf_df %>% 
    mutate(area = as.numeric(st_area(.))) %>% 
    st_drop_geometry()
  
  nat_area <- sf_area %>%
  filter(admin_level == 0) %>% 
  group_by(country, admin_level) %>% 
  summarize(national_area = sum(area))%>%
  select(!admin_level)
  
  subnat_area <- sf_area %>%
  filter(admin_level != 0) %>% 
  group_by(country, admin_level) %>% 
  summarize(subnat_area = sum(area))
  
area_prop <- subnat_area %>%
  left_join(nat_area, by =c("country")) %>%
  mutate(area_proportion = round(100*subnat_area / national_area, 2)) %>%
  filter(admin_level !=0) %>% 
  select(country, admin_level, area_proportion) %>% 
  rename(`Spatial Coverage (%)` = area_proportion) %>%
  arrange(country, admin_level)

area_prop
}

# MAI cases at grid level ---- 
## Helper functions ---
### this function is derived from postprocess_grid_mai_cases taxdat function by adding country name as a column.
postprocess_grid_mai_cases_with_ctry <- function(config_list,
                                       redo_aux = FALSE) {
  
  # Get genquant data
  genquant <- readRDS(config_list$file_names$stan_genquant_filename) 
  
  # Get mean annual incidence rates at space grid level
  mai_summary <- genquant$summary("space_grid_rates", custom_summaries())
  
  # Get population and average over space grid
  mean_pop_sf <- taxdat:::get_mean_pop_grid(config_list = config_list,
                                   redo = redo_aux)
  
  # Get the output shapefiles and join
  res <- mean_pop_sf %>% 
    dplyr::bind_cols(mai_summary) %>% 
    dplyr::select(-variable) %>% 
    dplyr::mutate(dplyr::across(.cols = c("mean", "q2.5", "q97.5"),
                                ~ . * pop)) %>% 
    dplyr::mutate(country = config_list$countries_name)
  
  res
}

### this function is also derived from the taxdat function (collapse_grid) by adding the country name as a new grouping variable.
collapse_grid_with_ctry <- function(df,
                          by_draw = FALSE) {
  
  u_grid <- df  %>%
    dplyr::group_by(rid, x, y,country) %>% 
    dplyr::slice(1) %>% 
    dplyr::select(rid, x, y, country,geom)
  
  
  if (!by_draw) {
    res <- df %>%
      sf::st_drop_geometry() %>% 
      dplyr::group_by(rid, x, y,country) %>% 
      dplyr::summarise(mean = mean(mean),
                       q2.5 = min(q2.5),
                       q97.5 = max(q97.5),
                       overlap = n() > 1) %>% 
      dplyr::inner_join(u_grid, .)
  } else {
    res <- df %>%
      sf::st_drop_geometry() %>% 
      dplyr::group_by(rid, x, y, country, .draw) %>% 
      dplyr::summarise(value = mean(value),
                       overlap = n() > 1) %>% 
      dplyr::inner_join(u_grid, .)
  }
  
  res
}

mai_grid_cases_stats <- run_all(
  config_dir = config_dir,
  fun = postprocess_grid_mai_cases_with_ctry,
  postprocess_fun = collapse_grid_with_ctry,
  fun_name = "mai_grid_cases",
  post_process_fun = collapse_grid_with_ctry,
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = F,
  redo_interm = F,
  redo_aux = F,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T) %>% 
  mutate(
    intended_run = TRUE
  )

# Cases by region ----
## update the get AFR region to include all other regions ----
### Helper functions ----
parse_global_region <- function(df) {
  
  if (!("global_region" %in% colnames(df))) {
    stop("global_region needs to be defined to be parsed")
  }
  
  df %>% 
    mutate(global_region = global_region %>% 
             str_replace("_", " ") %>% 
             str_to_title() %>% 
             str_replace("South East_asia",'South-East Asia'),
           global_region = factor(global_region, 
                                levels = get_global_region_levels()))
}

cases_by_region  <- run_all(
  config_dir = config_dir,
  fun = postprocess_adm0_cases,
  fun_name = "mai_cases_by_region",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws_by_global_region,
  postprocess_fun_opts = list(col = "country_cases"),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T) %>% 
  mutate(
    global_region = str_remove(variable,'country_cases_')
  ) %>% 
  parse_global_region()

overall_sim_stats <- run_all(
  config_dir = config_dir,
  fun = postprocess_mai_adm0_simulated_cases,
  fun_name = "mai_simulated_cases_all",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws,
  postprocess_fun_opts = list(col = "sim_country_cases"),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

# pop at risk ----
## Helper functions ----
pop_at_risk <- run_all(
  config_dir = config_dir,
  fun = postprocess_pop_at_risk,
  fun_name = "pop_at_risk",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

pop_at_risk_regions <- run_all(
  config_dir = config_dir,
  fun = postprocess_pop_at_risk_draws,
  fun_name = "pop_at_risk_by_region",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws_by_global_region,
  postprocess_fun_opts = list(col = "tot_pop_risk",
                              grouping_variables = c("admin_level", "risk_cat")),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

pop_at_risk_all <- run_all(
  config_dir = config_dir,
  fun = postprocess_pop_at_risk_draws,
  fun_name = "pop_at_risk_all",
  fun_opts = NULL,
  postprocess_fun = aggregate_and_summarise_draws,
  postprocess_fun_opts = list(col = "tot_pop_risk",
                              grouping_variables = c("admin_level", "risk_cat")),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

risk_categories_50 <- run_all(
  config_dir = config_dir,
  fun = postprocess_risk_category,
  fun_name = "risk_categories_50",
  fun_opts = list(cum_prob_thresh = 0.50),
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

# Get the MAI summary at all admin levels 
mai_stats <- run_all(
  config_dir = config_dir,
  fun = postprocess_mean_annual_incidence,
  fun_name = "mai",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T)

# Adm0 cases ----
mean_adm0_cases_by_time <- run_all(
  config_dir = config_dir,
  fun = postprocess_annual_adm0_cases,
  fun_name = "mai_adm0_cases_by_time",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T
)

# WHO ests from preprocess data ----
who_ests_by_time <- run_all(
  config_dir = config_dir,
  fun = postprocess_WHO_est,
  fun_name = "who_est",
  fun_opts = NULL,
  prefix = "2021_2024",
  suffix = NULL,
  error_handling = "stop",
  redo = FALSE,
  redo_interm = FALSE,
  redo_aux = FALSE,
  output_dir = params$output_dir,
  interm_dir = params$interm_dir,
  data_dir = params$data_dir,
  output_file_type = "rds",
  verbose = T
)

# Plotting helper function ---
color_run_intended <- function(){c("#A1A1A1")}
color_no_run_intended <- function(){c("#FFFFFF")}
color_afr_continent_fill <- function(){c("#FFFFFF")}

colors_lisa_clusters <- function(){c("lightgray", "#D40A07", "#4543C4", "#F26F6D", "#7C7AC2", "#424141", "#A059F7")}
coloramp_cases <- function(){c("#FFFFFF", "#FED98E", "#FE9929", "#D95F0E", "#993404")}
colors_risk_categories <- function() {
  c( paletteer::paletteer_d("fishualize::Epinephelus_striatus", direction = 1),"gray")
}

### Helper function ----
unpack_pop_at_risk <- function(df) {
  
  risk_cat_map <- get_risk_cat_dict()
  names(risk_cat_map) <- janitor::make_clean_names(risk_cat_map) %>% 
    str_remove("x")
  
  
  df %>% 
    mutate(
      risk_cat = str_extract(variable, str_c(rev(names(risk_cat_map)), collapse = "|")),
      risk_cat = factor(risk_cat_map[risk_cat], levels = risk_cat_map),
      admin_level = str_c("ADM", str_extract(variable, "(?<=adm)[0-9]+"))
    )
}
```

## Table 1. List of countries selected for model runs
```{r echo=FALSE,warning=FALSE,message=FALSE}
table1<-data.frame(country = intended_runs$country) %>% 
  get_global_region(ctry_col='country') %>% 
  mutate(model_setting = case_when(
    country %in% c("AGO","MYT","COM") ~ "skip",
    TRUE ~ "unknown"
  ))

# get model setting from the config files:
config_list <- list.files(config_dir,pattern = "\\.yml$",full.names=T)

for (idx in 1:length(config_list)) {
  config_tmp <- yaml::read_yaml(config_list[idx])
  table1[table1$country==config_tmp$countries_name,]$model_setting='standard'
  if(config_tmp$spatial_effect==F){
    table1[table1$country==config_tmp$countries_name,]$model_setting = "no w"
  } else{
    if(config_tmp$do_sd_w_mixture == F){
      table1[table1$country==config_tmp$countries_name,]$model_setting = "no mixture"
    }
  }
}

table1 %>% 
  arrange(model_setting,global_region) %>% 
   knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```

## Figure 1. Global Map: MAI cases at grid level
```{r global map, fig.width=12, fig.height=6, echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else{
fig_MAI_grid <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf,
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid,
         file = "fig1.png",
         width = 12,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}

print("The dark gray area represents countries that have not been modeled yet due to data entry, data audit, location audit, or memory issues. The light gray area represents areas with incidence < 1 case per year. Other white area represents countries which we don't plan to run.")
```

## Maps by region: MAI cases at grid level
### Figure 2. Africa
```{r AFR map,  fig.width=10, fig.height=6, echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_AFR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else{ fig_MAI_grid_Africa <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Africa')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf %>% filter(who_region == "AFR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_Africa,
         file = "fig1_AFR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 3. Eastern Mediterranean
```{r EMR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_EMR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {fig_MAI_grid_EMR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Eastern Mediterranean')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf %>% filter(who_region == "EMR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_EMR,
         file = "fig1_EMR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 4. South-East Asia
```{r SEAR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_SEAR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {
  fig_MAI_grid_SEAR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'South-East Asia')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = global_sf %>% filter(who_region == "SEAR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = T,
                           crop_margin_km = NULL,
                           crop_margin_ratio = 0.6) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.05, .2),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_SEAR,
         file = "fig1_SEAR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 5. Western Pacific
```{r WPR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_WPR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {# fix the projection of the WPR maps
wpr_sf <- global_sf %>% filter(who_region == "WPR")
wpr_fix <- wpr_sf %>%
  st_make_valid() %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES","DATELINEOFFSET=180"), quiet = TRUE) %>%
  st_shift_longitude()

fig_MAI_grid_WPR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Western Pacific')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf = wpr_fix,
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           crop_background = T,
                           crop_margin_km = NULL,
                           crop_margin_ratio = 0.06) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_WPR,
         file = "fig1_WPR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

### Figure 6. Americas
```{r AMR map, fig.width=10, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE}
fig_path <- file.path(params$cholera_dir, "fig1_AMR.png")

if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)

} else {
  fig_MAI_grid_AMR <- output_plot_map(sf_obj = mai_grid_cases_stats %>% 
                                  get_global_region(ctry_col = 'country') %>% 
                                  filter(str_detect(global_region,'Americas')) %>% 
                             mutate(log10_cases = log10(mean),
                                    period = "2021-2024"),
                           lakes_sf = NULL,
                           rivers_sf = NULL,
                           all_countries_sf =  global_sf %>% filter(who_region == "AMR"),
                           fill_var = "log10_cases",
                           fill_color_scale_type = "cases",
                           cholera_dir = params$cholera_dir,
                           #amr_crs = "+proj=robin +lon_0=-90 +datum=WGS84 +units=m +no_defs",
                           crop_background = T,
                           crop_margin_km = NULL,
                           crop_margin_ratio = 0.06) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.1, .3),
        panel.background = element_rect(fill = "white", color = "white")) +
  guides(fill = guide_colorbar("Mean annual incidence \n[cases/year]"))

ggsave(fig_MAI_grid_AMR,
         file = "fig1_AMR.png",
         width = 10,
         height = 6, 
         dpi = 300)
  knitr::include_graphics(fig_path)
}
```

## Figure 7. Bar plot: Cases by region 
```{r echo=FALSE,warning=FALSE,message=FALSE}
fig_cases_region <- cases_by_region %>% 
  mutate(global_region = factor(global_region, levels = get_global_region_levels()),
         period = '2021-2024') %>% 
  ggplot(aes(x = mean, y = global_region, fill = global_region)) +
  geom_bar(stat = "identity")  +
  geom_errorbarh(
    aes(xmin = q2.5, xmax = q97.5, y = global_region),
    height = .2
  )+
  scale_x_continuous(
    breaks = seq(0, 200000, by = 50000),
    labels = function(x) {
      formatC(x, digits = 0, big.mark = ",", format = "f")
    }) +
  scale_fill_manual(values = colors_global_regions()) +
  theme_bw() +
  theme(legend.position = 'none')+
  labs(x = "Mean annual cholera incidence [cases/year]", 
       y = "Region")

ggsave(fig_cases_region,
         file = "fig2.png",
         width = 12,
         height = 6, 
         dpi = 300)
print(fig_cases_region)

```

## Table 2. MAI by region
```{r echo=FALSE, warning=FALSE, message=FALSE}
table2 <- cases_by_region %>% 
  mutate(global_region = factor(global_region, levels = get_global_region_levels())) %>% 
  bind_rows(
    overall_sim_stats %>%
    mutate(global_region ="Total")
  ) %>% 
  mutate(
    `Mean Annual Cases (95% CrI)` = paste0(round(mean,0)," (",round(q2.5,0), " - ",round(q97.5,0),")")
  ) %>% 
  rename(
    `Global region` = global_region,
  ) %>% 
  select(
    `Global region`, `Mean Annual Cases (95% CrI)`
  ) 

table2 %>% 
  filter(`Global region` != 'Total') %>%
  arrange( `Global region`) %>% 
  bind_rows(
    table2[nrow(table2),]
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```

## Figure 8. Bar plot: Pop at risk by region 
```{r echo=FALSE,fig.height=6, fig.width=10, warning=FALSE,message=FALSE}
risk_pop_all <- pop_at_risk_all %>% 
      unpack_pop_at_risk() %>%
  filter( 
         admin_level == "ADM2",
         risk_cat != "<1") %>% 
  select(risk_cat, mean, q2.5, q97.5) %>% 
  mutate(risk_cat = as.character(risk_cat)) %>% 
  mutate(risk_cat = ifelse(risk_cat == ">100","\u2265100",risk_cat)) %>% 
  mutate(risk_cat = factor(risk_cat,levels = c("<1","1-10","10-20","20-50","50-100","\u2265100" )))

risk_pop_regions <- pop_at_risk_regions %>% 
    mutate(global_region = str_extract(variable, "(?<=tot_pop_risk_)(.)*(?=_adm)")) %>%
    parse_global_region() %>% 
    unpack_pop_at_risk() %>% 
  mutate(period = '2021-2024') %>% 
  filter( 
         admin_level == "ADM2",
         risk_cat != "<1") %>% 
  select(global_region, risk_cat, mean, q2.5, q97.5) %>% 
  mutate(risk_cat = as.character(risk_cat)) %>%
  mutate(risk_cat = ifelse(risk_cat == ">100","\u2265100",risk_cat)) %>% 
  mutate(risk_cat = factor(risk_cat,levels = c("<1","1-10","10-20","20-50","50-100","\u2265100" )))

# Figure 3A
fig_risk_cat <- risk_pop_regions %>%
  ggplot(aes(y = risk_cat, x = mean)) +
  geom_bar(aes(fill = global_region), stat = "identity", width = .5) +
  geom_errorbarh(data = risk_pop_all,
                inherit.aes = F,
                aes(xmin = q2.5, xmax = q97.5, y = risk_cat), height = 0.2) +
  geom_point(data = risk_pop_all, aes(x = mean)) +
  theme_bw() +
  scale_fill_manual(values = colors_global_regions()) +
  scale_x_continuous(labels = function(x) {formatC(x/1e6)}) +
  labs(y = "ADM2 incidence category per 100,000 population", x = "Population living in ADM2 units (millions)",fill="Region")+
  geom_segment(x = 250000000, xend = 250000000, y = "10-20", yend = "\u2265100", colour = "black") +
  geom_segment(x = 230000000, xend = 250000000, y = "10-20", yend = "10-20", colour = "black") +
  geom_segment(x = 230000000, xend = 250000000, y = "\u2265100", yend = "\u2265100", colour = "black") +
  annotate("segment", x = 250000000, xend = 260000000, y = 3.5, yend = 3.5, colour = "black") +
  annotate("text", x = 300000000, y = 3.5, label = '"High\nIncidence"')

ggsave(plot = fig_risk_cat,
         filename = 'fig_risk_cat.png',
         width = 12,
         height = 7,
         dpi = 300)
print(fig_risk_cat)


fig_path <- file.path(params$cholera_dir, "fig2_risk_pop_map.png")

if (!file.exists(fig_path)) {
# maps for pop at risk at admin2 using 50% as the threshold ----
# Mean annual incidence rates at ADM2 level
  mai_adm_all <- mai_stats %>% 
    mutate(log10_rate_per_1e5 = log10(mean * 1e5))
# Get unique spatial locations
  u_space_sf <- mai_adm_all %>% 
    group_by(location_period_id) %>%
    slice(1) %>% 
    ungroup() %>% 
    select(shapeName, admin_level, country, shp_id, location_period_id)

risk_pop_50_adm2 <- risk_categories_50 %>% 
    filter(admin_level == "ADM2") %>% 
    get_AFRO_region(ctry_col = "country")  %>% 
    mutate(AFRO_region = factor(AFRO_region, 
                                levels = get_AFRO_region_levels())) %>% 
    st_drop_geometry() %>% 
    mutate(risk_cat = as.character(risk_cat)) %>% 
    mutate(risk_cat = ifelse(risk_cat == ">100","\u2265100",risk_cat)) %>% 
    mutate(risk_cat = factor(risk_cat,levels = c("<1","1-10","10-20","20-50","50-100","\u2265100" )))

# Use 50% cutoff for main figure
p_fig_risk_pop_map <- risk_pop_50_adm2 %>% 
  mutate(risk_cat = factor(risk_cat, levels = rev(levels(risk_cat)))) %>% 
  select(-shp_id) %>% 
  inner_join(u_space_sf, .) %>% 
  output_plot_map(sf_obj = ., 
                  lakes_sf = NULL,
                  rivers_sf = NULL,
                  all_countries_sf = global_sf,
                  fill_var = "risk_cat",
                  fill_color_scale_type = "risk category",
                  cholera_dir = params$cholera_dir,
                  crop_background = F) +
  theme(strip.background = element_blank(),
        strip.text = element_text(size = 15),
        legend.position = c(.2, .3),
        panel.background = element_rect(fill = "white", color = "white"),
        text = element_text(size = 6),
        legend.key.size = unit(0.3,"cm"))+
  guides(fill = guide_legend("Incidence category\nper 100,000 pop"))

ggsave(p_fig_risk_pop_map,
         file = "fig2_risk_pop_map.png",
         width = 12,
         height = 6, 
         dpi = 300)
}

```

## Table 3. Risk cat by region
```{r echo=FALSE, warning=FALSE, message=FALSE}
table3 <- risk_pop_regions %>% 
  mutate(global_region = factor(global_region, levels = get_global_region_levels())) %>% 
  bind_rows(
    risk_pop_all %>%
    mutate(global_region ="Total")
  ) %>% 
  mutate(
    `Population (95% CrI)` = paste0(round(mean,0)," (",round(q2.5,0), " - ",round(q97.5,0),")")
  ) %>% 
  rename(
    `Global region` = global_region,
    `Risk category (per 100,000 population)` = risk_cat
  ) %>% 
  select(
    `Global region`, `Risk category (per 100,000 population)`,`Population (95% CrI)`
  ) 

table3 %>% 
  filter(`Global region` != 'Total') %>%
  arrange( `Global region`) %>% 
  bind_rows(
    table3%>% filter(`Global region` == 'Total') 
  ) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```


## Table 4. WHO Annual Report Comparison at the country level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
modeled_cases_by_country_by_time <- mean_adm0_cases_by_time %>% 
  select(country, TL, mean) %>%
  rename(mean_modeled_cases = mean)

who_ests_by_region_by_time <- who_ests_by_time %>% 
  st_drop_geometry() %>% 
  mutate(
    country = str_sub(location_name, start=-3),
    WHO_cases = suspected_cases
  ) %>% 
  select(country,TL,WHO_cases)
  
modeled_who_cases <- inner_join(modeled_cases_by_country_by_time,who_ests_by_region_by_time) %>% 
  get_global_region(ctry_col = 'country') %>% 
    mutate(WHO_cases_log = ifelse(WHO_cases > 0, WHO_cases, NA),
         mean_modeled_cases_log = ifelse(mean_modeled_cases > 0, mean_modeled_cases, NA))

table4 <- modeled_who_cases %>% 
  mutate(year = lubridate::year(TL),
         mean_modeled_cases = round(mean_modeled_cases,0)) %>% 
  arrange(global_region) %>% 
  select(global_region,country, year, mean_modeled_cases, WHO_cases)


table4 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```


## Figure 9. WHO Annual Report Comparison at the country level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
ggplot(modeled_who_cases %>% mutate(year = lubridate::year(TL)), 
       aes(x = WHO_cases_log, y = mean_modeled_cases_log, color = global_region)) +
  geom_point(size = 3, alpha = 0.7, na.rm = TRUE) +
  geom_text_repel(aes(label = country), size = 3, show.legend = FALSE, max.overlaps = 20) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  scale_x_log10(
    name = "Reported WHO cases",
    limits = c(1, 1e5),
    breaks = c(1, 100, 1e4)
  ) +
  scale_y_log10(
    name = "Modeled mean cases",
    limits = c(1, 1e5),
    breaks = c(1, 100, 1e4)
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    axis.text.x = element_text(vjust = 0),
    axis.text.y = element_text(hjust = 1)
  )+
  facet_wrap(~ year)

```


## Table 5. WHO Annual Report Comparison at the continent and global level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
table5 <- modeled_who_cases %>% 
  mutate(year = lubridate::year(TL)) %>% 
  group_by(global_region,year) %>% 
  summarize(
    Total_modeled_cases = round(sum(mean_modeled_cases),0),
    Total_WHO_reported_cases = sum(WHO_cases)
  ) %>% 
  ungroup() %>% 
  arrange(global_region) %>% 
  bind_rows(
    modeled_who_cases %>% 
  mutate(year = lubridate::year(TL)) %>% 
  group_by(year) %>% 
  summarize(
    Total_modeled_cases = round(sum(mean_modeled_cases),0),
    Total_WHO_reported_cases = sum(WHO_cases),
    global_region = "Global"
  )
  )


table5 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```


## Figure 10. WHO Annual Report Comparison at the continent and global level
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
ggplot(table5, 
       aes(x = Total_WHO_reported_cases, y = Total_modeled_cases, color = global_region)) +
  geom_point(size = 3, alpha = 0.7, na.rm = TRUE) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  scale_x_log10(
    name = "Reported WHO cases",
    limits = c(1, 1e6),
    breaks = c(1, 100, 1e4, 1e6)
  ) +
  scale_y_log10(
    name = "Modeled mean cases",
    limits = c(1, 1e6),
    breaks = c(1, 100, 1e4,1e6)
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    axis.text.x = element_text(vjust = 0),
    axis.text.y = element_text(hjust = 1)
  )+
  facet_wrap(~ year)

```

## Table 6. Data and temporal coverage at the subnational level by country-year
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
table6 <- summary_coverage(
  df = all_obs,
  TL_col = "TL",
  TR_col ="TR",
  sCh_col = "attributes.fields.suspected_cases",
  ref_TL_col ="ref_TL",
  ref_TR_col = "ref_TR",
  admin_level_col ="admin_level",
  censoring_col = "censoring",
  location_name_col = "location_name"
)

table6 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```

## Table 7. Max subnational data coverage by country-year
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}

tab <- table6 %>% 
  group_by(year, country) %>% 
  mutate(
    is_max_prop = `Proportion of subnational cases (%)` ==
                  max(`Proportion of subnational cases (%)`)
  ) %>% 
  arrange(desc(national_cases), `Proportion of subnational cases (%)`) %>% 
  mutate(
    highlight = is_max_prop &
      national_cases > 10000 &
      `Proportion of subnational cases (%)` < 10
  ) %>% 
  filter(is_max_prop == T)

rows_to_highlight <- which(tab$highlight)
library(dplyr)
library(knitr)
library(kableExtra)
tab %>% 
  select(!is_max_prop) %>% 
  select(!highlight) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped") %>% 
  row_spec(rows_to_highlight, background = "#FFE5B4")

```

## Table 8. Spatial coverage at the subnational level by country-year
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
table8 <- summary_spatial_coverage(sf_obj = all_shapefiles)

table8 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```
## Table 9. Private vs. public OCs
```{r echo=FALSE, fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
oc_public_private <- read.csv("Analysis/R/OC_public_private.csv")

all_obs %>% 
  distinct(OC_UID, country) %>% 
  mutate(OC_UID =as.integer(OC_UID)) %>% 
  left_join(oc_public_private) %>% 
  group_by(country) %>% 
  summarize(
    `Proportion of public OCs in stan input (%)` = round(length(is_public[is_public==T])/length(is_public)*100,1)
  ) %>% 
  arrange(country) %>% 
    knitr::kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped")) %>%
    kableExtra::kable_paper(full_width = F)

```

