---
title: "Case burden / scaling report"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    df_print: paged
params:
  country: NA
  config_dir: NA
  mai_admin_case_draws: NA
  medically_attended_sCh: NA
  medically_attended_cCh: NA
  cCh_mild: NA
  cCh_severe: NA
  all_cCh_mild: NA
  all_cCh_severe: NA
  all_cCh: NA
  positivity_draws: NA
  severity_props: NA
  care_seek_mild: NA
  care_seek_severe: NA
  reporting_ratio: NA
  severity_scalars: NA
  p_u5_draws: NA
  all_admin_sf: NA
  all_country_sf: NA
  lakes_sf: NA
  generated_at: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 5)
```

```{r helpers, include=TRUE}
# All the helper functions for the report

# ---- Config settings -------------------------------------------------------

# Recursively flattens a parsed YAML list (nested blocks like stan:, scaling:,
# file_names: included) into a two-column Setting/Value tibble, so "every
# config setting" ends up visible in the report, not just top-level scalars.
# A vector value (e.g. summary_admin_levels: [0, 1, 2]) is collapsed to a
# single comma-separated string rather than one row per element.
flatten_config <- function(x, prefix = "") {
  if (length(x) == 0) return(tibble::tibble(Setting = character(), Value = character()))
  purrr::imap_dfr(x, function(val, name) {
    key <- if (nzchar(prefix)) paste0(prefix, ".", name) else name
    if (is.list(val)) {
      if (length(val) == 0) return(tibble::tibble(Setting = key, Value = ""))
      flatten_config(val, key)
    } else {
      tibble::tibble(Setting = key, Value = paste(as.character(val), collapse = ", "))
    }
  })
}

# Reads every *.yml/*.yaml in config_dir once and flattens each into a
# Setting/Value table, keeping both the human-readable countries_name (e.g.
# "BDI") and the raw countries code (e.g. "2") from each file, since it is
# not certain from these scripts alone which one the draws' own "country"
# column holds -- get_country_config_tables() below matches against either.
load_all_configs <- function(config_dir) {
  config_files <- list.files(config_dir, pattern = "\\.ya?ml$", full.names = TRUE)
  if (length(config_files) == 0) {
    warning("No .yml/.yaml files found in ", config_dir, " -- config settings section will be empty")
    return(list())
  }
  purrr::map(config_files, function(f) {
    cfg <- yaml::read_yaml(f)
    start_lab <- if (is.null(cfg$start_time)) "?" else cfg$start_time
    end_lab <- if (is.null(cfg$end_time)) "?" else cfg$end_time
    list(
      file = basename(f),
      countries_name = cfg$countries_name,
      countries_code = cfg$countries,
      period_label = stringr::str_glue("{start_lab} to {end_lab}"),
      table = flatten_config(cfg)
    )
  })
}

# Named list of config tables (one per matching config file/period) for a
# single country value as it appears in the draws data (mai_admin_case_draws$country
# etc.) -- matched against either countries_name or countries_code so this
# works whichever convention that column turns out to use.
get_country_config_tables <- function(config_catalog, cty) {
  cty_chr <- as.character(cty)
  matches <- purrr::keep(config_catalog, function(x) {
    identical(as.character(x$countries_name), cty_chr) || identical(as.character(x$countries_code), cty_chr)
  })
  if (length(matches) == 0) return(list())
  stats::setNames(
    purrr::map(matches, "table"),
    purrr::map_chr(matches, ~ stringr::str_glue("{.x$file} ({.x$period_label})"))
  )
}


# ---- Scaling-step validation checks, filtered to one country --------------

# Re-runs the section-L validation checks (ratio-matches-expected-factor,
# row-count agreement, mild+severe == total) restricted to one country, so
# each country's report shows its own pass/fail table rather than a
# pipeline-wide one. Global (non-country) scaling inputs -- positivity_draws,
# care_seek_mild/severe -- are NOT filtered, since they have no "country"
# column and are broadcast to every country via combine_draws() by design
# (see comments in postprocess_scaling_burden.R).
run_scaling_checks <- function(cty, reporting_ratio,
                                mai_admin_case_draws, medically_attended_sCh,
                                medically_attended_cCh, cCh_mild, cCh_severe,
                                all_cCh_mild, all_cCh_severe, all_cCh,
                                positivity_draws, severity_props,
                                care_seek_mild, care_seek_severe) {

  filt <- function(df) if ("country" %in% names(df)) dplyr::filter(df, country == cty) else df

  before  <- filt(mai_admin_case_draws)
  sCh     <- filt(medically_attended_sCh)
  cCh     <- filt(medically_attended_cCh)
  mild    <- filt(cCh_mild)
  sev     <- filt(cCh_severe)
  a_mild  <- filt(all_cCh_mild)
  a_sev   <- filt(all_cCh_severe)
  final   <- filt(all_cCh)
  pos     <- positivity_draws
  sevp    <- filt(severity_props)
  csm     <- care_seek_mild
  css     <- care_seek_severe

  log <- list()
  check <- function(desc, ok) {
    message(if (ok) "PASS -- " else "FAIL -- ", "[", cty, "] ", desc)
    log[[length(log) + 1]] <<- tibble::tibble(check = desc, pass = ok)
    invisible(ok)
  }

  if (nrow(before) == 0) {
    check("no rows for this country in mai_admin_case_draws -- skipping remaining checks", FALSE)
    return(dplyr::bind_rows(log))
  }

  check_scaling_step <- function(bef, before_col, aft, after_col, factor_df, factor_col,
                                  factor_join_keys, label, invert = FALSE) {
    if (nrow(bef) != nrow(aft)) {
      check(paste0(label, ": before/after row counts differ (", nrow(bef), " vs ", nrow(aft),
                  ") -- cannot validate by row position"), FALSE)
      return(invisible(NULL))
    }
    combined <- dplyr::bind_cols(
      bef %>% dplyr::select(country, .draw, dplyr::all_of(before_col)),
      aft %>% dplyr::select(value_after = dplyr::all_of(after_col))
    ) %>%
      dplyr::inner_join(factor_df %>% dplyr::select(dplyr::all_of(c(factor_join_keys, factor_col))),
                         by = factor_join_keys) %>%
      dplyr::mutate(observed_ratio = value_after / !!rlang::sym(before_col),
                    # When the step DIVIDES by factor_col (invert = TRUE,
                    # e.g. care-seeking) the expected ratio is 1/factor_col.
                    expected = if (invert) 1 / !!rlang::sym(factor_col) else !!rlang::sym(factor_col),
                    diff = observed_ratio - expected)
    max_diff <- max(abs(combined$diff))
    check(sprintf("%-28s ratio range: [%.6f, %.6f]  |  max |diff|: %.2e",
                 label, min(combined$observed_ratio), max(combined$observed_ratio), max_diff),
          max_diff <= 1e-6)
    invisible(combined)
  }

  r1 <- dplyr::bind_cols(
    before %>% dplyr::select(admin_cases),
    sCh %>% dplyr::select(value_after = admin_cases)
  ) %>% dplyr::mutate(observed_ratio = value_after / admin_cases)
  check(sprintf("%-28s ratio range: [%.6f, %.6f]  (expect == %.6f, from reporting_ratio = %.6f)",
               "sCh (÷ratio)", min(r1$observed_ratio), max(r1$observed_ratio),
               1 / reporting_ratio, reporting_ratio),
        max(abs(r1$observed_ratio - 1 / reporting_ratio)) <= 1e-6)

  check_scaling_step(sCh, "admin_cases", cCh, "cCh", pos, "positivity", ".draw", "cCh (x positivity)")
  check_scaling_step(cCh, "cCh", mild, "cCh_mild", sevp, "prop_mild", c("country", ".draw"), "cCh_mild (x prop_mild)")
  check_scaling_step(cCh, "cCh", sev, "cCh_severe", sevp, "prop_severe", c("country", ".draw"), "cCh_severe (x prop_severe)")
  check_scaling_step(mild, "cCh_mild", a_mild, "all_cCh_mild", csm, "care_seeking", ".draw",
                      "all_cCh_mild (÷care_seek)", invert = TRUE)
  check_scaling_step(sev, "cCh_severe", a_sev, "all_cCh_severe", css, "care_seeking", ".draw",
                      "all_cCh_severe (÷care_seek)", invert = TRUE)

  if (nrow(a_mild) != nrow(a_sev) || nrow(a_mild) != nrow(final)) {
    check("all_cCh: all_cCh_mild/all_cCh_severe/all_cCh row counts disagree", FALSE)
  } else {
    r_final <- dplyr::bind_cols(
      a_mild %>% dplyr::select(all_cCh_mild),
      a_sev %>% dplyr::select(all_cCh_severe),
      final %>% dplyr::select(all_cCh)
    ) %>% dplyr::mutate(diff = all_cCh - (all_cCh_mild + all_cCh_severe))
    max_sum_diff <- max(abs(r_final$diff))
    check(sprintf("%-28s max |all_cCh - (mild+severe)|: %.2e", "all_cCh (sum)", max_sum_diff),
          max_sum_diff <= 1e-6)
  }

  dplyr::bind_rows(log)
}


# ---- Figures, filtered to one country --------------------------------------

# Human-readable names for the 8 steps of the scaling chain, matching the
# pipeline flowchart's own terminology (sCh = suspected cholera, cCh =
# confirmed cholera) rather than the raw variable names. Used only to build
# plot/facet labels below (funnel x-axis via build_step_summary(), the
# all-steps map titles via build_all_steps_sf()/short_label(), and the
# density facets via build_density_plots()) -- the underlying data columns
# (admin_cases, cCh, etc.) are untouched.
SCALING_STEP_NAMES <- c(
  admin_cases    = "reported sCh",
  sCh            = "med attended sCh",
  cCh            = "med attended cCh",
  cCh_mild       = "med attended mild cCh",
  cCh_severe     = "med attended severe cCh",
  all_cCh_mild   = "all mild cCh",
  all_cCh_severe = "all severe cCh",
  all_cCh        = "all cCh"
)

# Funnel: mean (+95% draw interval) total cases at each step of the chain,
# broken out by admin level and time period -- i.e. summed over admin UNITS
# within a given (admin_level, period)
# add_period_label() (same helper the maps/scatter use) derives `period`
# from period_start/period_end when present. Every step df here already
# carries location_period_id/admin_level/period_start/period_end -- same
# columns build_all_steps_sf() relies on for the same 8 steps.
build_step_summary <- function(cty, mai_admin_case_draws, medically_attended_sCh,
                                medically_attended_cCh, cCh_mild, cCh_severe,
                                all_cCh_mild, all_cCh_severe, all_cCh) {
  steps <- list(
    list(df = dplyr::filter(mai_admin_case_draws, country == cty),   col = "admin_cases",   label = stringr::str_glue("1. {SCALING_STEP_NAMES[['admin_cases']]}")),
    list(df = dplyr::filter(medically_attended_sCh, country == cty), col = "admin_cases",   label = stringr::str_glue("2. {SCALING_STEP_NAMES[['sCh']]} (÷reporting_ratio)")),
    list(df = dplyr::filter(medically_attended_cCh, country == cty), col = "cCh",           label = stringr::str_glue("3. {SCALING_STEP_NAMES[['cCh']]} (x positivity)")),
    list(df = dplyr::filter(cCh_mild, country == cty),               col = "cCh_mild",      label = stringr::str_glue("4a. {SCALING_STEP_NAMES[['cCh_mild']]}")),
    list(df = dplyr::filter(cCh_severe, country == cty),             col = "cCh_severe",    label = stringr::str_glue("4b. {SCALING_STEP_NAMES[['cCh_severe']]}")),
    list(df = dplyr::filter(all_cCh_mild, country == cty),           col = "all_cCh_mild",  label = stringr::str_glue("5a. {SCALING_STEP_NAMES[['all_cCh_mild']]} (÷care_seek)")),
    list(df = dplyr::filter(all_cCh_severe, country == cty),         col = "all_cCh_severe",label = stringr::str_glue("5b. {SCALING_STEP_NAMES[['all_cCh_severe']]} (÷care_seek)")),
    list(df = dplyr::filter(all_cCh, country == cty),                col = "all_cCh",       label = stringr::str_glue("6. {SCALING_STEP_NAMES[['all_cCh']]} (final)"))
  )
  purrr::map_dfr(steps, function(s) {
    if (nrow(s$df) == 0) {
      return(tibble::tibble(step = s$label, admin_level = NA_character_, period = NA_character_,
                            mean = NA_real_, q025 = NA_real_, q975 = NA_real_))
    }
    per_draw_total <- s$df %>%
      add_period_label() %>%
      dplyr::group_by(admin_level, period, .draw) %>%
      dplyr::summarise(total = sum(.data[[s$col]], na.rm = TRUE), .groups = "drop")
    per_draw_total %>%
      dplyr::group_by(admin_level, period) %>%
      dplyr::summarise(mean = mean(total), q025 = stats::quantile(total, 0.025),
                       q975 = stats::quantile(total, 0.975), .groups = "drop") %>%
      dplyr::mutate(step = s$label, .before = 1)
  })
}

# Net effect: one scatterplot's worth of data per admin level, one point per
# (location_period_id, .draw) combination. Each admin unit's draws
# are joined straight from admin_cases (raw input) to all_cCh (final
# output) on (country, location_period_id, admin_level, .draw).
build_net_effect_by_admin_level <- function(cty, mai_admin_case_draws, all_cCh) {
  before_cty <- mai_admin_case_draws %>% dplyr::filter(country == cty)
  after_cty  <- all_cCh %>% dplyr::filter(country == cty)

  period_cols <- intersect(c("period_start", "period_end"), names(before_cty))
  before_sel <- before_cty %>%
    dplyr::select(location_period_id, admin_level, .draw, dplyr::all_of(period_cols), admin_cases)
  after_sel <- after_cty %>%
    dplyr::select(location_period_id, admin_level, .draw, all_cCh)

  joined <- dplyr::inner_join(before_sel, after_sel,
                              by = c("location_period_id", "admin_level", ".draw")) %>%
    add_period_label()

  admin_levels <- sort(unique(joined$admin_level))
  purrr::map(admin_levels, ~ dplyr::filter(joined, admin_level == .x)) %>%
    stats::setNames(admin_levels)
}

# Density plots of admin_cases (raw input) vs. all_cCh (final output), one
# plot per (admin_level x time period) combination present for this country
# Named list, keyed "<level> -- <period>", in a stable sorted
# order so the report renders them consistently.
build_density_plots <- function(cty, mai_admin_case_draws, all_cCh) {
  before_cty <- mai_admin_case_draws %>% dplyr::filter(country == cty)
  after_cty  <- all_cCh %>% dplyr::filter(country == cty)

  has_periods <- "period_start" %in% names(before_cty) && "period_end" %in% names(before_cty)
  periods <- if (has_periods) {
    before_cty %>% dplyr::distinct(period_start, period_end) %>%
      dplyr::mutate(period = stringr::str_glue("{period_start}–{period_end}")) %>%
      dplyr::arrange(period_start)
  } else {
    tibble::tibble(period_start = NA, period_end = NA, period = "all")
  }

  admin_levels <- sort(unique(before_cty$admin_level))

  plots <- list()
  for (lvl in admin_levels) {
    for (i in seq_len(nrow(periods))) {
      p_start <- periods$period_start[i]; p_end <- periods$period_end[i]; p_label <- periods$period[i]

      b <- before_cty %>% dplyr::filter(admin_level == lvl)
      a <- after_cty  %>% dplyr::filter(admin_level == lvl)
      if (has_periods) {
        b <- b %>% dplyr::filter(period_start == p_start, period_end == p_end)
        a <- a %>% dplyr::filter(period_start == p_start, period_end == p_end)
      }
      if (nrow(b) == 0 || nrow(a) == 0) next

      density_df <- dplyr::bind_rows(
        b %>% dplyr::transmute(value = admin_cases, stage = stringr::str_glue("1. {SCALING_STEP_NAMES[['admin_cases']]} (raw input)")),
        a %>% dplyr::transmute(value = all_cCh,     stage = stringr::str_glue("2. {SCALING_STEP_NAMES[['all_cCh']]} (final output)"))
      )

      key <- stringr::str_glue("{lvl} — {p_label}")
      plots[[key]] <- ggplot2::ggplot(density_df, ggplot2::aes(x = value, fill = stage)) +
        ggplot2::geom_density(alpha = 0.6, color = NA) +
        ggplot2::facet_wrap(~stage, ncol = 1, scales = "free_y") +
        ggplot2::labs(title = stringr::str_glue("{cty} — {lvl} — {p_label}"),
                      x = "Mean cases per admin-unit draw", y = "Density") +
        ggplot2::theme_minimal() + ggplot2::theme(legend.position = "none")
    }
  }
  plots
}


# Scale factors used: scalars + density plots of every draw-level input 

# The two scalar factors in the scaling process (single
# numbers taken straight from the config): reporting_ratio and the two
# severity_* proportions. severity_scalars is whatever
# taxdat::get_config_severity_scalars() returns 
build_scalar_table <- function(reporting_ratio, severity_scalars) {
  tibble::tibble(
    Setting = c("reporting_ratio", "severity_u5", "severity_o5"),
    Value = c(reporting_ratio, severity_scalars$severity_u5, severity_scalars$severity_o5)
  )
}

# Picks the first column in df that isn't one of the known key/index columns
# -- used where a draws tibble's value column name isn't confirmed (p_u5_draws'
# own column, specifically), so we pick defensively rather than hardcode a
# guess that might not match.
pick_value_col <- function(df, exclude = c("country", ".draw")) {
  candidates <- setdiff(names(df), exclude)
  if (length(candidates) == 0) {
    stop("pick_value_col(): no candidate value column (all of ",
         paste(names(df), collapse = ", "), " are in the exclude list)")
  }
  candidates[[1]]
}

# One density plot of a single draw-level column. Returns NULL (rather than
# erroring) on an empty input, so a missing/empty factor just drops out of
# the report instead of failing the whole render.
build_one_density_plot <- function(df, value_col, title, fill = "#4472C4") {
  if (nrow(df) == 0 || !(value_col %in% names(df))) return(NULL)
  ggplot2::ggplot(df, ggplot2::aes(x = .data[[value_col]])) +
    ggplot2::geom_density(fill = fill, alpha = 0.6, color = NA) +
    ggplot2::labs(title = title, x = value_col, y = "Density") +
    ggplot2::theme_minimal()
}

# Density plots for the global (non-country) draw-level scaling inputs --
# test positivity and the two care-seeking proportions. These are broadcast
# to every country (no "country" column), so one set of plots covers the
# whole report, not one per country.
build_global_factor_density_plots <- function(positivity_draws, care_seek_mild, care_seek_severe) {
  plots <- list(
    "Test positivity (positivity_draws)" =
      build_one_density_plot(positivity_draws, "positivity", "Test positivity"),
    "Care-seeking, mild (care_seek_mild)" =
      build_one_density_plot(care_seek_mild, "care_seeking", "Care-seeking proportion — mild"),
    "Care-seeking, severe (care_seek_severe)" =
      build_one_density_plot(care_seek_severe, "care_seeking", "Care-seeking proportion — severe")
  )
  purrr::compact(plots)
}

# Density plots for the country-specific draw-level scaling inputs --
# p_u5_draws (country's posterior proportion of cases under 5) and the
# derived prop_mild/prop_severe (severity_props), filtered to one country.
build_country_factor_density_plots <- function(cty, p_u5_draws, severity_props) {
  plots <- list()

  p_u5_cty <- if ("country" %in% names(p_u5_draws)) dplyr::filter(p_u5_draws, country == cty) else p_u5_draws
  if (nrow(p_u5_cty) > 0) {
    p_u5_col <- pick_value_col(p_u5_cty, exclude = c("country", ".draw"))
    plots[["Proportion of cases under 5 (p_u5_draws)"]] <-
      build_one_density_plot(p_u5_cty, p_u5_col, stringr::str_glue("{cty} — proportion under 5"))
  }

  sevp_cty <- if ("country" %in% names(severity_props)) dplyr::filter(severity_props, country == cty) else severity_props
  if (nrow(sevp_cty) > 0) {
    plots[["Proportion mild, derived (prop_mild)"]] <-
      build_one_density_plot(sevp_cty, "prop_mild", stringr::str_glue("{cty} — proportion mild (derived)"))
    plots[["Proportion severe, derived (prop_severe)"]] <-
      build_one_density_plot(sevp_cty, "prop_severe", stringr::str_glue("{cty} — proportion severe (derived)"))
  }

  purrr::compact(plots)
}


# ---- Maps: per-admin-level choropleths, filtered to one country -----------
#
# one choropleth per admin level, country borders
# + optional lakes for geographic context, taxdat's own "cases" color scale
# and map_theme()

GEO_KEY <- c("country", "location_period_id", "admin_level")


prep_admin_sf <- function(cty, admin_sf) {
  admin_sf %>%
    dplyr::filter(country == cty) %>%
    dplyr::distinct(dplyr::across(dplyr::all_of(GEO_KEY)), .keep_all = TRUE) %>%
    dplyr::select(dplyr::all_of(GEO_KEY))
}

# Mean per admin unit for ONE stage/step, kept long (not pivoted wide) so
# multiple stages can be dplyr::bind_rows()'d together before the geometry
# join -- this is the per-admin-unit analogue of build_step_summary()'s
# per-country totals above.
summarise_admin_draws <- function(draws_df, cty, col, stage_label) {
  id_cols <- intersect(c("country", "location_period_id", "admin_level",
                         "period_start", "period_end"), names(draws_df))
  draws_df %>%
    dplyr::filter(country == cty) %>%
    dplyr::group_by(dplyr::across(dplyr::all_of(id_cols))) %>%
    dplyr::summarise(mean_cases = mean(.data[[col]], na.rm = TRUE), .groups = "drop") %>%
    dplyr::mutate(stage = stage_label)
}

add_period_label <- function(df) {
  if (all(c("period_start", "period_end") %in% names(df))) {
    df %>% dplyr::mutate(period = stringr::str_glue("{period_start}–{period_end}"))
  } else {
    df %>% dplyr::mutate(period = "all")
  }
}

# admin_cases (before) vs. all_cCh (after), joined to this country's
# geometry -- one row per (admin unit, period, stage).
build_before_after_sf <- function(cty, admin_sf, mai_admin_case_draws, all_cCh) {
  admin_sf_cty <- prep_admin_sf(cty, admin_sf)
  before_after <- dplyr::bind_rows(
    summarise_admin_draws(mai_admin_case_draws, cty, "admin_cases", "1. Before scaling (admin_cases)"),
    summarise_admin_draws(all_cCh,              cty, "all_cCh",    "2. After scaling (all_cCh)")
  ) %>% add_period_label()
  admin_sf_cty %>% dplyr::inner_join(before_after, by = GEO_KEY)
}

# All 8 steps of the case burden scaling, joined to this country's geometry -- the same
# steps/columns as build_step_summary() above, but per admin unit instead
# of summed to one country-level total per draw, so each step can be mapped.
build_all_steps_sf <- function(cty, admin_sf, mai_admin_case_draws, medically_attended_sCh,
                               medically_attended_cCh, cCh_mild, cCh_severe,
                               all_cCh_mild, all_cCh_severe, all_cCh) {
  admin_sf_cty <- prep_admin_sf(cty, admin_sf)
  steps <- list(
    list(df = mai_admin_case_draws,   col = "admin_cases",   label = stringr::str_glue("1. {SCALING_STEP_NAMES[['admin_cases']]}")),
    list(df = medically_attended_sCh, col = "admin_cases",   label = stringr::str_glue("2. {SCALING_STEP_NAMES[['sCh']]} (÷reporting_ratio)")),
    list(df = medically_attended_cCh, col = "cCh",           label = stringr::str_glue("3. {SCALING_STEP_NAMES[['cCh']]} (x positivity)")),
    list(df = cCh_mild,               col = "cCh_mild",      label = stringr::str_glue("4a. {SCALING_STEP_NAMES[['cCh_mild']]}")),
    list(df = cCh_severe,             col = "cCh_severe",    label = stringr::str_glue("4b. {SCALING_STEP_NAMES[['cCh_severe']]}")),
    list(df = all_cCh_mild,           col = "all_cCh_mild",  label = stringr::str_glue("5a. {SCALING_STEP_NAMES[['all_cCh_mild']]} (÷care_seek)")),
    list(df = all_cCh_severe,         col = "all_cCh_severe",label = stringr::str_glue("5b. {SCALING_STEP_NAMES[['all_cCh_severe']]} (÷care_seek)")),
    list(df = all_cCh,                col = "all_cCh",       label = stringr::str_glue("6. {SCALING_STEP_NAMES[['all_cCh']]} (final)"))
  )
  all_steps <- purrr::map_dfr(steps, ~ summarise_admin_draws(.x$df, cty, .x$col, .x$label)) %>%
    add_period_label()
  admin_sf_cty %>% dplyr::inner_join(all_steps, by = GEO_KEY)
}

# One admin-level, one stage/step choropleth. taxdat::color_scale(type = "cases")
# keeps the package's censoring rule (limits = c(1, NA), oob = censor),
# a mean under 1 case renders as "no data" gray
plot_admin_level_map <- function(sf_obj, all_countries_sf, lakes_sf = NULL, fill_var, title = NULL,
                                  shared_limits = NULL, legend_text_size = 6,
                                  legend_key_width = 0.35, legend_key_height = 0.7,
                                  legend_barwidth = NULL, legend_barheight = NULL,
                                  title_size = 9, legend_direction = "vertical",
                                  legend_position = "right") {
  if (nrow(sf_obj) == 0) return(NULL)
  bbox <- sf::st_bbox(sf_obj)
  pad_x <- max(diff(bbox[c("xmin", "xmax")]) * 0.08, 1e-3)
  pad_y <- max(diff(bbox[c("ymin", "ymax")]) * 0.08, 1e-3)

  fill_scale <- if (is.null(shared_limits)) {
    taxdat::color_scale(type = "cases", use_case = "ggplot map", use_log = FALSE)
  } else {
    ggplot2::scale_fill_gradientn(
      colours = c("#FFFFFF", "#FED98E", "#FE9929", "#D95F0E", "#993404"),
      limits = shared_limits, oob = scales::censor, na.value = "lightgray",
      breaks = scales::breaks_pretty(n = 3), labels = scales::label_comma(),
      guide = ggplot2::guide_colorbar(frame.colour = "black", ticks.colour = "black",
                                      barwidth = legend_barwidth, barheight = legend_barheight,
                                      direction = legend_direction,
                                      title.position = if (legend_direction == "horizontal") "top" else "right"))
  }

  p <- sf_obj %>%
    ggplot2::ggplot(ggplot2::aes(fill = !!rlang::sym(fill_var))) +
    ggplot2::geom_sf(data = all_countries_sf, inherit.aes = FALSE,
                     lwd = 0, alpha = 1, fill = taxdat:::color_run_intended()) +
    {
      if (!is.null(lakes_sf)) {
        ggplot2::geom_sf(inherit.aes = FALSE, data = lakes_sf,
                         fill = taxdat:::color_lake_fill(), color = taxdat:::color_lake_border(),
                         lwd = .06, alpha = 1)
      }
    } +
    ggplot2::geom_sf(lwd = 0.03, color = "white") +
    ggplot2::geom_sf(data = all_countries_sf, inherit.aes = FALSE,
                     lwd = .3, color = "black", alpha = 0) +
    fill_scale +
    ggplot2::coord_sf(xlim = c(bbox["xmin"] - pad_x, bbox["xmax"] + pad_x),
                      ylim = c(bbox["ymin"] - pad_y, bbox["ymax"] + pad_y)) +
    taxdat::map_theme() +
    ggplot2::theme(panel.border = ggplot2::element_blank(),
                   plot.title = ggplot2::element_text(size = title_size, face = "plain", hjust = 0),
                   legend.position = legend_position,
                   legend.title = ggplot2::element_blank(),
                   legend.text = ggplot2::element_text(size = legend_text_size),
                   legend.key.width = ggplot2::unit(legend_key_width, "lines"),
                   legend.key.height = ggplot2::unit(legend_key_height, "lines"))
  if (!is.null(title)) p <- p + ggplot2::labs(title = stringr::str_wrap(title, width = 18))
  p
}

short_label <- function(label) {
  label %>%
    stringr::str_remove("^[0-9]+[a-z]?\\.\\s*") %>%
    stringr::str_remove("\\s*\\([^)]*\\)\\s*$")
}

# Before/after, side by side (patchwork), one combined figure per admin level
build_before_after_maps <- function(before_after_sf, admin_levels, all_country_sf, lakes_sf) {
  if (nrow(before_after_sf) == 0) return(list())
  n_periods <- dplyr::n_distinct(before_after_sf$period)
  maps <- purrr::map(admin_levels, function(lvl) {
    lvl_sf <- before_after_sf %>% dplyr::filter(admin_level == lvl)
    if (nrow(lvl_sf) == 0) return(NULL)
    build_one <- function(stage_label) {
      stage_sf <- lvl_sf %>% dplyr::filter(stage == stage_label)
      p <- plot_admin_level_map(stage_sf, all_country_sf, lakes_sf,
                                fill_var = "mean_cases", title = short_label(stage_label))
      if (!is.null(p) && n_periods > 1) p <- p + ggplot2::facet_wrap(~period)
      p
    }
    p_before <- build_one("1. Before scaling (admin_cases)")
    p_after  <- build_one("2. After scaling (all_cCh)")
    if (is.null(p_before) || is.null(p_after)) return(NULL)
    patchwork::wrap_plots(p_before, p_after, ncol = 2) +
      patchwork::plot_annotation(title = stringr::str_glue("Case burden before vs. after scaling — {lvl}"))
  })
  purrr::compact(stats::setNames(maps, admin_levels))
}

# All 8 steps side by side (columns), one row of maps per time period
build_all_steps_maps <- function(all_steps_sf, admin_levels, all_country_sf, lakes_sf) {
  if (nrow(all_steps_sf) == 0) return(list())
  maps <- purrr::map(admin_levels, function(lvl) {
    lvl_sf <- all_steps_sf %>% dplyr::filter(admin_level == lvl)
    if (nrow(lvl_sf) == 0) return(NULL)
    steps <- unique(lvl_sf$stage)
    periods <- sort(unique(lvl_sf$period))

    shared_limits <- c(max(1, min(lvl_sf$mean_cases, na.rm = TRUE)),
                        max(lvl_sf$mean_cases, na.rm = TRUE))

    row_plots <- purrr::map(periods, function(per) {
      step_plots <- purrr::map(steps, function(st) {
        cell_sf <- lvl_sf %>% dplyr::filter(stage == st, period == per)
        plot_admin_level_map(cell_sf, all_country_sf, lakes_sf, fill_var = "mean_cases",
                             title = short_label(st), shared_limits = shared_limits,
                             legend_text_size = 20, legend_key_width = 2, legend_key_height = 4,
                             legend_barwidth = grid::unit(12, "cm"), legend_barheight = grid::unit(1.5, "cm"),
                             title_size = 22, legend_direction = "horizontal", legend_position = "bottom")
      })
      step_plots <- purrr::compact(step_plots)
      if (length(step_plots) == 0) return(NULL)
      patchwork::wrap_plots(step_plots, ncol = length(step_plots)) +
        patchwork::plot_layout(guides = "collect") +
        patchwork::plot_annotation(title = stringr::str_glue("Period: {per}"),
                                   theme = ggplot2::theme(plot.title = ggplot2::element_text(size = 26, face = "bold")))
    })
    row_plots <- purrr::compact(row_plots)
    if (length(row_plots) == 0) return(NULL)

    patchwork::wrap_plots(row_plots, ncol = 1) +
      patchwork::plot_layout(guides = "collect") +
      patchwork::plot_annotation(title = stringr::str_glue("All scaling steps, by time period — {lvl}"),
                                 theme = ggplot2::theme(plot.title = ggplot2::element_text(size = 30, face = "bold")))
  })
  purrr::compact(stats::setNames(maps, admin_levels))
}
```

```{r build, include=FALSE}
# Everything below is built from the raw params using the functions defined
# in the helpers chunk above.

config_catalog <- load_all_configs(params$config_dir)
config_tables  <- get_country_config_tables(config_catalog, params$country)

check_results <- run_scaling_checks(
  params$country, params$reporting_ratio,
  params$mai_admin_case_draws, params$medically_attended_sCh, params$medically_attended_cCh,
  params$cCh_mild, params$cCh_severe, params$all_cCh_mild, params$all_cCh_severe, params$all_cCh,
  params$positivity_draws, params$severity_props, params$care_seek_mild, params$care_seek_severe
)

step_summary <- build_step_summary(
  params$country, params$mai_admin_case_draws, params$medically_attended_sCh,
  params$medically_attended_cCh, params$cCh_mild, params$cCh_severe,
  params$all_cCh_mild, params$all_cCh_severe, params$all_cCh
)

net_effect_plots_data <- build_net_effect_by_admin_level(params$country, params$mai_admin_case_draws, params$all_cCh)

density_plots <- build_density_plots(params$country, params$mai_admin_case_draws, params$all_cCh)

scalar_table <- build_scalar_table(params$reporting_ratio, params$severity_scalars)

global_factor_plots <- build_global_factor_density_plots(
  params$positivity_draws, params$care_seek_mild, params$care_seek_severe
)

country_factor_plots <- build_country_factor_density_plots(
  params$country, params$p_u5_draws, params$severity_props
)

admin_levels_present <- sort(unique(
  dplyr::filter(params$mai_admin_case_draws, country == params$country)$admin_level
))

before_after_sf <- build_before_after_sf(
  params$country, params$all_admin_sf, params$mai_admin_case_draws, params$all_cCh
)
before_after_maps <- build_before_after_maps(
  before_after_sf, admin_levels_present, params$all_country_sf, params$lakes_sf
)

all_steps_sf <- build_all_steps_sf(
  params$country, params$all_admin_sf, params$mai_admin_case_draws, params$medically_attended_sCh,
  params$medically_attended_cCh, params$cCh_mild, params$cCh_severe,
  params$all_cCh_mild, params$all_cCh_severe, params$all_cCh
)
all_steps_maps <- build_all_steps_maps(
  all_steps_sf, admin_levels_present, params$all_country_sf, params$lakes_sf
)
```

# `r params$country`

Generated `r params$generated_at`.

## Config settings

Every setting from every config file matched to this country, so the exact
run that produced the figures below is fully reproducible from this page
alone.

```{r config-settings, results='asis'}
if (length(config_tables) == 0) {
  cat("_No config file could be matched to this country -- check that config_dir",
      "contains a .yml/.yaml with a matching countries_name or countries code._\n")
} else {
  purrr::iwalk(config_tables, function(tbl, config_label) {
    cat("\n### ", config_label, "\n\n")
    print(knitr::kable(tbl, col.names = c("Setting", "Value")))
    cat("\n")
  })
}
```

## Scaling pipeline funnel

Mean total cases (summed over admin units within each admin level/period) at each step of the scaling process, with 95% interval across posterior draws. One panel per admin level x time
period.

```{r funnel, fig.width=11, fig.height=9}
ggplot2::ggplot(step_summary, ggplot2::aes(x = factor(step, levels = unique(step)), y = mean)) +
  ggplot2::geom_col(fill = "#4472C4") +
  ggplot2::geom_errorbar(ggplot2::aes(ymin = q025, ymax = q975), width = 0.2, color = "grey30") +
  ggplot2::scale_y_continuous(labels = scales::comma) +
  ggplot2::facet_grid(admin_level ~ period, scales = "free_y") +
  ggplot2::labs(title = paste("Case burden at each scaling step --", params$country),
                subtitle = "Bars: mean total across draws. Whiskers: 95% draw interval.",
                x = NULL, y = "Total cases") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 30, hjust = 1))
```

## Net effect: final vs. raw, by admin level

One scatterplot per admin level this country has, faceted into one panel
per time-period config when this country has more than one. Each point is
one (admin unit, draw) combination -- i.e. NOT summed to a country-level
total per draw -- so this shows the net effect of the full chain at the
resolution the model actually operates at. Descriptive only -- points on
either side of the dashed y = x line are expected, since the chain mixes
inflating (÷) and deflating (×) steps that net out in either direction.

```{r scatter, results='asis', fig.height=6}
if (length(net_effect_plots_data) == 0) {
  cat("_No net-effect scatterplots could be built (no overlapping admin_level",
      "between the before and after draws)._\n")
} else {
  purrr::iwalk(net_effect_plots_data, function(df, lvl) {
    cat("\n### ", lvl, "\n\n")
    n_periods <- dplyr::n_distinct(df$period)
    p <- ggplot2::ggplot(df, ggplot2::aes(x = admin_cases, y = all_cCh)) +
      ggplot2::geom_point(alpha = 0.3, size = 0.8, color = "#4472C4") +
      ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "#C0504D") +
      # Linear, not log -- at admin-unit resolution (esp. ADM2), a lot of
      # admin_cases/all_cCh draws are exactly 0, and scale_x_log10()/
      # scale_y_log10() can't plot 0 (log(0) = -Inf): they'd silently drop
      # those rows (with just a "removed non-finite values" warning), which
      # at this resolution could be a large share of the points.
      ggplot2::scale_x_continuous(labels = scales::comma) +
      ggplot2::scale_y_continuous(labels = scales::comma) +
      ggplot2::labs(title = stringr::str_glue("Net effect of the full chain — {params$country} — {lvl}"),
                    subtitle = "One point per (admin unit, draw)",
                    x = "admin_cases (raw)", y = "all_cCh (final)") +
      ggplot2::theme_minimal()
    if (n_periods > 1) p <- p + ggplot2::facet_wrap(~period)
    print(p)
    cat("\n")
  })
}
```

## Density comparison, by admin level and time period

Raw (unlogged) `admin_cases` vs. `all_cCh` values across all admin units and
draws, shown separately for every admin level and time-period config this
country has -- not pooled, so each plot reflects the real spread at that
specific level and period rather than an average across them.

```{r density, results='asis', fig.height=6}
if (length(density_plots) == 0) {
  cat("_No density plots could be built (no overlapping admin_level / period",
      "combinations between the before and after draws)._\n")
} else {
  purrr::iwalk(density_plots, function(p, key) {
    cat("\n### ", key, "\n\n")
    print(p)
    cat("\n")
  })
}
```

## Maps: before vs. after scaling, by admin level

`admin_cases` (raw input) vs. `all_cCh` (final output), at every
admin level this country has. Each stage has its own color scale. Faceted
by time period when this country has more than one period config. Admin
units with a mean under 1 case render as the package's own "no data" gray
(same censoring rule used everywhere else in this pipeline's maps), not
necessarily an actual gap in the data.

```{r before-after-maps, results='asis', fig.width=12, fig.height=7}
if (length(before_after_maps) == 0) {
  cat("_No before/after maps could be built (no geometry matched this country's admin units)._\n")
} else {
  purrr::iwalk(before_after_maps, function(p, lvl) {
    cat("\n### ", lvl, "\n\n")
    print(p)
    cat("\n")
  })
}
```

## Maps: all scaling steps, by admin level and time period

All 8 steps of the case burden scaling process side by side, one row of maps per time period, all 8 steps
here share one color scale per admin level (ranged over every scaling step and
period at that level).

```{r all-steps-maps, results='asis', fig.width=36, fig.height=16}
if (length(all_steps_maps) == 0) {
  cat("_No all-steps maps could be built (no geometry matched this country's admin units)._\n")
} else {
  purrr::iwalk(all_steps_maps, function(p, lvl) {
    cat("\n### ", lvl, "\n\n")
    print(p)
    cat("\n")
  })
}
```

## Scale factors used

Every factor applied anywhere in the chain above, shown on its own terms:
a plain number for a scalar straight from the config, a density plot for
anything that is actually a posterior (a spread of draws, not one value).

### Global scalars

`reporting_ratio` and the two `severity_*` proportions are single numbers
taken directly from the matched config(s) above -- not draws, so they are
reported as-is rather than as a density.

```{r scalar-table}
knitr::kable(scalar_table, col.names = c("Setting", "Value"))
```

### Global draw-level factors

Test positivity and the two care-seeking proportions are posteriors from
the systematic review, shared across every country (no country-specific
version), so one set of plots covers the whole report.

```{r global-factor-density, results='asis', fig.height=4}
if (length(global_factor_plots) == 0) {
  cat("_No global factor density plots could be built._\n")
} else {
  purrr::iwalk(global_factor_plots, function(p, key) {
    cat("\n#### ", key, "\n\n")
    print(p)
    cat("\n")
  })
}
```

### Country-specific draw-level factors

The posterior proportion of cases under 5 (`p_u5_draws`, from the
age-distribution model) for this country, and the mild/severe split
(`prop_mild`/`prop_severe`) derived from it together with the global
severity scalars above.

```{r country-factor-density, results='asis', fig.height=4}
if (length(country_factor_plots) == 0) {
  cat("_No country-specific factor density plots could be built for this country._\n")
} else {
  purrr::iwalk(country_factor_plots, function(p, key) {
    cat("\n#### ", key, "\n\n")
    print(p)
    cat("\n")
  })
}
```

## Validation checks

Per-step checks confirming the observed before/after ratio matches the
scaling factor that step was supposed to apply, plus the mild+severe ==
total identities. Restricted to this country's rows.

```{r checks}
knitr::kable(check_results, col.names = c("Check", "Pass"))
```
