---
title: "Data Audit"
author: "Joshua Kaminsky"
date: "May 13, 2018"
output: html_document
params:
  seed:
    label: "Random Seed"
    value: 403
    input: text
  nsamp:
    label: "Number of documents to audit"
    value: 50
    input: text
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(taxdat)
set.seed(params$seed)
```

```{r}
setwd('~/svn/cholera-taxonomy/trunk/')
if(file.exists('taxonomy_data.Rdata')){
  load('taxonomy_data.Rdata')
} else {
  taxonomy_data <- suppressWarnings(read_taxonomy_data(taxonomy.directory = 'taxonomy-working/working-entry1/'))
  save(taxonomy_data,file = 'taxonomy_data.Rdata')
}
taxonomy_rows <- nrow(taxonomy_data)
unique_source_documents <- unique(taxonomy_data[['source_file']])
uids <- unique(taxonomy_data[['uid']])
print(paste("There are",taxonomy_rows,"reports of cases from",length(unique_source_documents),"divided into",length(uids),"unique ids"))
```

```{r}
missing_source_files <- dplyr::filter(taxonomy_data,is.na(source_file))
uid_with_missing_source_files <- sort(unique(missing_source_files$uid))
print(paste("There are",length(uid_with_missing_source_files),"uids without a corresponding source file.  The first 10 are",paste(head(uid_with_missing_source_files,10),collapse=' ')))
```
We have chosen these source files at random:
```{r}
chosen_source_files <- sample(unique_source_documents,params$nsamp)
print(chosen_source_files)
```
The chosen source files account for `r sum(taxonomy_data[['source_file']] %in% chosen_source_files)`, or `r sum(taxonomy_data[['source_file']] %in% chosen_source_files) / taxonomy_rows` percent of all rows.


```{r}
setwd('~/svn/cholera-taxonomy/trunk/taxonomy-working/working-entry1/SourceDocuments/')
default_exists <- file.exists(chosen_source_files)
public_exists <- file.exists(paste('Public',chosen_source_files,sep='/'))
restricted_exists <- file.exists(paste('Restricted',chosen_source_files,sep='/'))
any_exists <- default_exists | public_exists | restricted_exists
chosen_source_files[(!default_exists) & public_exists] <- paste("Public",chosen_source_files[(!default_exists) & public_exists],sep='/')
chosen_source_files[(!(default_exists | public_exists)) & restricted_exists] <- paste("Public",chosen_source_files[(!default_exists) & restricted_exists],sep='/')
print(paste("Could not find the file",chosen_source_files[!any_exists]))
chosen_files <- chosen_source_files[any_exists]
```

The remaining chosen source files account for `r sum(taxonomy_data[['source_file']] %in% chosen_files)`, or `r sum(taxonomy_data[['source_file']] %in% chosen_files) / taxonomy_rows` percent of all rows.
