---
output: revealjs::revealjs_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r,echo=FALSE,message=FALSE,warning=FALSE}
taxonomy_dir = "~/svn/cholera-taxonomy/trunk/taxonomy-verified/"
layers_dir = "~/svn/cholera-taxonomy/trunk/Layers/"
library(taxdat)
```

## Overview
#### Purpose
 - Create Cholera Taxonomy
 - Access Cholera Taxonomy
 - Represent Taxonomy through Shapefiles
 - Augment Taxonomy through Covariates
 - Manipulate Covariates as rasters
 - Aid in Modeling

#### Location
In `svn` at `trunk/packages/taxdat`

## Access Taxonomy

#### Functions
```{r,eval=FALSE}
read_description_taxonomy(
  taxonomy.directory,
  ...,
  uids)
read_epi_taxonomy(
  taxonomy.directory,
  uids)
read_taxonomy_data(
  taxonomy.directory,
  columns,
  ...)
aggregate_taxonomy_data(
 data,
 ...)
```
#### Sample
```{r,eval=FALSE}
data = read_taxonomy_data(
  taxonomy_dir,c('who_region','cases'),"!is.na(cases)")
aggregate_data <- 
  aggregate_taxonomy_data(data,'who_region')
```

## Create Taxonomy

#### Functions
```{r,eval=FALSE}
create_location_file(
  location,
  taxonomy_dir,
  replace.existing)
create_population_file(
  location,
  taxonomy_dir,
  replace.existing)
fix_country_name(country_name)                 #in progress
fix_location_name(location,taxonomy.directory) #in progress
lookup_WHO_region(country_name)
```
#### Sample
```{r,eval=FALSE}
create_location_file(
  'Africa_Malawi_Blantyre_TA Chigaru',
  taxonomy_dir = taxonomy_dir,
  replace.existing = FALSE)
```
#### <span style="color:red">-In Progress-</span>
 
## Shapefiles
#### Functions
```{r,eval=FALSE}
get_country_shapefile(name,taxonomy_dir)
get_country_sublevels(location_name,ISO_level,taxonomy_dir)
get_shape_file(location_name,taxonomy_dir)
exists_shape_file(location,taxonomy_dir)
```

#### Sample
```{r,}
shp <- get_shape_file("AFR_MWI_MW-BL",taxonomy_dir)
shp
```
-----
```{r,}
plot(shp$geometry,col='blue',axes=TRUE)
```

## Rasters
#### Functions
```{r,eval=FALSE}
aggregate_raster_xcells(raster_layer,fun)
aggregate_raster_xlayers(raster_layer,fun)
expand_extent(extent,expansion)
load_population_estimates(raster_layer,year,layers_dir) #in progress
```
#### Future Covariates
|Covariate           |source    |status         |
|--------------------|----------|---------------|
|Population          |WorldPop  |Done for Africa|
|Distance to Water   |HydroSHEDs|In Progress    |
|Access to Sanitation|Unknown   |Not Started    |
#### Sample
```{r}
case_estimates <- raster::brick("~/svn/cholera-taxonomy/trunk/manuscripts/GAVI Impact Estimation/data/afro_2010-2016_cases_raster_stack_upd.grd")
mean_cases <- aggregate_raster_xlayers(case_estimates,mean)
```

## Raster-Shapefile Interactions
#### Functions
```{r,eval=FALSE}
extract_country_from_raster(raster_layer,shapefile,partial_cover)
extract_shapefile_from_raster(shapefile,raster_layer,expansion)
apply_to_all_sublevels(
  location_name,raster_layer,ISO_level,
  fun,taxonomy_dir,fix_location_names,
  partial_cover,...)
```
#### Sample
```{r}
region_cases <- extract_country_from_raster(
  mean_cases,shp,TRUE)
```
-----
```{r}
plot(region_cases)
plot(shp$geometry,add=TRUE,axes=TRUE)
```

## Other functions in taxdat

#### Functions
```{r,eval=FALSE}
classify_date         # Modeling Data Availability
get_observed_cells    # (I didn't write this)
get_report_type       # Modeling Data Availability
rdist_stan_model      # (I didn't write this)
sample_stan_model     # (I didn't write this)
stan_result_summarize # (I didn't write this)
```

## Contributing to taxdat

#### Bug Reporting

* springloops.io/project/156721/tasks/
* What to put:
    + Code you ran
    + Error it gave

#### Feature Requesting

* What to put:
    + Desired input
    + Desired output
    + Enough code to know if it works

#### Future
* Push opened/closed issues to slack


## Future

 - Reading Taxonomy
     - Better Column Names
     - Time Series
 - Creating Taxonomy
     - Website for Data Entry*
     - Integration with validation script
 - Rasters
     - New Data
 - Shapefiles
     - Integrate ISOcodes with GADM shapefiles
 - Modeling
     - stan/jags/etc code
     - ForecastFramework Integration
