---
title: "Map Technicalities"
author: "Joshua Kaminsky"
date: "May 4, 2018"
output: html_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
library(taxdat)
taxdir = '~/svn/cholera-taxonomy/trunk/taxonomy-verified/'
# Get some shape file
cntry_name <- 'SLE'
year = 2015
loc_name <- paste(lookup_WHO_region(cntry_name),cntry_name,sep='_')
shp <- get_shape_file(loc_name,taxonomy_dir = taxdir)
google_pop <- 27580000
res1 <- 1
res2 <- 20
```
  This is an exploration of the different challenges involved in using raster and shapefile data together.  We will consider what happens when we try to look at the population of a particular country (`r cntry_name`).

  We will look at population, since its a ubiquitous covariate.  We first will consider how the gridsize of the raster affects the outcome population.  We consider the population at (`r res1`km)^2 and (`r res2`km)^2 resolutions.
```{r}
# Load a raster, and aggregate it
lhrl <- raster::raster(paste('~/svn/cholera-taxonomy/trunk/Layers/pop/AFR/AFR_PPP_',year,'_adj_v2.tif',sep=''))
lhrl <- raster::aggregate(lhrl,res1,fun=sum)
rhrl <- raster::aggregate(lhrl,round(res2/res1),fun=sum)
# Crop the rasters to the extent of the shapefile plus a bit extra (should be enough for at least 1 extra row of the aggregate raster)
lhcrl <- raster::crop(lhrl,expand_extent(raster::extent(sf::as_Spatial(shp$geometry)),(raster::res(rhrl) * 3 + 1)[1]),snap='out')
rhcrl <- raster::crop(rhrl,expand_extent(raster::extent(sf::as_Spatial(shp$geometry)),(raster::res(rhrl) * 3 + 1)[1]),snap='out')

## convert to shapefiles
lhshp <- sf::st_as_sf(raster::rasterToPolygons(lhcrl))
rhshp <- sf::st_as_sf(raster::rasterToPolygons(rhcrl))
## We will need area later for aggregation
lhshp$area_grid = as.numeric(sf::st_area(lhshp))
rhshp$area_grid = as.numeric(sf::st_area(rhshp))
## Keep track of which polygon is which
lhshp$idx_grid = 1:nrow(lhshp)
rhshp$idx_grid = 1:nrow(rhshp)
## Renaming Population
lhshp$population = lhshp[[paste('AFR_PPP_',year,'_adj_v2',sep='')]]
rhshp$population = rhshp[[paste('AFR_PPP_',year,'_adj_v2',sep='')]]
## Add in resolution
lhshp$resol = res1
rhshp$resol = res2
```
  There are two factors we consider when computing the area.  We want to consider which raster we use ( (`r res1`km)^2 or (`r res2`km)^2, and whether to adjust for gridcells only partially overlapping shapefiles (partial_cover).  We will compute the population all 4 ways, and look at the differences.
```{r}
#Combine the rasters as separate polygons in a single data frame (we can separate them again later)
allshp = rbind(lhshp,rhshp)
all_intersection <- sf::st_intersection(allshp,shp)
all_intersection <- dplyr::arrange(all_intersection,resol,idx_grid)
# Compute new area / old area to adjust population
# This mimics the behaviour of partial_cover
all_intersection$adjustment_factor <- as.numeric(st_area(all_intersection)/all_intersection$area_grid)
all_intersection_adj <- all_intersection
all_intersection$adjusted = FALSE
all_intersection_adj$adjusted = TRUE
all_intersection_adj$population <- all_intersection$population * all_intersection$adjustment_factor

all_intersection <- rbind(all_intersection,all_intersection_adj)

all_intersection %>%
  dplyr::group_by(resol,adjusted) %>%
  dplyr::summarize(
    population = sum(population),
  )  ->
  tmp
print(paste("At resolution",tmp$resol,ifelse(tmp$adjusted,"with population adjustments","without population adjustments"),"we obtain a population of",round(tmp$population),"people"))
```
Census data tells us that the true popluation of `r cntry_name` in `r year` is `r google_pop`.
```{r}
print(paste("At resolution",tmp$resol,ifelse(tmp$adjusted,"with population adjustments","without population adjustments"),"we obtain a relative error of",(round(tmp$population) - google_pop)/google_pop))
```
  The second task we consider is the following.  Given a region and its districts, compute the population of each district.  We will consider the accuracy in computing the population of the region, and also the information lost by summing the population of each district.
```{r}
# Get the subregion, and give it ids
subshp <- get_country_sublevels(cntry_name,2,taxonomy_dir = taxdir)
subshp$idx_sub <- 1:nrow(subshp)
subshp$area_sub <- as.numeric(st_area(subshp))

sub_intersection <- st_intersection(allshp,subshp)
sub_intersection$adjustment_factor_sub <- as.numeric(st_area(sub_intersection)/sub_intersection$area_grid)
sub_intersection_adj = sub_intersection
sub_intersection$adjusted = FALSE
sub_intersection_adj$adjusted = TRUE
sub_intersection_adj$population = sub_intersection$population * sub_intersection$adjustment_factor_sub

sub_intersection <- rbind(sub_intersection,sub_intersection_adj)

dplyr::filter(sub_intersection,resol==res2,!adjusted) %>% .[,c('idx_grid','idx_sub','population')] %>% plot
dplyr::filter(sub_intersection,resol==res2,adjusted) %>% .[,c('idx_grid','idx_sub','population','adjustment_factor_sub')] %>% plot

# sub_intersection$adjustment_factor_sub <- as.numeric(st_area(sub_intersection)/??)
sub_intersection %>%
  dplyr::group_by(resol,adjusted) %>%
  dplyr::summarize(population = sum(population)) ->
  tmp2

tmp3 <- dplyr::inner_join(
  as.data.frame(tmp)[,c('resol','adjusted','population')],
  as.data.frame(tmp2)[,c('resol','adjusted','population')],
  by=c('resol','adjusted')
)

print(paste("At resolution",tmp3$resol,ifelse(tmp3$adjusted,"with population adjustments","without population adjustments"),"we obtain a relative error of",(round(tmp3$population.x) - tmp3$population.y)/tmp3$population.y))
```